### 2020-03-13 research-cv/research-cv.tex
cv template - not complete - do not fork yet

%Research CV template for academics and researchers
%@TheDoctorRAB
\documentclass[letter,oneside,english,10pt,headinclude,headsepline]{amsart}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{bold-extra}
\usepackage{bibentry}
\usepackage{filecontents}
\usepackage[yyyymmdd]{datetime} %set preferred date format
\renewcommand{\dateseparator}{.} %set preferred date separator

\makeatletter %makes section in block caps with large font \section*{}
\renewcommand
\section{\@startsection{section}{1}%
  \z@{1.5\linespacing}{.25\linespacing}%
  {\bfseries\scshape\large\raggedright}}

\makeatletter %makes section in block caps with normal font \subsection*{}
\renewcommand
\subsection{\@startsection{subsection}{1}%
  \z@{.75\linespacing}{.25\linespacing}%
  {\bfseries\scshape\raggedright}}

\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$

\usepackage{fancyhdr} 
\pagestyle{fancy}
\fancyhf{} %page number on bottom right
\lhead{\scriptsize Title Name} %title and name
\chead{\scriptsize \textit{Vita}} %maybe something more specific here if desired
\rhead{\scriptsize \today} %date
\rfoot{\thepage} %page number

\title{Name}

%peer reviewed journal papers
\begin{filecontents}{peer-reviewed.bib} 
    @article{
        pr1,
        author = {},
        journal = {},
        pages = {},
        title = {{}},
        volume = {},
        year = {}
    }
\end{filecontents}

%books and book contributions
\begin{filecontents}{book-contribution.bib}
    @book{
        bk1,
        author = {},
        title = {{}},
        year = {},
        publisher = {{}}
        isbn = {}
    }
\end{filecontents}

%conference proceedings
\begin{filecontents}{conference-proceedings.bib}
    @conference{
        cf1,
        author = {},
        title = {{}},
        year = {},
        organization = {},
        address = {}
    }
\end{filecontents}

%reports, misc, non-refeered
\begin{filecontents}{reports.bib}
    @misc{
        rp1,
        author = {},
        title = {{}},
        institution = {},
        year = {}
    }
\end{filecontents}

%conference presentations - not the same as invited talks 
\begin{filecontents}{conference-presentations.bib}
    @conference{
        cf1,
        author = {},
        title = {{}},
        year = {},
        organization = {},
        address = {}
    }
\end{filecontents}

\begin{document}

%.bib files to create
\nobibliography{peer-reviewed,book-contribution,conference-proceedings,reports,conference-presentations}

%.bst file
\bibliographystyle{ieeetr} %custom bst file

\thispagestyle{fancy}

\begin{center}{
        \textsc{ %block caps font
            \textbf{
                {\large Name}\\
                Title \\
                Institution $\sq$ Department
                Address
                email $\sq$ twitter $\sq$ phone 
            }
        }
    }
\end{center}

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}} %horizontal line spanning margins

\section*{Education}
\noindent\textbf{University}\\
\textbf{Doctor of Philosophy $\sq$ Major} \hfill{\textit{Date}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Dissertation: }
    \item[]Examination fields: 
    \item[]Committee: 
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University}\\
\textbf{Master of Science $\sq$ Major} \hfill{\textit{Date}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Thesis: }
    \item[]Advisor: %committee
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University}\\
\textbf{Bachelor of Science $\sq$ Major and distinction(s)} \hfill{\textit{}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Capstone: }
    \item[] Advisor: Leo M. Bobek
\end{itemize}

%academic positions 
\section*{Research Experience}
\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor} \hfill{\textit{July 2015 - }}\\
Advanced fuel cycle analysis; risk assessment; neutronics; nonproliferation; scientific computing
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\indent\indent Coordinator - NPP Decommissioning and Used Fuel Management Certificate \hfill{\textit{August 2019 - }}
    \item[]\indent\indent Affiliate - Boise State University Energy Policy Institute \hfill{\textit{August 2019 - }}
    \item[]\indent\indent State of Idaho Professional Engineer, Faculty Restricted \hfill{\textit{October 2019 - }}
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Postdoctorate Researcher} \hfill{\textit{February 2009 - July 2012}}\\
A safeguards methodology was developed for remotely-handled nuclear materials facilities that proposes functional design components and a risk-informed framework in an effort to integrate safeguards with safety and security into facility design.
\vspace*{.75\baselineskip}

\noindent\textbf{The University of Tokyo $\sq$ Department of Nuclear Engineering/Management}\\
\textbf{Research Associate} \hfill{\textit{August 2007 - January 2009}}\\
Mathematical models for mass transport in the engineered barrier system of a high-level nuclear waste repository are established for bentonite extrusion and radionuclide transport under different environmental conditions to assess potential impacts on performance assessment.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Postdoctorate Researcher} \hfill{\textit{February 2007 - April 2007}}\\
Mathematical modeling of mass transport in the engineered barrier system of a high-level nuclear waste repository continued, to assess the potential of extruding bentonite to confine radionuclides.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Doctoral Candidate} \hfill{\textit{August 2005 - December 2006}}\\
The dissertation thesis focused on the mathematical modeling of mass transport in the engineered barrier system of a high-level nuclear waste repository. A mass transport model was established for radionuclides in a porous medium, bentonite extrusion model in a planar fracture to assess the potential to confine radionuclides.

\section*{Related Research Experience}
\noindent\textbf{Earth Sciences Division $\sq$ Lawrence Berkeley National Laboratory}\\
\textbf{Intern} \hfill{\textit{July 2001 - February 2002}}\\
Conducted data analysis for chaotic modeling of water flow in the unsaturated zone.
\vspace*{.75\baselineskip}

\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
\textbf{Major Qualifying Project} \hfill{\textit{August 1995 - May 1996}}\\
The Major Qualifying Project synthesizes previous undergraduate studies to solve problems or perform tasks in the major field and communicate results effectively. For this project, a logic algorithm was developed for reactivity derived from point kinetics equations and a programmable logic controller was modified for real time collection of data during nuclear reactor operation for use with experimental coursework and maintenance procedures.

\section*{Related Professional Experience}
\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
\textbf{Assistant Radiation Safety Officer} \hfill{\textit{October 1996 - August 1999}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Responded to emergencies concerning incidents involving radioactive material
    \item[]Maintained records of radiation exposures and dosimetry to campus personnel
    \item[]Maintained the full and current inventory of radioisotopes
    \item[]Performed calibrations for radiation detectors
    \item[]Instructed all radiological and nuclear reactor laboratory safety training
    \item[]Performed secretarial duties for Radiation, Health, and Safety Committee
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
\textbf{Senior Nuclear Reactor Operator \#70145} \hfill{\textit{August 1994 - August 1999}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Operated the university nuclear reactor for experimental research projects
    \item[]Trained reactor operator license candidates
    \item[]Performed corrective and preventative maintenance of reactor systems
    \item[]Modified operator training program to a computer based system
\end{itemize}

\section*{Awarded Projects} %chronologically
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item Lee Ostrom (PI), Richard N. Christensen, R. A. Borrelli, Haiyan Zhao (co-PIs) - University of Idaho. ORED Fall 2019 EIS: Portable XFR for use in supporting material research. ORED Equipment and Infrastructure Support. \textbf{\$40,000.} 2019.12.01 - 2020.11.30
    \item R. A. Borrelli (PI) - University of Idaho, Mark. D. DeHart (co-PI) - Idaho National Laboratory. Application and enhancement of MAMMOTH depletion capabilities. \textbf{\$36,894.} 2020.01.13 - 2020.12.31
    \item Richard N. Christensen (PI), R. A. Borrelli, Michael G. McKellar, Michael Haney, David Arcilesi (co-PIs) - University of Idaho, Richard Jacobson (co-PI) Idaho State University. NuScale Simulator at the Center for Advanced Energy Studies. Department of Energy Scientific Infrastructure Support for Consolidated Innovative Nuclear Research. \textbf{\$285,763.} 2019.10.01 - 2020.09.30
    \item R. A. Borrelli (PI) - University of Idaho, Dennis D. Keiser, Jr., (co-PI) - Idaho National Laboratory. Graduate Research Assistantship: Connecting U-Mo Fuel Processing, Microstructure, and Irradiation Performance. \textbf{\$52,070.57.} 2018.10.01-2019.09.30
    \item R. A. Borrelli (PI), Richard N. Christensen (co-PI) - University of Idaho, Brian T. Jaques (co-PI) - Boise State University, Piyush Sabharwall (co-PI) - Idaho National Laboratory, Mark Delligatti (co-PI) - Table Rock, LLC, Sakae Casting USA, LLC (co-PI). Modeling and design of borated aluminium cask for used fuel cooling. Idaho Global Entrepreneurial Mission (IGEM) - Idaho Commerce, \textbf{\$237,898.} 2018.01.01-2019.05.31
    \item R. A. Borrelli (PI) - University of Idaho, Dennis D. Keiser, Jr., (co-PI) - Idaho National Laboratory. Graduate Research Assistantship: Connecting U-Mo Fuel Processing, Microstructure, and Irradiation Performance. \textbf{\$36,180.} 2017.11.01-2018.05.31
    \item R. A. Borrelli (PI), Lee Ostrom (Senior Advisor) - University of Idaho, Stephen G. Johnson (Senior Advisor) - Idaho National Laboratory. Performance assessment of americium as fuel in radioisotope thermoelectric generators for deep space exploration. Idaho NASA EPSCoR Research Initiation Grant. \textbf{\$55,000.} 2017.08.01-2018.04.30
    \item Kelley Verner (PI), R. A. Borrelli, Marc T. Skinner, Emma Redfoot, Jieun Lee, Seth Dustin, John Peterson (co-PIs) - University of Idaho. Increasing the Go-on Rate in Southeast Idaho Through the Nexus of Food, Energy, and Water. University of Idaho Vandals Big Ideas Project. \textbf{\$23,984.} 2017.07.01-2018.06.30
    \item R. A. Borrelli (PI) - University of Idaho, Jason Hales (co-PI) - Idaho National Laboratory. Graduate Research Assistantship: Idaho National Laboratory Code Documentation. \textbf{\$35,435.} 2016.10.01-2017.06.30
    \item Vivek Utgikar (PI), Fatih Aydogan, Krishnan Raja, Raghunath Kanakala, R. A. Borrelli, Haiyan Zhao, Matthew Swenson (co-PIs) - University of Idaho. University of Idaho Nuclear Engineering Faculty Development Program. United States Regulatory Commission Faculty Development Grant. \textbf{\$434,048.} 2015.09.29 - 2019.09.30
\end{enumerate}

\section*{Equipment Acquisitions}
\noindent University of Idaho, Idaho State University, Idaho National Laboratory. Western Services Corporation Pressurized Water Nuclear Reactor Simulator.

\section*{Thesis Committees}
\subsection*{Major Professor}
\noindent\textit{Current}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Kelley Verner, Ph.D. Candidate - Materials science and nuclear fuels analysis
    \item[]Joseph Christensen, Ph.D. - Criticality safety modeling
    \item[]John Peterson, Ph.D - Nuclear cybersecurity
    \item[]J. Seth Dustin, MS - Satellite RTG performance assessment
    \item[]Olin Calvin, Ph.D. - Enhancement of MAMMOTH depletion capabilities
    \item[]Teyen Widdicombe, Ph.D. - RTG satellite design
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textit{Graduates}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]John Peterson, MS - Molten salt reactor neutronics design
    \item[]Emma Redfoot, MS - Allocating heat and electricity in a nuclear renewable hybrid energy system coupled with a water purification system
    \item[]Jieun Lee, MS - Risk-informed safeguards of pyroprocessing for advanced nuclear fuel concepts
    \item[]Trevor MacLean, MEng - Cybersecurity modeling of non-critical nuclear power plant instrumentation
    \item[]Malachi Tolman, MEng - INL BISON code documentation
\end{itemize}

\subsection*{Member}
\noindent\textit{Graduates}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]D. Devin Imholte, MS - Conceptual design of the Advanced Test Reactor non-destructive examination system
    \item[]John Biersdorf, MEng - Precipitation changes to Idaho National Laboratory over time
    \item[]Winfred Sowah, MS - Thermal behavior of cold plated storage cask for light water reactor nuclear fuels
    \vspace*{.05in}
    \item[]\textit{Idaho State University}
    \item[]Pedro Mena, MS - Reactor transient classification using machine learning 
\end{itemize}

\section*{Refereed Journal Publications}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{pr1}.
    \item\bibentry{bor20b}.
    \item\bibentry{bor20c}.
    \item\bibentry{bor19a}.
    \item\bibentry{bor19b}.
    \item\bibentry{bor19c}.
    \item\bibentry{bor18a}.
    \item\bibentry{bor17a}.
    \item\bibentry{bor17b}.
    \item\bibentry{bor16a}.
    \item\bibentry{bor14a}.
    \item\bibentry{bor14b}.
    \item\bibentry{bor14c}.
    \item\bibentry{bor13a}.
    \item\bibentry{bor13b}.
    \item\bibentry{bor11a}.
    \item\bibentry{bor08a}.
    \item\bibentry{bor08b}.
\end{enumerate}

\section*{Book Contribution}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{bkbor19}.
    \item\bibentry{bkbor15}.
\end{enumerate}

\section*{Refereed Conference Proceedings}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{cfbor19a}.
    \item\bibentry{cfbor19b}.
    \item\bibentry{cfbor19c}.
    \item\bibentry{cfbor19d}.
    \item\bibentry{cfbor19e}.
    \item\bibentry{cfbor18a}.
    \item\bibentry{cfbor18b}.
    \item\bibentry{cfbor18c}.
    \item\bibentry{cfbor18d}.
    \item\bibentry{cfbor17a}.
    \item\bibentry{cfbor17b}.
    \item\bibentry{cfbor17c}.
    \item\bibentry{cfbor17d}.
    \item\bibentry{cfbor17e}.
    \item\bibentry{cfbor16a}.
    \item\bibentry{cfbor13a}.
    \item\bibentry{cfbor13b}.
    \item\bibentry{cfbor12a}.
    \item\bibentry{cfbor11a}.
    \item\bibentry{cfbor10a}.
    \item\bibentry{cfbor10b}.
    \item\bibentry{cfbor09a}.
    \item\bibentry{cfbor09b}.
    \item\bibentry{cfbor08a}.
    \item\bibentry{cfbor07a}.
    \item\bibentry{cfbor07b}.
    \item\bibentry{cfbor06a}.
    \item\bibentry{cfbor96a}.
\end{enumerate}

\section*{Non-Refereed Technical Reports}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{rpbor20a}.
    \item\bibentry{rpbor19a}.
    \item\bibentry{rpbor18a}.
    \item\bibentry{rpbor15a}.
    \item\bibentry{rpbor12a}.
    \item\bibentry{rpbor12b}.
    \item\bibentry{rpbor11a}.
    \item\bibentry{rpbor10a}.
    \item\bibentry{rpbor10b}.
    \item\bibentry{rpbor09a}.
    \item\bibentry{rpbor07a}.
    \item\bibentry{rpbor07b}.
    \item\bibentry{rpbor07c}.
    \item\bibentry{rpbor06a}.
\end{enumerate}

\section*{Conference Presentations}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{cfpbor19a}.
    \item\bibentry{cfpbor19b}.
    \item\bibentry{cfpbor19c}.
    \item\bibentry{cfpbor19d}.
    \item\bibentry{cfpbor19e}.
    \item\bibentry{cfpbor19f}.
    \item\bibentry{cfpbor18a}.
    \item\bibentry{cfpbor18b}.
    \item\bibentry{cfpbor18c}.
    \item\bibentry{cfpbor18d}.
    \item\bibentry{cfpbor18e}.
    \item\bibentry{cfpbor17a}.
    \item\bibentry{cfpbor17b}.
    \item\bibentry{cfpbor17c}.
    \item\bibentry{cfpbor17d}.
    \item\bibentry{cfpbor17e}.
    \item\bibentry{cfpbor16a}.
    \item\bibentry{cfpbor13a}.
    \item\bibentry{cfpbor13b}.
    \item\bibentry{cfpbor12a}.
    \item\bibentry{cfpbor11a}.
    \item\bibentry{cfpbor10a}.
    \item\bibentry{cfpbor10b}.
    \item\bibentry{cfpbor09a}.
    \item\bibentry{cfpbor09b}.
    \item\bibentry{cfpbor08a}.
    \item\bibentry{cfpbor07a}.
    \item\bibentry{cfpbor07b}.
    \item\bibentry{cfpbor06a}.
\end{enumerate}

\section*{Teaching Experience}
\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE502: Historical examinations of heterogeneity in nuclear criticality safety \hfill{Spring 2020}}\\
\hspace*{\fill}\textit{directed study}\\
Using published nuclear criticality safety references, this course will conduct an examination of the effect of heterogeneity with respect to nuclear criticality safety. As part of the history of nuclear criticality safety, a number of critical experiments have been conducted using arrays of fissile material in an attempt to quantify the effect of heterogeneity in the determination of safe handling limits. In these attempts, a number of low-enriched experiments were examined and converted in their critical dimensions to establish a useful baseline from which other limits could be extrapolated. It is of interest to the field of nuclear criticality safety to improve the understanding of the effect of heterogeneity on the critical characteristics of multiplying fissile systems, particularly in the range of intermediate enrichment. It is of further interest to the field that a methodology be established which can be used to evaluate these types of systems for practical nuclear criticality safety applications, especially the development of nuclear criticality safety limits. To that end, this course will identify relevant data in the literature used to generate historical experiments and apply MCNP to model these experiments in order to understand and evaluate assumptions and restrictions raised in the experiments.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE502: Heterogeneity comparisons of intermediate enrichment uranium in critical systems \hfill{Spring 2020}}\\
\hspace*{\fill}\textit{directed study}\\
Using the International Criticality Safety Benchmark Evaluation Project (ICSBEP) handbook of evaluated critical experiments, conduct an examination of the effect of heterogeneity in intermediate-enrichment uranium systems. The ICSBEP handbook contains descriptions and evaluations of critical experiments conducted in facilities throughout the world. The reach of the handbook stretches to the beginning of the history of nuclear engineering. In those evaluations, a variety of methods have been discussed and described which convert a system of known or unknown degree of heterogeneity into a simplified homogeneous model, which is a traditional method for examining the critical characteristics of multiplying systems. The specific methodology for this conversion varies between evaluations and is explained in some cases, where other cases are less descriptive. It is of interest to the field of nuclear criticality safety to improve the understanding of the effect of heterogeneity on the critical characteristics of multiplying fissile systems, particularly in the range of intermediate enrichment. It is of further interest to the field that a methodology be established which can be used to evaluate these types of systems for practical nuclear criticality safety applications, especially the development of nuclear criticality safety limits. This course will identify and evaluate relevant benchmark experiments for heterogeneity effects using MCNP to establish new baseline models from the benchmark handbook.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE502: Nuclear integrated energy systems \hfill{Spring 2020}}\\
\hspace*{\fill}\textit{directed study}\\
Nuclear renewable hybrid energy systems enable a nuclear reactor to load follow with a renewable energy source. These must be designed to distribute energy dynamically by supplying electricity to the grid while using either thermal or electrical energy for industrial applications. This takes advantage of the flexible distribution of electricity or heat to maximize profit. The industrial process serves as a load sink for the excess heat or electricity produced by the nuclear reactor. Economic challenges to the current United States nuclear light water reactor (LWR) fleet have led to early plant closures. While LWRs primarily deliver baseload electricity, there is no reason why nuclear energy produced by these reactors cannot be used to provide energy to a range of industrial applications. This directed study course will identify feasible systems, products, and commodities that could be produced by existing nuclear plants. As part of this, cost and potential profitability will be analyzed within the context of market structures and grid reliability.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE527: Nuclear material storage, transport, disposal \hfill{Spring 2020}}\\
There is a wide range of nuclear materials that are stored, transported and disposed of each day. The materials include medical radioisotopes, new fuel pellets, used fuel, and industrial radioisotopes. This course will cover the regulations that govern nuclear material storage, transportation and disposal, as well as the engineering requirements and practical aspects of handling these materials.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE535: Nuclear Criticality Safety I \hfill{Spring 2020}}\\
This course applies uses the foundation of applied nuclear physics to develop and explain the international and domestic rules and practices that are used to prevent inadvertent criticality in fuel cycle applications such as used fuel storage and processing.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE585: Nuclear Fuel Cycle Analysis \hfill{Fall 2017}}\\
This course presents the nuclear fuel cycle can as an holistic system with components related in many complex ways. This course focuses on systems analysis of components that comprise the nuclear fuel cycle to understand the contemporary challenges facing nuclear energy.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{TM529: Risk Assessment \hfill{Spring 2019; 2018; 2017; 2016}}\\
This course is designed to provide students with an understanding of how to perform a comprehensive risk assessment applicable to a wide variety of engineering problems in many different disciplines. The course will focus on failure mode and effect analysis, fault tree analysis, probabilistic risk analysis, and human reliability analysis. The course will also cover fundamental probability and statistics content.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
\textbf{Assistant Professor}\\ 
\textit{NE450: Principles of Nuclear Engineering \hfill{Fall 2019; 2018; 2017; 2016; 2015}}\\
In this course, an overview of fundamental nuclear engineering principles and how these are practically applied to contemporary, nuclear engineering problems will be presented.  The topics covered in this course include: nuclear physics and reactions, materials science, radiation protection, energy production, fuel cycle analysis, advanced reactor design, fusion, nonproliferation, back-end management, and risk assessment and safety.  Throughout the course, the ethical considerations with regards to engineering problems within these fields will also be discussed.
\vspace*{.75\baselineskip}

\noindent\textbf{Diablo Valley College $\sq$ Department of Architecture and Engineering}\\
\textbf{Adjunct Professor}\\ 
\textit{ENGIN110: Introduction to Engineering \hfill{Spring 2015; 2014; 2013; Fall 2014}}\\
This course introduces students to fundamental engineering principles. Students learn how these are applied to contemporary engineering problems through laboratory exercises, homework assignments, design projects, interviews with professional engineers, and field trips to engineering companies. Topics include: materials science, risk assessment and safety, critical problem-solving, engineering analysis, engineering design processes, project development, engineering software, and presentation tools. The role of the engineer in society, professionalism, and engineering ethics are major themes. The emphasis is on creative problem-solving, teamwork, and effective communication, both in presentation and writing.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Instructor}\\
\textit{NE92: Issues in Nuclear Science and Engineering \hfill{Fall 2011}}\\
This course provides undergraduate students with an overview of the nuclear engineering profession, including fundamental nuclear engineering principles and how these are practically applied to nuclear engineering problems. The topics covered include nuclear physics and reactions, materials science, radiation protection, energy production, fuel cycle analysis, advanced reactor design, fusion, nonproliferation, back-end management, risk assessment, and safety. Throughout the course, the ethical considerations concerning engineering problems within these fields are also addressed through a comprehensive, student-driven course project.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Instructor}\\
\textit{NE375: Teaching Techniques in Nuclear Engineering \hfill{Fall 2011; 2010}}\\
This course acquaints graduate student instructors (GSIs) with teaching techniques for courses in the Department of Nuclear Engineering. The GSI will have several duties far beyond grading assignments and/or examinations: conducting discussion sessions, review lectures, or laboratory experiments. The GSI, therefore, needs to develop the appropriate tools to use when facing these pedagogical challenges. Three students from the 2010 course received the Outstanding Graduate Student Instructor Award given by the UC-Berkeley Graduate Student Instructor Teaching \& Resource Center.
\vspace*{.75\baselineskip}

\noindent\textbf{The University of Tokyo $\sq$ Department of Nuclear Engineering/Management}\\
\textbf{Part time lecturer}\\
\textit{Technical English for Scientists \hfill{Winter, Summer 2008; Winter 2007}}\\
This course provided the opportunity for non-native English speaking students to develop technical communication skills; i.e., presenting scientific and technical material to an informed audience at an international conference. In this course, the ‘assertion evidence design’ concept for technical presentation of scientific topics was applied to student research interests. Transmutable skills focused on the professional communication of scientific research in various public speaking formats and a comfortable familiarity with the English language to establish a stronger foundation for technical writing.

\section*{Related Teaching Experience}
\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Graduate Student Instructor}\\
\textit{NE375: Teaching Techniques in Nuclear Engineering \hfill{Fall 2006}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Coordinated guest lecturers from departments within the College of Engineering
    \item[]Prepared lectures for effective teaching strategies for the undergraduate classroom
    \item[]Assessed individual student technical presentations and overall course grading
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textit{E124: Ethics and the Impact of Technology on Society \hfill{Spring 2006; 2005; 2004}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Conducted multiple discussion sections on a weekly basis and review lectures
    \item[]Supervised research projects based on current, ethical and scientific issues 
    \item[]Assessed individual student presentations, projects, and overall course grading
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textit{IDS110: Introduction to Computing \hfill{Fall 2004}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Conducted multiple laboratory sessions on a weekly basis
    \item[]Supervised undergraduate research projects focused on web based education
    \item[]Assessed laboratory assignments and project grading
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textit{NE92: Issues in Nuclear Science and Engineering \hfill{Spring 2002; 2000}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Coordinated guest lecturers from Department of Nuclear Engineering
    \item[]Conducted review lectures
    \item[]Developed examinations and homework assignments
    \item[]Assessed overall course grading
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textit{NE275: Principles and Methods of Risk Analysis \hfill{Fall 2001}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]This graduate course requires a deeper understanding of the subject matter, due to the student body. The course was one of three in the curriculum with the highest credit load. The main responsibility in this was to advise and grade semester projects and presentations based on risk assessments of engineering systems.
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Reader}\\
\noindent\textit{NE150: Introduction to Nuclear Reactor Theory \hfill{Spring 2003}}\\
\noindent\textit{NE104: Radiation Detection and Nuclear Instrumentation Laboratory \hfill{Fall 2002}}\\
\noindent\textit{NE107: Introduction to Imaging \hfill{Spring 2001}}\\
\noindent\textit{NE120: Nuclear Materials \hfill{Fall 2000}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Supervised laboratory sessions
    \item[]Assessed examinations, homework assignments, laboratory reports, final grades
    \item[]Conducted review lectures
\end{itemize}

\section*{Professional Service}
\subsection*{University of Idaho}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Faculty Advisor - American Nuclear Society, University of Idaho Student Section
    \item[]Member - Graduate Faculty, University of Idaho
    \item[]Member - NRC Student Fellowship Oversight Committee, Nuclear Engineering Program
    \item[]Member - Nuclear Engineering Program Admissions Committee
    \item[]Member - Idaho Falls Center for Higher Education Safety Committee
\end{itemize}

\subsection*{Academic Search Committees}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{2018}
    \item[]Nuclear Engineering Faculty, Idaho State University, Idaho Falls Polytechnic Institute
            \vspace{.05in}
    \item[]\textit{2017}
    \item[]Mechanical/Nuclear Engineering Faculty, University of Idaho
\end{itemize}

\subsection*{Peer Reviewer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Regular periods}
    \item[]American Nuclear Society Annual and Winter Meetings 
    \item[]IEEE Transactions on Nuclear Science 
    \item[]American Nuclear Society Fuel Cycle and Waste Management Division John Randall Scholarship 
    \item[]Nuclear Science User Facilities 
    \item[]Advances in Engineering Software 
    \item[]Nuclear Engineering and Technology 
    \item[]Annals of Nuclear Energy 
    \item[]Progress in Nuclear Energy 
    \item[]Energy Science \& Engineering 
    \item[]Nuclear Engineering and Design 
    \item[]International Journal of Nuclear Energy 
            \vspace{.05in}
    \item[]\textit{2020}
    \item[]American Nuclear Society Student Conference - North Carolina State University
            \vspace{.05in}
    \item[]\textit{2019}
    \item[]John Wiley \& Sons, Inc. 
    \item[]Khalifa University of Science and Technology 
    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest 
    \item[]American Nuclear Society Student Conference - Virginia Commonwealth University  
        \vspace{.05in}
    \item[]\textit{2018}
    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest 
    \item[]USDOE - SBIR/STTR Phase I Release 2 
    \item[]American Nuclear Society Student Conference - University of Florida  
        \vspace{.05in}
    \item[]\textit{2017}
    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest 
    \item[]USDOE - SBIR/STTR Phase II Release 2 
    \item[]USDOE - SBIR/STTR Phase II Release 1 
    \item[]USDOE - Office of Nuclear Energy, Consolidated Innovative Nuclear Research 
    \item[]American Nuclear Society Student Conference -  University of Pittsburgh 
        \vspace{.05in}
    \item[]\textit{2016}
    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest 
    \item[]USDOE - SBIR/STTR Phase I Release 2 
    \item[]FY17 TI Portfolio, Bonneville Power Administration, Office of Technology Innovation 
    \item[]American Nuclear Society Student Conference - University of Wisconsin-Madison 
        \vspace{.05in}
    \item[]\textit{2015}
    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest
    \item[]FY16 TI Portfolio, Bonneville Power Administration, Office of Technology Innovation 
    \item[]USDOE - Advanced Research Projects Agency-Energy Concept Papers, Open 2015 FOA 
        \vspace{.05in}
    \item[]\textit{2012}
    \item[]USDOE - Advanced Research Projects Agency-Energy Review Panel - Arlington, Virginia
        \vspace{.05in}
    \item[]\textit{2011}
    \item[]International Conf., High-Level Radioactive Waste Management - Albuquerque, New Mexico
        \vspace{.05in}
    \item[]\textit{2010}
    \item[]Clays in Natural \& Engineered Barriers for Radioactive Waste Confinement - Nantes, France
        \vspace{.05in}
    \item[]\textit{2007}
    \item[]Clays in Natural \& Engineered Barriers for Radioactive Waste Confinement - Lille, France 
\end{itemize}

\subsection*{Conference Committees}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]Co-Chair, Technical Program Committee, 2018 Advances in Nuclear Nonproliferation Technology and Policy Conference, American Nuclear Society, 11-15 November, 2018, Orlando, Florida
    \item[]Technical program committee, Advances in Nuclear Nonproliferation Technology and Policy Conference: Bridging the Gaps in Nuclear Nonproliferation, 25-30 September, 2016, Santa Fe, New Mexico
    \item[]Technical program paper review committee, Advances in Nuclear Nonproliferation Technology and Policy Conference: Bridging the Gaps in Nuclear Nonproliferation, 25-30 September, 2016, Santa Fe, New Mexico
\end{itemize}

\subsection*{Technical Session Organizer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]Cybersecurity for nuclear installations, American Nuclear Society Winter Meeting, 17-21 November, 2019, Washington, D. C. \textit{(co-Organizer with Prof. Jamie B. Coble, University of Tennessee-Knoxville)}
\end{itemize}

\subsection*{Technical Session Chair}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]Spent fuel storage and transportation, American Nuclear Society Winter Meeting, 17-21 November, 2019, Washington, D. C.
    \item[]Cybersecurity for nuclear installations, American Nuclear Society Winter Meeting, 17-21 November, 2019, Washington, D. C. 
    \item[]Data synthesis for pyroprocessing safeguards, 2018 Advances in Nuclear Nonproliferation Technology and Policy Conference (ANTPC), American Nuclear Society, 11-15 November, 2018, Orlando Florida
    \item[]Special session - Prof. Joonhong Ahn Memorial, International High-Level Radioactive Waste Management Conference, 09-13 April, 2017, Charlotte, North Carolina
    \item[]Nonproliferation policy, concepts, and approaches: Treaty verification regimes, state-level concepts and fuel cycle analysis, Advances in Nuclear Nonproliferation Technology and Policy Conference: Bridging the Gaps in Nuclear Nonproliferation, 25-30 September, 2016, Santa Fe, New Mexico
    \item[]Security, safeguards, and non-proliferation, International Conf., High-Level Radioactive Waste Management, 10-14 April 2011, Albuquerque, New Mexico
    \item[]Used Fuel recycling technologies-I, International Congress on Advances in Nuclear Power Plants (ICAPP ‘10) 13-17 June, 2010, San Diego, California
    \item[]Engineered systems and transport processes, International Conf., High-Level Radioactive Waste Management, 07-11 September, 2008, Las Vegas, Nevada
    \item[]Challenges in nuclear waste disposal: Sociological aspects and technical approaches, Global Center of Excellence, 06 December, 2007, The University of Tokyo, Tokyo Japan
\end{itemize}

\subsection*{Symposia Organizer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]Nuclear cybersecurity research initiatives annual meeting, Center for Advanced Energy Studies, 27-28 July, 2017, Idaho Falls, Idaho
    \item[]Nuclear cybersecurity research focus area identification annual meeting, Center for Advanced Energy Studies, 21-22 July, 2016, Idaho Falls, Idaho
    \item[]Technical implications of nuclear energy system options, Symposium on scientific and institutional aspects of advanced systems for spent nuclear fuels in emerging nuclear countries, Center for International Security and Cooperation, 29-30 September, 2011, Stanford University, Palo Alto, California
\end{itemize}

\subsection*{Invited Talks}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{University of Idaho $\sq$ Idaho Falls Center for Higher Education}
    \item[]Strategies and success for ethical research $\sq$ Vandal Advantage Graduate Student Orientation \hfill{\textit{August 2019; 2018}}
        \vspace{.05in}
    \item[]\textit{Seminars}
    \item[]University of Tennessee-Knoxville Department of Nuclear Engineering \hfill{\textit{October 2019}}
        \vspace{.05in}
    \item[]\textit{Lightning Talks}
    \item[]Idaho National Laboratory Nuclear Science \& Technology Research Planning Meeting \hfill{\textit{February 2018}}
    \item[]Idaho National Laboratory Energy \& Environment Research Planning Meeting \hfill{\textit{November 2017}}
        \vspace{.05in}
    \item[]\textit{Outreach}
    \item[]P3/TRIO Upward Bound STEM Day \hfill{\textit{December 2015}}
        \vspace{.05in}
    \item[]\textit{Lectures}
    \item[]Stanford University Pre-Collegiate Summer Institutes \hfill{\textit{July 2014}}
\end{itemize}

\subsection*{Community Service}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{College of Eastern Idaho Machine Tool Technology Advisory Board} \hfill{\textit{2018}}
        \vspace{.05in}
    \item[]\textit{Idaho American Nuclear Society Smoke Detector Donation Program} \hfill{\textit{2016 - }}
    \item[]Administration and delivery of smoke detectors to counties in need across the State of Idaho. Over the past fourteen years, we have worked with more than 70 fire departments to donate more than 5700 smoke detectors to Idaho residents. From 2016-19, we donated nearly 1800 smoke detectors to Arimo, Ashton, Bancroft, Bear Lake, Clear Creek, Declo, Downey, Grace, Hamer, Lava Hot Springs, Roberts, Shelley, and Soda Springs, across southeastern Idaho; Centerville, Clear Creek, Horseshoe Bend, Idaho City, Lowman, Placerville and Valley of the Pines in Boise County; and north to the panhandle in Coeur D'Alene, Mullan, Shoshone, North Side, and West Pend.
        \vspace{.05in}
    \item[]\textit{Idaho American Nuclear Society Highway Cleanup} \hfill{\textit{2016 - }}
    \item[]Garbage cleanup of Miles 122-124 on Interstate 15 twice per year
\end{itemize}

\subsection*{Outreach and Related Professional Activities}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Utah State University Graduate School Fair \hfill{\textit{September 2019}}
    \item[]Montana Tech Career Fair    \hfill{\textit{September 2019; March 2018}}
    \item[]American Nuclear Society Diversity Social UI ANS Student Sponsorship \hfill{\textit{June 2018; November 2017; June 2017}}
    \item[]University of Idaho Moscow Campus Recruiting \hfill{\textit{January 2020; October 2018; March 2017}}
    \item[]Center for Advanced Energy Studies Seminar Series \hfill{\textit{October 2015-17}}
    \item[]Department of Energy consent based siting meeting \hfill{\textit{July 2016}}
    \item[]PHYSOR University of Idaho Sponsorship \hfill{\textit{April 2016}}
    \item[]Boise State University Nuclear Research Summit \hfill{\textit{March 2016}}
    \item[]UI \& BYU American Nuclear Society Student Social \hfill{\textit{October 2018; February 2016}}
    \item[]BYU-Idaho Career Fair \hfill{\textit{October 2015}}
\end{itemize}

\subsection*{Professional Training}
\noindent\textbf{Los Angeles}\\
\textbf{Participant}\\
\textit{National Science Foundation Grant Development Conference} \hfill{\textit{May 2019}}\\
Key officials representing each NSF program directorate, administrative office, Office of General Counsel, and Office of the Inspector General will participate in this two-day conference. The conference is considered a must, particularly for new faculty, researchers, educators and administrators who want to gain insight into a wide range of important and timely issues at NSF, including: the state of current funding; the proposal and award process; and current and recently updated policies and
procedures.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Illinois Urbana-Champaign}\\
\textbf{Invited Participant}\\
\textit{Collaborative Open Source Curriculum Development Workshop} \hfill{\textit{July 2018}}\\
This workshop concluded a year of faculty interaction at six universities to develop curricula for courses common across the same disciplines at multiple universities in order to reduce the amount of time that any individual professor spends on creating what is essentially duplicate materials. The method proposed in this workshop is based on open source software development, where code is shared in online repositories, reviewed by peers, and contributed to the main project.
\vspace*{.75\baselineskip}

\noindent\textbf{Generation Atomic + GAIN}\\
\textbf{Facilitator}\\
\textit{Nuclear Advocacy and Communications Training} \hfill{\textit{June 2018}}\\
Opposition groups claim nuclear power plants are unsafe. Recently, the U.S. nuclear power industry has been characterized as too expensive and dangerous when compared to other energy sources. As members of the nuclear community, we know that the success of nuclear energy has never been more important to ensuring a positive future for the world – but what can we do to make a difference? This workshop will leave participants energized to tell today’s nuclear power story and be
well-equipped with the tools to do so. Convincing others about the benefits of nuclear involves more than just laying out the facts. Thoughtful and personal storytelling bridges gaps when speaking those who are unfamiliar with the technology by explaining the personal and moral reasons that we work in this field. Telling our personal stories and motivations for working in nuclear creates common ground from which we can better explain nuclear’s benefits: whether it’s as a mother talking to a
father, a surfer talking to a skier, or a cook talking to a conservationist, the human stories that nuclear makes possible are our strongest tools when speaking to the public. The most effective nuclear advocacy takes place at the interpersonal level when we strike up conversations with peers and even better, strangers. Because you can never know who it might be sitting across from you at that dinner party or next to you on the airplane, it’s important to practice having open, considerate
conversations with people of all backgrounds. 
\vspace*{.75\baselineskip}

\noindent\textbf{Pacific Northwest National Laboratory}\\
\textbf{Invited Participant}\\
\textit{Cyber Security Course for Safeguards Practitioners} \hfill{\textit{April 2018}}\\
The course is designed for early to mid-career safeguards practitioners (technical instrument developers, instrument users, policy advisors, etc.) who will benefit from a greater understanding of cyber security threats and how to reduce risks to safeguards systems and processes. This 3.5 day course is designed to teach safeguards and cybersecurity experts how to recognize and mitigate potential cybersecurity vulnerabilities in emerging safeguards instrumentation, information systems, and conduct of operations. This training features classroom style learning opportunities through hands-on exercises and provides plenty of time for questions and discussion. Participants will learn new cyber security skills, use cyber security tools, and collaborate with one another and cyber experts to resolve challenges. They will gain an understanding of cyber security principles and a better awareness of cyber risks associated with safeguards systems. Exercises will include puzzles, exploits of attended and unattended monitoring systems, blended physical and cyber attacks on fictional nuclear facilities, and network defense.
\vspace*{.75\baselineskip}

\noindent\textbf{Idaho National Laboratory Nuclear Science and Technology}\\
\textbf{Invited Participant}\\
\textit{Collaborative Research Planning Meeting} \hfill{\textit{February 2018}}\\
The Center for Advanced Energy Studies (CAES) is a catalyst for collaborative projects focused on energy research, achieved via connections between the CAES entities – Idaho National Laboratory (INL), Boise State University, Idaho State University, University of Idaho, and University of Wyoming – and beyond. Through a series of strategic planning meetings, CAES leadership aims to develop a set of focused research directions. The meeting is intended to establish new collaboration, along with a list of prioritized goals and actions items that will steer internal research investments with the intent of growing sustainable, externally-funded programs. The planning meeting will focus on a strategic area tied to one or more INL directorates and will bring together the appropriate INL and university leadership and researchers.
\vspace*{.75\baselineskip}

\noindent\textbf{Idaho National Laboratory National and Homeland Security Sci \& Tech}\\
\textbf{Invited Participant}\\
\textit{Collaborative Research Planning Meeting} \hfill{\textit{February 2018}}\\
The Center for Advanced Energy Studies (CAES) is a catalyst for collaborative projects focused on energy research, achieved via connections between the CAES entities – Idaho National Laboratory (INL), Boise State University, Idaho State University, University of Idaho, and University of Wyoming – and beyond. Through a series of strategic planning meetings, CAES leadership aims to develop a set of focused research directions. The meeting is intended to establish new collaboration, along with a list of prioritized goals and actions items that will steer internal research investments with the intent of growing sustainable, externally-funded programs. The planning meeting will focus on a strategic area tied to one or more INL directorates and will bring together the appropriate INL and university leadership and researchers.
\vspace*{.75\baselineskip}

\noindent\textbf{Idaho National Laboratory Energy \& Environment Science and Technology}\\
\textbf{Invited Participant}\\
\textit{Collaborative Research Planning Meeting} \hfill{\textit{November 2017}}\\
The Center for Advanced Energy Studies (CAES) is a catalyst for collaborative projects focused on energy research, achieved via connections between the CAES entities – Idaho National Laboratory (INL), Boise State University, Idaho State University, University of Idaho, and University of Wyoming – and beyond. Through a series of strategic planning meetings, CAES leadership aims to develop a set of focused research directions. The meeting is intended to establish new collaboration, along with a list of prioritized goals and actions items that will steer internal research investments with the intent of growing sustainable, externally-funded programs. The planning meeting will focus on a strategic area tied to one or more INL directorates and will bring together the appropriate INL and university leadership and researchers.
\vspace*{.75\baselineskip}

\noindent\textbf{Idaho Falls Post Register}\\
\textbf{Participant}\\
\textit{Intermountain Energy Summit} \hfill{\textit{August 2017; 2016; 2015}}\\
This summit is held annually and covers energy issues unique to the intermountain region. Participants include faculty from local universities, researchers from national laboratories, energy companies, and politicians. This year, the theme is energy security with a focus on nuclear, renewable, and alternative energy sources and continued advancements in grid and cybersecurity.
\vspace*{.75\baselineskip}

\noindent\textbf{Idaho National Laboratory}\\
\textbf{Project Mentor}\\
\textit{Modeling, Experimentation, Validation (MeV) Summer School} \hfill{\textit{July 2017}}\\
The MeV Summer School provides enhanced training for engineers and applied scientists involved in design, licensing, and operation of current and advanced nuclear reactor systems through a multi-faceted learning approach of lectures, tours, and hands-on activities. The school is being organized through the cooperation of national laboratories, industry, government agencies, and universities that share the goal of building a strong workforce to support global nuclear expansion. The faculty will be drawn from the top experts in academia, industry, and government. The general organization and conduct of the school will be overseen by an international board of senior experts. A local secretariat will provide technical, logistical and administrative support to students and faculty. It is the aim of the school to foster the development of a next-generation network of scientists and engineers capable of advancing nuclear energy in the 21st century through integrated modeling and experimentation.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Illinois Urbana-Champaign}\\
\textbf{Invited participant}\\
\textit{PyNE Summit} \hfill{\textit{June 2017}}\\
PyNE is a suite of tools to aid in computational nuclear science and engineering. PyNE seeks to provide native implementations of common nuclear algorithms, as well as Python bindings and I/O support for other industry standard nuclear codes.
\vspace*{.75\baselineskip}

\noindent\textbf{University of Illinois Urbana-Champaign}\\
\textbf{Invited Participant}\\
\textit{Collaborative Open Source Curriculum Development Workshop} \hfill{\textit{June 2017}}\\
This workshop included faculty at six universities to develop curricula for courses common across the same disciplines at multiple universities in order to reduce the amount of time that any individual professor spends on creating what is essentially duplicate materials. The method proposed in this workshop is based on open source software development, where code is shared in online repositories, reviewed by peers, and contributed to the main project.
\vspace*{.75\baselineskip}

\noindent\textbf{Pacific Northwest National Laboratory}\\
\textbf{Invited Participant}\\
\textit{Pacific Northwest National Laboratory Safeguards Laboratory Day} \hfill{\textit{May 2019; 2018; 2017}}\\
Students and faculty from the University of Idaho were invited to Pacific Northwest National Laboratory to learn about the research activities at the laboratory. The day also included hands-on safeguards and security experiments conducted at laboratory facilities, such as materials accounting and vehicle searches.
\vspace*{.75\baselineskip}

\noindent\textbf{Department of Energy}\\
\textbf{Participant}\\
\textit{Consent-Based Siting Public Meeting} \hfill{\textit{July 2016}}\\
The Department of Energy is in the initial phase of developing a consent-based process for siting the facilities needed to store and dispose of the nation’s spent nuclear fuel and high-level radioactive waste.  A consent-based approach to siting relies on understanding the views of the public, stakeholders, and governments at the local, state, and tribal levels.  In this first phase, the Department is engaging with interested groups and individuals to learn about what elements are important to consider in designing an enduring approach to siting.  This session is an opportunity for the public to share thoughts and perspectives through a facilitated discussion.
\vspace*{.75\baselineskip}

\noindent\textbf{Global American Business Institute}\\
\textbf{Invited Participant}\\
\textit{Trilateral Nuclear Energy Dialogue: Korea, Japan, United States} \hfill{\textit{July 2016}}\\
Convene a high-level private workshop among preeminent Korean, Japanese, and American experts in nuclear energy and nuclear policy issues, with the intention of fostering relationships, confidence building, and seeking potential areas for trilateral cooperation. In keeping with the overarching theme of previous discussions—the back-end fuel cycle—this meeting seeks to underscore the role of advanced nuclear energy and fuel cycle technologies. Although the obstacles impeding permanent solutions to spent fuel and radioactive waste are largely political, this dialogue aims to highlight the potential of cutting-edge technologies in addressing the policy, environmental, and public acceptance challenges facing management of the nuclear fuel cycle, in addition to opportunities for international collaboration in the research, development, demonstration, and deployment of such technologies.
\vspace*{.75\baselineskip}

\noindent\textbf{Pacific Northwest National Laboratory}\\
\textbf{Invited Participant}\\
\textit{Next Generation Safeguards Initiative Summer Course} \hfill{\textit{June 2016}}\\
This course, offered through the DOE/NNSA Next Generation Safeguards Initiative (NGSI), covers major international safeguards procedures currently in use in IAEA member nations. Daily lectures were supplemented with hands-on safeguards activities conducted by IAEA safeguards inspectors and researchers at PNNL. Participants included faculty, postdoctorate researchers, and graduate students.
\vspace*{.75\baselineskip}

\noindent\textbf{Boise State University}\\
\textbf{Participant}\\
\textit{Idaho's Role in Nuclear: Clean Energy Powered by the Next Generation} \hfill{\textit{March 2016}}\\
Boise State University is proud to bring globally recognized leaders in nuclear energy to address the benefits and challenges associated with nuclear energy production and its role in supplying clean energy for a growing world. The summit will also include a panel discussion with John Kotek, Assistant Director of Nuclear Energy, U.S. Department of Energy; Dr. Mark Peters, Laboratory Director for the Idaho National Laboratory; Mark Rudin, Vice President for Research at Boise State University; Mike McGough, Chief Commercial Officer at NuScale Power, and Dr. Harold Blackman, Associate Vice President for Research and Economic Development at Boise State University. The panel will address questions about the benefits of and concerns around nuclear power.
\vspace*{.75\baselineskip}

\noindent\textbf{Portland State University}\\
\textbf{Participant}\\
\textit{National Science Foundation Grant Development Conference} \hfill{\textit{February 2016}}\\
Key officials representing each NSF program directorate, administrative office, Office of General Counsel, and Office of the Inspector General will participate in this two-day conference. The conference is considered a must, particularly for new faculty, researchers, educators and administrators who want to gain insight into a wide range of important and timely issues at NSF, including: the state of current funding; the proposal and award process; and current and recently updated policies and procedures.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley}\\
\textbf{Invited Participant}\\
\textit{Proliferation Resistance and Physical Protection Working Group Workshop} \hfill{\textit{November 2015}}\\
The PR\&PP methodology was developed within the Generation IV International Forum (GIF) to provide a structured framework to assess the proliferation resistance and physical protection robustness of Gen IV nuclear energy systems, and to guide designers to further improve their systems. This workshop is intended to familiarize non-experts in this field with the broad aspects of the methodology and its applications. The PR\&PP Working Group will present an overview of the methodology to an audience of  students, academics, and members of the GIF community who wish to become more familiar with the PR\&PP methodology. To illustrate the methodology, its application to a hypothetical nuclear energy system will be examined. Workshop participants will be divided into subgroups that will consider different proliferation and security threats, and will identify important design features and approaches that contribute to the system’s resilience to these threats. Following these subgroup sessions, workshop participants will reconvene to review insights from the subgroups. Finally, an open discussion will be held to obtain feedback from the participants on the GIF approach to PR\&PP with the objective of refining the methodology and its presentation to the wider community of academics and prospective GIF users.
\vspace*{.75\baselineskip}

\noindent\textbf{State of Idaho Board of Education $\sq$ Boise, Idaho}\\
\textbf{Invited participant}\\
\textit{Open Education Resources Development} \hfill{\textit{October 2015}}\\
This workshop focused on the use of open source educational materials in order to produce an online textbook as a supplement to existing commercial textbooks. An online textbook allows flexibility for faculty to augment content without requiring multiple textbooks for a course. An online textbook allows the educational content of a course to be more closely aligned with the desired learning outcomes. Two online texts have been developed: Principles of Nuclear Engineering and Risk Assessment.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Discussant}\\
\textit{Advanced Summer School of Radioactive Waste Disposal with Social-Scientific Literacy} \hfill{\textit{August 2011}}\\
\textit{Reflections on the Fukushima Nuclear Accident and Beyond}\\
This advanced summer school was established in conjunction with the Department of Nuclear Engineering/Management, the University of Tokyo and the Department of Nuclear Engineering, University of California, Berkeley to provide Ph.D. students and early-career nuclear engineers with education in social sciences and engineering. The goal was to foster a next generation of engineers capable of understanding the public and societal needs, contributing to the societal decision making, and taking a responsible role as engineering experts in society. The discussant leads student group activities by stimulating questions from students and corroborating with the chair to develop a summary of lectures.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Invited Participant}\\
\textit{Minner Fellows Program} \hfill{\textit{June 2011}}\\
The objective of this program was to develop a framework for making ethical judgments in engineering. Because engineering faculty and graduate students play a leadership role in the development of these technologies, it is essential that they become aware the ethical, legal and social ramifications of them. The course focused on context, or the embodiment of moral maturity and ethical expertise, in the same way that faculty and graduate students embody engineering and technical expertise.
\vspace*{.75\baselineskip}

\noindent\textbf{Hawai'i Tokai International College}\\
\textbf{Project Mentor}\\
\textit{Advanced Summer School of Radioactive Waste Disposal with Social-Scientific Literacy} \hfill{\textit{August 2010}}\\
Special emphasis was placed on integrating nuclear science and engineering with social science. A series of lectures and student group discussions were conducted, followed by a student workshop in which projects were developed, under the theme of ‘nuclear engineers in society,’ including topics such as the safety of a high level waste repository and nuclear systems for non-nuclear weapons states. Project mentors provided guidance, direction, and oversight. The school ended with a series of project presentations and submittal of project reports.
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
\textbf{Student}\\
\textit{Advanced Summer School of Radioactive Waste Disposal with Social-Scientific Literacy} \hfill{\textit{August 2009}}\\
In this summer school, The integration of nuclear science and engineering with social science was emphasized through a series of lectures, panel and group discussions. Students directed discussions based on the activities each day. The school culminated in a tour of the Waste Isolation Pilot Plant (WIPP).
\vspace*{.75\baselineskip}

\noindent\textbf{University of California-Berkeley $\sq$ Graduate Student Instructor Teaching \& Resource Center}\\
\textbf{Participant}\\
\textit{Summer Institute for Preparing Future Faculty} \hfill{\textit{May - June 2005}}\\
This unique program is for Doctoral Candidates with an interest in an academic career. Many aspects of teaching are covered: course design, syllabus development, teaching and learning assessment, teaching and learning strategies, and the creation of a teaching portfolio. The program exposes candidates to faculty in several disciplines both within and outside the university; thus allowing for the dissemination of the full scope of teaching methods and skills, as well as broadening of perspectives with regards to the entire teaching profession.
\vspace*{.75\baselineskip}

\subsection*{Awards and Fellowships}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textbf{University of Idaho}
    \item[]\textit{American Nuclear Society University of Idaho Student Section}
    \item[]Samuel Glasstone Award for Public Service $\sq$ Second Place \hfill{\textit{2019}}
    \item[]Certificate of Distinction \hfill{\textit{2019}}
        \vspace{.05in}
    \item[]\textbf{University of California-Berkeley}
    \item[]Nuclear Engineering Department Block Grant Fellowship \hfill{\textit{2005}}
    \item[]Outstanding Graduate Student Instructor Award \hfill{\textit{2003}}
    \item[]Katherina S. DeSharton Fellowship \hfill{\textit{1999}}
    \item[]Hamilton Family Memorial Fellowship \hfill{\textit{1999}}
        \vspace{.05in}
    \item[]\textbf{United States Department of Energy $\sq$ Office of Civilian Radioactive Waste Management}
    \item[]Civilian Radioactive Waste Management Fellowship \hfill{\textit{2000 - 2004}}
        \vspace{.05in}
    \item[]\textbf{Nuclear Energy Institute}
    \item[]National Academy for Nuclear Training Fellowship \hfill{\textit{1999}}
\end{itemize}

\subsection*{Professional Societies and Positions}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textbf{American Nuclear Society}
    \item[]Executive Committee $\sq$ Nonproliferation Policy Division \hfill{\textit{2019 - 2022}}
    \item[]Executive Committee $\sq$ Student Sections Committee \hfill{\textit{2018 - 2021}}
    \item[]Executive Committee $\sq$ Fuel Cycle and Waste Management Division, American Nuclear Society \hfill{\textit{2018 - 2021}}
        \vspace{.05in}
    \item[]\textbf{Idaho Section of the American Nuclear Society}
    \item[]Community Service \hfill{\textit{2016 - }}
    \item[]Board of Directors \hfill{\textit{2018 - 2019}}
        \vspace{.05in}
    \item[]Tau Beta Pi Engineering Society
\end{itemize}

\end{document}

### 2020-04-01 research-cv/research-cv.tex
2 page

@@
 %.bst file
-\bibliographystyle{ieeetr} %custom bst file
+\bibliographystyle{} %custom bst file
 
@@
     \item[]\textit{Thesis: }
-    \item[]Advisor: %committee
+    \item[]Advisor: 
 \end{itemize}
@@
     \item[]\textit{Capstone: }
-    \item[] Advisor: Leo M. Bobek
+    \item[] Advisor: 
 \end{itemize}
 
-%academic positions 
-\section*{Research Experience}
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor} \hfill{\textit{July 2015 - }}\\
-Advanced fuel cycle analysis; risk assessment; neutronics; nonproliferation; scientific computing
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\indent\indent Coordinator - NPP Decommissioning and Used Fuel Management Certificate \hfill{\textit{August 2019 - }}
-    \item[]\indent\indent Affiliate - Boise State University Energy Policy Institute \hfill{\textit{August 2019 - }}
-    \item[]\indent\indent State of Idaho Professional Engineer, Faculty Restricted \hfill{\textit{October 2019 - }}
-\end{itemize}
+\section*{Research Experience} %academic positions
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title} \hfill{\textit{From - To}}\\
+Brief summary 
 \vspace*{.75\baselineskip}
 
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Postdoctorate Researcher} \hfill{\textit{February 2009 - July 2012}}\\
-A safeguards methodology was developed for remotely-handled nuclear materials facilities that proposes functional design components and a risk-informed framework in an effort to integrate safeguards with safety and security into facility design.
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title} \hfill{\textit{From - To}}\\
+Brief summary
+
+\section*{Related Research Experience} %like internships
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title} \hfill{\textit{From - To}}\\
+Brief summary 
 \vspace*{.75\baselineskip}
 
-\noindent\textbf{The University of Tokyo $\sq$ Department of Nuclear Engineering/Management}\\
-\textbf{Research Associate} \hfill{\textit{August 2007 - January 2009}}\\
-Mathematical models for mass transport in the engineered barrier system of a high-level nuclear waste repository are established for bentonite extrusion and radionuclide transport under different environmental conditions to assess potential impacts on performance assessment.
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title} \hfill{\textit{From - To}}\\
+Brief summary
+
+\section*{Related Professional Experience} %anything else
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title} \hfill{\textit{From - To}}\\
+Brief summary 
 \vspace*{.75\baselineskip}
 
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Postdoctorate Researcher} \hfill{\textit{February 2007 - April 2007}}\\
-Mathematical modeling of mass transport in the engineered barrier system of a high-level nuclear waste repository continued, to assess the potential of extruding bentonite to confine radionuclides.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Doctoral Candidate} \hfill{\textit{August 2005 - December 2006}}\\
-The dissertation thesis focused on the mathematical modeling of mass transport in the engineered barrier system of a high-level nuclear waste repository.
-A mass transport model was established for radionuclides in a porous medium, bentonite extrusion model in a planar fracture to assess the potential to confine radionuclides.
-
-\section*{Related Research Experience}
-\noindent\textbf{Earth Sciences Division $\sq$ Lawrence Berkeley National Laboratory}\\
-\textbf{Intern} \hfill{\textit{July 2001 - February 2002}}\\
-Conducted data analysis for chaotic modeling of water flow in the unsaturated zone.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
-\textbf{Major Qualifying Project} \hfill{\textit{August 1995 - May 1996}}\\
-The Major Qualifying Project synthesizes previous undergraduate studies to solve problems or perform tasks in the major field and communicate results effectively.
-For this project, a logic algorithm was developed for reactivity derived from point kinetics equations and a programmable logic controller was modified for real time collection of data during nuclear reactor operation for use with experimental coursework and maintenance procedures.
-
-\section*{Related Professional Experience}
-\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
-\textbf{Assistant Radiation Safety Officer} \hfill{\textit{October 1996 - August 1999}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Responded to emergencies concerning incidents involving radioactive material
-    \item[]Maintained records of radiation exposures and dosimetry to campus personnel
-    \item[]Maintained the full and current inventory of radioisotopes
-    \item[]Performed calibrations for radiation detectors
-    \item[]Instructed all radiological and nuclear reactor laboratory safety training
-    \item[]Performed secretarial duties for Radiation, Health, and Safety Committee
-\end{itemize}
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Leslie C. Wilbur Nuclear Reactor Facility $\sq$ Worcester Polytechnic Institute}\\
-\textbf{Senior Nuclear Reactor Operator \#70145} \hfill{\textit{August 1994 - August 1999}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Operated the university nuclear reactor for experimental research projects
-    \item[]Trained reactor operator license candidates
-    \item[]Performed corrective and preventative maintenance of reactor systems
-    \item[]Modified operator training program to a computer based system
-\end{itemize}
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title} \hfill{\textit{From - To}}\\
+Brief summary
 
@@
 \begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item Lee Ostrom (PI), Richard N.
-Christensen, R.
-A.
-Borrelli, Haiyan Zhao (co-PIs) - University of Idaho.
-ORED Fall 2019 EIS: Portable XFR for use in supporting material research.
-ORED Equipment and Infrastructure Support.
-\textbf{\$40,000.} 2019.12.01 - 2020.11.30
-    \item R.
-A.
-Borrelli (PI) - University of Idaho, Mark.
-D.
-DeHart (co-PI) - Idaho National Laboratory.
-Application and enhancement of MAMMOTH depletion capabilities.
-\textbf{\$36,894.} 2020.01.13 - 2020.12.31
-    \item Richard N.
-Christensen (PI), R.
-A.
-Borrelli, Michael G.
-McKellar, Michael Haney, David Arcilesi (co-PIs) - University of Idaho, Richard Jacobson (co-PI) Idaho State University.
-NuScale Simulator at the Center for Advanced Energy Studies.
-Department of Energy Scientific Infrastructure Support for Consolidated Innovative Nuclear Research.
-\textbf{\$285,763.} 2019.10.01 - 2020.09.30
-    \item R.
-A.
-Borrelli (PI) - University of Idaho, Dennis D.
-Keiser, Jr., (co-PI) - Idaho National Laboratory.
-Graduate Research Assistantship: Connecting U-Mo Fuel Processing, Microstructure, and Irradiation Performance.
-\textbf{\$52,070.57.} 2018.10.01-2019.09.30
-    \item R.
-A.
-Borrelli (PI), Richard N.
-Christensen (co-PI) - University of Idaho, Brian T.
-Jaques (co-PI) - Boise State University, Piyush Sabharwall (co-PI) - Idaho National Laboratory, Mark Delligatti (co-PI) - Table Rock, LLC, Sakae Casting USA, LLC (co-PI).
-Modeling and design of borated aluminium cask for used fuel cooling.
-Idaho Global Entrepreneurial Mission (IGEM) - Idaho Commerce, \textbf{\$237,898.} 2018.01.01-2019.05.31
-    \item R.
-A.
-Borrelli (PI) - University of Idaho, Dennis D.
-Keiser, Jr., (co-PI) - Idaho National Laboratory.
-Graduate Research Assistantship: Connecting U-Mo Fuel Processing, Microstructure, and Irradiation Performance.
-\textbf{\$36,180.} 2017.11.01-2018.05.31
-    \item R.
-A.
-Borrelli (PI), Lee Ostrom (Senior Advisor) - University of Idaho, Stephen G.
-Johnson (Senior Advisor) - Idaho National Laboratory.
-Performance assessment of americium as fuel in radioisotope thermoelectric generators for deep space exploration.
-Idaho NASA EPSCoR Research Initiation Grant.
-\textbf{\$55,000.} 2017.08.01-2018.04.30
-    \item Kelley Verner (PI), R.
-A.
-Borrelli, Marc T.
-Skinner, Emma Redfoot, Jieun Lee, Seth Dustin, John Peterson (co-PIs) - University of Idaho.
-Increasing the Go-on Rate in Southeast Idaho Through the Nexus of Food, Energy, and Water.
-University of Idaho Vandals Big Ideas Project.
-\textbf{\$23,984.} 2017.07.01-2018.06.30
-    \item R.
-A.
-Borrelli (PI) - University of Idaho, Jason Hales (co-PI) - Idaho National Laboratory.
-Graduate Research Assistantship: Idaho National Laboratory Code Documentation.
-\textbf{\$35,435.} 2016.10.01-2017.06.30
-    \item Vivek Utgikar (PI), Fatih Aydogan, Krishnan Raja, Raghunath Kanakala, R.
-A.
-Borrelli, Haiyan Zhao, Matthew Swenson (co-PIs) - University of Idaho.
-University of Idaho Nuclear Engineering Faculty Development Program.
-United States Regulatory Commission Faculty Development Grant.
-\textbf{\$434,048.} 2015.09.29 - 2019.09.30
+    \item
+    \item
+    \item
 \end{enumerate}
 
-\section*{Equipment Acquisitions}
-\noindent University of Idaho, Idaho State University, Idaho National Laboratory. Western Services Corporation Pressurized Water Nuclear Reactor Simulator.
-
 \section*{Thesis Committees}
-\subsection*{Major Professor}
+\subsection*{Major Professor} %or adviser, whatever the official title is
 \noindent\textit{Current}
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Kelley Verner, Ph.D. Candidate - Materials science and nuclear fuels analysis
-    \item[]Joseph Christensen, Ph.D. - Criticality safety modeling
-    \item[]John Peterson, Ph.D - Nuclear cybersecurity
-    \item[]J. Seth Dustin, MS - Satellite RTG performance assessment
-    \item[]Olin Calvin, Ph.D. - Enhancement of MAMMOTH depletion capabilities
-    \item[]Teyen Widdicombe, Ph.D. - RTG satellite design
+    \item[]Student Name, Degree - Topic
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]John Peterson, MS - Molten salt reactor neutronics design
-    \item[]Emma Redfoot, MS - Allocating heat and electricity in a nuclear renewable hybrid energy system coupled with a water purification system
-    \item[]Jieun Lee, MS - Risk-informed safeguards of pyroprocessing for advanced nuclear fuel concepts
-    \item[]Trevor MacLean, MEng - Cybersecurity modeling of non-critical nuclear power plant instrumentation
-    \item[]Malachi Tolman, MEng - INL BISON code documentation
+    \item[]Student Name, Degree - Thesis Title 
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]D. Devin Imholte, MS - Conceptual design of the Advanced Test Reactor non-destructive examination system
-    \item[]John Biersdorf, MEng - Precipitation changes to Idaho National Laboratory over time
-    \item[]Winfred Sowah, MS - Thermal behavior of cold plated storage cask for light water reactor nuclear fuels
-    \vspace*{.05in}
-    \item[]\textit{Idaho State University}
-    \item[]Pedro Mena, MS - Reactor transient classification using machine learning 
+    \item[]Student Name, Degree - Thesis Title 
 \end{itemize}
@@
     \item\bibentry{pr1}.
-    \item\bibentry{bor20b}.
-    \item\bibentry{bor20c}.
-    \item\bibentry{bor19a}.
-    \item\bibentry{bor19b}.
-    \item\bibentry{bor19c}.
-    \item\bibentry{bor18a}.
-    \item\bibentry{bor17a}.
-    \item\bibentry{bor17b}.
-    \item\bibentry{bor16a}.
-    \item\bibentry{bor14a}.
-    \item\bibentry{bor14b}.
-    \item\bibentry{bor14c}.
-    \item\bibentry{bor13a}.
-    \item\bibentry{bor13b}.
-    \item\bibentry{bor11a}.
-    \item\bibentry{bor08a}.
-    \item\bibentry{bor08b}.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item\bibentry{bkbor19}.
-    \item\bibentry{bkbor15}.
+    \item\bibentry{bk1}.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item\bibentry{cfbor19a}.
-    \item\bibentry{cfbor19b}.
-    \item\bibentry{cfbor19c}.
-    \item\bibentry{cfbor19d}.
-    \item\bibentry{cfbor19e}.
-    \item\bibentry{cfbor18a}.
-    \item\bibentry{cfbor18b}.
-    \item\bibentry{cfbor18c}.
-    \item\bibentry{cfbor18d}.
-    \item\bibentry{cfbor17a}.
-    \item\bibentry{cfbor17b}.
-    \item\bibentry{cfbor17c}.
-    \item\bibentry{cfbor17d}.
-    \item\bibentry{cfbor17e}.
-    \item\bibentry{cfbor16a}.
-    \item\bibentry{cfbor13a}.
-    \item\bibentry{cfbor13b}.
-    \item\bibentry{cfbor12a}.
-    \item\bibentry{cfbor11a}.
-    \item\bibentry{cfbor10a}.
-    \item\bibentry{cfbor10b}.
-    \item\bibentry{cfbor09a}.
-    \item\bibentry{cfbor09b}.
-    \item\bibentry{cfbor08a}.
-    \item\bibentry{cfbor07a}.
-    \item\bibentry{cfbor07b}.
-    \item\bibentry{cfbor06a}.
-    \item\bibentry{cfbor96a}.
+    \item\bibentry{cf1}.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item\bibentry{rpbor20a}.
-    \item\bibentry{rpbor19a}.
-    \item\bibentry{rpbor18a}.
-    \item\bibentry{rpbor15a}.
-    \item\bibentry{rpbor12a}.
-    \item\bibentry{rpbor12b}.
-    \item\bibentry{rpbor11a}.
-    \item\bibentry{rpbor10a}.
-    \item\bibentry{rpbor10b}.
-    \item\bibentry{rpbor09a}.
-    \item\bibentry{rpbor07a}.
-    \item\bibentry{rpbor07b}.
-    \item\bibentry{rpbor07c}.
-    \item\bibentry{rpbor06a}.
+    \item\bibentry{rp1}.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item\bibentry{cfpbor19a}.
-    \item\bibentry{cfpbor19b}.
-    \item\bibentry{cfpbor19c}.
-    \item\bibentry{cfpbor19d}.
-    \item\bibentry{cfpbor19e}.
-    \item\bibentry{cfpbor19f}.
-    \item\bibentry{cfpbor18a}.
-    \item\bibentry{cfpbor18b}.
-    \item\bibentry{cfpbor18c}.
-    \item\bibentry{cfpbor18d}.
-    \item\bibentry{cfpbor18e}.
-    \item\bibentry{cfpbor17a}.
-    \item\bibentry{cfpbor17b}.
-    \item\bibentry{cfpbor17c}.
-    \item\bibentry{cfpbor17d}.
-    \item\bibentry{cfpbor17e}.
-    \item\bibentry{cfpbor16a}.
-    \item\bibentry{cfpbor13a}.
-    \item\bibentry{cfpbor13b}.
-    \item\bibentry{cfpbor12a}.
-    \item\bibentry{cfpbor11a}.
-    \item\bibentry{cfpbor10a}.
-    \item\bibentry{cfpbor10b}.
-    \item\bibentry{cfpbor09a}.
-    \item\bibentry{cfpbor09b}.
-    \item\bibentry{cfpbor08a}.
-    \item\bibentry{cfpbor07a}.
-    \item\bibentry{cfpbor07b}.
-    \item\bibentry{cfpbor06a}.
+    \item\bibentry{cf1}.
 \end{enumerate}
@@
 \section*{Teaching Experience}
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor}\\ 
-\textit{NE502: Historical examinations of heterogeneity in nuclear criticality safety \hfill{Spring 2020}}\\
-\hspace*{\fill}\textit{directed study}\\
-Using published nuclear criticality safety references, this course will conduct an examination of the effect of heterogeneity with respect to nuclear criticality safety.
-As part of the history of nuclear criticality safety, a number of critical experiments have been conducted using arrays of fissile material in an attempt to quantify the effect of heterogeneity in the determination of safe handling limits.
-In these attempts, a number of low-enriched experiments were examined and converted in their critical dimensions to establish a useful baseline from which other limits could be extrapolated.
-It is of interest to the field of nuclear criticality safety to improve the understanding of the effect of heterogeneity on the critical characteristics of multiplying fissile systems, particularly in the range of intermediate enrichment.
-It is of further interest to the field that a methodology be established which can be used to evaluate these types of systems for practical nuclear criticality safety applications, especially the development of nuclear criticality safety limits.
-To that end, this course will identify relevant data in the literature used to generate historical experiments and apply MCNP to model these experiments in order to understand and evaluate assumptions and restrictions raised in the experiments.
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title}\\ 
+\textit{Course Number: Title \hfill{Semester}}\\
+Summary
 \vspace*{.75\baselineskip}
 
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor}\\ 
-\textit{NE502: Heterogeneity comparisons of intermediate enrichment uranium in critical systems \hfill{Spring 2020}}\\
-\hspace*{\fill}\textit{directed study}\\
-Using the International Criticality Safety Benchmark Evaluation Project (ICSBEP) handbook of evaluated critical experiments, conduct an examination of the effect of heterogeneity in intermediate-enrichment uranium systems.
-The ICSBEP handbook contains descriptions and evaluations of critical experiments conducted in facilities throughout the world.
-The reach of the handbook stretches to the beginning of the history of nuclear engineering.
-In those evaluations, a variety of methods have been discussed and described which convert a system of known or unknown degree of heterogeneity into a simplified homogeneous model, which is a traditional method for examining the critical characteristics of multiplying systems.
-The specific methodology for this conversion varies between evaluations and is explained in some cases, where other cases are less descriptive.
-It is of interest to the field of nuclear criticality safety to improve the understanding of the effect of heterogeneity on the critical characteristics of multiplying fissile systems, particularly in the range of intermediate enrichment.
-It is of further interest to the field that a methodology be established which can be used to evaluate these types of systems for practical nuclear criticality safety applications, especially the development of nuclear criticality safety limits.
-This course will identify and evaluate relevant benchmark experiments for heterogeneity effects using MCNP to establish new baseline models from the benchmark handbook.
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title}\\ 
+\textit{Course Number: Title \hfill{Semester}}\\
+Summary
+
+\section*{Related Teaching Experience} %for TA, etc.
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title}\\ 
+\textit{Course Number: Title \hfill{Semester}}\\
+Summary
 \vspace*{.75\baselineskip}
 
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor}\\ 
-\textit{NE502: Nuclear integrated energy systems \hfill{Spring 2020}}\\
-\hspace*{\fill}\textit{directed study}\\
-Nuclear renewable hybrid energy systems enable a nuclear reactor to load follow with a renewable energy source.
-These must be designed to distribute energy dynamically by supplying electricity to the grid while using either thermal or electrical energy for industrial applications.
-This takes advantage of the flexible distribution of electricity or heat to maximize profit.
-The industrial process serves as a load sink for the excess heat or electricity produced by the nuclear reactor.
-Economic challenges to the current United States nuclear light water reactor (LWR) fleet have led to early plant closures.
-While LWRs primarily deliver baseload electricity, there is no reason why nuclear energy produced by these reactors cannot be used to provide energy to a range of industrial applications.
-This directed study course will identify feasible systems, products, and commodities that could be produced by existing nuclear plants.
-As part of this, cost and potential profitability will be analyzed within the context of market structures and grid reliability.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor}\\ 
-\textit{NE527: Nuclear material storage, transport, disposal \hfill{Spring 2020}}\\
-There is a wide range of nuclear materials that are stored, transported and disposed of each day.
-The materials include medical radioisotopes, new fuel pellets, used fuel, and industrial radioisotopes.
-This course will cover the regulations that govern nuclear material storage, transportation and disposal, as well as the engineering requirements and practical aspects of handling these materials.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor}\\ 
-\textit{NE535: Nuclear Criticality Safety I \hfill{Spring 2020}}\\
-This course applies uses the foundation of applied nuclear physics to develop and explain the international and domestic rules and practices that are used to prevent inadvertent criticality in fuel cycle applications such as used fuel storage and processing.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor}\\ 
-\textit{NE585: Nuclear Fuel Cycle Analysis \hfill{Fall 2017}}\\
-This course presents the nuclear fuel cycle can as an holistic system with components related in many complex ways.
-This course focuses on systems analysis of components that comprise the nuclear fuel cycle to understand the contemporary challenges facing nuclear energy.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor}\\ 
-\textit{TM529: Risk Assessment \hfill{Spring 2019; 2018; 2017; 2016}}\\
-This course is designed to provide students with an understanding of how to perform a comprehensive risk assessment applicable to a wide variety of engineering problems in many different disciplines.
-The course will focus on failure mode and effect analysis, fault tree analysis, probabilistic risk analysis, and human reliability analysis.
-The course will also cover fundamental probability and statistics content.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of Idaho $\sq$ Idaho Falls Center for Higher Education $\sq$ Nuclear Engineering Program}\\
-\textbf{Assistant Professor}\\ 
-\textit{NE450: Principles of Nuclear Engineering \hfill{Fall 2019; 2018; 2017; 2016; 2015}}\\
-In this course, an overview of fundamental nuclear engineering principles and how these are practically applied to contemporary, nuclear engineering problems will be presented.
-The topics covered in this course include: nuclear physics and reactions, materials science, radiation protection, energy production, fuel cycle analysis, advanced reactor design, fusion, nonproliferation, back-end management, and risk assessment and safety.
-Throughout the course, the ethical considerations with regards to engineering problems within these fields will also be discussed.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Diablo Valley College $\sq$ Department of Architecture and Engineering}\\
-\textbf{Adjunct Professor}\\ 
-\textit{ENGIN110: Introduction to Engineering \hfill{Spring 2015; 2014; 2013; Fall 2014}}\\
-This course introduces students to fundamental engineering principles.
-Students learn how these are applied to contemporary engineering problems through laboratory exercises, homework assignments, design projects, interviews with professional engineers, and field trips to engineering companies.
-Topics include: materials science, risk assessment and safety, critical problem-solving, engineering analysis, engineering design processes, project development, engineering software, and presentation tools.
-The role of the engineer in society, professionalism, and engineering ethics are major themes.
-The emphasis is on creative problem-solving, teamwork, and effective communication, both in presentation and writing.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Instructor}\\
-\textit{NE92: Issues in Nuclear Science and Engineering \hfill{Fall 2011}}\\
-This course provides undergraduate students with an overview of the nuclear engineering profession, including fundamental nuclear engineering principles and how these are practically applied to nuclear engineering problems.
-The topics covered include nuclear physics and reactions, materials science, radiation protection, energy production, fuel cycle analysis, advanced reactor design, fusion, nonproliferation, back-end management, risk assessment, and safety.
-Throughout the course, the ethical considerations concerning engineering problems within these fields are also addressed through a comprehensive, student-driven course project.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Instructor}\\
-\textit{NE375: Teaching Techniques in Nuclear Engineering \hfill{Fall 2011; 2010}}\\
-This course acquaints graduate student instructors (GSIs) with teaching techniques for courses in the Department of Nuclear Engineering.
-The GSI will have several duties far beyond grading assignments and/or examinations: conducting discussion sessions, review lectures, or laboratory experiments.
-The GSI, therefore, needs to develop the appropriate tools to use when facing these pedagogical challenges.
-Three students from the 2010 course received the Outstanding Graduate Student Instructor Award given by the UC-Berkeley Graduate Student Instructor Teaching \& Resource Center.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{The University of Tokyo $\sq$ Department of Nuclear Engineering/Management}\\
-\textbf{Part time lecturer}\\
-\textit{Technical English for Scientists \hfill{Winter, Summer 2008; Winter 2007}}\\
-This course provided the opportunity for non-native English speaking students to develop technical communication skills; i.e., presenting scientific and technical material to an informed audience at an international conference.
-In this course, the ‘assertion evidence design’ concept for technical presentation of scientific topics was applied to student research interests.
-Transmutable skills focused on the professional communication of scientific research in various public speaking formats and a comfortable familiarity with the English language to establish a stronger foundation for technical writing.
-
-\section*{Related Teaching Experience}
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Graduate Student Instructor}\\
-\textit{NE375: Teaching Techniques in Nuclear Engineering \hfill{Fall 2006}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Coordinated guest lecturers from departments within the College of Engineering
-    \item[]Prepared lectures for effective teaching strategies for the undergraduate classroom
-    \item[]Assessed individual student technical presentations and overall course grading
-\end{itemize}
-\vspace*{.75\baselineskip}
-
-\noindent\textit{E124: Ethics and the Impact of Technology on Society \hfill{Spring 2006; 2005; 2004}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Conducted multiple discussion sections on a weekly basis and review lectures
-    \item[]Supervised research projects based on current, ethical and scientific issues 
-    \item[]Assessed individual student presentations, projects, and overall course grading
-\end{itemize}
-\vspace*{.75\baselineskip}
-
-\noindent\textit{IDS110: Introduction to Computing \hfill{Fall 2004}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Conducted multiple laboratory sessions on a weekly basis
-    \item[]Supervised undergraduate research projects focused on web based education
-    \item[]Assessed laboratory assignments and project grading
-\end{itemize}
-\vspace*{.75\baselineskip}
-
-\noindent\textit{NE92: Issues in Nuclear Science and Engineering \hfill{Spring 2002; 2000}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Coordinated guest lecturers from Department of Nuclear Engineering
-    \item[]Conducted review lectures
-    \item[]Developed examinations and homework assignments
-    \item[]Assessed overall course grading
-\end{itemize}
-\vspace*{.75\baselineskip}
-
-\noindent\textit{NE275: Principles and Methods of Risk Analysis \hfill{Fall 2001}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]This graduate course requires a deeper understanding of the subject matter, due to the student body.
-The course was one of three in the curriculum with the highest credit load.
-The main responsibility in this was to advise and grade semester projects and presentations based on risk assessments of engineering systems.
-\end{itemize}
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Reader}\\
-\noindent\textit{NE150: Introduction to Nuclear Reactor Theory \hfill{Spring 2003}}\\
-\noindent\textit{NE104: Radiation Detection and Nuclear Instrumentation Laboratory \hfill{Fall 2002}}\\
-\noindent\textit{NE107: Introduction to Imaging \hfill{Spring 2001}}\\
-\noindent\textit{NE120: Nuclear Materials \hfill{Fall 2000}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Supervised laboratory sessions
-    \item[]Assessed examinations, homework assignments, laboratory reports, final grades
-    \item[]Conducted review lectures
-\end{itemize}
+\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
+\textbf{Title}\\ 
+\textit{Course Number: Title \hfill{Semester}}\\
+Summary
 
 \section*{Professional Service} 
-\subsection*{University of Idaho}
+\subsection*{University/Institution} %department/college related activities
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Faculty Advisor - American Nuclear Society, University of Idaho Student Section
-    \item[]Member - Graduate Faculty, University of Idaho
-    \item[]Member - NRC Student Fellowship Oversight Committee, Nuclear Engineering Program
-    \item[]Member - Nuclear Engineering Program Admissions Committee
-    \item[]Member - Idaho Falls Center for Higher Education Safety Committee
+    \item[]
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{2018}
-    \item[]Nuclear Engineering Faculty, Idaho State University, Idaho Falls Polytechnic Institute
+    \item[]\textit{Year}
+    \item[]Search committee %don't say it was a failed search 
             \vspace{.05in}
-    \item[]\textit{2017}
-    \item[]Mechanical/Nuclear Engineering Faculty, University of Idaho
+    \item[]\textit{Year}
+    \item[]Search committee %don't say it was a failed search 
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{Regular periods}
-    \item[]American Nuclear Society Annual and Winter Meetings 
-    \item[]IEEE Transactions on Nuclear Science 
-    \item[]American Nuclear Society Fuel Cycle and Waste Management Division John Randall Scholarship 
-    \item[]Nuclear Science User Facilities 
-    \item[]Advances in Engineering Software 
-    \item[]Nuclear Engineering and Technology 
-    \item[]Annals of Nuclear Energy 
-    \item[]Progress in Nuclear Energy 
-    \item[]Energy Science \& Engineering 
-    \item[]Nuclear Engineering and Design 
-    \item[]International Journal of Nuclear Energy 
+    \item[]\textit{Regular periods} %for journals/conferences on a regular basis
+    \item[] 
             \vspace{.05in}
-    \item[]\textit{2020}
-    \item[]American Nuclear Society Student Conference - North Carolina State University
+    \item[]\textit{Year} %specific one-time reviewing
+    \item[] 
             \vspace{.05in}
-    \item[]\textit{2019}
-    \item[]John Wiley \& Sons, Inc. 
-    \item[]Khalifa University of Science and Technology 
-    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest 
-    \item[]American Nuclear Society Student Conference - Virginia Commonwealth University  
-        \vspace{.05in}
-    \item[]\textit{2018}
-    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest 
-    \item[]USDOE - SBIR/STTR Phase I Release 2 
-    \item[]American Nuclear Society Student Conference - University of Florida  
-        \vspace{.05in}
-    \item[]\textit{2017}
-    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest 
-    \item[]USDOE - SBIR/STTR Phase II Release 2 
-    \item[]USDOE - SBIR/STTR Phase II Release 1 
-    \item[]USDOE - Office of Nuclear Energy, Consolidated Innovative Nuclear Research 
-    \item[]American Nuclear Society Student Conference -  University of Pittsburgh 
-        \vspace{.05in}
-    \item[]\textit{2016}
-    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest 
-    \item[]USDOE - SBIR/STTR Phase I Release 2 
-    \item[]FY17 TI Portfolio, Bonneville Power Administration, Office of Technology Innovation 
-    \item[]American Nuclear Society Student Conference - University of Wisconsin-Madison 
-        \vspace{.05in}
-    \item[]\textit{2015}
-    \item[]American Nuclear Society Idaho Section - Idaho High School Essay Contest
-    \item[]FY16 TI Portfolio, Bonneville Power Administration, Office of Technology Innovation 
-    \item[]USDOE - Advanced Research Projects Agency-Energy Concept Papers, Open 2015 FOA 
-        \vspace{.05in}
-    \item[]\textit{2012}
-    \item[]USDOE - Advanced Research Projects Agency-Energy Review Panel - Arlington, Virginia
-        \vspace{.05in}
-    \item[]\textit{2011}
-    \item[]International Conf., High-Level Radioactive Waste Management - Albuquerque, New Mexico
-        \vspace{.05in}
-    \item[]\textit{2010}
-    \item[]Clays in Natural \& Engineered Barriers for Radioactive Waste Confinement - Nantes, France
-        \vspace{.05in}
-    \item[]\textit{2007}
-    \item[]Clays in Natural \& Engineered Barriers for Radioactive Waste Confinement - Lille, France 
+    \item[]\textit{Year} %specific one-time reviewing
+    \item[] 
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
-    \item[]Co-Chair, Technical Program Committee, 2018 Advances in Nuclear Nonproliferation Technology and Policy Conference, American Nuclear Society, 11-15 November, 2018, Orlando, Florida
-    \item[]Technical program committee, Advances in Nuclear Nonproliferation Technology and Policy Conference: Bridging the Gaps in Nuclear Nonproliferation, 25-30 September, 2016, Santa Fe, New Mexico
-    \item[]Technical program paper review committee, Advances in Nuclear Nonproliferation Technology and Policy Conference: Bridging the Gaps in Nuclear Nonproliferation, 25-30 September, 2016, Santa Fe, New Mexico
+    \item[]
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
-    \item[]Cybersecurity for nuclear installations, American Nuclear Society Winter Meeting, 17-21 November, 2019, Washington, D.
-C.
-\textit{(co-Organizer with Prof.
-Jamie B.
-Coble, University of Tennessee-Knoxville)}
+    \item[]
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
-    \item[]Spent fuel storage and transportation, American Nuclear Society Winter Meeting, 17-21 November, 2019, Washington, D. C.
-    \item[]Cybersecurity for nuclear installations, American Nuclear Society Winter Meeting, 17-21 November, 2019, Washington, D. C. 
-    \item[]Data synthesis for pyroprocessing safeguards, 2018 Advances in Nuclear Nonproliferation Technology and Policy Conference (ANTPC), American Nuclear Society, 11-15 November, 2018, Orlando Florida
-    \item[]Special session - Prof. Joonhong Ahn Memorial, International High-Level Radioactive Waste Management Conference, 09-13 April, 2017, Charlotte, North Carolina
-    \item[]Nonproliferation policy, concepts, and approaches: Treaty verification regimes, state-level concepts and fuel cycle analysis, Advances in Nuclear Nonproliferation Technology and Policy Conference: Bridging the Gaps in Nuclear Nonproliferation, 25-30 September, 2016, Santa Fe, New Mexico
-    \item[]Security, safeguards, and non-proliferation, International Conf., High-Level Radioactive Waste Management, 10-14 April 2011, Albuquerque, New Mexico
-    \item[]Used Fuel recycling technologies-I, International Congress on Advances in Nuclear Power Plants (ICAPP ‘10) 13-17 June, 2010, San Diego, California
-    \item[]Engineered systems and transport processes, International Conf., High-Level Radioactive Waste Management, 07-11 September, 2008, Las Vegas, Nevada
-    \item[]Challenges in nuclear waste disposal: Sociological aspects and technical approaches, Global Center of Excellence, 06 December, 2007, The University of Tokyo, Tokyo Japan
+    \item[]
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
-    \item[]Nuclear cybersecurity research initiatives annual meeting, Center for Advanced Energy Studies, 27-28 July, 2017, Idaho Falls, Idaho
-    \item[]Nuclear cybersecurity research focus area identification annual meeting, Center for Advanced Energy Studies, 21-22 July, 2016, Idaho Falls, Idaho
-    \item[]Technical implications of nuclear energy system options, Symposium on scientific and institutional aspects of advanced systems for spent nuclear fuels in emerging nuclear countries, Center for International Security and Cooperation, 29-30 September, 2011, Stanford University, Palo Alto, California
+    \item[]
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{University of Idaho $\sq$ Idaho Falls Center for Higher Education}
-    \item[]Strategies and success for ethical research $\sq$ Vandal Advantage Graduate Student Orientation \hfill{\textit{August 2019; 2018}}
+    \item[]\textit{University/Institution $\sq$ Department} %speaking at graduate orientation, etc.
+    \item[]Title $\sq$ Purpose \hfill{\textit{Dates}}
         \vspace{.05in}
-    \item[]\textit{Seminars}
-    \item[]University of Tennessee-Knoxville Department of Nuclear Engineering \hfill{\textit{October 2019}}
+    \item[]\textit{Seminars} %typical department seminar talks
+    \item[]University/Institution Department \hfill{\textit{Date}}
         \vspace{.05in}
-    \item[]\textit{Lightning Talks}
-    \item[]Idaho National Laboratory Nuclear Science \& Technology Research Planning Meeting \hfill{\textit{February 2018}}
-    \item[]Idaho National Laboratory Energy \& Environment Research Planning Meeting \hfill{\textit{November 2017}}
+    \item[]\textit{Lightning Talks} %throw everything in there 
+    \item[]Talk \hfill{\textit{Date}}
         \vspace{.05in}
     \item[]\textit{Outreach}
-    \item[]P3/TRIO Upward Bound STEM Day \hfill{\textit{December 2015}}
+    \item[]Event \hfill{\textit{Date}}
         \vspace{.05in}
-    \item[]\textit{Lectures}
-    \item[]Stanford University Pre-Collegiate Summer Institutes \hfill{\textit{July 2014}}
+    \item[]\textit{Lectures} %invited to lecture in a course
+    \item[]University/Institution - Course or topic \hfill{\textit{Date}}
 \end{itemize}
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{College of Eastern Idaho Machine Tool Technology Advisory Board} \hfill{\textit{2018}}
+    \item[]\textit{Event} \hfill{\textit{Date}}
+    \item[]Summary 
         \vspace{.05in}
-    \item[]\textit{Idaho American Nuclear Society Smoke Detector Donation Program} \hfill{\textit{2016 - }}
-    \item[]Administration and delivery of smoke detectors to counties in need across the State of Idaho.
-Over the past fourteen years, we have worked with more than 70 fire departments to donate more than 5700 smoke detectors to Idaho residents.
-From 2016-19, we donated nearly 1800 smoke detectors to Arimo, Ashton, Bancroft, Bear Lake, Clear Creek, Declo, Downey, Grace, Hamer, Lava Hot Springs, Roberts, Shelley, and Soda Springs, across southeastern Idaho; Centerville, Clear Creek, Horseshoe Bend, Idaho City, Lowman, Placerville and Valley of the Pines in Boise County; and north to the panhandle in Coeur D'Alene, Mullan, Shoshone, North Side, and West Pend.
-        \vspace{.05in}
-    \item[]\textit{Idaho American Nuclear Society Highway Cleanup} \hfill{\textit{2016 - }}
-    \item[]Garbage cleanup of Miles 122-124 on Interstate 15 twice per year
+    \item[]\textit{Event} \hfill{\textit{Date}}
+    \item[]Summary 
 \end{itemize}
 
-\subsection*{Outreach and Related Professional Activities}
+\subsection*{Outreach and Related Professional Activities} %career fairs, etc.
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Utah State University Graduate School Fair \hfill{\textit{September 2019}}
-    \item[]Montana Tech Career Fair    \hfill{\textit{September 2019; March 2018}}
-    \item[]American Nuclear Society Diversity Social UI ANS Student Sponsorship \hfill{\textit{June 2018; November 2017; June 2017}}
-    \item[]University of Idaho Moscow Campus Recruiting \hfill{\textit{January 2020; October 2018; March 2017}}
-    \item[]Center for Advanced Energy Studies Seminar Series \hfill{\textit{October 2015-17}}
-    \item[]Department of Energy consent based siting meeting \hfill{\textit{July 2016}}
-    \item[]PHYSOR University of Idaho Sponsorship \hfill{\textit{April 2016}}
-    \item[]Boise State University Nuclear Research Summit \hfill{\textit{March 2016}}
-    \item[]UI \& BYU American Nuclear Society Student Social \hfill{\textit{October 2018; February 2016}}
-    \item[]BYU-Idaho Career Fair \hfill{\textit{October 2015}}
+    \item[]Event \hfill{\textit{Date}}
 \end{itemize}
@@
 \subsection*{Professional Training}
-\noindent\textbf{Los Angeles}\\
-\textbf{Participant}\\
-\textit{National Science Foundation Grant Development Conference} \hfill{\textit{May 2019}}\\
-Key officials representing each NSF program directorate, administrative office, Office of General Counsel, and Office of the Inspector General will participate in this two-day conference.
-The conference is considered a must, particularly for new faculty, researchers, educators and administrators who want to gain insight into a wide range of important and timely issues at NSF, including: the state of current funding; the proposal and award process; and current and recently updated policies and
-procedures.
+\noindent\textbf{University/Institution}\\
+\textbf{Role}\\
+\textit{Title of Event} \hfill{\textit{Date}}\\
+Summary
 \vspace*{.75\baselineskip}
 
-\noindent\textbf{University of Illinois Urbana-Champaign}\\
-\textbf{Invited Participant}\\
-\textit{Collaborative Open Source Curriculum Development Workshop} \hfill{\textit{July 2018}}\\
-This workshop concluded a year of faculty interaction at six universities to develop curricula for courses common across the same disciplines at multiple universities in order to reduce the amount of time that any individual professor spends on creating what is essentially duplicate materials.
-The method proposed in this workshop is based on open source software development, where code is shared in online repositories, reviewed by peers, and contributed to the main project.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Generation Atomic + GAIN}\\
-\textbf{Facilitator}\\
-\textit{Nuclear Advocacy and Communications Training} \hfill{\textit{June 2018}}\\
-Opposition groups claim nuclear power plants are unsafe.
-Recently, the U.S.
-nuclear power industry has been characterized as too expensive and dangerous when compared to other energy sources.
-As members of the nuclear community, we know that the success of nuclear energy has never been more important to ensuring a positive future for the world – but what can we do to make a difference?
-This workshop will leave participants energized to tell today’s nuclear power story and be
-well-equipped with the tools to do so.
-Convincing others about the benefits of nuclear involves more than just laying out the facts.
-Thoughtful and personal storytelling bridges gaps when speaking those who are unfamiliar with the technology by explaining the personal and moral reasons that we work in this field.
-Telling our personal stories and motivations for working in nuclear creates common ground from which we can better explain nuclear’s benefits: whether it’s as a mother talking to a
-father, a surfer talking to a skier, or a cook talking to a conservationist, the human stories that nuclear makes possible are our strongest tools when speaking to the public.
-The most effective nuclear advocacy takes place at the interpersonal level when we strike up conversations with peers and even better, strangers.
-Because you can never know who it might be sitting across from you at that dinner party or next to you on the airplane, it’s important to practice having open, considerate
-conversations with people of all backgrounds. 
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Pacific Northwest National Laboratory}\\
-\textbf{Invited Participant}\\
-\textit{Cyber Security Course for Safeguards Practitioners} \hfill{\textit{April 2018}}\\
-The course is designed for early to mid-career safeguards practitioners (technical instrument developers, instrument users, policy advisors, etc.) who will benefit from a greater understanding of cyber security threats and how to reduce risks to safeguards systems and processes.
-This 3.5 day course is designed to teach safeguards and cybersecurity experts how to recognize and mitigate potential cybersecurity vulnerabilities in emerging safeguards instrumentation, information systems, and conduct of operations.
-This training features classroom style learning opportunities through hands-on exercises and provides plenty of time for questions and discussion.
-Participants will learn new cyber security skills, use cyber security tools, and collaborate with one another and cyber experts to resolve challenges.
-They will gain an understanding of cyber security principles and a better awareness of cyber risks associated with safeguards systems.
-Exercises will include puzzles, exploits of attended and unattended monitoring systems, blended physical and cyber attacks on fictional nuclear facilities, and network defense.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Idaho National Laboratory Nuclear Science and Technology}\\
-\textbf{Invited Participant}\\
-\textit{Collaborative Research Planning Meeting} \hfill{\textit{February 2018}}\\
-The Center for Advanced Energy Studies (CAES) is a catalyst for collaborative projects focused on energy research, achieved via connections between the CAES entities – Idaho National Laboratory (INL), Boise State University, Idaho State University, University of Idaho, and University of Wyoming – and beyond.
-Through a series of strategic planning meetings, CAES leadership aims to develop a set of focused research directions.
-The meeting is intended to establish new collaboration, along with a list of prioritized goals and actions items that will steer internal research investments with the intent of growing sustainable, externally-funded programs.
-The planning meeting will focus on a strategic area tied to one or more INL directorates and will bring together the appropriate INL and university leadership and researchers.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Idaho National Laboratory National and Homeland Security Sci \& Tech}\\
-\textbf{Invited Participant}\\
-\textit{Collaborative Research Planning Meeting} \hfill{\textit{February 2018}}\\
-The Center for Advanced Energy Studies (CAES) is a catalyst for collaborative projects focused on energy research, achieved via connections between the CAES entities – Idaho National Laboratory (INL), Boise State University, Idaho State University, University of Idaho, and University of Wyoming – and beyond.
-Through a series of strategic planning meetings, CAES leadership aims to develop a set of focused research directions.
-The meeting is intended to establish new collaboration, along with a list of prioritized goals and actions items that will steer internal research investments with the intent of growing sustainable, externally-funded programs.
-The planning meeting will focus on a strategic area tied to one or more INL directorates and will bring together the appropriate INL and university leadership and researchers.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Idaho National Laboratory Energy \& Environment Science and Technology}\\
-\textbf{Invited Participant}\\
-\textit{Collaborative Research Planning Meeting} \hfill{\textit{November 2017}}\\
-The Center for Advanced Energy Studies (CAES) is a catalyst for collaborative projects focused on energy research, achieved via connections between the CAES entities – Idaho National Laboratory (INL), Boise State University, Idaho State University, University of Idaho, and University of Wyoming – and beyond.
-Through a series of strategic planning meetings, CAES leadership aims to develop a set of focused research directions.
-The meeting is intended to establish new collaboration, along with a list of prioritized goals and actions items that will steer internal research investments with the intent of growing sustainable, externally-funded programs.
-The planning meeting will focus on a strategic area tied to one or more INL directorates and will bring together the appropriate INL and university leadership and researchers.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Idaho Falls Post Register}\\
-\textbf{Participant}\\
-\textit{Intermountain Energy Summit} \hfill{\textit{August 2017; 2016; 2015}}\\
-This summit is held annually and covers energy issues unique to the intermountain region.
-Participants include faculty from local universities, researchers from national laboratories, energy companies, and politicians.
-This year, the theme is energy security with a focus on nuclear, renewable, and alternative energy sources and continued advancements in grid and cybersecurity.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Idaho National Laboratory}\\
-\textbf{Project Mentor}\\
-\textit{Modeling, Experimentation, Validation (MeV) Summer School} \hfill{\textit{July 2017}}\\
-The MeV Summer School provides enhanced training for engineers and applied scientists involved in design, licensing, and operation of current and advanced nuclear reactor systems through a multi-faceted learning approach of lectures, tours, and hands-on activities.
-The school is being organized through the cooperation of national laboratories, industry, government agencies, and universities that share the goal of building a strong workforce to support global nuclear expansion.
-The faculty will be drawn from the top experts in academia, industry, and government.
-The general organization and conduct of the school will be overseen by an international board of senior experts.
-A local secretariat will provide technical, logistical and administrative support to students and faculty.
-It is the aim of the school to foster the development of a next-generation network of scientists and engineers capable of advancing nuclear energy in the 21st century through integrated modeling and experimentation.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of Illinois Urbana-Champaign}\\
-\textbf{Invited participant}\\
-\textit{PyNE Summit} \hfill{\textit{June 2017}}\\
-PyNE is a suite of tools to aid in computational nuclear science and engineering.
-PyNE seeks to provide native implementations of common nuclear algorithms, as well as Python bindings and I/O support for other industry standard nuclear codes.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of Illinois Urbana-Champaign}\\
-\textbf{Invited Participant}\\
-\textit{Collaborative Open Source Curriculum Development Workshop} \hfill{\textit{June 2017}}\\
-This workshop included faculty at six universities to develop curricula for courses common across the same disciplines at multiple universities in order to reduce the amount of time that any individual professor spends on creating what is essentially duplicate materials.
-The method proposed in this workshop is based on open source software development, where code is shared in online repositories, reviewed by peers, and contributed to the main project.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Pacific Northwest National Laboratory}\\
-\textbf{Invited Participant}\\
-\textit{Pacific Northwest National Laboratory Safeguards Laboratory Day} \hfill{\textit{May 2019; 2018; 2017}}\\
-Students and faculty from the University of Idaho were invited to Pacific Northwest National Laboratory to learn about the research activities at the laboratory.
-The day also included hands-on safeguards and security experiments conducted at laboratory facilities, such as materials accounting and vehicle searches.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Department of Energy}\\
-\textbf{Participant}\\
-\textit{Consent-Based Siting Public Meeting} \hfill{\textit{July 2016}}\\
-The Department of Energy is in the initial phase of developing a consent-based process for siting the facilities needed to store and dispose of the nation’s spent nuclear fuel and high-level radioactive waste.
-A consent-based approach to siting relies on understanding the views of the public, stakeholders, and governments at the local, state, and tribal levels.
-In this first phase, the Department is engaging with interested groups and individuals to learn about what elements are important to consider in designing an enduring approach to siting.
-This session is an opportunity for the public to share thoughts and perspectives through a facilitated discussion.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Global American Business Institute}\\
-\textbf{Invited Participant}\\
-\textit{Trilateral Nuclear Energy Dialogue: Korea, Japan, United States} \hfill{\textit{July 2016}}\\
-Convene a high-level private workshop among preeminent Korean, Japanese, and American experts in nuclear energy and nuclear policy issues, with the intention of fostering relationships, confidence building, and seeking potential areas for trilateral cooperation.
-In keeping with the overarching theme of previous discussions—the back-end fuel cycle—this meeting seeks to underscore the role of advanced nuclear energy and fuel cycle technologies.
-Although the obstacles impeding permanent solutions to spent fuel and radioactive waste are largely political, this dialogue aims to highlight the potential of cutting-edge technologies in addressing the policy, environmental, and public acceptance challenges facing management of the nuclear fuel cycle, in addition to opportunities for international collaboration in the research, development, demonstration, and deployment of such technologies.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Pacific Northwest National Laboratory}\\
-\textbf{Invited Participant}\\
-\textit{Next Generation Safeguards Initiative Summer Course} \hfill{\textit{June 2016}}\\
-This course, offered through the DOE/NNSA Next Generation Safeguards Initiative (NGSI), covers major international safeguards procedures currently in use in IAEA member nations.
-Daily lectures were supplemented with hands-on safeguards activities conducted by IAEA safeguards inspectors and researchers at PNNL.
-Participants included faculty, postdoctorate researchers, and graduate students.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Boise State University}\\
-\textbf{Participant}\\
-\textit{Idaho's Role in Nuclear: Clean Energy Powered by the Next Generation} \hfill{\textit{March 2016}}\\
-Boise State University is proud to bring globally recognized leaders in nuclear energy to address the benefits and challenges associated with nuclear energy production and its role in supplying clean energy for a growing world.
-The summit will also include a panel discussion with John Kotek, Assistant Director of Nuclear Energy, U.S.
-Department of Energy; Dr.
-Mark Peters, Laboratory Director for the Idaho National Laboratory; Mark Rudin, Vice President for Research at Boise State University; Mike McGough, Chief Commercial Officer at NuScale Power, and Dr.
-Harold Blackman, Associate Vice President for Research and Economic Development at Boise State University.
-The panel will address questions about the benefits of and concerns around nuclear power.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Portland State University}\\
-\textbf{Participant}\\
-\textit{National Science Foundation Grant Development Conference} \hfill{\textit{February 2016}}\\
-Key officials representing each NSF program directorate, administrative office, Office of General Counsel, and Office of the Inspector General will participate in this two-day conference.
-The conference is considered a must, particularly for new faculty, researchers, educators and administrators who want to gain insight into a wide range of important and timely issues at NSF, including: the state of current funding; the proposal and award process; and current and recently updated policies and procedures.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley}\\
-\textbf{Invited Participant}\\
-\textit{Proliferation Resistance and Physical Protection Working Group Workshop} \hfill{\textit{November 2015}}\\
-The PR\&PP methodology was developed within the Generation IV International Forum (GIF) to provide a structured framework to assess the proliferation resistance and physical protection robustness of Gen IV nuclear energy systems, and to guide designers to further improve their systems.
-This workshop is intended to familiarize non-experts in this field with the broad aspects of the methodology and its applications.
-The PR\&PP Working Group will present an overview of the methodology to an audience of  students, academics, and members of the GIF community who wish to become more familiar with the PR\&PP methodology.
-To illustrate the methodology, its application to a hypothetical nuclear energy system will be examined.
-Workshop participants will be divided into subgroups that will consider different proliferation and security threats, and will identify important design features and approaches that contribute to the system’s resilience to these threats.
-Following these subgroup sessions, workshop participants will reconvene to review insights from the subgroups.
-Finally, an open discussion will be held to obtain feedback from the participants on the GIF approach to PR\&PP with the objective of refining the methodology and its presentation to the wider community of academics and prospective GIF users.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{State of Idaho Board of Education $\sq$ Boise, Idaho}\\
-\textbf{Invited participant}\\
-\textit{Open Education Resources Development} \hfill{\textit{October 2015}}\\
-This workshop focused on the use of open source educational materials in order to produce an online textbook as a supplement to existing commercial textbooks.
-An online textbook allows flexibility for faculty to augment content without requiring multiple textbooks for a course.
-An online textbook allows the educational content of a course to be more closely aligned with the desired learning outcomes.
-Two online texts have been developed: Principles of Nuclear Engineering and Risk Assessment.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Discussant}\\
-\textit{Advanced Summer School of Radioactive Waste Disposal with Social-Scientific Literacy} \hfill{\textit{August 2011}}\\
-\textit{Reflections on the Fukushima Nuclear Accident and Beyond}\\
-This advanced summer school was established in conjunction with the Department of Nuclear Engineering/Management, the University of Tokyo and the Department of Nuclear Engineering, University of California, Berkeley to provide Ph.D.
-students and early-career nuclear engineers with education in social sciences and engineering.
-The goal was to foster a next generation of engineers capable of understanding the public and societal needs, contributing to the societal decision making, and taking a responsible role as engineering experts in society.
-The discussant leads student group activities by stimulating questions from students and corroborating with the chair to develop a summary of lectures.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Invited Participant}\\
-\textit{Minner Fellows Program} \hfill{\textit{June 2011}}\\
-The objective of this program was to develop a framework for making ethical judgments in engineering.
-Because engineering faculty and graduate students play a leadership role in the development of these technologies, it is essential that they become aware the ethical, legal and social ramifications of them.
-The course focused on context, or the embodiment of moral maturity and ethical expertise, in the same way that faculty and graduate students embody engineering and technical expertise.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{Hawai'i Tokai International College}\\
-\textbf{Project Mentor}\\
-\textit{Advanced Summer School of Radioactive Waste Disposal with Social-Scientific Literacy} \hfill{\textit{August 2010}}\\
-Special emphasis was placed on integrating nuclear science and engineering with social science.
-A series of lectures and student group discussions were conducted, followed by a student workshop in which projects were developed, under the theme of ‘nuclear engineers in society,’ including topics such as the safety of a high level waste repository and nuclear systems for non-nuclear weapons states.
-Project mentors provided guidance, direction, and oversight.
-The school ended with a series of project presentations and submittal of project reports.
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley $\sq$ Department of Nuclear Engineering}\\
-\textbf{Student}\\
-\textit{Advanced Summer School of Radioactive Waste Disposal with Social-Scientific Literacy} \hfill{\textit{August 2009}}\\
-In this summer school, The integration of nuclear science and engineering with social science was emphasized through a series of lectures, panel and group discussions.
-Students directed discussions based on the activities each day.
-The school culminated in a tour of the Waste Isolation Pilot Plant (WIPP).
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University of California-Berkeley $\sq$ Graduate Student Instructor Teaching \& Resource Center}\\
-\textbf{Participant}\\
-\textit{Summer Institute for Preparing Future Faculty} \hfill{\textit{May - June 2005}}\\
-This unique program is for Doctoral Candidates with an interest in an academic career.
-Many aspects of teaching are covered: course design, syllabus development, teaching and learning assessment, teaching and learning strategies, and the creation of a teaching portfolio.
-The program exposes candidates to faculty in several disciplines both within and outside the university; thus allowing for the dissemination of the full scope of teaching methods and skills, as well as broadening of perspectives with regards to the entire teaching profession.
-\vspace*{.75\baselineskip}
+\noindent\textbf{University/Institution}\\
+\textbf{Role}\\
+\textit{Title of Event} \hfill{\textit{Date}}\\
+Summary
 
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textbf{University of Idaho}
-    \item[]\textit{American Nuclear Society University of Idaho Student Section}
-    \item[]Samuel Glasstone Award for Public Service $\sq$ Second Place \hfill{\textit{2019}}
-    \item[]Certificate of Distinction \hfill{\textit{2019}}
+    \item[]\textbf{University/Institution}
+    \item[]Award or fellowship \hfill{\textit{Date}}
         \vspace{.05in}
-    \item[]\textbf{University of California-Berkeley}
-    \item[]Nuclear Engineering Department Block Grant Fellowship \hfill{\textit{2005}}
-    \item[]Outstanding Graduate Student Instructor Award \hfill{\textit{2003}}
-    \item[]Katherina S. DeSharton Fellowship \hfill{\textit{1999}}
-    \item[]Hamilton Family Memorial Fellowship \hfill{\textit{1999}}
-        \vspace{.05in}
-    \item[]\textbf{United States Department of Energy $\sq$ Office of Civilian Radioactive Waste Management}
-    \item[]Civilian Radioactive Waste Management Fellowship \hfill{\textit{2000 - 2004}}
-        \vspace{.05in}
-    \item[]\textbf{Nuclear Energy Institute}
-    \item[]National Academy for Nuclear Training Fellowship \hfill{\textit{1999}}
-\end{itemize}
+    \item[]\textbf{University/Institution}
+    \item[]Award or fellowship \hfill{\textit{Date}}
 
@@
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textbf{American Nuclear Society}
-    \item[]Executive Committee $\sq$ Nonproliferation Policy Division \hfill{\textit{2019 - 2022}}
-    \item[]Executive Committee $\sq$ Student Sections Committee \hfill{\textit{2018 - 2021}}
-    \item[]Executive Committee $\sq$ Fuel Cycle and Waste Management Division, American Nuclear Society \hfill{\textit{2018 - 2021}}
+    \item[]\textbf{Society}
+    \item[]Position \hfill{\textit{From - To}}
         \vspace{.05in}
-    \item[]\textbf{Idaho Section of the American Nuclear Society}
-    \item[]Community Service \hfill{\textit{2016 - }}
-    \item[]Board of Directors \hfill{\textit{2018 - 2019}}
-        \vspace{.05in}
-    \item[]Tau Beta Pi Engineering Society
+    \item[]\textbf{Society}
+    \item[]Position \hfill{\textit{From - To}}
 \end{itemize}

### 2020-04-22 journal/journal-paper-standard-coverletter.tex
journal paper

%TheDoctorRAB
%Used for first draft or revised manuscript
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage{xcolor} %change font color
\usepackage{filecontents}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}
\usepackage{times}
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent
\usepackage{enumitem}
\usepackage{boldline}

\usepackage{xr}
\externaldocument{} %aux file needed for cross references

\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag

%%% move page number to bottom right
\usepackage{fancyhdr}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\thepage}
\pagestyle{fancy}
%%%

\begin{document}

\thispagestyle{empty} %start with page number 1 on second page

\begin{flushright}
    \today \\
    Lead author contact information
\end{flushright}

\noindent Dr. Editor Name \\
Editor-in-Chief \\
\textit{Journal} \\ \\

\noindent Dear Dr. Editor Name: \\

\noindent We would like to submit the (revised, original) manuscript to \textit{Journal} entitled, `Fancy Title'. \\

\noindent (Each of the three reviewer comments were studied in detail, and a careful response was prepared for each comment. In the marked manuscript, omissions are recorded \sout{as follows}. For revisions, \edit{colored font was used}, and a footnote was provided to indicate the comment from the reviewer.\fn{R1 - Comment from Reviewer 1.})\\

\noindent Thank you (again) for this opportunity. Please refer to my contact information above.

\vspace*{\fill}
\begin{flushright}
    Sincerely,\\
    Lead author
\end{flushright}
\noindent \small{encl.: Marked Manuscript, Clean Manuscript, Response to Reviewer 1, Response to Reviewer 2, Response to Reviewer 3} %only major documents

\end{document}

### 2020-08-17 proposals/white-paper/white-paper.tex

\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{caption}
\captionsetup[table]{skip=11pt} %sets a space after table caption
\usepackage{times}
\usepackage{enumitem}
\usepackage[labelfont=bf]{caption}

\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations

%%%move page number to bottom right
\usepackage{fancyhdr}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\thepage}
\pagestyle{fancy}
%%%

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
\renewcommand{\headrulewidth}{0.5pt} %turn off line in header
\lhead{\scriptsize Name}
\chead{\scriptsize Title, subject, agency, etc.}
\rhead{\scriptsize \today}
\rfoot{\thepage}

\begin{document}

\begin{center}\textbf{Title}\end{center}

\noindent\textbf{Summary of the Proposed Project.} 
\\

\noindent\textbf{Overall Objective.}
\\

\noindent\textbf{Importance and Relevance to Objectives.}
\\

\noindent\textbf{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project.
\\

\noindent\textbf{Task I. Title.}
\\

\noindent\textbf{Task II. Title.}
\\

\noindent\textbf{Task III. Title.}
\\

\noindent\textbf{Task N. Title.}

\begin{table}[h!]
    \centering
    \caption{Timeframe for Execution of Proposed Project.}
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        \textbf{Tasks} & \textbf{M} & \textbf{M} & \textbf{M} & \textbf{M} & \textbf{M} \\
        \hline
        Task I & & & & & \\
        \hline
        Task II & & & & & \\
        \hline
        Task III & & & & & \\
        \hline
    \end{tabular}
    \label{tab-timeframe}
\end{table}

% uncomment to prepare references
%\bibliographystyle{}
%\setlength{\bibhang}{0pt}
%\bibliography{}

\end{document}

### 2020-08-18 proposals/white-paper/white-paper.tex
white paper
white paper update

@@
-\documentclass[11pt,a4paper]{article}
+%@TheDoctorRAB
+%Standard white paper/preproposal format when there is a page limit
+%neup.bst designed to use numbered citations in order of appearance, short author list
+\documentclass[11pt,letterpaper]{article}
 \usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
@@
 \usepackage{caption}
-\captionsetup[table]{skip=11pt} %sets a space after table caption
+\captionsetup[table]{skip=0pt} %sets a space after table caption
 \usepackage{times}
 \usepackage{enumitem}
-\usepackage[labelfont=bf]{caption}
+%\usepackage[labelfont=bf]{caption}
 
-\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations
-
-%%%move page number to bottom right
-\usepackage{fancyhdr}
-\fancyhf{}
-\renewcommand{\headrulewidth}{0pt}
-\rfoot{\thepage}
-\pagestyle{fancy}
-%%%
+\usepackage[numbers]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
+\setlength{\bibsep}{0pt} %sets space between references
+\renewcommand{\bibsection}{} %suppresses large 'references' heading
+\renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading
 
@@
 
+\begin{filecontents}{references.bib}
+\end{filecontents}
+
 \begin{document}
 
-\begin{center}\textbf{Title}\end{center}
+\begin{center}\textbf{Title}\end{center}\\
 
@@
 
-% uncomment to prepare references
-%\bibliographystyle{}
-%\setlength{\bibhang}{0pt}
-%\bibliography{}
+\noindent\textbf{References}
+\bibliographystyle{neup}
+\setlength{\bibhang}{0pt}
+\bibliography{references}
 

### 2020-08-18 proposals/white-paper/white-paper.tex
white-paper = preproposal

@@
 \usepackage{ulem} %strikethrough
-\usepackage{xcolor} %change font color
+\usepackage{xcolor,colortbl} %change font color
 \usepackage{graphicx}
@@
 \setcounter{secnumdepth}{5} %set subsection to nth level
-\usepackage{caption}
-\captionsetup[table]{skip=0pt} %sets a space after table caption
 \usepackage{times}
@@
 %\usepackage[labelfont=bf]{caption}
+
+\usepackage[singlelinecheck=false]{caption}
+\captionsetup[table]{skip=0pt} %sets a space after table caption
+\captionsetup[figure]{skip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+
+\usepackage{wrapfig}
+\setlength{\intextsep}{0.10mm}
+\setlength{\columnsep}{0.10mm}
 
@@
 \renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading
+
+\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
+\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
+\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
+\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
 
@@
 \noindent\textbf{Summary of the Proposed Project.} 
+\\
+
+\noindent\textbf{Motivation.}
 \\
@@
     \centering
-    \caption{Timeframe for Execution of Proposed Project.}
-    \begin{tabular}{|l|l|l|l|l|l|}
+    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
+    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
         \hline
-        \textbf{Tasks} & \textbf{M} & \textbf{M} & \textbf{M} & \textbf{M} & \textbf{M} \\
+        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
+        \multicolumn{4}{|c|}{\textbf{Y1}}&
+        \multicolumn{4}{|c|}{\textbf{Y2}}&
+        \multicolumn{4}{|c|}{\textbf{Y3}}\\
+        \cline{2-13}
+        &
+        \textbf{Q1}& 
+        \textbf{Q2}& 
+        \textbf{Q3}& 
+        \textbf{Q4}& 
+        \textbf{Q1}& 
+        \textbf{Q2}& 
+        \textbf{Q3}& 
+        \textbf{Q4}& 
+        \textbf{Q1}& 
+        \textbf{Q2}& 
+        \textbf{Q3}& 
+        \textbf{Q4}\\
         \hline
-        Task I & & & & & \\
+        I. & & & & & & & & & & & & \\
         \hline
-        Task II & & & & & \\
+        II. & & & & & & & & & & & & \\
         \hline
-        Task III & & & & & \\
+        III. & & & & & & & & & & & & \\
+        \hline
+        IV. & & & & & & & & & & & & \\
+        \hline
+        V. & & & & & & & & & & & & \\
+        \hline
+        VI. & & & & & & & & & & & & \\
+        \hline
+        VII. & & & & & & & & & & & & \\
         \hline
@@
 
+%wrap figure around text
+%move to wherever in the text 
+%{l} fixes it on the left margin
+%\begin{wrapfigure}{l}{0.x\textwidth}
+%       \includegraphics[width=0.(x-2)\textwidth]{}
+%    \caption{}
+%    \label{fig-}
+%\end{wrapfigure}
+
 \end{document}

### 2020-08-24 proposals/doe-proposal/proposal-narrative.tex

\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough
\usepackage{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{times}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{tabulary}
%\usepackage[labelfont=bf]{caption}

\usepackage[singlelinecheck=false]{caption}
\captionsetup[table]{skip=0pt} %sets a space after table caption
\captionsetup[figure]{skip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format

\usepackage{wrapfig}
\setlength{\intextsep}{0.20mm}
\setlength{\columnsep}{0.20mm}

\usepackage[numbers]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
\setlength{\bibsep}{0pt} %sets space between references
\renewcommand{\bibsection}{} %suppresses large 'references' heading
\renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
\renewcommand{\headrulewidth}{0pt} %set line thickness in header
%\lhead{\scriptsize Name}
%\chead{\scriptsize Title, subject, agency, etc.}
%\rhead{\scriptsize \today}
\rfoot{\thepage}

\begin{filecontents}{references.bib}
\end{filecontents}

\begin{document}

{\centering 
    \textbf{Title\\
    Call \\
    }
    Name (PI) - Affiliation\\
    Name (co-PI) - Affiliation 
\par
}
\vspace{\baselineskip}

\noindent\textbf{Summary of the Proposed Project.}

%\begin{wrapfigure}{l}{0.32\textwidth}
%    \includegraphics[width=0.30\textwidth]{}
%    \captionsetup{justification=centering}
%    \caption{WSC simulator.}
%    \label{fig-wsc-simulator}
%\end{wrapfigure}
\noindent 
\\
\noindent\textbf{Motivation.} \textit{Context.}

\noindent\textbf{Overall Objective.} The overall objective of this project is to 
\\

\noindent\textbf{Research Focus.} The N workscopes in this project are - 
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\textit{Title (Lead - )}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item
            \item
        \end{itemize}
\end{enumerate}

\vspace{\baselineskip}

\noindent\textbf{Importance and Relevance to Objectives.} \textit{Background.}

\textit{Relevant literature.}

\textit{Unique project features.} 
\\

\noindent\textbf{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project. Many of the Tasks overlap. Research will be concurrent and mutually dependent across the investigators.\\

\noindent\textbf{Workscope 1. Task I. Title.} (\textit{Lead - ; Support - }) 
\\

\noindent\textbf{Workscope N. Task X. Crosscutting Issues.} (\textit{Lead - PI; Support - All}) Lessons learned will be identified for project outcomes. Additional discussion will cover -
\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{itemize}

\noindent\textbf{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} We anticipate the following outcomes -
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{enumerate}

\vspace{\baselineskip}

\begin{table}[H]
    \centering
    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
    \begin{tabular}{|p{0.27\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}\\
        \cline{2-13}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}\\
        \hline
        I. 
        &\x\textbf{I} 
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        & \\
        \hline
        II. 
        &\x\textbf{II} 
        &
        &
        &
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & \\
        \hline
        III. 
        &\x\textbf{III} 
        &
        &
        &
        &
        &
        & 
        & 
        & 
        & 
        & 
        & \\
        \hline
        IV. 
        &\x\textbf{IV} 
        & 
        & 
        &
        &
        &
        &
        & 
        & 
        & 
        & 
        & \\
        \hline
        V. 
        &\x\textbf{V} 
        & 
        & 
        &
        &
        &
        &
        &
        &
        &
        &  
        & \\
        \hline
        VI. 
        &\x\textbf{VI} 
        & 
        & 
        & 
        & 
        & 
        &
        &
        &
        &
        & 
        & \\
        \hline
        VII. Crosscutting issues 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        &
        &\x\textbf{VII}
        &\x\textbf{VII} \\
        \hline
    \end{tabular}
    \label{tab-timeframe}
\end{table}

\vspace{\baselineskip}

\begin{table}[H]
    \centering
    \caption*{\textbf{Milestones.}}
    \begin{tabular}{|l|l|l|}
        \hline
        \multicolumn{1}{|c|}{\textbf{Milestone}}
        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        0. Project\\logistics
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        0.1. Kick-off report, roles, and responsibilities.\\
        0.2. Annual reports.\\
        0.3. Agency administrative requirements.\\
        0.4. Final project report.\\
        0.5. Journal paper submission.\\
        0.6. Professional society conference presentations.
        \end{tabular}
        & 
        \begin{tabular}[c]{@{}l@{}}
        0.1. Y1-Q2\\
        0.2. Annually\\
        0.3. Quarterly\\
        0.4. Y3-Q4\\
        0.5. Annually\\
        0.6. Annually
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        1. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        1.1. \\
        1.2. \\
        1.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        1.1. \\
        1.2. \\
        1.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        2. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        2.1. \\
        2.2. \\
        2.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        2.1. \\
        2.2. \\
        2.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        3.1. \\
        3.2. \\
        3.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        3.1. \\
        3.2. \\
        3.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        4. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        4.1. \\
        4.2. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        4.1. \\
        4.2. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        5. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        5.1. \\
        5.2  \\
        5.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        5.1. \\
        5.2. \\
        5.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        6. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        6.1. \\
        6.2. \\
        6.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        6.1. \\
        6.2. \\
        6.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        7. Discuss\\crosscutting\\issues
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        7.1. Identify lessons learned.\\
        7.2. Develop future research and educational pathways.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        7.1. Y3-Q3\\
        7.2. Y3-Q4
        \end{tabular}
        \\
        \hline
    \end{tabular}
    \label{tab-milestones}
\end{table}

\vspace{\baselineskip}

\noindent\textbf{Contribution to Advancing State of the Art in Nuclear Engineering and Cybersecurity.} 
\\

\noindent\textbf{Description of Facilities to be Utilized to Execute Scope.} 
\\

\noindent\textbf{Challenges to Accomplish Tasks and Planned Mitigations.} 
\\

\begin{table}[H]
    \centering
    \begin{tabular}{|p{0.45\linewidth}|p{0.45\linewidth}|}
        \hline
        \multicolumn{1}{|c|}{\textbf{Challenges to accomplish tasks}}
        &\multicolumn{1}{|c|}{\textbf{Planned mitigations}}\\
        \hline

        & \\
        \hline

        & \\
        \hline

        & \\
        \hline

        & \\
        \hline

        & \\
        \hline
    \end{tabular}
    \label{tab-milestones}
\end{table}

\vspace{\baselineskip}

\noindent\textbf{Information, Data, and Plans.} All information has been presented in the technical scope.\\

\noindent\textbf{Quality Assurance.} Our project team have practiced a QA approach, consistent with the graded approach established by the DOE Technical Integration Office, per the NEUP website and any additional requirements deemed necessary during contracting. All projects undergo safety review by experts. We have followed this QA expectation in all ongoing awards.\\

\noindent\textbf{Mandatory Requirements.} We abide by current and pending information on nuclear-related federal funding contained in Form 3204. The Mandatory, Go/No-go, requirements will be coordinated with the institutional Office of Sponsored Research, the general counsel, and the Office of Technology Transfer. Each PI noted below will assume responsibility as the point of contact.\\

\begin{table}[h!]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        \textbf{No.}
        &\textbf{Requirement}
        &\textbf{Responsibility}
        &\textbf{Evaluation}\\
        \hline
        1
        &Commitment to reporting and budget requirements
        &All PIs
        &Go/No-go \\
        \hline
        2
        &10 CFR 851 Worker Safety and Health Program
        &All PIs
        &Go/No-go \\
        \hline
        3
        &Export Control
        &All PIs
        &Go/No-go \\
        \hline
        4
        &Standard Research Subcontract
        &All PIs
        &Go/No-go \\
        \hline
        5
        &Quality Assurance
        &All PIs
        &Go/No-go \\
        \hline
        6
        &Commitment to prepare additional contract elements
        &All PIs
        &Go/No-go \\
        \hline
    \end{tabular}
    \label{tab-mandatory-requirements}
\end{table}

\vspace{\baselineskip}

\noindent\textbf{References}
\bibliographystyle{neup}
\setlength{\bibhang}{0pt}
\bibliography{references}

\end{document}

### 2020-09-08 proposals/benefit-of-collaboration/benefit-of-collaboration.tex

--- 2020-08-24 proposals/doe-proposal/proposal-narrative.tex
@@
 \usepackage{multirow}
-\usepackage{tabularx}
-\usepackage{tabulary}
 %\usepackage[labelfont=bf]{caption}
@@
 \usepackage{wrapfig}
-\setlength{\intextsep}{0.20mm}
-\setlength{\columnsep}{0.20mm}
+\setlength{\intextsep}{0.10mm}
+\setlength{\columnsep}{0.10mm}
 
@@
 
-\begin{filecontents}{references.bib}
-\end{filecontents}
-
 \begin{document}
@@
 {\centering 
-    \textbf{Title\\
-    Call \\
+    \textbf{BENEFIT OF COLLABORATORS\\
+    Title\\
+    Call\\
     }
     Name (PI) - Affiliation\\
-    Name (co-PI) - Affiliation 
+    Name (co-PI) - 
 \par
 }
+
 \vspace{\baselineskip}
@@
 
-%\begin{wrapfigure}{l}{0.32\textwidth}
-%    \includegraphics[width=0.30\textwidth]{}
-%    \captionsetup{justification=centering}
-%    \caption{WSC simulator.}
-%    \label{fig-wsc-simulator}
-%\end{wrapfigure}
-\noindent 
-\\
-\noindent\textbf{Motivation.} \textit{Context.}
-
-\noindent\textbf{Overall Objective.} The overall objective of this project is to 
-\\
+\noindent\textbf{Motivation.}
 
@@
         \end{itemize}
+    \item\textit{Crosscutting Issues (Full team)}
+        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+            \item Identify lessons learned
+            \item Develop future research pathways
+        \end{itemize}
 \end{enumerate}
@@
 
-\noindent\textbf{Importance and Relevance to Objectives.} \textit{Background.}
-
-\textit{Relevant literature.}
-
-\textit{Unique project features.} 
+\noindent\textbf{Team.} This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members.
+The contribution of each is noted.
+The corresponding facilities are briefly described thereafter.
 \\
 
-\noindent\textbf{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project.
-Many of the Tasks overlap.
-Research will be concurrent and mutually dependent across the investigators.\\
-
-\noindent\textbf{Workscope 1. Task I. Title.} (\textit{Lead - ; Support - }) 
+\noindent\textbf{Prof./Dr.
+Name} (Ph.D., Degree Granting Institution) is a \textit{title} at \textit{Affiliation}, etc.
+His/Her/Their research focus is in \textit{area of expertise}.
+Prof./Dr.
+Name is the PI of this project and will be responsible for progress and achievement of all objectives, tasks, and deliverables.
+He/She/They has expertise in \textit{topics contained in text of narrative} from \textit{where/how this expertise was acquired}.
+He/She/They teach \textit{relevant courses} at \textit{Affiliation}.
 \\
 
-\noindent\textbf{Workscope N. Task X. Crosscutting Issues.} (\textit{Lead - PI; Support - All}) Lessons learned will be identified for project outcomes. Additional discussion will cover -
-\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item
-    \item
-    \item
-\end{itemize}
-
-\noindent\textbf{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} We anticipate the following outcomes -
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item
-    \item
-    \item
-\end{enumerate}
-
-\vspace{\baselineskip}
-
-\begin{table}[H]
-    \centering
-    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
-    \begin{tabular}{|p{0.27\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
-        \multicolumn{4}{|c|}{\textbf{Y1}}&
-        \multicolumn{4}{|c|}{\textbf{Y2}}&
-        \multicolumn{4}{|c|}{\textbf{Y3}}\\
-        \cline{2-13}
-        &
-        \textbf{Q1}& 
-        \textbf{Q2}& 
-        \textbf{Q3}& 
-        \textbf{Q4}& 
-        \textbf{Q1}& 
-        \textbf{Q2}& 
-        \textbf{Q3}& 
-        \textbf{Q4}& 
-        \textbf{Q1}& 
-        \textbf{Q2}& 
-        \textbf{Q3}& 
-        \textbf{Q4}\\
-        \hline
-        I. 
-        &\x\textbf{I} 
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        & \\
-        \hline
-        II. 
-        &\x\textbf{II} 
-        &
-        &
-        &
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & \\
-        \hline
-        III. 
-        &\x\textbf{III} 
-        &
-        &
-        &
-        &
-        &
-        & 
-        & 
-        & 
-        & 
-        & 
-        & \\
-        \hline
-        IV. 
-        &\x\textbf{IV} 
-        & 
-        & 
-        &
-        &
-        &
-        &
-        & 
-        & 
-        & 
-        & 
-        & \\
-        \hline
-        V. 
-        &\x\textbf{V} 
-        & 
-        & 
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &  
-        & \\
-        \hline
-        VI. 
-        &\x\textbf{VI} 
-        & 
-        & 
-        & 
-        & 
-        & 
-        &
-        &
-        &
-        &
-        & 
-        & \\
-        \hline
-        VII. Crosscutting issues 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        &
-        &\x\textbf{VII}
-        &\x\textbf{VII} \\
-        \hline
-    \end{tabular}
-    \label{tab-timeframe}
-\end{table}
-
-\vspace{\baselineskip}
-
-\begin{table}[H]
-    \centering
-    \caption*{\textbf{Milestones.}}
-    \begin{tabular}{|l|l|l|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Milestone}}
-        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
-        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        0. Project\\logistics
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        0.1. Kick-off report, roles, and responsibilities.\\
-        0.2. Annual reports.\\
-        0.3. Agency administrative requirements.\\
-        0.4. Final project report.\\
-        0.5. Journal paper submission.\\
-        0.6. Professional society conference presentations.
-        \end{tabular}
-        & 
-        \begin{tabular}[c]{@{}l@{}}
-        0.1. Y1-Q2\\
-        0.2. Annually\\
-        0.3. Quarterly\\
-        0.4. Y3-Q4\\
-        0.5. Annually\\
-        0.6. Annually
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        1. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        1.1. \\
-        1.2. \\
-        1.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        1.1. \\
-        1.2. \\
-        1.3. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        2. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        2.1. \\
-        2.2. \\
-        2.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        2.1. \\
-        2.2. \\
-        2.3. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        3.1. \\
-        3.2. \\
-        3.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        3.1. \\
-        3.2. \\
-        3.3. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        4. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        4.1. \\
-        4.2. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        4.1. \\
-        4.2. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        5. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        5.1. \\
-        5.2  \\
-        5.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        5.1. \\
-        5.2. \\
-        5.3. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        6. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        6.1. \\
-        6.2. \\
-        6.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        6.1. \\
-        6.2. \\
-        6.3. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        7. Discuss\\crosscutting\\issues
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        7.1. Identify lessons learned.\\
-        7.2. Develop future research and educational pathways.
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        7.1. Y3-Q3\\
-        7.2. Y3-Q4
-        \end{tabular}
-        \\
-        \hline
-    \end{tabular}
-    \label{tab-milestones}
-\end{table}
-
-\vspace{\baselineskip}
-
-\noindent\textbf{Contribution to Advancing State of the Art in Nuclear Engineering and Cybersecurity.} 
+\noindent\textbf{Prof./Dr.
+Name} (Ph.D., Degree Granting Institution) is a \textit{title} at \textit{Affiliation}, etc.
+His/Her/Their research focus is in \textit{area of expertise}.
+Prof./Dr.
+Name is the co-PI of this project and will contibute expertise in \textit{related project tasks}.
+He/She/They also is/was \textit{related experience} from \textit{where/how this expertise was acquired}.
+He/She/They teach \textit{relevant courses} at \textit{Affiliation}.
 \\
 
-\noindent\textbf{Description of Facilities to be Utilized to Execute Scope.} 
+\noindent\textbf{Important Research Facility/Equipment} is \textit{description as relevant to project.}
 \\
 
-\noindent\textbf{Challenges to Accomplish Tasks and Planned Mitigations.} 
+\noindent\textbf{Work Project Documentation, Quality Control.} The co-PIs have practiced a QA approach, consistent with that established by the DOE Technical Integration Office, per NEUP website and any additional requirements deemed necessary during contracting.
+All projects undergo safety review by experts.
+We have followed this QA expectation in all ongoing awards.
+We abide by current and pending information on nuclear-related federal funding contained in Form 3204.
+The Mandatory, Go/No-go, requirements will be coordinated with UI’s Office of Sponsored Research, the general counsel and Technology Transfer.
+The PIs assume responsibility as the POC and follow these requirements: 1) Commitment to reporting and budget requirements, 2) 10CFR851 Worker Safety and Health Program, 3) Export Control and 4) Quality Assurance.
 \\
 
-\begin{table}[H]
-    \centering
-    \begin{tabular}{|p{0.45\linewidth}|p{0.45\linewidth}|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Challenges to accomplish tasks}}
-        &\multicolumn{1}{|c|}{\textbf{Planned mitigations}}\\
-        \hline
-
-        & \\
-        \hline
-
-        & \\
-        \hline
-
-        & \\
-        \hline
-
-        & \\
-        \hline
-
-        & \\
-        \hline
-    \end{tabular}
-    \label{tab-milestones}
-\end{table}
-
-\vspace{\baselineskip}
-
-\noindent\textbf{Information, Data, and Plans.} All information has been presented in the technical scope.\\
-
-\noindent\textbf{Quality Assurance.} Our project team have practiced a QA approach, consistent with the graded approach established by the DOE Technical Integration Office, per the NEUP website and any additional requirements deemed necessary during contracting.
-All projects undergo safety review by experts.
-We have followed this QA expectation in all ongoing awards.\\
-
-\noindent\textbf{Mandatory Requirements.} We abide by current and pending information on nuclear-related federal funding contained in Form 3204.
-The Mandatory, Go/No-go, requirements will be coordinated with the institutional Office of Sponsored Research, the general counsel, and the Office of Technology Transfer.
-Each PI noted below will assume responsibility as the point of contact.\\
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{|c|c|c|c|}
-        \hline
-        \textbf{No.}
-        &\textbf{Requirement}
-        &\textbf{Responsibility}
-        &\textbf{Evaluation}\\
-        \hline
-        1
-        &Commitment to reporting and budget requirements
-        &All PIs
-        &Go/No-go \\
-        \hline
-        2
-        &10 CFR 851 Worker Safety and Health Program
-        &All PIs
-        &Go/No-go \\
-        \hline
-        3
-        &Export Control
-        &All PIs
-        &Go/No-go \\
-        \hline
-        4
-        &Standard Research Subcontract
-        &All PIs
-        &Go/No-go \\
-        \hline
-        5
-        &Quality Assurance
-        &All PIs
-        &Go/No-go \\
-        \hline
-        6
-        &Commitment to prepare additional contract elements
-        &All PIs
-        &Go/No-go \\
-        \hline
-    \end{tabular}
-    \label{tab-mandatory-requirements}
-\end{table}
-
-\vspace{\baselineskip}
-
-\noindent\textbf{References}
-\bibliographystyle{neup}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
-
 \end{document}

### 2020-09-08 proposals/white-paper/white-paper.tex
neup template directory setup
update white paper

@@
 \usepackage{enumitem}
+\usepackage{multirow}
 %\usepackage[labelfont=bf]{caption}
@@
 
-\begin{center}\textbf{Title}\end{center}\\
+{\centering 
+    \textbf{Title\\
+    Call\\
+    }
+    Name (PI) - Affiliation\\
+    Name (co-PI) - Affiliation 
+\par
+}
+\vspace{\baselineskip}
 
@@
 \noindent\textbf{Task N. Title.}
+\\
+
+\noindent\textbf{Logical Path to Work Accomplishment.
+Major Deliverables and Outcomes.} We anticipate the following outcomes: (1), (2), (3), (4), (5), and (6) Identify lessons learned and engage in future pathways and partnerships.
+\\
+
+\noindent\textbf{Estimated Cost of the Project.} We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
+\\
 
@@
         \hline
-        I. & & & & & & & & & & & & \\
+        I. 
+        &\x\textbf{I}
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & \\
         \hline
-        II. & & & & & & & & & & & & \\
+        II. 
+        &\x\textbf{II} 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & \\
         \hline
-        III. & & & & & & & & & & & & \\
+        III. 
+        &\x\textbf{III} 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & \\
         \hline
-        IV. & & & & & & & & & & & & \\
+        IV. 
+        &\x\textbf{IV}
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & \\
         \hline
-        V. & & & & & & & & & & & & \\
+        V. 
+        &\x\textbf{V} 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & \\
         \hline
-        VI. & & & & & & & & & & & & \\
+        VI. 
+        &\x\textbf{VI} 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & \\
         \hline
-        VII. & & & & & & & & & & & & \\
+        VII. 
+        &\x\textbf{VII} 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & 
+        & \\
         \hline
@@
 %{l} fixes it on the left margin
+%{L} floats
 %\begin{wrapfigure}{l}{0.x\textwidth}

### 2020-09-08 proposals/doe-proposal/proposal-narrative.tex
latex syntax fixup

@@
         \end{itemize}
+    \item\textit{Cross Cutting Issues (Full team)}
+        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+            \item Identify lessons learned
+            \item Develop future research pathways
+        \end{itemize}
 \end{enumerate}
@@
 Many of the Tasks overlap.
-Research will be concurrent and mutually dependent across the investigators.\\
+Research will be concurrent and mutually dependent across the investigators.
+\\
 
@@
     \item
+    \item Identification of lessons learned and engagement in future pathways and partnerships.
 \end{enumerate}
@@
         \multicolumn{4}{|c|}{\textbf{Y2}}&
-        \multicolumn{4}{|c|}{\textbf{Y3}}\\
+        \multicolumn{4}{|c|}{\textbf{Y3}}
+        \\
         \cline{2-13}
@@
         \textbf{Q3}& 
-        \textbf{Q4}\\
+        \textbf{Q4}
+        \\
         \hline
@@
         &
-        & \\
+        & 
+        \\
         \hline
@@
         & 
-        & \\
+        & 
+        \\
         \hline
@@
         &  
-        & \\
+        & 
+        \\
         \hline
@@
         &\x\textbf{VII}
-        &\x\textbf{VII} \\
+        &\x\textbf{VII} 
+        \\
         \hline
@@
 
-\noindent\textbf{Contribution to Advancing State of the Art in Nuclear Engineering and Cybersecurity.} 
+\noindent\textbf{Contribution to Advancing State of the Art in Nuclear Engineering and .} 
 \\
@@
         \multicolumn{1}{|c|}{\textbf{Challenges to accomplish tasks}}
-        &\multicolumn{1}{|c|}{\textbf{Planned mitigations}}\\
+        &\multicolumn{1}{|c|}{\textbf{Planned mitigations}}
+        \\
         \hline
 
-        & \\
+        & 
+        \\
         \hline
 
-        & \\
+        & 
+        \\
         \hline
 
-        & \\
+        & 
+        \\
         \hline
 
-        & \\
+        & 
+        \\
         \hline
 
-        & \\
+        & 
+        \\
         \hline
@@
         &\textbf{Responsibility}
-        &\textbf{Evaluation}\\
+        &\textbf{Evaluation}
+        \\
         \hline
@@
         &All PIs
-        &Go/No-go \\
+        &Go/No-go 
+        \\
         \hline

### 2020-09-15 proposals/doe-proposal/proposal-narrative.tex
spacing on proposals reduced

@@
 }
-\vspace{\baselineskip}
+
+\vspace{0.5\baselineskip}
 
@@
 \noindent
-\\
+
+\vspace{0.5\baselineskip}
+
 \noindent\textbf{Motivation.} \textit{Context.}
 
+\vspace{0.5\baselineskip}
+
 \noindent\textbf{Overall Objective.} The overall objective of this project is to
-\\
+
+\vspace{0.5\baselineskip}
 
@@
 
-\vspace{\baselineskip}
+\vspace{0.5\baselineskip}
 
@@
 \textit{Unique project features.}
-\\
+
+\vspace{0.5\baselineskip}
 
@@
 Research will be concurrent and mutually dependent across the investigators.
-\\
+
+\vspace{0.25\baselineskip}
 
 \noindent\textbf{Workscope 1. Task I. Title.} (\textit{Lead - ; Support - })
-\\
+
+\vspace{0.25\baselineskip}
 
@@
 \end{itemize}
+
+\vspace{0.5\baselineskip}
 
@@
 \vspace{\baselineskip}
+\vspace{0.5\baselineskip}
 
 \noindent\textbf{Contribution to Advancing State of the Art in Nuclear Engineering and .}
-\\
+
+\vspace{0.5\baselineskip}
 
 \noindent\textbf{Description of Facilities to be Utilized to Execute Scope.}
-\\
+
+\vspace{0.5\baselineskip}
 
 \noindent\textbf{Challenges to Accomplish Tasks and Planned Mitigations.}
-\\
+
+\vspace{0.5\baselineskip}
 
@@
 
-\vspace{\baselineskip}
+\vspace{0.5\baselineskip}
 
-\noindent\textbf{Information, Data, and Plans.} All information has been presented in the technical scope.\\
+\noindent\textbf{Information, Data, and Plans.} All information has been presented in the technical scope.
+
+\vspace{0.5\baselineskip}
 
@@
 All projects undergo safety review by experts.
-We have followed this QA expectation in all ongoing awards.\\
+We have followed this QA expectation in all ongoing awards.
+
+\vspace{0.5\baselineskip}
 
@@
 The Mandatory, Go/No-go, requirements will be coordinated with the institutional Office of Sponsored Research, the general counsel, and the Office of Technology Transfer.
-Each PI noted below will assume responsibility as the point of contact.\\
+Each PI noted below will assume responsibility as the point of contact.
+
+\vspace{0.5\baselineskip}
 

### 2020-11-12 proposals/white-paper/white-paper.tex
latex syntax fixup
spacing on proposals reduced
table L update for raggedright
style fix
section mods for proposals

@@
 \newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
+
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+
+%\paragraph and \subparagraph modifiers
+% no indent for each
+% after \z@ pads whitespace on the top
+% em sets the distance after heading to text horizonally
+
+\makeatletter
+\renewcommand\paragraph{%
+    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
+    {\normalfont \normalsize \bfseries}}%
+
+\makeatletter
+\renewcommand\subparagraph{%
+    \@startsection{subparagraph}{5}{\z@ }{0.45\baselineskip}{-1em}
+    {\normalfont \normalsize \itshape }}%
+
+\makeatletter
+\renewcommand\subsection{%
+    \@startsection{subsection}{2}{\z@ }{0.75\baselineskip}{0.25\baselineskip}
+    { \large \bfseries}}%
 
@@
 \noindent\textbf{Task N. Title.}
-\\
-
-\noindent\textbf{Logical Path to Work Accomplishment.
-Major Deliverables and Outcomes.} We anticipate the following outcomes: (1), (2), (3), (4), (5), and (6) Identify lessons learned and engage in future pathways and partnerships.
-\\
-
-\noindent\textbf{Estimated Cost of the Project.} We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
 \\

### 2020-12-01 proposal-documents/statement-of-work/statement-of-work.tex
white paper template update

%@TheDoctorRAB
%statement of work
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{caption}
\captionsetup[table]{skip=11pt} %sets a space after table caption
\usepackage{times}
\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent
\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations
\usepackage{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}

%\usepackage{xr} %document crossreferencing
%\externaldocument{/path/to/auxfilename} %aux file needed

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag

\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %turn off line in header
\lhead{\scriptsize Funding Agency}
\chead{\scriptsize Statement of Work - \textit{Name}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

\begin{document}

\begin{center}{\textbf{Specific funding call}}
\end{center}

\begin{center}{\textbf{Proposal Title}}\end{center}

    \begin{center}{Name (co-PI) or (PI)\\University $\sq$ Department}
\end{center}

\noindent Prof./Dr. LastName will collaborate/partner/join (list team just as institutions or people if you prefer)...introductory statement of what proposal will do.\\

\noindent\textbf{Work will include - }
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item As 
    \item many
    \item as
    \item needed
    \item ! 
\end{enumerate}

\end{document}

### 2020-12-02 proposal-documents/data-management-plan/data-management-plan.tex
data management plan

%@TheDoctorRAB
%Use for original, revised, clean manuscripts
\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{caption}
\captionsetup[table]{skip=11pt} %sets a space after table caption
\usepackage{times}
\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent
\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations
\usepackage{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}
\usepackage{hyperref}

%\usepackage{xr} %document crossreferencing
%\externaldocument{/path/to/auxfilename} %aux file needed

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column

\makeatletter
\renewcommand\paragraph{%
    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
    {\normalfont \normalsize \bfseries}}%

\makeatletter
\renewcommand\subparagraph{%
    \@startsection{subparagraph}{5}{\z@ }{0.45\baselineskip}{-1em}
    {\normalfont \normalsize \itshape }}%

\makeatletter
\renewcommand\subsection{%
    \@startsection{subsection}{2}{\z@ }{0.75\baselineskip}{0.25\baselineskip}
    { \large \bfseries}}%

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
\renewcommand{\headrulewidth}{0pt} %turn off line in header
%\lhead{\scriptsize NSF CPS 20-563}
%\chead{\scriptsize Data Management Plan}
%\rhead{\scriptsize \today}
\rfoot{\thepage}

\begin{document}

{\centering 
    \textbf{Title\\
    Data Management Plan\\
    \vspace{0.05in}
    }
    Name (PI) - Affiliation 
\par
}

%\noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}} %horizontal line spanning margins

\subsection*{Types of data and materials}
%Data specific to project tasks. List according to workscope.
\noindent During the course of the project, the following data and materials will be generated and collected -
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
    \item
    \item
\end{enumerate}

\subsection*{Data and metadata standards}
%Making sure the agency knows that the teams knows what to do with the data. Edit as needed. 
\noindent Data will be saved in spreadsheets and text files; e.g., csv, tab delimited, etc. Literature and other written materials will be in pdf. All data will be archived on each Investigator's password protected office computer(s), regularly backed-up on external hard drives that will also be password protected, and on the \textit{Specific Institution file sharing system; e.g., OneDrive}. Handwritten notes will be transcribed into LaTeX files or similar word processing files. All files will be named with appropriate and standard convention, reflective of the metadata. Other materials; e.g., output from computational tools (used for any postprocessing of the data), will be stored in their standard format, with supporting documentation as pdf or a `README.txt'. Images and maps will be also stored in standard format; e.g., jpg, as appropriate. Metadata standards are based on the historically best practices based on staff expertise and widespread community use - \href{https://libraries.mit.edu/data-management/}{MIT data management guidance}.

\subsection*{Physical and/or cyber resources and facilities}
\noindent The PI will establish a shared research data space in the cloud; e.g., SharePoint, etc., with project members for storing and sharing soft copies of data and materials. Project-generated data will be archived by the project team. These data will be used in this project as relevant to defined project tasks. Physical resources will be stored in each Investigator's laboratory/office with restricted card key access.

\subsection*{Policies for access and sharing}
%Check with home institution for these paragraphs.
\noindent Collected data and materials will be made available to the general research community as appropriate depending on copyright, confidentiality, and proprietary restrictions.

\paragraph*{Access and sharing.}
\noindent All data and materials will be freely available to project researchers with access to the shared research data storage space. Handwritten documentation will be stored in laboratory notebooks and/or digitally copied/transcribed and stored in the shared space. Collaborators will have access to data and materials upon request and as appropriate with PI acknowledgement. Data and materials will be published and made accessible to the general research community as the research progresses. Investigators retain the right to use the data created under this project before opening it up to wider use. Presentations and publications in conference proceedings and peer-reviewed journals due to project progress will be documented and reported to the sponsor agency.

\paragraph*{Provisions for appropriate protection of privacy, confidentiality, security, intellectual property, or other rights or requirements.}
\noindent While the intention is to broadly disseminate results, it is understood that the project team may be in possession of confidential/proprietary information and may create intellectual property. Information will be made publicly available through standard channels. Throughout the project period, and thereafter, utmost care will be directed to the safeguarding of data that might be deemed sensitive. Such data will be stored in locked cabinets or on secure servers. During the communication of data files only university or company email servers will be used under secure connections. Sensitive data will not be communicated through unsecured wireless networks. Online meetings will be held through PI coordination using the \textit{Institution videoconferencing platform; e.g., Zoom, Teams} with appropriate authentication; e.g., passcodes.

\subsection*{Policies and provisions for reuse and redistribution}
\noindent Data and related materials will be archived for at least three years following the completion of the project. Each Investigators' institution have a dedicated staff of computer support specialists. No special software or tools will be needed to access the data and materials when they are archived. Access will be limited to Investigators and those granted permission to the research data storage space. Data will be archived with the \textit{Specific Institution Repository} and will be
prepared for public release after a reasonable length of time to be determined by the community of interest through the process of peer-review and program management. For additional information about \textit{Specific Institution Repository} institutional data management capabilities, policies and procedures, please contact \textit{Contact Person} at \textit{contact information}.

\subsection*{Roles and responsibilities}
\noindent Investigators will be responsible for postdoctorate and student documents and store data and materials in the manner described herein, as well as for holding long-term purview of the data. Students will be required to review this data management plan, and the standards website noted above prior to initiating research. Any individual on the project that creates any data and materials will hold responsibility for proper documentation and storage with oversight provided by the direct mentor. Investigators will monitor and review the data management and the data management plan, along with the students involved each quarter. As individuals depart the project, they will communicate data and materials under their direct responsibility to the respective Investigator and any incoming replacement. Data will be stored and automatically backed up by the \textit{Specific Institution Information Technology Center}.

\end{document}

### 2020-12-02 reviewer-response/reviewerX-response.tex
reload

%@TheDoctorRAB
\documentclass[11pt,a4paper]{article} 
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in, bmargin=1in]{geometry} 
\usepackage{setspace} 
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage[yyyymmdd]{datetime}
\usepackage{fixltx2e}
\renewcommand{\dateseparator}{.}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{times}
\usepackage{enumitem}
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent

%to crossref between files
%clear both directories
%pdflatex manuscript first
%pdflatex this file next
%filename does not require extension here
\usepackage{xr}
\externaldocument{path/to/marked/manuscript/filename} %crossref through aux file

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag

\makeatletter %make text labels
\newcommand{\labeltext}[3][]{%
    \@bsphack%
    \csname phantomsection\endcsname %in case hyperref is used
    \def\tst{#1}%
    \def\labelmarkup{} %how to markup the label itself
    %\def\refmarkup{\labelmarkup} %How to markup the reference
    \def\refmarkup{}%
    \ifx\tst\empty\def\@currentlabel{\refmarkup{#2}}{\label{#3}}%
    \else\def\@currentlabel{\refmarkup{#1}}{\label{#3}}\fi%
    \@esphack%
    \labelmarkup{#2}% visible printed text.
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
\lhead{\scriptsize Manuscript ID}
\chead{\scriptsize Reviewer N}
\rhead{\scriptsize \today}
\rfoot{\thepage} %move page number to bottom right

\begin{document}

\begin{center}\textbf{Response to Reviewer}\end{center}

\noindent Thank you for the peer review of this manuscript. Each comment was considered carefully. The manuscript has been revised accordingly in the hope that the updated paper is worthy of publication. A detailed response to each comment is provided in this document.

\begin{center}\textbf{Responses to Reviewer Comments}\end{center}

\leftskip0in\relax \rightskip0in\relax
\noindent\textbf{General comments.}\\
\noindent Reviewer comment.  \\

\leftskip.25in\relax \rightskip.25in\relax
\noindent Author response. \\

\noindent Revisions - 
\begin{enumerate}[leftmargin=.5in,rightmargin=.25in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\labeltext{Statement on how authors will revise the manuscript accordingly.}{X-label-name}
\end{enumerate}
\vspace*{\baselineskip}

%how it works
%in marked manuscript, just \ref{X-label-name} (X = Reviewer X), and then the text in \labeltext{} will be referenced

%repeat as needed

\newpage

\leftskip0in\relax \rightskip0in\relax
\noindent\textbf{Editorial comments.}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item Page X-Line Number N - Abstract 1 - \labeltext{Reviewer editorial comment}{X-ed1}\\
        Author response 
        \vspace{.1in}
    \item Page X-Line Number N - \labeltext{Reviewer editorial comment}{X-ed2}\\
        Author response 
        \vspace{.1in}

    %repeat as needed

\end{enumerate}

\end{document}

### 2020-12-02 peer-reviewer/peer-reviewer.tex
reload

--- 2020-12-01 proposal-documents/statement-of-work/statement-of-work.tex
@@
-%@TheDoctorRAB
-%statement of work
 \documentclass[11pt,a4paper]{article}
@@
 \usepackage{footnotehyper}
-%\usepackage{subfig}
+\usepackage{subfig}
 \usepackage[yyyymmdd]{datetime} %date format
 \renewcommand{\dateseparator}{.}
-\graphicspath{{../../img/}} %path to graphics
+\graphicspath{{../img/}} %path to graphics
 \setcounter{secnumdepth}{5} %set subsection to nth level
@@
 \usepackage{caption}
-\usepackage{subcaption}
 \usepackage[labelfont=bf]{caption}
 \usepackage{chngcntr}
-
-%\usepackage{xr} %document crossreferencing
-%\externaldocument{/path/to/auxfilename} %aux file needed
+\usepackage{hyperref}
 
@@
 \newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
-
 \newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
+\renewcommand\labelenumi{(\theenumi)} %changes 1. to (1) in enumerated list
 
@@
 \fancyhf{} %move page number to bottom right
-%\renewcommand{\headrulewidth}{0pt} %turn off line in header
-\lhead{\scriptsize Funding Agency}
-\chead{\scriptsize Statement of Work - \textit{Name}}
+\renewcommand{\headrulewidth}{0.5pt} %turn off line in header
+\lhead{\scriptsize ID}
+\chead{\scriptsize Peer review - \textit{Authors(s)}}
 \rhead{\scriptsize \today}
@@
 
-\begin{center}{\textbf{Specific funding call}}
-\end{center}
+\begin{titlepage}
+    \title{
+        Title\\
+    }
+    \author{
+        Name
+        \\ \\ \\
+        Affiliation 
+        \\ \\
+        Submitted to: \textit{Journal Name}\\[ID]
+        \\ \\ \\
+        editor 
+    }
+\clearpage %not have page number on title page
+\maketitle
+\thispagestyle{empty} %start with page number 1 on second page
+\end{titlepage}
 
-\begin{center}{\textbf{Proposal Title}}\end{center}
+\noindent\textbf{Preface.}
 
-    \begin{center}{Name (co-PI) or (PI)\\University $\sq$ Department}
-\end{center}
+\noindent\textbf{General comments.}
 
-\noindent Prof./Dr. LastName will collaborate/partner/join (list team just as institutions or people if you prefer)...introductory statement of what proposal will do.\\
+\noindent\textbf{Section comments.}
 
-\noindent\textbf{Work will include - }
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item As 
-    \item many
-    \item as
-    \item needed
-    \item ! 
+\noindent\textbf{Line items.}
+\begin{enumerate}[leftmargin=*]
 \end{enumerate}

### 2020-12-02 research-cv/abbreviated-research-two-page-cv.tex
reload

--- 2020-04-01 research-cv/research-cv.tex
@@
-%Research CV template for academics and researchers
 %@TheDoctorRAB
@@
 \usepackage{filecontents}
-\usepackage[yyyymmdd]{datetime} %set preferred date format
-\renewcommand{\dateseparator}{.} %set preferred date separator
+\usepackage[yyyymmdd]{datetime}
+\renewcommand{\dateseparator}{.}
 
@@
 \fancyhf{} %page number on bottom right
-\lhead{\scriptsize Title Name} %title and name
-\chead{\scriptsize \textit{Vita}} %maybe something more specific here if desired
+\lhead{\scriptsize Title Name}
+\chead{\scriptsize \textit{Abbrv. Vita}}
 \rhead{\scriptsize \today} %date
@@
 
-%peer reviewed journal papers
+%\natexlab not working - remove from bbl file
 \begin{filecontents}{peer-reviewed.bib} 
@@
 
-%books and book contributions
-\begin{filecontents}{book-contribution.bib}
-    @book{
-        bk1,
-        author = {},
-        title = {{}},
-        year = {},
-        publisher = {{}}
-        isbn = {}
-    }
-\end{filecontents}
-
-%conference proceedings
-\begin{filecontents}{conference-proceedings.bib}
-    @conference{
-        cf1,
-        author = {},
-        title = {{}},
-        year = {},
-        organization = {},
-        address = {}
-    }
-\end{filecontents}
-
-%reports, misc, non-refeered
-\begin{filecontents}{reports.bib}
-    @misc{
-        rp1,
-        author = {},
-        title = {{}},
-        institution = {},
-        year = {}
-    }
-\end{filecontents}
-
-%conference presentations - not the same as invited talks 
-\begin{filecontents}{conference-presentations.bib}
-    @conference{
-        cf1,
-        author = {},
-        title = {{}},
-        year = {},
-        organization = {},
-        address = {}
-    }
-\end{filecontents}
-
 \begin{document}
 
-%.bib files to create
-\nobibliography{peer-reviewed,book-contribution,conference-proceedings,reports,conference-presentations}
-
-%.bst file
-\bibliographystyle{} %custom bst file
+\nobibliography{peer-reviewed} %bib file
+\bibliographystyle{standard} %custom bst file
 
@@
 
-\begin{center}{
+{\centering 
         \textsc{ %block caps font
             \textbf{
-                {\large Name}\\
-                Title \\
-                Institution $\sq$ Department
-                Address
-                email $\sq$ twitter $\sq$ phone 
+                Name $\sq$ Title \\
+                University/Institution $\sq$ Department \\
+                Address 1 $\sq$ Address 2\\
+                email $\sq$ @Twitter $\sq$ office phone 
             }
         }
-    }
-\end{center}
+\par}
 
@@
 
-\section*{Education}
-\noindent\textbf{University}\\
-\textbf{Doctor of Philosophy $\sq$ Major} \hfill{\textit{Date}}
+\subsection*{Education and Training}
+\noindent University $\sq$ Doctor of Philosophy $\sq$ Major \hfill{Date}\\
+University $\sq$ Master of Science $\sq$ Major \hfill{Date}\\
+University $\sq$ Bachelor of Science $\sq$ Major \hfill{Date}
+
+\subsection*{Research and Professional Experience}
+\noindent University $\sq$ Location $\sq$ Department
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{Dissertation: }
-    \item[]Examination fields: 
-    \item[]Committee: 
+    \item[]Title/Position \hfill{From - To}
 \end{itemize}
-\vspace*{.75\baselineskip}
+\vspace*{.5\baselineskip}
 
-\noindent\textbf{University}\\
-\textbf{Master of Science $\sq$ Major} \hfill{\textit{Date}}
+\noindent University $\sq$ Location $\sq$ Department
 \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{Thesis: }
-    \item[]Advisor: 
-\end{itemize}
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University}\\
-\textbf{Bachelor of Science $\sq$ Major and distinction(s)} \hfill{\textit{}}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{Capstone: }
-    \item[] Advisor: 
+    \item[]Title/Position \hfill{From - To}
 \end{itemize}
 
-\section*{Research Experience} %academic positions
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title} \hfill{\textit{From - To}}\\
-Brief summary 
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title} \hfill{\textit{From - To}}\\
-Brief summary
-
-\section*{Related Research Experience} %like internships
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title} \hfill{\textit{From - To}}\\
-Brief summary 
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title} \hfill{\textit{From - To}}\\
-Brief summary
-
-\section*{Related Professional Experience} %anything else
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title} \hfill{\textit{From - To}}\\
-Brief summary 
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title} \hfill{\textit{From - To}}\\
-Brief summary
-
-\section*{Awarded Projects} %chronologically
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
+\subsection*{Awarded Projects} %chronologically
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
     \item
@@
 
-\section*{Thesis Committees}
-\subsection*{Major Professor} %or adviser, whatever the official title is
-\noindent\textit{Current}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Student Name, Degree - Topic
-\end{itemize}
-\vspace*{.75\baselineskip}
-
-\noindent\textit{Graduates}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Student Name, Degree - Thesis Title 
-\end{itemize}
-
-\subsection*{Member}
-\noindent\textit{Graduates}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Student Name, Degree - Thesis Title 
-\end{itemize}
-
-\section*{Refereed Journal Publications}
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
+\subsection*{Relevant Publications\hfill{*students}} 
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
     \item\bibentry{pr1}.
@@
 
-\section*{Book Contribution}
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item\bibentry{bk1}.
+\subsection*{Relevant Courses Taught}
+\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+    \item[]University $\sq$ Location $\sq$ Department 
+    \item[] Course Number: Title 
+        \vspace{.05in}
+    \item[]University $\sq$ Location $\sq$ Department 
+    \item[] Course Number: Title 
+\end{itemize}
+
+\subsection*{Synergistic Activities}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+    \item
+    \item
+    \item
+    \item
+    \item
 \end{enumerate}
 
-\section*{Refereed Conference Proceedings}
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item\bibentry{cf1}.
-\end{enumerate}
-
-\section*{Non-Refereed Technical Reports}
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item\bibentry{rp1}.
-\end{enumerate}
-
-\section*{Conference Presentations}
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
-    \item\bibentry{cf1}.
-\end{enumerate}
-
-\section*{Teaching Experience}
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title}\\ 
-\textit{Course Number: Title \hfill{Semester}}\\
-Summary
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title}\\ 
-\textit{Course Number: Title \hfill{Semester}}\\
-Summary
-
-\section*{Related Teaching Experience} %for TA, etc.
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title}\\ 
-\textit{Course Number: Title \hfill{Semester}}\\
-Summary
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
-\textbf{Title}\\ 
-\textit{Course Number: Title \hfill{Semester}}\\
-Summary
-
-\section*{Professional Service} 
-\subsection*{University/Institution} %department/college related activities
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]
-\end{itemize}
-
-\subsection*{Academic Search Committees}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{Year}
-    \item[]Search committee %don't say it was a failed search 
-            \vspace{.05in}
-    \item[]\textit{Year}
-    \item[]Search committee %don't say it was a failed search 
-\end{itemize}
-
-\subsection*{Peer Reviewer}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{Regular periods} %for journals/conferences on a regular basis
-    \item[] 
-            \vspace{.05in}
-    \item[]\textit{Year} %specific one-time reviewing
-    \item[] 
-            \vspace{.05in}
-    \item[]\textit{Year} %specific one-time reviewing
-    \item[] 
-\end{itemize}
-
-\subsection*{Conference Committees}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
-    \item[]
-\end{itemize}
-
-\subsection*{Technical Session Organizer}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
-    \item[]
-\end{itemize}
-
-\subsection*{Technical Session Chair}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
-    \item[]
-\end{itemize}
-
-\subsection*{Symposia Organizer}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
-    \item[]
-\end{itemize}
-
-\subsection*{Invited Talks}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{University/Institution $\sq$ Department} %speaking at graduate orientation, etc.
-    \item[]Title $\sq$ Purpose \hfill{\textit{Dates}}
-        \vspace{.05in}
-    \item[]\textit{Seminars} %typical department seminar talks
-    \item[]University/Institution Department \hfill{\textit{Date}}
-        \vspace{.05in}
-    \item[]\textit{Lightning Talks} %throw everything in there 
-    \item[]Talk \hfill{\textit{Date}}
-        \vspace{.05in}
-    \item[]\textit{Outreach}
-    \item[]Event \hfill{\textit{Date}}
-        \vspace{.05in}
-    \item[]\textit{Lectures} %invited to lecture in a course
-    \item[]University/Institution - Course or topic \hfill{\textit{Date}}
-\end{itemize}
-
-\subsection*{Community Service}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textit{Event} \hfill{\textit{Date}}
-    \item[]Summary 
-        \vspace{.05in}
-    \item[]\textit{Event} \hfill{\textit{Date}}
-    \item[]Summary 
-\end{itemize}
-
-\subsection*{Outreach and Related Professional Activities} %career fairs, etc.
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]Event \hfill{\textit{Date}}
-\end{itemize}
-
-\subsection*{Professional Training}
-\noindent\textbf{University/Institution}\\
-\textbf{Role}\\
-\textit{Title of Event} \hfill{\textit{Date}}\\
-Summary
-\vspace*{.75\baselineskip}
-
-\noindent\textbf{University/Institution}\\
-\textbf{Role}\\
-\textit{Title of Event} \hfill{\textit{Date}}\\
-Summary
-
-\subsection*{Awards and Fellowships}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textbf{University/Institution}
-    \item[]Award or fellowship \hfill{\textit{Date}}
-        \vspace{.05in}
-    \item[]\textbf{University/Institution}
-    \item[]Award or fellowship \hfill{\textit{Date}}
-
-\subsection*{Professional Societies and Positions}
-\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item[]\textbf{Society}
-    \item[]Position \hfill{\textit{From - To}}
-        \vspace{.05in}
-    \item[]\textbf{Society}
-    \item[]Position \hfill{\textit{From - To}}
-\end{itemize}
-
 \end{document}

### 2021-01-08 proposal-documents/doe/benefit-of-collaboration/benefit-of-collaboration.tex
doe templates

--- 2020-09-08 proposals/benefit-of-collaboration/benefit-of-collaboration.tex
@@
 \usepackage{multirow}
+\usepackage{tabularx}
+\usepackage{tabulary}
+\usepackage{gensymb}
+\usepackage{longtable}
 %\usepackage[labelfont=bf]{caption}
@@
 \usepackage{wrapfig}
-\setlength{\intextsep}{0.10mm}
-\setlength{\columnsep}{0.10mm}
+\setlength{\intextsep}{0.20mm}
+\setlength{\columnsep}{0.20mm}
 
-\usepackage[numbers]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
+\usepackage[numbers,sort&compress]{natbib} 
+%'numbers' - numbered citations
+%'round' - (1) instead [1]
+%'sort&compress - [1-3] instead [1,2,3]
 \setlength{\bibsep}{0pt} %sets space between references
@@
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
+\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
 \newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
@@
 \newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
+
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+
+\makeatletter
+\renewcommand\paragraph{%
+    \@startsection{paragraph}{4}{\z@ }{0.35\baselineskip}{-1em}
+    {\normalfont \normalsize \bfseries}}%
+
+\makeatletter
+\renewcommand\subparagraph{%
+    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
+    {\normalfont \normalsize \itshape }}%
+
+\makeatletter
+\renewcommand\subsection{%
+    \@startsection{subsection}{2}{\z@ }{0.50\baselineskip}{0.10\baselineskip}
+    { \normalfont \bfseries}}%
 
@@
     \textbf{BENEFIT OF COLLABORATORS\\
-    Title\\
-    Call\\
+    Advanced Data Integration for Materials Accounting of a Bulk Nuclear Materials Handling Facility\\
+    FC-3: Materials Protection, Accounting, and Control Technology\\
     }
-    Name (PI) - Affiliation\\
-    Name (co-PI) - 
+    R. A. Borrelli (PI) - University of Idaho $\sq$ Idaho Falls Center for Higher Education 
 \par
@@
 
-\vspace{\baselineskip}
+\subsection*{Summary of the Proposed Project}
 
-\noindent\textbf{Summary of the Proposed Project.}
+\subsection*{Motivation} 
+\paragraph*{Context.}
 
-\noindent\textbf{Motivation.}
+\paragraph*{Challenges to nuclear materials accounting.}
 
-\noindent\textbf{Research Focus.} The N workscopes in this project are - 
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\subsection*{Overall Objective}
+
+\subsection*{Research Focus} 
+\noindent Project workscopes are summarized. 
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
     \item\textit{Title (Lead - )}
@@
         \end{itemize}
-    \item\textit{Crosscutting Issues (Full team)}
+    \item\textit{}
         \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item Identify lessons learned
-            \item Develop future research pathways
+            \item 
+            \item 
+        \end{itemize}
+    \item\textit{}
+        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+            \item 
+            \item  
+        \end{itemize}
+    \item\textit{Conclusions - Crosscutting issues (Full team)}
+        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+            \item Identify lessons learned.
+            \item Develop future research pathways.
         \end{itemize}
@@
 
-\vspace{\baselineskip}
-
-\noindent\textbf{Team.} This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members.
+\subsection*{Team} This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members.
 The contribution of each is noted.
 The corresponding facilities are briefly described thereafter.
-\\
 
-\noindent\textbf{Prof./Dr.
-Name} (Ph.D., Degree Granting Institution) is a \textit{title} at \textit{Affiliation}, etc.
+\paragraph*{Prof./Dr. Firstname Lastname (Ph.D., University, Department).} 
+\noindent Prof/Dr.
+Lastname is a \textit{title} at \textit{Current affiliation}, etc.
 His/Her/Their research focus is in \textit{area of expertise}.
@@
 He/She/They has expertise in \textit{topics contained in text of narrative} from \textit{where/how this expertise was acquired}.
-He/She/They teach \textit{relevant courses} at \textit{Affiliation}.
-\\
+He/She/They teach \textit{relevant courses} at \textit{Current affiliation}.
 
-\noindent\textbf{Prof./Dr.
-Name} (Ph.D., Degree Granting Institution) is a \textit{title} at \textit{Affiliation}, etc.
+\paragraph*{Prof./Dr. Firstname Lastname (Ph.D., University, Department).} 
+\noindent Prof./Dr.
+Lastname is a \textit{title} at \textit{Affiliation}, etc.
 His/Her/Their research focus is in \textit{area of expertise}.
@@
 He/She/They teach \textit{relevant courses} at \textit{Affiliation}.
-\\
 
-\noindent\textbf{Important Research Facility/Equipment} is \textit{description as relevant to project.}
-\\
+\subsection*{Important Research Facility/Equipment}
+\noindent The Important Research Facility/Equipment is \textit{description as relevant to project.}
 
-\noindent\textbf{Work Project Documentation, Quality Control.} The co-PIs have practiced a QA approach, consistent with that established by the DOE Technical Integration Office, per NEUP website and any additional requirements deemed necessary during contracting.
+\subsection*{Work Project Documentation, Quality Control} 
+\noindent The PI has a practiced a QA approach, consistent with that established by the DOE Technical Integration Office, per NEUP website and any additional requirements deemed necessary during contracting.
 All projects undergo safety review by experts.
@@
 We abide by current and pending information on nuclear-related federal funding contained in Form 3204.
-The Mandatory, Go/No-go, requirements will be coordinated with UI’s Office of Sponsored Research, the general counsel and Technology Transfer.
-The PIs assume responsibility as the POC and follow these requirements: 1) Commitment to reporting and budget requirements, 2) 10CFR851 Worker Safety and Health Program, 3) Export Control and 4) Quality Assurance.
-\\
+The Mandatory, Go/No-go, requirements will be coordinated with The University of Idaho Office of Sponsored Research, the general counsel and Technology Transfer.
+The PI assumes responsibility as the POC and follow these requirements: 1) Commitment to reporting and budget requirements, 2) 10CFR851 Worker Safety and Health Program, 3) Export Control and 4) Quality Assurance.
 

### 2021-01-08 proposal-documents/doe/capabilities/doe-capabilities.tex
doe templates

--- 2021-01-08 proposal-documents/doe/benefit-of-collaboration/benefit-of-collaboration.tex
@@
 {\centering 
-    \textbf{BENEFIT OF COLLABORATORS\\
-    Advanced Data Integration for Materials Accounting of a Bulk Nuclear Materials Handling Facility\\
-    FC-3: Materials Protection, Accounting, and Control Technology\\
+    \textbf{CAPABILITIES\\
+    Title\\
+    Call/Technical Scope\\
     }
-    R. A. Borrelli (PI) - University of Idaho $\sq$ Idaho Falls Center for Higher Education 
+    Name (PI) - Affiliation\\
+    Name (co-PI) - Affiliation
 \par
@@
 
-\subsection*{Summary of the Proposed Project}
+\subsection*{University I Capabilities}
 
-\subsection*{Motivation} 
-\paragraph*{Context.}
+\paragraph*{Scientific computing environment capabilities.}
 
-\paragraph*{Challenges to nuclear materials accounting.}
+\paragraph*{Other equipment/facilities specifically used for the project capabilities.}
 
-\subsection*{Overall Objective}
+\subsection*{University II Capabilities}
 
-\subsection*{Research Focus} 
-\noindent Project workscopes are summarized. 
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item\textit{Title (Lead - )}
-        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item 
-            \item 
-        \end{itemize}
-    \item\textit{}
-        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item 
-            \item 
-        \end{itemize}
-    \item\textit{}
-        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item 
-            \item  
-        \end{itemize}
-    \item\textit{Conclusions - Crosscutting issues (Full team)}
-        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item Identify lessons learned.
-            \item Develop future research pathways.
-        \end{itemize}
-\end{enumerate}
+\paragraph*{Scientific computing environment capabilities.}
 
-\subsection*{Team} This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members.
-The contribution of each is noted.
-The corresponding facilities are briefly described thereafter.
-
-\paragraph*{Prof./Dr. Firstname Lastname (Ph.D., University, Department).} 
-\noindent Prof/Dr.
-Lastname is a \textit{title} at \textit{Current affiliation}, etc.
-His/Her/Their research focus is in \textit{area of expertise}.
-Prof./Dr.
-Name is the PI of this project and will be responsible for progress and achievement of all objectives, tasks, and deliverables.
-He/She/They has expertise in \textit{topics contained in text of narrative} from \textit{where/how this expertise was acquired}.
-He/She/They teach \textit{relevant courses} at \textit{Current affiliation}.
-
-\paragraph*{Prof./Dr. Firstname Lastname (Ph.D., University, Department).} 
-\noindent Prof./Dr.
-Lastname is a \textit{title} at \textit{Affiliation}, etc.
-His/Her/Their research focus is in \textit{area of expertise}.
-Prof./Dr.
-Name is the co-PI of this project and will contibute expertise in \textit{related project tasks}.
-He/She/They also is/was \textit{related experience} from \textit{where/how this expertise was acquired}.
-He/She/They teach \textit{relevant courses} at \textit{Affiliation}.
-
-\subsection*{Important Research Facility/Equipment}
-\noindent The Important Research Facility/Equipment is \textit{description as relevant to project.}
-
-\subsection*{Work Project Documentation, Quality Control} 
-\noindent The PI has a practiced a QA approach, consistent with that established by the DOE Technical Integration Office, per NEUP website and any additional requirements deemed necessary during contracting.
-All projects undergo safety review by experts.
-We have followed this QA expectation in all ongoing awards.
-We abide by current and pending information on nuclear-related federal funding contained in Form 3204.
-The Mandatory, Go/No-go, requirements will be coordinated with The University of Idaho Office of Sponsored Research, the general counsel and Technology Transfer.
-The PI assumes responsibility as the POC and follow these requirements: 1) Commitment to reporting and budget requirements, 2) 10CFR851 Worker Safety and Health Program, 3) Export Control and 4) Quality Assurance.
+\paragraph*{Other equipment/facilities specifically used for the project capabilities.}
 

### 2021-01-08 proposal-documents/doe/coordination-and-management-plan/doe-coordination-and-management-plan.tex
doe templates

--- 2021-01-08 proposal-documents/doe/capabilities/doe-capabilities.tex
@@
 {\centering 
-    \textbf{CAPABILITIES\\
+    \textbf{COORDINATION AND MANAGEMENT PLAN\\
     Title\\
@@
 
-\subsection*{University I Capabilities}
+\subsection*{Project Collaborators}
+\noindent The proposed project is a collaboration between Affiliation I and Affiliation II.
+Affiliation I is the lead institution and will coordinate the overall project.
+Further information regarding team member expertise and contributions are contained in the Benefits of Collaboration and Capabilities document.
 
-\paragraph*{Scientific computing environment capabilities.}
+\subsection*{PI Roles and Responsibilities}
+\noindent Affiliation I is the lead institution for the project.
+This project team consists of the Principal Investigator (PI), co-Principal Investigator (co-PI), and list others.
+The PI will oversee administrative duties and manage the project throughout the project duration.
+The PI and team all hold responsibility for implementing the proposed milestones and deliverables as defined by the schedule in the Technical Narrative.
+The research proposed in this project will be conducted by graduate students under the guidance, direction, and mentorship of the PI and co-PIs.
+Periodic meetings will be held to maintain satisfactory progress on this project.
+The PI and team will also serve on thesis committees for the graduate students.
 
-\paragraph*{Other equipment/facilities specifically used for the project capabilities.}
+\subsection*{Communication Plans}
+\noindent A kickoff conference will be held within the first quarter of the project period.
+A central, online repository will be created and maintained by Affiliation I.
+This will be the hub for communication and exchange of relevant documents.
+Regular project meetings will be held monthly for team members for performance updates and related project issues to address as they arise.
+A full project review will be conducted annually and include a written summary of progress.
+Reporting to the United States Department of Energy will include quarterly reports, annual report, and technical deliverables defined in the Technical Narrative.
 
-\subsection*{University II Capabilities}
+\subsection*{Process and Procedures for Making Decisions and Resolving Conflicts}
+\noindent Decision-making is based on the contract signed by Affiliation I and the United States Department of Energy.
+While major changes in the research direction are rare, this will first be coordinated with the sponsor if necessary, with a subsequent meeting for the team members to hold discussions and arrive at a consensus.
+If necessary, a majority vote amongst the PI and team will be held.
+PI and team all hold an equal vote, regardless of the funding distribution.
+Based on this, the PI will contact the Federal and Technical Point-of-Contact to inform them of the decision.
+The PI will inform the Federal and Technical Point-of-Contact regarding research progress, new challenges, and relevant solutions.
 
-\paragraph*{Scientific computing environment capabilities.}
+\subsection*{Publications}
+\noindent Quarterly and annual reporting requirements will be prepared by the PI with supporting contributions from the team based on individual research Tasks presented in the Technical Narrative.
+Peer-reviewed journal publications and conference presentations will be prepared at the discretion of the PI and team but discussed collectively at the regular project meetings.
 
-\paragraph*{Other equipment/facilities specifically used for the project capabilities.}
+\subsection*{Intellectual Property}
+\noindent Project members are employees of Affiliation I, Affiliation II, and others. Intellectual property rights are retained by each employee and employer, per individual employment contract.
 

### 2021-01-08 proposal-documents/doe/narrative/doe-proposal-narrative.tex
doe templates

\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough
\usepackage{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{times}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{tabulary}
\usepackage{gensymb}
\usepackage{longtable}
%\usepackage[labelfont=bf]{caption}

\usepackage[singlelinecheck=false]{caption}
\captionsetup[table]{skip=0pt} %sets a space after table caption
\captionsetup[figure]{skip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format

\usepackage{wrapfig}
\setlength{\intextsep}{0.20mm}
\setlength{\columnsep}{0.20mm}

\usepackage[numbers,sort&compress]{natbib} 
%'numbers' - numbered citations
%'round' - (1) instead [1]
%'sort&compress - [1-3] instead [1,2,3]
\setlength{\bibsep}{0pt} %sets space between references
\renewcommand{\bibsection}{} %suppresses large 'references' heading
\renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column

\makeatletter
\renewcommand\paragraph{%
    \@startsection{paragraph}{4}{\z@ }{0.35\baselineskip}{-1em}
    {\normalfont \normalsize \bfseries}}%

\makeatletter
\renewcommand\subparagraph{%
    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
    {\normalfont \normalsize \itshape }}%

\makeatletter
\renewcommand\subsection{%
    \@startsection{subsection}{2}{\z@ }{0.50\baselineskip}{0.10\baselineskip}
    { \normalfont \bfseries}}%

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
\renewcommand{\headrulewidth}{0pt} %set line thickness in header
%\lhead{\scriptsize Name}
%\chead{\scriptsize Title, subject, agency, etc.}
%\rhead{\scriptsize \today}
\rfoot{\thepage}

%cite in order of appearance if using neup.bst
\begin{filecontents}{references.bib} 
\end{filecontents}

\begin{document}

{\centering 
    \textbf{Title\\
    Call/Technical Scope\\
    }
    Name (PI) - Affiliation\\
    Name (co-PI) - Affiliation
\par
}

\subsection*{Summary of the Proposed Project}

%\begin{wrapfigure}{l}{0.42\textwidth}
%    \includegraphics[width=0.40\textwidth]{flowsheet.jpg}
%    \captionsetup{justification=centering,belowskip=-0.7mm}
%    \caption{Pyroprocessing flowsheet.}
%    \label{fig-flowsheet}
%\end{wrapfigure}

\subsection*{Motivation} 
\paragraph*{Context.}

\paragraph*{Something else.}

\subsection*{Overall Objective}

\subsection*{Research Focus} 
\noindent Project workscopes are summarized. 
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\textit{Title (Lead - )}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item 
        \end{itemize}
    \item\textit{}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item 
        \end{itemize}
    \item\textit{}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item  
        \end{itemize}
    \item\textit{Conclusions - Crosscutting issues (Full team)}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item Identify lessons learned.
            \item Develop future research pathways.
        \end{itemize}
\end{enumerate}

\subsection*{Importance and Relevance to Objectives}  
\paragraph*{Background.} 
\subparagraph*{}

\subparagraph*{}

\subparagraph*{}

\paragraph*{}

\paragraph*{}

\subparagraph*{}

\subparagraph*{}

\paragraph*{Unique project features.}

\subsection*{Logical Path, Workscope, Description of Tasks} 
\paragraph*{Workscope 1 - Title.} 
\subparagraph*{Task I. Title.}

\subparagraph*{Task II. Title.}

\subparagraph*{Task III. Title.}

\subparagraph*{Task IV. Title.}

\paragraph*{Workscope 2 - Title.} 
\subparagraph*{Task V. Title.}

\paragraph*{Workscope 6. Conclusions.}
\subparagraph*{Task N. Crosscutting Issues.} 
\noindent Lessons learned will be identified for project outcomes. Selected additional discussion will cover, but not limited to, the following -
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item 
    \item  
    \item 
\end{enumerate}

\paragraph*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
\noindent The following outcomes are anticipated -
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item 
    \item
    \item
\end{enumerate}

%\noindent\textbf{Estimated Cost of the Project.} The maximum amount of \$400,000 is requested for the 2 year time period at \$200,000 per year.
%

\begin{longtable}{|L{0.27\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
    \label{tab-timeframe}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}
        \\
        \cline{2-13}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}
        \\
        \hline
        I. 
        &\x\textbf{I} 
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        \\
        \hline
        II. 
        &\x\textbf{II} 
        &\x\textbf{II} 
        &
        &
        &
        &
        &
        &
        &
        & 
        & 
        & 
        \\
        \hline
        III. 
        &\x\textbf{III} 
        &
        &
        &
        &
        &
        &
        &
        &
        &
        & 
        & 
        \\
        \hline
        IV. 
        & 
        &\x\textbf{IV} 
        & 
        &
        &
        &
        &
        &
        &
        &
        &
        & 
        \\
        \hline
        V. 
        & 
        &\x\textbf{V} 
        &\x\textbf{V} 
        &\x\textbf{V}
        &
        &
        &
        &
        &
        &
        &
        &
        \\
        \hline
        VI. 
        & 
        & 
        & 
        &\x\textbf{VI}
        & 
        &
        &
        &
        &
        & 
        &
        &
        \\
        \hline
        VII. 
        & 
        & 
        & 
        &\x\textbf{VII}
        & 
        &
        &
        &
        &
        & 
        &
        &
        \\
        \hline
        VIII. 
        & 
        & 
        & 
        & 
        &\x\textbf{VIII} 
        & 
        &
        &
        &
        &
        &
        &
        \\
        \hline
        IX. 
        & 
        & 
        & 
        &\x\textbf{IX} 
        &\x\textbf{IX} 
        & 
        &
        &
        &
        &
        &
        &
        \\
        \hline
        X. 
        & 
        & 
        &
        &
        &
        &
        & 
        & 
        &\x\textbf{X} 
        &\x\textbf{X} 
        &\x\textbf{X}
        &\x\textbf{X}
        \\
        \hline
        XI. Crosscutting issues 
        & 
        & 
        &
        &
        &
        &
        & 
        & 
        & 
        &
        &\x\textbf{VII}
        &\x\textbf{VII} 
        \\
        \hline
\end{longtable}

\vspace{-\baselineskip}

\begin{longtable}{|l|l|l|}
    \caption*{\textbf{Milestones.}}
    \label{tab-milestones}\\
        \hline
        \multicolumn{1}{|c|}{\textbf{Milestone}}
        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        0. Project\\logistics
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        0.1. Kick-off report, roles, and responsibilities.\\
        0.2. Annual reports.\\
        0.3. Agency administrative requirements.\\
        0.4. Final project report.\\
        0.5. Journal paper submission.\\
        0.6. Professional society conference presentations.
        \end{tabular}
        & 
        \begin{tabular}[c]{@{}l@{}}
        0.1. Y1-Q2\\
        0.2. Annually\\
        0.3. Quarterly\\
        0.4. Y2-Q4\\
        0.5. Annually\\
        0.6. Annually
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        1. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        1.1.  \\
        1.2. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        1.1.  \\
        1.2.  
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        2. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        2.1. \\
        2.2. \\
        2.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        2.1. \\
        2.2. \\
        2.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        3.1. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        3.1. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        4. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        4.1. \\
        4.2. \\
        4.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        4.1. \\
        4.2. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        5. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        5.1. \\
        5.2. \\
        5.3. \\
        5.4. \\
        5.5. 
        \end{tabular}
        & 
        \begin{tabular}[c]{@{}l@{}}
        5.1. \\
        5.2. \\
        5.3. \\
        5.4. \\
        5.5. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        6. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        6.1. \\
        6.2.  
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        6.1. \\
        6.2. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        7. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        7.1. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        7.1. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        8. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        8.1. \\
        8.2. \\
        8.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        8.1. \\
        8.2. \\
        8.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        9. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        9.1. \\
        9.2. \\
        9.3. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        9.1. \\
        9.2. \\
        9.3. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        10. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        10.1. \\
        10.2. \\
        10.3. \\
        10.4. \\
        10.5. \\
        10.6. 
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        10.1. \\
        10.2. \\
        10.3. \\
        10.4. \\
        10.5. \\
        10.6. 
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
        11. Discuss\\crosscutting\\issues
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        11.1. Identify lessons learned.\\
        11.2. Develop future research and educational pathways.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
        11.1. Y3-Q3\\
        11.2. Y3-Q4
        \end{tabular}
        \\
        \hline
\end{longtable}

\paragraph*{Contribution to advancing state of the art in a, b, and c.}
\noindent This research plan and deliverables will advance the state-of-the-art in a, b, and, c as it is expected to - (1), (2), (3), and (4).

\paragraph*{Description of facilities to be utilized to execute scope.}

\paragraph*{Challenges to accomplish tasks and planned mitigations.} 
\noindent The PI is based at a United States Research University. The co-PIs are based at \textit{Affiliations}. This proposed project supports the goals and research interests of the institutions in the field of \textit{major fields}.

\vspace{-\baselineskip}

\begin{longtable}{|L{0.45\linewidth}|L{0.45\linewidth}|}
    \caption*{}
    \label{tab-risk}\\
        \hline
        \multicolumn{1}{|c|}{\textbf{Challenges to accomplish tasks}}
        &\multicolumn{1}{|c|}{\textbf{Planned mitigations}}\\
        \hline

        & 
        \\
        \hline

        &  
        \\
        \hline

        &  
        \\
        \hline

        & 
        \\
        \hline
\end{longtable}

\paragraph*{Information, data, and plans.} 
\noindent All information has been presented in the technical scope.

\paragraph*{Quality assurance.} 
\noindent Our project team have practiced a QA approach, consistent with the graded approach established by the DOE Technical Integration Office, per the NEUP website and any additional requirements deemed necessary during contracting. All projects undergo safety review by experts. We have followed this QA expectation in all ongoing awards.

\paragraph*{Mandatory requirements.} 
\noindent We abide by current and pending information on nuclear-related federal funding contained in Form 3204. The Mandatory, Go/No-go, requirements will be coordinated with the institutional Office of Sponsored Research, the general counsel, and the Office of Technology Transfer. Each PI noted below will assume responsibility as the point of contact.

\vspace{-\baselineskip}

\begin{longtable}{|c|c|c|c|}
    \caption*{}
    \label{tab-mandatory-requirements}\\
        \hline
        \textbf{No.}
        &\textbf{Requirement}
        &\textbf{Responsibility}
        &\textbf{Evaluation}\\
        \hline
        1
        &Commitment to reporting and budget requirements
        &All PIs
        &Go/No-go 
        \\
        \hline
        2
        &10 CFR 851 Worker Safety and Health Program
        &All PIs
        &Go/No-go 
        \\
        \hline
        3
        &Export Control
        &All PIs
        &Go/No-go 
        \\
        \hline
        4
        &Standard Research Subcontract
        &All PIs
        &Go/No-go 
        \\
        \hline
        5
        &Quality Assurance
        &All PIs
        &Go/No-go 
        \\
        \hline
        6
        &Commitment to prepare additional contract elements
        &All PIs
        &Go/No-go 
        \\
        \hline
\end{longtable}

\vspace{-0.50\baselineskip}

\noindent\textbf{References}
\bibliographystyle{neup}
\setlength{\bibhang}{0pt}
\bibliography{references}

\end{document}

### 2021-03-18 proposal-documents/doe/narrative/doe-proposal-narrative.tex
added content to narratives for formattingg

@@
+%@TheDoctorRAB
+%Standard white paper/preproposal format when there is a page limit
+%neup.bst designed to use numbered citations in order of appearance, short author list
+%nsf.st is for numbers, full author list
+%standard.bst is inline citations with author last name
 \documentclass[11pt,letterpaper]{article}
@@
 \usepackage{setspace}
-\usepackage{ulem} %strikethrough
+\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
 \usepackage{xcolor,colortbl} %change font color
@@
 \usepackage{tablefootnote}
-\usepackage{subfig}
-\usepackage[yyyymmdd]{datetime}
+\usepackage{footnotehyper}
+%\usepackage{subfig}
+\usepackage[yyyymmdd]{datetime} %date format
 \renewcommand{\dateseparator}{.}
-\graphicspath{{../img/}}
+\graphicspath{{../img/}} %path to graphics
 \setcounter{secnumdepth}{5} %set subsection to nth level
 \usepackage{times}
+\usepackage{tabto} %general tabbed spacing
+\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
+%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
+\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst, neup.bst
 \usepackage{enumitem}
-\usepackage{float}
+\usepackage{boldline}
+\usepackage{makecell}
+\usepackage{booktabs}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{physics}
+\usepackage{tabularx}
 \usepackage{multirow}
-\usepackage{tabularx}
-\usepackage{tabulary}
-\usepackage{gensymb}
-\usepackage{longtable}
-%\usepackage[labelfont=bf]{caption}
+\usepackage{lscape}
+\usepackage{array}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage[labelfont=bf]{caption}
+\usepackage{chngcntr}
+%\usepackage{hyperref}
+\usepackage{sectsty}
+\usepackage{pdfpages}
+\usepackage{textcomp}
+\usepackage{lastpage}
+\usepackage[toc,title]{appendix}
+\usepackage[figure,table]{totalcount}
+\usepackage[acronym,nomain,nonumberlist]{glossaries}
+\makenoidxglossaries
 
 \usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=0pt} %sets a space after table caption
-\captionsetup[figure]{skip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+\captionsetup[table]{skip=7pt} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
 
@@
 
-\usepackage[numbers,sort&compress]{natbib} 
-%'numbers' - numbered citations
-%'round' - (1) instead [1]
-%'sort&compress - [1-3] instead [1,2,3]
-\setlength{\bibsep}{0pt} %sets space between references
-\renewcommand{\bibsection}{} %suppresses large 'references' heading
-\renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading
+%\usepackage{xr} %for revisions - will cross reference from one file to here
+%\externaldocument{/path/to/auxfilename} %aux file needed
 
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
-\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
 \newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
 \newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
+\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
 \newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\acf}{\acrfull} %full acronym
+\newcommand{\acl}{\acrlong} %long acronym
+\newcommand{\acs}{\acrshort} %short acronym
 
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+
+\makeatletter
+\renewcommand\tableofcontents{%
+    \@starttoc{toc}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoffigures{%
+    \@starttoc{lof}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoftables{%
+    \@starttoc{lot}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\section{%
+    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
+    {\normalfont \normalsize \bfseries}}%
 
@@
 \renewcommand\subparagraph{%
-    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
+    \@startsection{subparagraph}{5}{\z@ }{0.25\baselineskip}{-1em}
     {\normalfont \normalsize \itshape }}%
@@
 \renewcommand\subsection{%
-    \@startsection{subsection}{2}{\z@ }{0.50\baselineskip}{0.10\baselineskip}
-    { \normalfont \bfseries}}%
+    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
+    { \large \normalsize \bfseries}}%
+
+%\sectionfont{\normalsize}
+%\subparagraphfont{\normalfont\itshape}
+
+\setlength{\bibsep}{0pt} %sets space between references
+\renewcommand{\bibsection}{} %suppresses large 'references' heading
+\renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading
 
@@
 \fancyhf{} %move page number to bottom right
-\renewcommand{\headrulewidth}{0pt} %set line thickness in header
-%\lhead{\scriptsize Name}
-%\chead{\scriptsize Title, subject, agency, etc.}
+\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+%\lhead{\scriptsize agency}
+%\chead{\scriptsize title}
 %\rhead{\scriptsize \today}
@@
 
-%cite in order of appearance if using neup.bst
 \begin{filecontents}{references.bib} 
 \end{filecontents}
+
+%\newacronym{}{}{}
+
+%spacing options
+%\onehalfspacing %linespacing
+%\setstretch{1.05} %linespacing
+%\spacing{1.25} %equivalent to 1.5 line spacing in Word
 

### 2021-06-23 manuscript/document-package/draft-manuscript/draft-manuscript.tex

%@TheDoctorRAB
%Use for original, revised, clean manuscripts
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level

%fonts
\usepackage{times}
%arial - uncomment next two lines
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}

\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
%\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
\usepackage{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}
%\usepackage{hyperref}
\usepackage{sectsty}
\usepackage{textcomp}
\usepackage{lastpage}
\usepackage{xargs} %for \newcommandx
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
\usepackage[toc,page]{appendix}
\usepackage[figure,table]{totalcount}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries

\usepackage[singlelinecheck=false]{caption}
\captionsetup[table]{skip=7pt,labelsep=period} %sets a space after table caption
\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format

\usepackage{wrapfig}
\setlength{\intextsep}{0.20mm}
\setlength{\columnsep}{0.20mm}

%\usepackage{xr} %for revisions - will cross reference from one file to here
%\externaldocument{/path/to/auxfilename} %aux file needed

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
\newcommand{\acf}{\acrfull} %full acronym
\newcommand{\acl}{\acrlong} %long acronym
\newcommand{\acs}{\acrshort} %short acronym

\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column

\makeatletter
\renewcommand\tableofcontents{%
    \@starttoc{toc}%
}
\makeatother

\makeatletter
\renewcommand\listoffigures{%
    \@starttoc{lof}%
}
\makeatother

\makeatletter
\renewcommand\listoftables{%
    \@starttoc{lot}%
}
\makeatother

\makeatletter
\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
\makeatother

%\makeatletter
%\renewcommand\section{%
%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
%    {\normalfont \normalsize \bfseries}}%

%\makeatletter
%\renewcommand\paragraph{%
%    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
%    {\normalfont \normalsize \bfseries}}%

%\makeatletter
%\renewcommand\subparagraph{%
%    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
%    {\normalfont \normalsize \itshape }}%

%\makeatletter
%\renewcommand\subsection{%
%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
%    { \large \normalsize \bfseries}}%

%\setlength{\bibsep}{0pt} %sets space between references
%\renewcommand{\bibsection}{} %suppresses large 'references' heading
%\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize }
\chead{\scriptsize \textit{ - Draft Manuscript}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

\begin{filecontents}{references.bib} 
\end{filecontents}

%\newacronym{}{}{}

\begin{document}

\begin{titlepage}
    \title{}
    \author{
        , 
        , 
        \textsuperscript{*}
        \\ \\ \\
        \\

        \\ \\ \\
        \textsuperscript{*}
    }
\clearpage %not have page number on title page
\maketitle
\vspace*{\fill}
\begin{flushright}{
        \noindent Number of pages - \pageref{LastPage} \\
        \noindent Number of tables - \totaltables \\
        \noindent Number of figures - \totalfigures 
}
\end{flushright}
\thispagestyle{empty} %start with page number 1 on second page
\end{titlepage}

\onehalfspacing %linespacing
\linenumbers %toggle line numbers
\pagewiselinenumbers %reset line numbers on new page
\modulolinenumbers[3] %line numbering interval

\section*{Abstract}

\newpage

\printnoidxglossary

\newpage

\section{Introduction} \label{sec-intro}

\subsection{Motivation} \label{sec-motiv}

\subsection{Goals} \label{sec-goals}

\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
    \item 
    \item  
    \item 
\end{enumerate}

\newpage

\section{Background} \label{sec-bak}

\newpage

\section{Theory} \label{sec-theo}

\newpage

\section{Methodology} \label{sec-meth}

\newpage

\section{Results} \label{sec-res}
\subsection{Objective} \label{sec-obj}

\newpage

\section{Discussion} \label{sec-disc}

\newpage

\section{Future work} \label{sec-fwk}

\newpage

\section{Summary remarks} \label{sec-sum}

Major results and implications include - 
\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{itemize}

\newpage

\section*{Acknowledgements}

\newpage

\bibliographystyle{standard}
\setlength{\bibhang}{0pt}
\bibliography{references}

\newpage

\section*{Tables}

{%
\let\oldnumberline\numberline%
\renewcommand{\numberline}{\tablename~\oldnumberline}%
\listoftables%
}

\newpage

%\begin{table}[h!]
%    \centering
%    \caption{Title}
%        \begin{tabular}{|c|c|c|c|}
%            \hline
%            A&
%            B&
%            C&
%            D
%            \\
%            \hline
%            X
%            &X
%            &X
%            &X
%            \\
%            \hline
%        \end{tabular}
%    \label{tab-label}
%\end{table}

\newpage

%\begin{spacing}{1}
%\begin{longtable}{|c|c|c|c|c|}
%    \caption{Title}
%    \label{tab-label-name} \\
%    \hline
%    \multicolumn{1}{|c|}{A}&
%    \multicolumn{1}{c|}{B}&
%    \multicolumn{1}{c|}{C}&
%    \multicolumn{1}{c|}{D}&
%    \multicolumn{1}{c|}{E}
%    \\
%    \hline
%    \endfirsthead
%    \multicolumn{5}{c}{{\tablename\ \thetable{} - continued}} \\
%    \hline
%    \multicolumn{1}{|c|}{A}&
%    \multicolumn{1}{c|}{B}&
%    \multicolumn{1}{c|}{C}&
%    \multicolumn{1}{c|}{D}&
%    \multicolumn{1}{c|}{E}
%    \\
%    \hline
%    \endhead
%    \hline
%    \endfoot
%    \hline
%    \endlastfoot
%    X
%    &X
%    &X
%    &X
%    &X
%    \\
%    \hline
%\end{longtable}
%\end{spacing}

\newpage

\section*{Figures}

{%
\let\oldnumberline\numberline%
\renewcommand{\numberline}{\figurename~\oldnumberline}%
\listoffigures%
}

\newpage

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.X\textwidth]{.png}
%    \caption{}
%    \label{fig-label-name}
%\end{figure}

\newpage

%\appendix

%\begin{appendices}

%\renewcommand{\thesection}{\Roman{section}}

%\section{} \label{}

%\end{appendices}

\end{document}

### 2021-06-23 manuscript/document-package/references/references.tex

--- 2021-06-23 manuscript/document-package/draft-manuscript/draft-manuscript.tex
@@
 \usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=7pt,labelsep=period} %sets a space after table caption
+\captionsetup[table]{skip=7pti,labelsep=period} %sets a space after table caption
 \captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
@@
 
-\makeatletter
-\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
-\makeatother
-
 %\makeatletter
@@
 \lhead{\scriptsize }
-\chead{\scriptsize \textit{ - Draft Manuscript}}
+\chead{\scriptsize \textit{- Draft Manuscript}}
 \rhead{\scriptsize \today}
 \rfoot{\thepage}
-
-\begin{filecontents}{references.bib} 
-\end{filecontents}
-
-%\newacronym{}{}{}
 
@@
 \begin{titlepage}
-    \title{}
+    \title{Applying Analytic Hierarchy Process to Industrial Process Design in a Nuclear Renewable Hybrid Energy System}
     \author{
@@
 \maketitle
-\vspace*{\fill}
-\begin{flushright}{
-        \noindent Number of pages - \pageref{LastPage} \\
-        \noindent Number of tables - \totaltables \\
-        \noindent Number of figures - \totalfigures 
-}
-\end{flushright}
+
 \thispagestyle{empty} %start with page number 1 on second page
@@
 
-\section*{Abstract}
-
-\newpage
-
-\printnoidxglossary
-
-\newpage
-
-\section{Introduction} \label{sec-intro}
-
-\subsection{Motivation} \label{sec-motiv}
-
-\subsection{Goals} \label{sec-goals}
-
-\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
-    \item 
-    \item  
-    \item 
-\end{enumerate}
-
-\newpage
-
-\section{Background} \label{sec-bak}
-
-\newpage
-
-\section{Theory} \label{sec-theo}
-
-\newpage
-
-\section{Methodology} \label{sec-meth}
-
-\newpage
-
-\section{Results} \label{sec-res}
-\subsection{Objective} \label{sec-obj}
-
-\newpage
-
-\section{Discussion} \label{sec-disc}
-
-\newpage
-
-\section{Future work} \label{sec-fwk}
-
-\newpage
-
-\section{Summary remarks} \label{sec-sum}
-
-Major results and implications include - 
-\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
-    \item
-    \item
-    \item
-\end{itemize}
-
-\newpage
-
-\section*{Acknowledgements}
-
-\newpage
+\nocite{*}
 
@@
 
-\newpage
-
-\section*{Tables}
-
-{%
-\let\oldnumberline\numberline%
-\renewcommand{\numberline}{\tablename~\oldnumberline}%
-\listoftables%
-}
-
-\newpage
-
-%\begin{table}[h!]
-%    \centering
-%    \caption{Title}
-%        \begin{tabular}{|c|c|c|c|}
-%            \hline
-%            A&
-%            B&
-%            C&
-%            D
-%            \\
-%            \hline
-%            X
-%            &X
-%            &X
-%            &X
-%            \\
-%            \hline
-%        \end{tabular}
-%    \label{tab-label}
-%\end{table}
-
-\newpage
-
-%\begin{spacing}{1}
-%\begin{longtable}{|c|c|c|c|c|}
-%    \caption{Title}
-%    \label{tab-label-name} \\
-%    \hline
-%    \multicolumn{1}{|c|}{A}&
-%    \multicolumn{1}{c|}{B}&
-%    \multicolumn{1}{c|}{C}&
-%    \multicolumn{1}{c|}{D}&
-%    \multicolumn{1}{c|}{E}
-%    \\
-%    \hline
-%    \endfirsthead
-%    \multicolumn{5}{c}{{\tablename\ \thetable{} - continued}} \\
-%    \hline
-%    \multicolumn{1}{|c|}{A}&
-%    \multicolumn{1}{c|}{B}&
-%    \multicolumn{1}{c|}{C}&
-%    \multicolumn{1}{c|}{D}&
-%    \multicolumn{1}{c|}{E}
-%    \\
-%    \hline
-%    \endhead
-%    \hline
-%    \endfoot
-%    \hline
-%    \endlastfoot
-%    X
-%    &X
-%    &X
-%    &X
-%    &X
-%    \\
-%    \hline
-%\end{longtable}
-%\end{spacing}
-
-\newpage
-
-\section*{Figures}
-
-{%
-\let\oldnumberline\numberline%
-\renewcommand{\numberline}{\figurename~\oldnumberline}%
-\listoffigures%
-}
-
-\newpage
-
-%\begin{figure}[h!]
-%    \centering
-%    \includegraphics[width=0.X\textwidth]{.png}
-%    \caption{}
-%    \label{fig-label-name}
-%\end{figure}
-
-\newpage
-
-%\appendix
-
-%\begin{appendices}
-
-%\renewcommand{\thesection}{\Roman{section}}
-
-%\section{} \label{}
-
-%\end{appendices}
-
 \end{document}

### 2021-07-06 proposal-documents/white-paper/white-paper-general-preproposal.tex
white paper update and phd white paper aded

--- 2021-03-18 proposal-documents/doe/narrative/doe-proposal-narrative.tex
@@
 %@TheDoctorRAB
-%Standard white paper/preproposal format when there is a page limit
-%neup.bst designed to use numbered citations in order of appearance, short author list
-%nsf.st is for numbers, full author list
-%standard.bst is inline citations with author last name
+%standard white paper/preproposal format
+%
+%%%%%
+%
+%REFERENCES
+%
+%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
+%nsf.bst - numbered citations in order of appearance, full author list in references section
+%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
+%ans.bst is for ANS only. 
+%
+%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
+%bst renders the author list itself
+%
+%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
+%
+%title = {{}} for all
+%
+%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
+%standard.bst \cite{-} - Borrelli (2021) in the text
+%standard.bst lists references alphabetically
+%the rest list numerically
+%
+%%%%%
 \documentclass[11pt,letterpaper]{article}
@@
 \usepackage{ulem} %strikethrough - do not \sout{\cite{}}
-\usepackage{xcolor,colortbl} %change font color
+\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
 \usepackage{graphicx}
@@
 \setcounter{secnumdepth}{5} %set subsection to nth level
+
+%fonts
 \usepackage{times}
+%arial - uncomment next two lines
+%\usepackage{helvet}
+%\renewcommand{\familydefault}{\sfdefault}
+
 \usepackage{tabto} %general tabbed spacing
@@
 %\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
-\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst, neup.bst
+\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
 \usepackage{enumitem}
@@
 \usepackage{sectsty}
-\usepackage{pdfpages}
 \usepackage{textcomp}
 \usepackage{lastpage}
-\usepackage[toc,title]{appendix}
+\usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
+\usepackage[toc,page]{appendix}
 \usepackage[figure,table]{totalcount}
@@
 \usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=7pt} %sets a space after table caption
+\captionsetup[table]{skip=7pt,labelsep=period} %sets a space after table caption
 \captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
@@
 \newcommand{\acs}{\acrshort} %short acronym
+
+\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
+\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
+\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
+\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 
@@
 \makeatletter
+\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
+\makeatother
+
+\makeatletter
 \renewcommand\section{%
@@
 \renewcommand\paragraph{%
-    \@startsection{paragraph}{4}{\z@ }{0.35\baselineskip}{-1em}
+    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
     {\normalfont \normalsize \bfseries}}%
@@
 \renewcommand\subparagraph{%
-    \@startsection{subparagraph}{5}{\z@ }{0.25\baselineskip}{-1em}
+    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
     {\normalfont \normalsize \itshape }}%
@@
 
-%\sectionfont{\normalsize}
-%\subparagraphfont{\normalfont\itshape}
-
 \setlength{\bibsep}{0pt} %sets space between references
 \renewcommand{\bibsection}{} %suppresses large 'references' heading
-\renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading
+\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
 
@@
 \fancyhf{} %move page number to bottom right
-\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-%\lhead{\scriptsize agency}
-%\chead{\scriptsize title}
-%\rhead{\scriptsize \today}
+%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+\lhead{\scriptsize Agency}
+\chead{\scriptsize \textit{Title}}
+\rhead{\scriptsize \today}
 \rfoot{\thepage}
@@
 \begin{filecontents}{references.bib} 
+    @misc{
+        nye15a,
+        author = {Nye, Jr., Joseph S.},
+        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
+        year = {2015},
+        note = {{The Washington Post}}
+    }
+    @article{
+        mil20a,
+        author = {Miller, James N.},
+        title = {No to no first use — for now},
+        journal = {Bulletin of the Atomic Scientists},
+        volume = {76},
+        pages = {8},
+        year  = {2020}
+    }
+    @incollection{
+        mil17a,
+        author = {Miller, Steven E.},
+        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
+        booktitle = {Understanding Cyber Conflict: 14 Analogies},
+        publisher = {Georgetown University Press},
+        year = {2017},
+        editor = {Perkovich, George and Levite, Ariel E.},
+        pages = {161}
+    }
+    @conference{
+        ben20a,
+        author = {Benjamin, Jacob and Haney, Michael},
+        title = {{Nonproliferation of Cyber Weapons}},
+        year = { 2020},
+        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
+        address = {Las Vegas, Nevada}
+    }
 \end{filecontents}
 
+%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
 %\newacronym{}{}{}
@@
 
+%linenumbering
+%\linenumbers %toggle line numbers
+%\pagewiselinenumbers %reset line numbers on new page
+%\modulolinenumbers[3] %line numbering interval
+
 \begin{document}
@@
     \textbf{Title\\
-    Call/Technical Scope\\
+    Call\\
     }
-    Name (PI) - Affiliation\\
+    Name (PI) - Affiliation; Name (co-PI) - Affiliation\\
     Name (co-PI) - Affiliation
@@
 
-\subsection*{Summary of the Proposed Project}
+\noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}} %horizontal line spanning margins
 
-%\begin{wrapfigure}{l}{0.42\textwidth}
-%    \includegraphics[width=0.40\textwidth]{flowsheet.jpg}
-%    \captionsetup{justification=centering,belowskip=-0.7mm}
-%    \caption{Pyroprocessing flowsheet.}
-%    \label{fig-flowsheet}
-%\end{wrapfigure}
+\section*{Abstract}
+%may not be needed
 
-\subsection*{Motivation} 
-\paragraph*{Context.}
+\paragraph*{Summary of the Proposed Project.}
 
-\paragraph*{Something else.}
+\paragraph*{Motivation.}
 
-\subsection*{Overall Objective}
+\paragraph*{Overall Objective.}
 
-\subsection*{Research Focus} 
-\noindent Project workscopes are summarized. 
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item\textit{Title (Lead - )}
-        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item 
-            \item 
-        \end{itemize}
-    \item\textit{}
-        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item 
-            \item 
-        \end{itemize}
-    \item\textit{}
-        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item 
-            \item  
-        \end{itemize}
-    \item\textit{Conclusions - Crosscutting issues (Full team)}
-        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item Identify lessons learned.
-            \item Develop future research pathways.
-        \end{itemize}
-\end{enumerate}
+\paragraph*{Importance and Relevance to Objectives.} 
+\subparagraph*{Background.}
 
-\subsection*{Importance and Relevance to Objectives}  
-\paragraph*{Background.} 
-\subparagraph*{}
+\subparagraph*{Relevant literature.}
 
-\subparagraph*{}
+%for a 3 page preproposal, limit above subject matter to the first page
 
-\subparagraph*{}
+\paragraph*{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project.
 
-\paragraph*{}
-
-\paragraph*{}
-
-\subparagraph*{}
-
-\subparagraph*{}
-
-\paragraph*{Unique project features.}
-
-\subsection*{Logical Path, Workscope, Description of Tasks} 
-\paragraph*{Workscope 1 - Title.} 
+\paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
 \subparagraph*{Task I. Title.}
@@
 
+\paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
 \subparagraph*{Task III. Title.}
@@
 
-\paragraph*{Workscope 2 - Title.} 
-\subparagraph*{Task V. Title.}
+\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
+\subparagraph*{Task VII. Crosscutting issues.}
 
-\paragraph*{Workscope 6. Conclusions.}
-\subparagraph*{Task N. Crosscutting Issues.} 
-\noindent Lessons learned will be identified for project outcomes. Selected additional discussion will cover, but not limited to, the following -
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\paragraph*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
+We anticipate the following outcomes - 
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
     \item
@@
     \item
+    \item Identify lessons learned and engage in future pathways and partnerships.
 \end{enumerate}
 
-\paragraph*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
-\noindent The following outcomes are anticipated -
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item
-    \item
-    \item 
-    \item
-    \item
-\end{enumerate}
+\paragraph*{Estimated Cost of the Project.} 
+We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
 
-%\noindent\textbf{Estimated Cost of the Project.} The maximum amount of \$400,000 is requested for the 2 year time period at \$200,000 per year.
-%
+%limiting tasks, deliverables to one page allows for more references to be included on the third page, for a 3 page limit
 
-\begin{longtable}{|L{0.27\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
+%\begin{table}[h!]
+%    \centering
+%    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
+%    \begin{tabular}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
+\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
+        \captionsetup{margin=-9pt}
         \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
-    \label{tab-timeframe}\\
+        \label{tab-timeline}\\
         \hline
@@
         I. 
-        &\x\textbf{I} 
+        &\x\textbf{X}
         & 
@@
         II. 
-        &\x\textbf{II} 
-        &\x\textbf{II} 
+        &\x\textbf{X} 
+        & 
         & 
@@
         III. 
-        &\x\textbf{III} 
+        &\x\textbf{X} 
         & 
@@
         IV. 
+        &\x\textbf{X}
         & 
-        &\x\textbf{IV} 
         & 
@@
         V. 
+        &\x\textbf{X} 
         & 
-        &\x\textbf{V} 
-        &\x\textbf{V} 
-        &\x\textbf{V}
+        & 
+        & 
         & 
@@
         VI. 
+        &\x\textbf{X} 
         & 
@@
         & 
-        &\x\textbf{VI}
         & 
@@
         \hline
-        VII. 
+        VII. Crosscutting issues
         & 
         & 
-        & 
-        &\x\textbf{VII}
-        & 
-        &
-        &
-        &
-        &
-        & 
-        &
-        &
-        \\
-        \hline
-        VIII. 
-        & 
-        & 
-        & 
-        & 
-        &\x\textbf{VIII} 
-        & 
-        &
-        &
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        IX. 
-        & 
-        & 
-        & 
-        &\x\textbf{IX} 
-        &\x\textbf{IX} 
-        & 
-        &
-        &
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        X. 
         & 
@@
         &\x\textbf{X} 
-        &\x\textbf{X}
-        &\x\textbf{X}
         \\
         \hline
-        XI. Crosscutting issues 
-        & 
-        & 
-        &
-        &
-        &
-        &
-        & 
-        & 
-        & 
-        &
-        &\x\textbf{VII}
-        &\x\textbf{VII} 
-        \\
-        \hline
+%    \end{tabular}
+%    \label{tab-timeframe}
+%\end{table}
 \end{longtable}
 
-\vspace{-\baselineskip}
+\newpage
+%remove page break if there are page limits
+%\vspace{0.5\baselineskip}
 
-\begin{longtable}{|l|l|l|}
-    \caption*{\textbf{Milestones.}}
-    \label{tab-milestones}\\
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Milestone}}
-        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
-        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        0. Project\\logistics
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        0.1. Kick-off report, roles, and responsibilities.\\
-        0.2. Annual reports.\\
-        0.3. Agency administrative requirements.\\
-        0.4. Final project report.\\
-        0.5. Journal paper submission.\\
-        0.6. Professional society conference presentations.
-        \end{tabular}
-        & 
-        \begin{tabular}[c]{@{}l@{}}
-        0.1. Y1-Q2\\
-        0.2. Annually\\
-        0.3. Quarterly\\
-        0.4. Y2-Q4\\
-        0.5. Annually\\
-        0.6. Annually
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        1. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        1.1.  \\
-        1.2. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        1.1.  \\
-        1.2.  
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        2. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        2.1. \\
-        2.2. \\
-        2.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        2.1. \\
-        2.2. \\
-        2.3. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        3.1. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        3.1. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        4. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        4.1. \\
-        4.2. \\
-        4.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        4.1. \\
-        4.2. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        5. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        5.1. \\
-        5.2. \\
-        5.3. \\
-        5.4. \\
-        5.5. 
-        \end{tabular}
-        & 
-        \begin{tabular}[c]{@{}l@{}}
-        5.1. \\
-        5.2. \\
-        5.3. \\
-        5.4. \\
-        5.5. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        6. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        6.1. \\
-        6.2.  
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        6.1. \\
-        6.2. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        7. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        7.1. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        7.1. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        8. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        8.1. \\
-        8.2. \\
-        8.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        8.1. \\
-        8.2. \\
-        8.3. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        9. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        9.1. \\
-        9.2. \\
-        9.3. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        9.1. \\
-        9.2. \\
-        9.3. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        10. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        10.1. \\
-        10.2. \\
-        10.3. \\
-        10.4. \\
-        10.5. \\
-        10.6. 
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        10.1. \\
-        10.2. \\
-        10.3. \\
-        10.4. \\
-        10.5. \\
-        10.6. 
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-        11. Discuss\\crosscutting\\issues
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        11.1. Identify lessons learned.\\
-        11.2. Develop future research and educational pathways.
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-        11.1. Y3-Q3\\
-        11.2. Y3-Q4
-        \end{tabular}
-        \\
-        \hline
-\end{longtable}
-
-\paragraph*{Contribution to advancing state of the art in a, b, and c.}
-\noindent This research plan and deliverables will advance the state-of-the-art in a, b, and, c as it is expected to - (1), (2), (3), and (4).
-
-\paragraph*{Description of facilities to be utilized to execute scope.}
-
-\paragraph*{Challenges to accomplish tasks and planned mitigations.} 
-\noindent The PI is based at a United States Research University.
-The co-PIs are based at \textit{Affiliations}.
-This proposed project supports the goals and research interests of the institutions in the field of \textit{major fields}.
-
-\vspace{-\baselineskip}
-
-\begin{longtable}{|L{0.45\linewidth}|L{0.45\linewidth}|}
-    \caption*{}
-    \label{tab-risk}\\
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Challenges to accomplish tasks}}
-        &\multicolumn{1}{|c|}{\textbf{Planned mitigations}}\\
-        \hline
-
-        & 
-        \\
-        \hline
-
-        &  
-        \\
-        \hline
-
-        &  
-        \\
-        \hline
-
-        & 
-        \\
-        \hline
-\end{longtable}
-
-\paragraph*{Information, data, and plans.} 
-\noindent All information has been presented in the technical scope.
-
-\paragraph*{Quality assurance.} 
-\noindent Our project team have practiced a QA approach, consistent with the graded approach established by the DOE Technical Integration Office, per the NEUP website and any additional requirements deemed necessary during contracting.
-All projects undergo safety review by experts.
-We have followed this QA expectation in all ongoing awards.
-
-\paragraph*{Mandatory requirements.} 
-\noindent We abide by current and pending information on nuclear-related federal funding contained in Form 3204.
-The Mandatory, Go/No-go, requirements will be coordinated with the institutional Office of Sponsored Research, the general counsel, and the Office of Technology Transfer.
-Each PI noted below will assume responsibility as the point of contact.
-
-\vspace{-\baselineskip}
-
-\begin{longtable}{|c|c|c|c|}
-    \caption*{}
-    \label{tab-mandatory-requirements}\\
-        \hline
-        \textbf{No.}
-        &\textbf{Requirement}
-        &\textbf{Responsibility}
-        &\textbf{Evaluation}\\
-        \hline
-        1
-        &Commitment to reporting and budget requirements
-        &All PIs
-        &Go/No-go 
-        \\
-        \hline
-        2
-        &10 CFR 851 Worker Safety and Health Program
-        &All PIs
-        &Go/No-go 
-        \\
-        \hline
-        3
-        &Export Control
-        &All PIs
-        &Go/No-go 
-        \\
-        \hline
-        4
-        &Standard Research Subcontract
-        &All PIs
-        &Go/No-go 
-        \\
-        \hline
-        5
-        &Quality Assurance
-        &All PIs
-        &Go/No-go 
-        \\
-        \hline
-        6
-        &Commitment to prepare additional contract elements
-        &All PIs
-        &Go/No-go 
-        \\
-        \hline
-\end{longtable}
-
-\vspace{-0.50\baselineskip}
-
-\noindent\textbf{References}
-\bibliographystyle{neup}
+\section*{References}
+\bibliographystyle{nsf}
 \setlength{\bibhang}{0pt}
@@
 
+%wrap figure around text
+%move to wherever in the text 
+%{l} fixes it on the left margin
+%{L} floats
+%\begin{wrapfigure}{l}{0.x\textwidth}
+%       \includegraphics[width=0.(x-2)\textwidth]{}
+%    \caption{}
+%    \label{fig-}
+%\end{wrapfigure}
+
 \end{document}

### 2021-07-06 proposal-documents/white-paper/white-paper-phd-proposal.tex
white paper update and phd white paper aded

--- 2021-07-06 proposal-documents/white-paper/white-paper-general-preproposal.tex
@@
 %REFERENCES
-%
 %neup.bst - numbered citations in order of appearance, short author list with et al in reference section
@@
 %%%%%
-\documentclass[11pt,letterpaper]{article}
+\documentclass[11pt,a4paper]{article}
 \usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Agency}
-\chead{\scriptsize \textit{Title}}
+\lhead{\scriptsize Title Keyword}
+\chead{\scriptsize \textit{Name - PhD White Paper Project Proposal}}
 \rhead{\scriptsize \today}
@@
     \textbf{Title\\
-    Call\\
+    PhD White Paper Project Proposal\\
     }
-    Name (PI) - Affiliation; Name (co-PI) - Affiliation\\
-    Name (co-PI) - Affiliation
+    \vspace{0.10in}
+    Name\\
+    University\\
+    Department
 \par
@@
 \section*{Abstract}
-%may not be needed
 
@@
 
-\paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
+\paragraph*{Workscope 1 - Title.} 
 \subparagraph*{Task I. Title.}
@@
 
-\paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
-\subparagraph*{Task III. Title.}
+\paragraph*{Workscope 2 - Title.} 
+\subparagraph*{Task II. Title.}
 
@@
 
-\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
+\paragraph*{Workscope 3 - Future outlook.}
 \subparagraph*{Task VII. Crosscutting issues.}
@@
 
-\paragraph*{Estimated Cost of the Project.} 
-We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
+%\paragraph*{Estimated Cost of the Project.} 
+%We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
 
@@
 
+{\small
 %\begin{table}[h!]
@@
 %    \begin{tabular}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
-\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
-        \captionsetup{margin=-9pt}
+\begin{longtable}{|L{0.07\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+%        \captionsetup{margin=-9pt}
         \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
@@
         \multicolumn{4}{|c|}{\textbf{Y2}}&
-        \multicolumn{4}{|c|}{\textbf{Y3}}
+        \multicolumn{4}{|c|}{\textbf{Y3}}&
+        \multicolumn{4}{|c|}{\textbf{Y4}}
         \\
-        \cline{2-13}
+        \cline{2-17}
         &
+        \textbf{Q1}& 
+        \textbf{Q2}& 
+        \textbf{Q3}& 
+        \textbf{Q4}& 
         \textbf{Q1}& 
@@
         & 
+        & 
+        & 
+        & 
+        & 
         \\
@@
         &\x\textbf{X}
+        & 
+        & 
+        & 
+        & 
         & 
@@
         & 
+        & 
+        & 
+        & 
+        & 
         \\
         \hline
-        VII. Crosscutting issues
+        VII.
+        & 
+        & 
+        & 
+        & 
         & 
@@
 \end{longtable}
-
+}
 \newpage

### 2021-07-13 proposal-documents/white-paper/white-paper-general-preproposal.tex

@@
 \usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=7pt,labelsep=period} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
 
@@
 \begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
-        \captionsetup{margin=-9pt}
+%       \captionsetup{margin=-0pt}
         \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}

### 2021-07-28 manuscript/document-package/draft-manuscript/draft-manuscript.tex
acronym fix
added commenting for journal template

@@
 %Use for original, revised, clean manuscripts
+%
+%%%%%
+%
+%REFERENCES
+%
+%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
+%nsf.bst - numbered citations in order of appearance, full author list in references section
+%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
+%ans.bst is for ANS only. 
+%
+%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
+%bst renders the author list itself
+%
+%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
+%
+%title = {{}} for all
+%
+%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
+%standard.bst \cite{-} - Borrelli (2021) in the text
+%standard.bst lists references alphabetically
+%the rest list numerically
+%select reference style line 54
+%
+%%%%%
+%
 \documentclass[11pt,a4paper]{article}
@@
 \usepackage{filecontents}
-\usepackage{tablefootnote}
 \usepackage{footnotehyper}
@@
 
-%fonts
+%%%%% fonts
 \usepackage{times}
@@
 %\renewcommand{\familydefault}{\sfdefault}
+%%%%%
+
+%%%%% references
+\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
+%\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+%%%%%
+
+%%%%% tables and figures
+\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+\usepackage{tablefootnote}
+\usepackage{tabularx}
+\usepackage{multirow}
+
+\usepackage[singlelinecheck=false,labelfont=bf]{caption}
+\usepackage{subcaption}
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+
+\usepackage{wrapfig} %wraps figures around text
+\setlength{\intextsep}{0.20mm}
+\setlength{\columnsep}{0.20mm}
+%%%%%
 
 \usepackage{tabto} %general tabbed spacing
-\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
 \usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
-%\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
 \usepackage{enumitem}
@@
 \usepackage{physics}
-\usepackage{tabularx}
-\usepackage{multirow}
 \usepackage{lscape}
 \usepackage{array}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage[labelfont=bf]{caption}
 \usepackage{chngcntr}
@@
 \usepackage{xargs} %for \newcommandx
+
 \usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
@@
 
-\usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=7pt,labelsep=period} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
-
-\usepackage{wrapfig}
-\setlength{\intextsep}{0.20mm}
-\setlength{\columnsep}{0.20mm}
-
 %\usepackage{xr} %for revisions - will cross reference from one file to here
@@
 
+%%%%% user shortcuts
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
@@
 \newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
+
 \newcommand{\acf}{\acrfull} %full acronym
@@
 \newcommand{\acs}{\acrshort} %short acronym
+
+\newcommand{\acfp}{\acrfullpl} %full acronym plural
+\newcommand{\aclp}{\acrlongpl} %long acronym plural
+\newcommand{\acsp}{\acrshortpl} %short acronym plural
 
@@
 %\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
+%%%%%
 
+%%%%% header and footer
 \usepackage{fancyhdr}
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize }
-\chead{\scriptsize \textit{ - Draft Manuscript}}
+\lhead{\scriptsize Manuscript ID - Load following}
+\chead{\scriptsize \textit{First Author et al. - Draft Manuscript}}
 \rhead{\scriptsize \today}
 \rfoot{\thepage}
+%%%%%
 
 \begin{filecontents}{references.bib} 
+        @misc{
+        nye15a,
+        author = {Nye, Jr., Joseph S.},
+        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
+        year = {2015},
+        note = {{The Washington Post}}
+    }
+    @article{
+        mil20a,
+        author = {Miller, James N.},
+        title = {No to no first use — for now},
+        journal = {Bulletin of the Atomic Scientists},
+        volume = {76},
+        pages = {8},
+        year  = {2020}
+    }
+    @incollection{
+        mil17a,
+        author = {Miller, Steven E.},
+        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
+        booktitle = {Understanding Cyber Conflict: 14 Analogies},
+        publisher = {Georgetown University Press},
+        year = {2017},
+        editor = {Perkovich, George and Levite, Ariel E.},
+        pages = {161}
+    }
+    @conference{
+        ben20a,
+        author = {Benjamin, Jacob and Haney, Michael},
+        title = {{Nonproliferation of Cyber Weapons}},
+        year = { 2020},
+        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
+        address = {Las Vegas, Nevada}
+    }
 \end{filecontents}
+
+%%%%% acronyms
+% alphabetical ordering is automated
+%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+%\newacronym{}{}{}
+%%%%%
 
@@
 
+%%%%% spacing options
 \onehalfspacing %linespacing
+%\setstretch{1.05} %linespacing
+%\spacing{1.25} %equivalent to 1.5 line spacing in Word
+
+%%%%% linenumbering
 \linenumbers %toggle line numbers
@@
 \modulolinenumbers[3] %line numbering interval
+%%%%%
 

### 2021-08-10 manuscript/document-package/draft-manuscript/draft-manuscript.tex

@@
         address = {Las Vegas, Nevada}
+    }
+    @book{
+        saa80a,
+        author = {Saaty, Thomas L.},
+        title = {{The analytical hierarchy process}},
+        publisher = {{McGraw-Hill, Inc.}},
+        year = {1980},
+        address = {New York}
     }

### 2021-08-16 proposal-documents/doe/benefit-of-collaboration/benefit-of-collaboration.tex
doe templates updated with current preamble

@@
+%@TheDoctorRAB
+%standard white paper/preproposal format
+%
+%%%%%
+%
+%REFERENCES
+%
+%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
+%nsf.bst - numbered citations in order of appearance, full author list in references section
+%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
+%ans.bst is for ANS only. 
+%
+%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
+%bst renders the author list itself
+%
+%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
+%
+%title = {{}} for all
+%
+%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
+%standard.bst \cite{-} - Borrelli (2021) in the text
+%standard.bst lists references alphabetically
+%the rest list numerically
+%
+%%%%%
 \documentclass[11pt,letterpaper]{article}
@@
 \usepackage{setspace}
-\usepackage{ulem} %strikethrough
-\usepackage{xcolor,colortbl} %change font color
+\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
+\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
 \usepackage{graphicx}
@@
 \usepackage{tablefootnote}
-\usepackage{subfig}
-\usepackage[yyyymmdd]{datetime}
+\usepackage{footnotehyper}
+%\usepackage{subfig}
+\usepackage[yyyymmdd]{datetime} %date format
 \renewcommand{\dateseparator}{.}
-\graphicspath{{../img/}}
+\graphicspath{{../img/}} %path to graphics
 \setcounter{secnumdepth}{5} %set subsection to nth level
+
+%fonts
 \usepackage{times}
+%arial - uncomment next two lines
+%\usepackage{helvet}
+%\renewcommand{\familydefault}{\sfdefault}
+
+\usepackage{tabto} %general tabbed spacing
+\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
+%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
+\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
 \usepackage{enumitem}
-\usepackage{float}
+\usepackage{boldline}
+\usepackage{makecell}
+\usepackage{booktabs}
+\usepackage{amssymb}
+\usepackage{gensymb}
+\usepackage{amsmath}
+\usepackage{physics}
+\usepackage{tabularx}
 \usepackage{multirow}
-\usepackage{tabularx}
-\usepackage{tabulary}
-\usepackage{gensymb}
-\usepackage{longtable}
-%\usepackage[labelfont=bf]{caption}
+\usepackage{lscape}
+\usepackage{array}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage[labelfont=bf]{caption}
+\usepackage{chngcntr}
+%\usepackage{hyperref}
+\usepackage{sectsty}
+\usepackage{textcomp}
+\usepackage{lastpage}
+\usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
+\usepackage[toc,page]{appendix}
+\usepackage[figure,table]{totalcount}
+\usepackage[acronym,nomain,nonumberlist]{glossaries}
+\makenoidxglossaries
 
 \usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=0pt} %sets a space after table caption
-\captionsetup[figure]{skip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
 
@@
 
-\usepackage[numbers,sort&compress]{natbib} 
-%'numbers' - numbered citations
-%'round' - (1) instead [1]
-%'sort&compress - [1-3] instead [1,2,3]
-\setlength{\bibsep}{0pt} %sets space between references
-\renewcommand{\bibsection}{} %suppresses large 'references' heading
-\renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading
+%\usepackage{xr} %for revisions - will cross reference from one file to here
+%\externaldocument{/path/to/auxfilename} %aux file needed
 
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
-\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
 \newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
 \newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
+\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
 \newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\acf}{\acrfull} %full acronym
+\newcommand{\acl}{\acrlong} %long acronym
+\newcommand{\acs}{\acrshort} %short acronym
+
+\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
+\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
+\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
+\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 
@@
 \makeatletter
+\renewcommand\tableofcontents{%
+    \@starttoc{toc}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoffigures{%
+    \@starttoc{lof}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoftables{%
+    \@starttoc{lot}%
+}
+\makeatother
+
+\makeatletter
+\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
+\makeatother
+
+\makeatletter
+\renewcommand\section{%
+    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
+    {\normalfont \normalsize \bfseries}}%
+
+\makeatletter
 \renewcommand\paragraph{%
-    \@startsection{paragraph}{4}{\z@ }{0.35\baselineskip}{-1em}
+    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
     {\normalfont \normalsize \bfseries}}%
@@
 \renewcommand\subsection{%
-    \@startsection{subsection}{2}{\z@ }{0.50\baselineskip}{0.10\baselineskip}
-    { \normalfont \bfseries}}%
+    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
+    { \large \normalsize \bfseries}}%
+
+\setlength{\bibsep}{0pt} %sets space between references
+\renewcommand{\bibsection}{} %suppresses large 'references' heading
+\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
 
@@
 \fancyhf{} %move page number to bottom right
-\renewcommand{\headrulewidth}{0pt} %set line thickness in header
-%\lhead{\scriptsize Name}
-%\chead{\scriptsize Title, subject, agency, etc.}
+\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+%\lhead{\scriptsize Agency}
+%\chead{\scriptsize \textit{Title}}
 %\rhead{\scriptsize \today}
 \rfoot{\thepage}
+
+\begin{filecontents}{references.bib} 
+    @misc{
+        nye15a,
+        author = {Nye, Jr., Joseph S.},
+        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
+        year = {2015},
+        note = {{The Washington Post}}
+    }
+    @article{
+        mil20a,
+        author = {Miller, James N.},
+        title = {No to no first use — for now},
+        journal = {Bulletin of the Atomic Scientists},
+        volume = {76},
+        pages = {8},
+        year  = {2020}
+    }
+    @incollection{
+        mil17a,
+        author = {Miller, Steven E.},
+        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
+        booktitle = {Understanding Cyber Conflict: 14 Analogies},
+        publisher = {Georgetown University Press},
+        year = {2017},
+        editor = {Perkovich, George and Levite, Ariel E.},
+        pages = {161}
+    }
+    @conference{
+        ben20a,
+        author = {Benjamin, Jacob and Haney, Michael},
+        title = {{Nonproliferation of Cyber Weapons}},
+        year = { 2020},
+        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
+        address = {Las Vegas, Nevada}
+    }
+\end{filecontents}
+
+%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+%\newacronym{}{}{}
+
+%spacing options
+%\onehalfspacing %linespacing
+%\setstretch{1.05} %linespacing
+%\spacing{1.25} %equivalent to 1.5 line spacing in Word
+
+%linenumbering
+%\linenumbers %toggle line numbers
+%\pagewiselinenumbers %reset line numbers on new page
+%\modulolinenumbers[3] %line numbering interval
 
@@
     \textbf{BENEFIT OF COLLABORATORS\\
-    Advanced Data Integration for Materials Accounting of a Bulk Nuclear Materials Handling Facility\\
-    FC-3: Materials Protection, Accounting, and Control Technology\\
+    Title \\
+    Call\\
     }
-    R. A. Borrelli (PI) - University of Idaho $\sq$ Idaho Falls Center for Higher Education 
+    Personnel - Affiliation 
 \par

### 2021-08-16 proposal-documents/doe/data-management-plan/data-management-plan.tex
doe templates
doe templates updated with current preamble

--- 2020-12-02 proposal-documents/data-management-plan/data-management-plan.tex
@@
 %@TheDoctorRAB
-%Use for original, revised, clean manuscripts
+%standard white paper/preproposal format
+%
+%%%%%
+%
+%REFERENCES
+%
+%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
+%nsf.bst - numbered citations in order of appearance, full author list in references section
+%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
+%ans.bst is for ANS only. 
+%
+%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
+%bst renders the author list itself
+%
+%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
+%
+%title = {{}} for all
+%
+%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
+%standard.bst \cite{-} - Borrelli (2021) in the text
+%standard.bst lists references alphabetically
+%the rest list numerically
+%
+%%%%%
 \documentclass[11pt,letterpaper]{article}
@@
 \usepackage{ulem} %strikethrough - do not \sout{\cite{}}
-\usepackage{xcolor} %change font color
+\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
 \usepackage{graphicx}
@@
 \renewcommand{\dateseparator}{.}
-\graphicspath{{../../img/}} %path to graphics
+\graphicspath{{../img/}} %path to graphics
 \setcounter{secnumdepth}{5} %set subsection to nth level
-\usepackage{caption}
-\captionsetup[table]{skip=11pt} %sets a space after table caption
+
+%fonts
 \usepackage{times}
+%arial - uncomment next two lines
+%\usepackage{helvet}
+%\renewcommand{\familydefault}{\sfdefault}
+
 \usepackage{tabto} %general tabbed spacing
 \usepackage{longtable} %need to put label at top under caption then \\ - use spacing
-\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent
-\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations
+\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
+%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
+\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
 \usepackage{enumitem}
@@
 \usepackage{amssymb}
+\usepackage{gensymb}
 \usepackage{amsmath}
@@
 \usepackage{chngcntr}
-\usepackage{hyperref}
+%\usepackage{hyperref}
+\usepackage{sectsty}
+\usepackage{textcomp}
+\usepackage{lastpage}
+\usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
+\usepackage[toc,page]{appendix}
+\usepackage[figure,table]{totalcount}
+\usepackage[acronym,nomain,nonumberlist]{glossaries}
+\makenoidxglossaries
 
-%\usepackage{xr} %document crossreferencing
+\usepackage[singlelinecheck=false]{caption}
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+
+\usepackage{wrapfig}
+\setlength{\intextsep}{0.20mm}
+\setlength{\columnsep}{0.20mm}
+
+%\usepackage{xr} %for revisions - will cross reference from one file to here
 %\externaldocument{/path/to/auxfilename} %aux file needed
@@
 \newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
+\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\acf}{\acrfull} %full acronym
+\newcommand{\acl}{\acrlong} %long acronym
+\newcommand{\acs}{\acrshort} %short acronym
+
+\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
+\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
+\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
+\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 
@@
 \makeatletter
+\renewcommand\tableofcontents{%
+    \@starttoc{toc}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoffigures{%
+    \@starttoc{lof}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoftables{%
+    \@starttoc{lot}%
+}
+\makeatother
+
+\makeatletter
+\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
+\makeatother
+
+\makeatletter
+\renewcommand\section{%
+    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
+    {\normalfont \normalsize \bfseries}}%
+
+\makeatletter
 \renewcommand\paragraph{%
-    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
+    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
     {\normalfont \normalsize \bfseries}}%
@@
 \renewcommand\subparagraph{%
-    \@startsection{subparagraph}{5}{\z@ }{0.45\baselineskip}{-1em}
+    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
     {\normalfont \normalsize \itshape }}%
@@
 \renewcommand\subsection{%
-    \@startsection{subsection}{2}{\z@ }{0.75\baselineskip}{0.25\baselineskip}
-    { \large \bfseries}}%
+    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
+    { \large \normalsize \bfseries}}%
+
+\setlength{\bibsep}{0pt} %sets space between references
+\renewcommand{\bibsection}{} %suppresses large 'references' heading
+\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
 
@@
 \fancyhf{} %move page number to bottom right
-\renewcommand{\headrulewidth}{0pt} %turn off line in header
-%\lhead{\scriptsize NSF CPS 20-563}
-%\chead{\scriptsize Data Management Plan}
+\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+%\lhead{\scriptsize Agency}
+%\chead{\scriptsize \textit{Title}}
 %\rhead{\scriptsize \today}
 \rfoot{\thepage}
+
+\begin{filecontents}{references.bib} 
+    @misc{
+        nye15a,
+        author = {Nye, Jr., Joseph S.},
+        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
+        year = {2015},
+        note = {{The Washington Post}}
+    }
+    @article{
+        mil20a,
+        author = {Miller, James N.},
+        title = {No to no first use — for now},
+        journal = {Bulletin of the Atomic Scientists},
+        volume = {76},
+        pages = {8},
+        year  = {2020}
+    }
+    @incollection{
+        mil17a,
+        author = {Miller, Steven E.},
+        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
+        booktitle = {Understanding Cyber Conflict: 14 Analogies},
+        publisher = {Georgetown University Press},
+        year = {2017},
+        editor = {Perkovich, George and Levite, Ariel E.},
+        pages = {161}
+    }
+    @conference{
+        ben20a,
+        author = {Benjamin, Jacob and Haney, Michael},
+        title = {{Nonproliferation of Cyber Weapons}},
+        year = { 2020},
+        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
+        address = {Las Vegas, Nevada}
+    }
+\end{filecontents}
+
+%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+%\newacronym{}{}{}
+
+%spacing options
+%\onehalfspacing %linespacing
+%\setstretch{1.05} %linespacing
+%\spacing{1.25} %equivalent to 1.5 line spacing in Word
+
+%linenumbering
+%\linenumbers %toggle line numbers
+%\pagewiselinenumbers %reset line numbers on new page
+%\modulolinenumbers[3] %line numbering interval
 

### 2021-08-16 proposal-documents/doe/preproposal/preproposal.tex
doe templates updated with current preamble

--- 2021-07-13 proposal-documents/white-paper/white-paper-general-preproposal.tex
@@
 \fancyhf{} %move page number to bottom right
-%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Agency}
-\chead{\scriptsize \textit{Title}}
-\rhead{\scriptsize \today}
+\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+%\lhead{\scriptsize Agency}
+%\chead{\scriptsize \textit{Title}}
+%\rhead{\scriptsize \today}
 \rfoot{\thepage}
@@
     }
-    Name (PI) - Affiliation; Name (co-PI) - Affiliation\\
+    Name (PI) - Affiliation\\
     Name (co-PI) - Affiliation 
@@
 
-\section*{Abstract}
-%may not be needed
-
 \paragraph*{Summary of the Proposed Project.} 
+\noindent
 
 \paragraph*{Motivation.}
+\noindent
 
 \paragraph*{Overall Objective.}
+\noindent
 
@@
 \subparagraph*{Background.} 
+\noindent
 
 \subparagraph*{Relevant literature.}
+\noindent
 
@@
 
+\vspace{0.25\baselineskip}
+
 \paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
 \subparagraph*{Task I. Title.}
+\noindent
 
 \subparagraph*{Task II. Title.}
+\noindent
 
 \paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
-\subparagraph*{Task III. Title.}
+\subparagraph*{Task II. Title.}
+\noindent
 
 \subparagraph*{Task IV. Title.}
-
-\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
-\subparagraph*{Task VII. Crosscutting issues.}
+\noindent
 
 \paragraph*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
-We anticipate the following outcomes - 
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
+\noindent We anticipate the following outcomes - 
+\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
     \item
@@
 \paragraph*{Estimated Cost of the Project.} 
-We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
+\noindent We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
 
@@
 \begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
-%       \captionsetup{margin=-0pt}
         \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
@@
         I. 
-        &\x\textbf{X}
+        &\x\textbf{I}
         & 
@@
         II. 
-        &\x\textbf{X} 
+        &\x\textbf{II} 
         & 
@@
         III. 
-        &\x\textbf{X} 
+        &\x\textbf{III} 
         & 
@@
         IV. 
-        &\x\textbf{X}
+        &\x\textbf{IV}
         & 
@@
         V. 
-        &\x\textbf{X} 
+        &\x\textbf{V} 
         & 
@@
         VI. 
-        &\x\textbf{X} 
+        &\x\textbf{VI} 
         & 
@@
         & 
-        &\x\textbf{X} 
-        &\x\textbf{X} 
+        &\x\textbf{VII} 
+        &\x\textbf{VII} 
         \\
@@
 
-\section*{References}
-\bibliographystyle{nsf}
+\noindent\textbf{References}
+\bibliographystyle{neup}
 \setlength{\bibhang}{0pt}

### 2021-08-16 proposal-documents/doe/statement-of-work/statement-of-work.tex
doe templates
doe templates updated with current preamble

--- 2020-12-01 proposal-documents/statement-of-work/statement-of-work.tex
@@
 %@TheDoctorRAB
-%statement of work
-\documentclass[11pt,a4paper]{article}
+%standard white paper/preproposal format
+%
+%%%%%
+%
+%REFERENCES
+%
+%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
+%nsf.bst - numbered citations in order of appearance, full author list in references section
+%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
+%ans.bst is for ANS only. 
+%
+%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
+%bst renders the author list itself
+%
+%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
+%
+%title = {{}} for all
+%
+%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
+%standard.bst \cite{-} - Borrelli (2021) in the text
+%standard.bst lists references alphabetically
+%the rest list numerically
+%
+%%%%%
+\documentclass[11pt,letterpaper]{article}
 \usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
@@
 \usepackage{chngcntr}
+%\usepackage{hyperref}
+\usepackage{sectsty}
+\usepackage{textcomp}
+\usepackage{lastpage}
+\usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
+\usepackage[toc,page]{appendix}
+\usepackage[figure,table]{totalcount}
+\usepackage[acronym,nomain,nonumberlist]{glossaries}
+\makenoidxglossaries
 
-%\usepackage{xr} %document crossreferencing
+\usepackage[singlelinecheck=false]{caption}
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+
+\usepackage{wrapfig}
+\setlength{\intextsep}{0.20mm}
+\setlength{\columnsep}{0.20mm}
+
+%\usepackage{xr} %for revisions - will cross reference from one file to here
 %\externaldocument{/path/to/auxfilename} %aux file needed
@@
 \newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
+\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
+\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
+\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\acf}{\acrfull} %full acronym
+\newcommand{\acl}{\acrlong} %long acronym
+\newcommand{\acs}{\acrshort} %short acronym
 
-\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
+\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
+\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
+\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
+\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+
+\makeatletter
+\renewcommand\tableofcontents{%
+    \@starttoc{toc}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoffigures{%
+    \@starttoc{lof}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoftables{%
+    \@starttoc{lot}%
+}
+\makeatother
+
+\makeatletter
+\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
+\makeatother
+
+\makeatletter
+\renewcommand\section{%
+    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
+    {\normalfont \normalsize \bfseries}}%
+
+\makeatletter
+\renewcommand\paragraph{%
+    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
+    {\normalfont \normalsize \bfseries}}%
+
+\makeatletter
+\renewcommand\subparagraph{%
+    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
+    {\normalfont \normalsize \itshape }}%
+
+\makeatletter
+\renewcommand\subsection{%
+    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
+    { \large \normalsize \bfseries}}%
+
+\setlength{\bibsep}{0pt} %sets space between references
+\renewcommand{\bibsection}{} %suppresses large 'references' heading
+\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
 
@@
 \fancyhf{} %move page number to bottom right
-%\renewcommand{\headrulewidth}{0pt} %turn off line in header
-\lhead{\scriptsize Funding Agency}
-\chead{\scriptsize Statement of Work - \textit{Name}}
-\rhead{\scriptsize \today}
+\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+%\lhead{\scriptsize Agency}
+%\chead{\scriptsize \textit{Title}}
+%\rhead{\scriptsize \today}
 \rfoot{\thepage}
+
+\begin{filecontents}{references.bib} 
+    @misc{
+        nye15a,
+        author = {Nye, Jr., Joseph S.},
+        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
+        year = {2015},
+        note = {{The Washington Post}}
+    }
+    @article{
+        mil20a,
+        author = {Miller, James N.},
+        title = {No to no first use — for now},
+        journal = {Bulletin of the Atomic Scientists},
+        volume = {76},
+        pages = {8},
+        year  = {2020}
+    }
+    @incollection{
+        mil17a,
+        author = {Miller, Steven E.},
+        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
+        booktitle = {Understanding Cyber Conflict: 14 Analogies},
+        publisher = {Georgetown University Press},
+        year = {2017},
+        editor = {Perkovich, George and Levite, Ariel E.},
+        pages = {161}
+    }
+    @conference{
+        ben20a,
+        author = {Benjamin, Jacob and Haney, Michael},
+        title = {{Nonproliferation of Cyber Weapons}},
+        year = { 2020},
+        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
+        address = {Las Vegas, Nevada}
+    }
+\end{filecontents}
+
+%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+%\newacronym{}{}{}
+
+%spacing options
+%\onehalfspacing %linespacing
+%\setstretch{1.05} %linespacing
+%\spacing{1.25} %equivalent to 1.5 line spacing in Word
+
+%linenumbering
+%\linenumbers %toggle line numbers
+%\pagewiselinenumbers %reset line numbers on new page
+%\modulolinenumbers[3] %line numbering interval
 

### 2021-08-16 proposal-documents/doe/narrative/doe-proposal-narrative.tex

@@
 \usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=7pt} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
 
@@
 \renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-%\lhead{\scriptsize agency}
-%\chead{\scriptsize title}
+%\lhead{\scriptsize Agency}
+%\chead{\scriptsize \textit{Title}}
 %\rhead{\scriptsize \today}
@@
 %\spacing{1.25} %equivalent to 1.5 line spacing in Word
+
+%linenumbering
+%\linenumbers %toggle line numbers
+%\pagewiselinenumbers %reset line numbers on new page
+%\modulolinenumbers[3] %line numbering interval
 

### 2021-09-07 proposal-documents/doe/benefit-of-collaboration/benefit-of-collaboration.tex
added float package

@@
 \usepackage{footnotehyper}
+\usepackage{float}
 %\usepackage{subfig}
@@
 
-\subsection*{Summary of the Proposed Project}
+\subsection*{Summary of the Proposed Project.}
 
-\subsection*{Motivation} 
-\paragraph*{Context.}
+\subsection*{Motivation.} 
+%\paragraph*{Context.}
 
-\paragraph*{Challenges to nuclear materials accounting.}
+\subsection*{Overall Objective.}
 
-\subsection*{Overall Objective}
-
-\subsection*{Research Focus} 
+\subsection*{Research Focus.} 
 \noindent Project workscopes are summarized. 
@@
 
-\subsection*{Team} This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members.
+\subsection*{Team.} 
+This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members.
 The contribution of each is noted.
@@
 
-\subsection*{Important Research Facility/Equipment}
+\subsection*{Important Research Facility/Equipment.}
 \noindent The Important Research Facility/Equipment is \textit{description as relevant to project.}
 
-\subsection*{Work Project Documentation, Quality Control} 
+\subsection*{Work Project Documentation, Quality Control.} 
 \noindent The PI has a practiced a QA approach, consistent with that established by the DOE Technical Integration Office, per NEUP website and any additional requirements deemed necessary during contracting.

### 2021-10-25 proposal-documents/white-paper/white-paper-general-preproposal.tex
acronym fix
doe templates updated with current preamble
update to white paper general

@@
 \usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
-\usepackage{enumitem}
+\usepackage[inline]{enumitem}
 \usepackage{boldline}
@@
 
+\usepackage[firstpage]{draftwatermark}
+\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+\SetWatermarkScale{0.35}
+
 \usepackage[singlelinecheck=false]{caption}
@@
 %linenumbering
-%\linenumbers %toggle line numbers
-%\pagewiselinenumbers %reset line numbers on new page
-%\modulolinenumbers[3] %line numbering interval
+\linenumbers %toggle line numbers
+\pagewiselinenumbers %reset line numbers on new page
+\modulolinenumbers[1] %line numbering interval
 
 \begin{document}
+
+{\centering 
+    \textbf{Agency - Call \\
+    Federal POC - , Technical POC - \\
+    General budget\\
+    }
+\par
+}
+
+\noindent Text of call.
+
+\newpage
 
@@
 \paragraph*{Summary of the Proposed Project.} 
+\subparagraph*{Proposal.}
+
+\subparagraph*(Key features of the project.)
 
 \paragraph*{Motivation.}
+\subparagraph*(Context.)
 
 \paragraph*{Overall Objective.}
+
+\subsection*{Research Focus and Workscopes.} 
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+    \item\textit{Workscope title (Lead - )}
+        \begin{itemize}[leftmargin=*,topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+            \item Task 
+            \item Task 
+            \item Task 
+            \item Task 
+        \end{itemize}
+    \item\textit{Concluding work (Full team)}
+        \begin{itemize}[leftmargin=*,topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+            \item Discuss crosscutting issues
+        \end{itemize}
+\end{enumerate}
 
@@
 
+\subparagraph*{Recently funded work.}
 %for a 3 page preproposal, limit above subject matter to the first page
+%research focus will have to go
+
+\paragraph*{Unique project features.}
 
@@
 \newpage
+
+\begin{longtable}{|l|l|l|} %comment out for page limits
+    \caption*{\textbf{Milestones.}}
+    \label{tab-milestones}\\
+    \hline
+        \multicolumn{1}{|c|}{\textbf{Milestone}}
+        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
+        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
+        \hline
+        \begin{tabular}[c]{@{}l@{}}
+            0. Project logistics
+        \end{tabular}
+        &
+        \begin{tabular}[c]{@{}l@{}}
+            0.1. Kick-off report, roles, and responsibilities.\\
+            0.2. Annual reports.\\
+            0.3. Agency administrative requirements.\\
+            0.4. Final project report.\\
+            0.5. Journal paper submission.\\
+            0.6. Conference presentations.
+        \end{tabular}
+        &
+        \begin{tabular}[c]{@{}l@{}}
+            0.1. Y1-Q2\\
+            0.2. Annually\\
+            0.3. Quarterly\\
+            0.4. Y3-Q4\\
+            0.5. Annually\\
+            0.6. Annually
+        \end{tabular}
+        \\
+        \hline
+        \begin{tabular}[c]{@{}l@{}}
+            1.
+        \end{tabular}
+        &
+        \begin{tabular}[c]{@{}l@{}}
+            1.1.
+
+        \end{tabular}
+        &
+        \begin{tabular}[c]{@{}l@{}}
+            1.1. YX-QN
+        \end{tabular}
+        \\
+        \hline
+        \begin{tabular}[c]{@{}l@{}}
+            15. Crosscutting\\issues
+        \end{tabular}
+        &
+        \begin{tabular}[c]{@{}l@{}}
+            15.1. Identify lessons learned.\\
+            15.2. Develop future pathways and partnerships.
+        \end{tabular}
+        &
+        \begin{tabular}[c]{@{}l@{}}
+            15.1. YEND-Q3\\
+            15.2. YEND-Q4
+        \end{tabular}
+        \\
+        \hline
+\end{longtable}
+
+\newpage
 %remove page break if there are page limits

### 2021-11-04 proposal-documents/white-paper/white-paper-phd-proposal.tex
acronym fix
doe templates updated with current preamble
added float package
white paper updates

@@
 %REFERENCES
+%
 %neup.bst - numbered citations in order of appearance, short author list with et al in reference section
@@
 %%%%%
-\documentclass[11pt,a4paper]{article}
+\documentclass[11pt,letterpaper]{article}
 \usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
@@
 %\renewcommand{\familydefault}{\sfdefault}
+%%%%%
 
+%%%%% references
+%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
+\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+%%%%%
+
+%%%%% tables and figures
+\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+\usepackage{tablefootnote}
+\usepackage{tabularx}
+\usepackage{multirow}
 \usepackage{tabto} %general tabbed spacing
-\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+
+\usepackage[singlelinecheck=false,labelfont=bf]{caption}
+\usepackage{subcaption}
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+
+\usepackage{wrapfig} %wraps figures around text
+\setlength{\intextsep}{0.20mm}
+\setlength{\columnsep}{0.20mm}
+%%%%%
+
 \usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
-\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
-\usepackage{enumitem}
+\usepackage[inline]{enumitem}
 \usepackage{boldline}
@@
 \usepackage{amssymb}
+\usepackage{gensymb}
 \usepackage{amsmath}
 \usepackage{physics}
-\usepackage{tabularx}
-\usepackage{multirow}
 \usepackage{lscape}
 \usepackage{array}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage[labelfont=bf]{caption}
 \usepackage{chngcntr}
@@
 \makenoidxglossaries
+
+\usepackage[firstpage]{draftwatermark}
+\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+\SetWatermarkScale{0.35}
 
@@
     \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
-    {\normalfont \normalsize \bfseries}}%
+    {\Large \normalfont \bfseries}}%
 
@@
     \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
-    { \large \normalsize \bfseries}}%
+    { \large \normalfont \bfseries}}%
 
@@
 \renewcommand{\bibsection}{} %suppresses large 'references' heading
-\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
+\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading
 
@@
 
-%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+%%%%% acronyms
+% alphabetical ordering is automated
+\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
+\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
+\newacronym{inl}{INL}{Idaho National Laboratory}
+\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{anl}{ANL}{Argonne National Laboratory}
+\newacronym{npp}{NPP}{Nuclear Power Plant}
+\newacronym{smr}{SMR}{Small Modular Reactor}
+\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
+\newacronym{nus}{NuScale}{NuScale Power, LLC}
+\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
+\newacronym{ci}{CI}{Consistency Index}
+\newacronym{cr}{CR}{Consistency Ratio}
+\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
+\newacronym{lwr}{LWR}{Light Water Reactor}
+\newacronym{eia}{EIA}{U.S. Energy Information Administration}
+\newacronym{oer}{OER}{Online Educational Resource}
+\newacronym{lms}{LMS}{Learning Management System}
 %\newacronym{}{}{}
+%%%%%
 
@@
 %\pagewiselinenumbers %reset line numbers on new page
-%\modulolinenumbers[3] %line numbering interval
+%\modulolinenumbers[1] %line numbering interval
 
@@
 
-\section*{Abstract}
+\begin{center}\subsection*{Abstract}\end{center}
 
@@
 
-\paragraph*{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project.
+\paragraph*{Logical Path, Work Scope, Description of Tasks.}
 
-\paragraph*{Workscope 1 - Title.} 
-\subparagraph*{Task I. Title.}
+\paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
+\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Title.}
+    \item\textit{Title.}
+    \item\textit{Title.}
+\end{enumerate}
 
-\subparagraph*{Task II. Title.}
+\paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
+\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Title.}
+    \item\textit{Title.}
+    \item\textit{Title.}
+\end{enumerate}
 
-\paragraph*{Workscope 2 - Title.} 
-\subparagraph*{Task II. Title.}
-
-\subparagraph*{Task IV. Title.}
-
-\paragraph*{Workscope 3 - Future outlook.}
-\subparagraph*{Task VII. Crosscutting issues.}
+\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
+\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Crosscutting issues.}
+\end{enumerate}
 
 \paragraph*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
-We anticipate the following outcomes - 
+The following outcomes are anticipated - 
 \begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
@@
 
-%\paragraph*{Estimated Cost of the Project.} 
-%We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
-
-%limiting tasks, deliverables to one page allows for more references to be included on the third page, for a 3 page limit
-
-{\small
-%\begin{table}[h!]
-%    \centering
-%    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
-%    \begin{tabular}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
-\begin{longtable}{|L{0.07\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+\begin{scriptsize}
+\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
 %        \captionsetup{margin=-9pt}
@@
         \hline
-%    \end{tabular}
-%    \label{tab-timeframe}
-%\end{table}
 \end{longtable}
-}
+\end{scriptsize}
+
 \newpage
+
 %remove page break if there are page limits
@@
 
-\section*{References}
+\paragraph*{References}
 \bibliographystyle{nsf}

### 2021-11-04 proposal-documents/white-paper/white-paper-general-preproposal.tex

@@
 %\renewcommand{\familydefault}{\sfdefault}
+%%%%%
 
+%%%%% references
+%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
+\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+%%%%%
+
+%%%%% tables and figures
+\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+\usepackage{tablefootnote}
+\usepackage{tabularx}
+\usepackage{multirow}
 \usepackage{tabto} %general tabbed spacing
-\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+
+\usepackage[singlelinecheck=false,labelfont=bf]{caption}
+\usepackage{subcaption}
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+
+\usepackage{wrapfig} %wraps figures around text
+\setlength{\intextsep}{0.20mm}
+\setlength{\columnsep}{0.20mm}
+%%%%%
+
 \usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
-\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
 \usepackage[inline]{enumitem}
@@
 
-\section*{Abstract}
 %may not be needed
+\begin{center}\subsection*{Abstract}\end{center}
 
@@
 
-\subparagraph*(Key features of the project.)
+\subparagraph*{Key features of the project.}
 
 \paragraph*{Motivation.}
-\subparagraph*(Context.)
+\subparagraph*{Context.}
 
@@
 
-\paragraph*{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project.
+\paragraph*{Logical Path, Work Scope, Description of Tasks.}
 
 \paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
-\subparagraph*{Task I. Title.}
-
-\subparagraph*{Task II. Title.}
+\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Title.}
+    \item\textit{Title.}
+    \item\textit{Title.}
+\end{enumerate}
 
 \paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
-\subparagraph*{Task III. Title.}
-
-\subparagraph*{Task IV. Title.}
+\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Title.}
+    \item\textit{Title.}
+    \item\textit{Title.}
+\end{enumerate}
 
 \paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
-\subparagraph*{Task VII. Crosscutting issues.}
+\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Crosscutting issues.}
+\end{enumerate}
 
@@
 
-%\begin{table}[h!]
-%    \centering
-%    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
-%    \begin{tabular}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
-\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
+\begin{longtable}{|L{0.23\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
 %       \captionsetup{margin=-0pt}
@@
         \hline
-%    \end{tabular}
-%    \label{tab-timeframe}
-%\end{table}
 \end{longtable}
@@
 
+%not typically needed in a preproposal, but good to do 
 \begin{longtable}{|l|l|l|} %comment out for page limits
@@
 \newpage
+
 %remove page break if there are page limits

### 2021-11-18 peer-reviewer/peer-reviewer.tex
review update

@@
+%@TheDoctorRAB
+%Use for original, revised, clean manuscripts
+%
+%%%%%
+%
+%REFERENCES
+%
+%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
+%nsf.bst - numbered citations in order of appearance, full author list in references section
+%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
+%ans.bst is for ANS only. 
+%
+%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
+%bst renders the author list itself
+%
+%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
+%
+%title = {{}} for all
+%
+%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
+%standard.bst \cite{-} - Borrelli (2021) in the text
+%standard.bst lists references alphabetically
+%the rest list numerically
+%select reference style line 54
+%
+%%%%%
+%
 \documentclass[11pt,a4paper]{article}
@@
 \usepackage{ulem} %strikethrough - do not \sout{\cite{}}
-\usepackage{xcolor} %change font color
+\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
 \usepackage{graphicx}
 \usepackage{filecontents}
-\usepackage{tablefootnote}
 \usepackage{footnotehyper}
-\usepackage{subfig}
+%\usepackage{subfig}
 \usepackage[yyyymmdd]{datetime} %date format
@@
 \setcounter{secnumdepth}{5} %set subsection to nth level
-\usepackage{caption}
-\captionsetup[table]{skip=11pt} %sets a space after table caption
+
+%%%%% fonts
 \usepackage{times}
+%arial - uncomment next two lines
+%\usepackage{helvet}
+%\renewcommand{\familydefault}{\sfdefault}
+%%%%%
+
+%%%%% references
+\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
+%\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+%%%%%
+
+%%%%% tables and figures
+\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+\usepackage{tablefootnote}
+\usepackage{tabularx}
+\usepackage{multirow}
+
+\usepackage[singlelinecheck=false,labelfont=bf]{caption}
+\usepackage{subcaption}
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+
+\usepackage{wrapfig} %wraps figures around text
+\setlength{\intextsep}{0.20mm}
+\setlength{\columnsep}{0.20mm}
+%%%%%
+
 \usepackage{tabto} %general tabbed spacing
-\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
-\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent
-\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations
+\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
 \usepackage{enumitem}
@@
 \usepackage{physics}
-\usepackage{tabularx}
-\usepackage{multirow}
 \usepackage{lscape}
 \usepackage{array}
-\usepackage{caption}
-\usepackage[labelfont=bf]{caption}
 \usepackage{chngcntr}
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
+\usepackage{sectsty}
+\usepackage{textcomp}
+\usepackage{lastpage}
+\usepackage{xargs} %for \newcommandx
 
+\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
+\usepackage[toc,page]{appendix}
+\usepackage[figure,table]{totalcount}
+\usepackage[acronym,nomain,nonumberlist]{glossaries}
+\makenoidxglossaries
+
+\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
+\SetWatermarkText{\shortstack{CONFIDENTIAL\\do not distribute}}
+\SetWatermarkScale{0.25}
+
+%\usepackage{xr} %for revisions - will cross reference from one file to here
+%\externaldocument{/path/to/auxfilename} %aux file needed
+
+%%%%% user shortcuts
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
@@
 \newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
-\renewcommand\labelenumi{(\theenumi)} %changes 1. to (1) in enumerated list
+\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
+\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
 
+\newcommand{\acf}{\acrfull} %full acronym
+\newcommand{\acl}{\acrlong} %long acronym
+\newcommand{\acs}{\acrshort} %short acronym
+
+\newcommand{\acfp}{\acrfullpl} %full acronym plural
+\newcommand{\aclp}{\acrlongpl} %long acronym plural
+\newcommand{\acsp}{\acrshortpl} %short acronym plural
+
+\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
+\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
+\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
+\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+
+\makeatletter
+\renewcommand\tableofcontents{%
+    \@starttoc{toc}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoffigures{%
+    \@starttoc{lof}%
+}
+\makeatother
+
+\makeatletter
+\renewcommand\listoftables{%
+    \@starttoc{lot}%
+}
+\makeatother
+
+\makeatletter
+\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
+\makeatother
+
+%\makeatletter
+%\renewcommand\section{%
+%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
+%    {\normalfont \normalsize \bfseries}}%
+
+%\makeatletter
+%\renewcommand\paragraph{%
+%    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
+%    {\normalfont \normalsize \bfseries}}%
+
+%\makeatletter
+%\renewcommand\subparagraph{%
+%    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
+%    {\normalfont \normalsize \itshape }}%
+
+%\makeatletter
+%\renewcommand\subsection{%
+%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
+%    { \large \normalsize \bfseries}}%
+
+%\setlength{\bibsep}{0pt} %sets space between references
+%\renewcommand{\bibsection}{} %suppresses large 'references' heading
+%\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
+%%%%%
+
+%%%%% header and footer
 \usepackage{fancyhdr}
@@
 \fancyhf{} %move page number to bottom right
-\renewcommand{\headrulewidth}{0.5pt} %turn off line in header
+%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
 \lhead{\scriptsize ID}
-\chead{\scriptsize Peer review - \textit{Authors(s)}}
+\chead{\scriptsize Peer review - \textit{Authors}}
 \rhead{\scriptsize \today}
 \rfoot{\thepage}
+%%%%%
+
+\begin{filecontents}{references.bib}
+    @misc{
+        nye15a,
+        author = {Nye, Jr., Joseph S.},
+        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
+        year = {2015},
+        note = {{The Washington Post}}
+    }
+    @article{
+        mil20a,
+        author = {Miller, James N.},
+        title = {No to no first use — for now},
+        journal = {Bulletin of the Atomic Scientists},
+        volume = {76},
+        pages = {8},
+        year  = {2020}
+    }
+    @incollection{
+        mil17a,
+        author = {Miller, Steven E.},
+        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
+        booktitle = {Understanding Cyber Conflict: 14 Analogies},
+        publisher = {Georgetown University Press},
+        year = {2017},
+        editor = {Perkovich, George and Levite, Ariel E.},
+        pages = {161}
+    }
+    @conference{
+        ben20a,
+        author = {Benjamin, Jacob and Haney, Michael},
+        title = {{Nonproliferation of Cyber Weapons}},
+        year = { 2020},
+        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
+        address = {Las Vegas, Nevada}
+    }
+    @book{
+        saa80a,
+        author = {Saaty, Thomas L.},
+        title = {{The analytical hierarchy process}},
+        publisher = {{McGraw-Hill, Inc.}},
+        year = {1980},
+        address = {New York}
+    }
+\end{filecontents}
+
+%%%%% acronyms
+% alphabetical ordering is automated
+%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+%\newacronym{lac}{LAC}{linear attenuation coefficient}
+%\newacronym{mac}{MAC}{mass attenuation coefficient}
+%\newacronym{hvl}{HVL}{half value layer}
+%\newacronym{tvl}{TVL}{tenth value layer}
+%\newacronym{mfp}{MFP}{mean free path}
+%\newacronym{zff}{Zeff}{effective atomic number}
+%\newacronym{rpe}{RPE}{radiation protection efficiency}
+%%%%%
 
@@
 
-\begin{titlepage}
-    \title{
-        Title\\
+\begin{titlepage} %do not use [] in this field
+    \title{Title\\
     }
-    \author{
-        Name
-        \\ \\ \\
-        Affiliation 
+    \author{Primary Author no more than two then use et al.
         \\ \\
-        Submitted to: \textit{Journal Name}\\[ID]
+        Primary Affiliation
+        \\ \\
+        Submitted to: \textit{Journal}\\
+        ID
         \\ \\ \\
@@
 
-\noindent\textbf{Preface.}
+\section*{Abstract}
 
-\noindent\textbf{General comments.}
+\newpage
 
-\noindent\textbf{Section comments.}
+\section*{Preface} 
+Please consider the review to be a conversation amongst colleagues.
+The authors don't necessarily need to defend their position.
+I don't really dispute any of the content.
+This review is about editing the manuscript in a way to produce a publishable journal paper.
+The authors don't have to agree with all of the points raised in the review, but the courtesy of a response to these comments is expected.
 
-\noindent\textbf{Line items.}
-\begin{enumerate}[leftmargin=*]
+\section*{General comments} 
+\subsection*{Style}
+
+\subsection*{Content}
+\subsection*{Literature review}
+
+\subsection*{Figures and tables}
+Figures require a descriptive caption that should be further explained in the text; e.g., what is being plotted, what is important about the plot, and what is the main takeaway from the plot.
+In general, the figures are not explained adequately.
+Similarly with tables.
+
+\subsection*{Equations}
+The parameters in an equation should be defined with units, even if it is obvious. For example, clearly, $\rho$ is density, but the units thereof could be $kg/m^3$, $g/cm^3$, etc.
+
+\newpage
+
+\part*{Sections of the paper}
+\section*{Abstract}
+
+\section{Introduction}
+
+\section{}
+\subsection{}
+
+\section{Results and discussion}
+
+\section{Conclusions}
+
+\newpage
+
+\part*{Line items}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
+    \item  
 \end{enumerate}
 
+\newpage
+
+\part*{Final remarks on the review}
+
 \end{document}

### 2021-11-19 manuscript/document-package/coverletter/coverletter.tex

--- 2021-06-23 manuscript/document-package/references/references.tex
@@
-%@TheDoctorRAB
-%Use for original, revised, clean manuscripts
+%TheDoctorRAB
+%Used for first draft or revised manuscript
 \documentclass[11pt,a4paper]{article}
@@
 \pagestyle{fancy}
-\fancyhf{} %move page number to bottom right
-%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize }
-\chead{\scriptsize \textit{- Draft Manuscript}}
-\rhead{\scriptsize \today}
-\rfoot{\thepage}
+\fancyhf{}
+\renewcommand{\headrulewidth}{0pt}
+\rhead{
+    \includegraphics[width=0.3\textwidth]{logo.png} \\
+    \begin{scriptsize}
+        1776 Science Center Drive \\
+        Idaho Falls, ID 83402 \\
+        208.282.7979 \\ 
+    \end{scriptsize}
+}
+
+\cfoot{
+    \begin{scriptsize}
+        To enrich education through diversity, the University of Idaho is an equal opportunity/affirmative action employer.
+    \end{scriptsize}
+}
+
+\rfoot{\thepage} %page number on bottom right
 
@@
 
-\begin{titlepage}
-    \title{Applying Analytic Hierarchy Process to Industrial Process Design in a Nuclear Renewable Hybrid Energy System}
-    \author{
-        , 
-        , 
-        \textsuperscript{*}
-        \\ \\ \\
-        \\
+\begin{flushright}
+\noindent \\
+\noindent \\
+\noindent \textit{}\\
+\end{flushright}
 
-        \\ \\ \\
-        \textsuperscript{*}
+\hfill{\footnotesize\today}
+
+\noindent Dear Dr. : \\
+
+\noindent We would like to submit the original manuscript to \textit{} for peer review entitled, `'.
+
+%\noindent (Each of the three reviewer comments were studied in detail, and a careful response was prepared for each comment.
+In the marked manuscript, omissions are recorded \sout{as follows}.
+For revisions, \edit{colored font was used}, and a footnote was provided to indicate the comment from the reviewer.\fn{R1 - Comment from Reviewer 1.})\\
+
+\vspace{0.50\baselineskip}
+
+\noindent Thank you again for the opportunity to publish in \textit{}.
+
+\vspace*{\fill}
+{\footnotesize
+\begin{flushright}
+    Sincerely, \\
+    Prof. R. A. Borrelli \\
+    University of Idaho $\sq$ Idaho Falls Center for Higher Education \\
+    Department of Nuclear Engineering and Industrial Management \\
+    Center for Advanced Energy Studies \\
+    995 MK Simpson Boulevard, Idaho Falls ID 83401 \\
+    rborrelli@uidaho.edu \\
+    208.533.8122
+    TheDoctorRAB.github.io
+\end{flushright}
 }
-\clearpage %not have page number on title page
-\maketitle
-
-\thispagestyle{empty} %start with page number 1 on second page
-\end{titlepage}
-
-\onehalfspacing %linespacing
-\linenumbers %toggle line numbers
-\pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[3] %line numbering interval
-
-\nocite{*}
-
-\bibliographystyle{standard}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
+%\noindent \small{encl.: Marked Manuscript, Clean Manuscript, Response to Reviewer 1, Response to Reviewer 2, Response to Reviewer 3} %only major documents
+\noindent {\footnotesize encl.: Draft Manuscript} %only major documents
 

### 2022-01-25 journal/manuscript/document-package/declaration-of-competing-interests/declaration-of-competing-interests.tex
reset

--- 2021-06-23 manuscript/document-package/references/references.tex
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize }
-\chead{\scriptsize \textit{- Draft Manuscript}}
+\lhead{\scriptsize Journal}
+\chead{\scriptsize \textit{Author - Draft Manuscript}}
 \rhead{\scriptsize \today}
@@
 \begin{titlepage}
-    \title{Applying Analytic Hierarchy Process to Industrial Process Design in a Nuclear Renewable Hybrid Energy System}
+    \title{}
     \author{
@@
 
+\section*{Declaration of competing interests}
+
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+
 \thispagestyle{empty} %start with page number 1 on second page
@@
 
-\onehalfspacing %linespacing
-\linenumbers %toggle line numbers
-\pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[3] %line numbering interval
-
-\nocite{*}
-
-\bibliographystyle{standard}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
-
 \end{document}

### 2022-01-25 journal/manuscript/document-package/draft-manuscript/draft-manuscript.tex
reset

--- 2021-08-10 manuscript/document-package/draft-manuscript/draft-manuscript.tex
@@
 \usepackage{chngcntr}
-%\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \usepackage{sectsty}
@@
 \usepackage{xargs} %for \newcommandx
-
-\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
-\usepackage[toc,page]{appendix}
+\usepackage{gensymb}
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
+\usepackage[toc,title]{appendix}
 \usepackage[figure,table]{totalcount}
@@
 \makenoidxglossaries
+
+%%%%% watermark
+\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
+\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+\SetWatermarkScale{0.25}
+%%%%%
 
@@
 \newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+\newcommandx{\rab}[2][1=]{\author=RAB,tickmarkheight=0.15cm,todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 

### 2022-01-25 journal/manuscript/document-package/guidelines/guidelines.tex
reset

%%%%%
%@TheDoctorRAB
%Guide for draft-manuscript.tex with standard.bst or nsf.bst
%Just complile and read
%Packages here don't matter
%%%%%
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level

%fonts
\usepackage{times}
%arial - uncomment next two lines
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}

\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
%\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
\usepackage{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}
%\usepackage{hyperref}
\usepackage{sectsty}
\usepackage{textcomp}
\usepackage{lastpage}
\usepackage{xargs} %for \newcommandx
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
\usepackage[toc,page]{appendix}
\usepackage[figure,table]{totalcount}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries

\usepackage[singlelinecheck=false]{caption}
\captionsetup[table]{skip=7pt,labelsep=period} %sets a space after table caption
\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format

\usepackage{wrapfig}
\setlength{\intextsep}{0.20mm}
\setlength{\columnsep}{0.20mm}

%\usepackage{xr} %for revisions - will cross reference from one file to here
%\externaldocument{/path/to/auxfilename} %aux file needed

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize Information on preparing a journal paper}
%\chead{\scriptsize \textit{ - Draft Manuscript}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

\begin{document}

\section*{General}
There are a lot of documents to prepare when submitting a manuscript to the journal. These are all teed up in the document-package folder. \textit{Do them last.} Start by actually writing the paper with the draft-manuscript.tex file. The rest is leftover from before the digital age.

\subsection*{Images}
Put all images in the img folder. The draft-manuscript.tex file has the path setup so you don't have to specify it in the file, just the file name.

\section*{Citations}
The draft-manuscript.tex file is set up for two citations formats - standard and nsf. Or neup.bst, which is just a short version of nsf.bst. Line 51 is for standard.bst. Line 52 is for the others. Set the bst filename on line 322.

For standard.bst, you have to use \verb=\citep{bor20a}=. This gives, (Borrelli, 2020) in the text. It's a common form for most journals. If you do \verb=\cite{bor20a}=, then you get Borrelli (2020) in the text.

This helps if you want to write something like - 
\begin{quote}
    Borrelli (2020) argues that object-orientied programming can effectively model safeguards-by-design.
\end{quote}

For multiple citations, just do \verb=\citep{bor20a,clo19a}= and it will do (Borrelli 2020; Clooney 2019) automatically.

If we have to use nsf.bst, then \verb=\citep= and \verb=\cite= both with just give \texttt{[1]}, but if you used \verb=\cite= with standard and switch to nsf, then you have to put `Ref.' in front of it, so it's a pain. I've submitted all my papers with standard.bst and literally no reviewer has commented on it.

\subsection*{Adding references to the tex file}
Line 178/179 is the filecontents/references.bib to add the reference information. Some people make a separate bib file. I think this is easier to do everything in the main tex file. Some example references are already set up as a guide. In general, people way overboard on the citation information or use ridiculous types. All that is needed is enough for someone to do a search and find the material that was cited in the paper. Really, that only is @article for a journal paper, @misc for a technical report, like INL reports, and @conference for a conference proceedings. I also included @book and @incollection. The latter is rare. I don't even use @book much. Anything outside of these can be covered with @misc. Web page URLs and DOIs aren't really necessary. I do not use @techreport because it renders `Tec. Rep.' in the citation list, and it drives me up the wall. For techical reports, I recommend @misc because in the \verb=note= = \verb={{}}= field, just put the report number, and everyone knows it is a technical report.

Keep the \verb={{}}= for \verb=title= = \verb={{}}= and \verb=note= = \verb={{}}= because it will output verbatim what is in the field.

For a journal paper, you don't need the number; the volume is sufficient, and you don't need the page range; the starting page is sufficient.

For authors, the format is - 
\begin{quote}
    \verb=@author= = \verb={Borrelli, R. A. and Clooney, George}=
\end{quote}

I'm throwing George a bone giving him the last author credit.

Enter all authors into the author field, even if there's 17. standard.bst is set up to add `et al.' if there are more than two of them inline, but in the references, all the authors are listed. The others just render numbers inline. nsf.bst will list all the authors in the references. NSF requires this. It's also just a courtesy to include everyone on a paper. neup.bst will render only the first author and `et al.' in the references section.

If the author is an organization, like an NRC report, then just do  - 
\begin{quote}
    \verb=@author= = \verb={{Nuclear Regulatory Commission}}= 
\end{quote}
with the double \verb={{}}=.

\newpage

\section*{Manuscript}
\subsection*{Contents}
The \verb=\section{}= level headings are suggestions, but generally common to journal papers. I strongly recommend to keep Motivation and Goals. I typically like to separate Results; where you talk about the data, and Discussion; where you say what the data means and why it's important.

Future Work is always important because it tells reviewers that you know the context of the work. You can also discuss here if you've made any assumptions, how you can test/verify them, etc.

\subsection*{Acronyms}
I set up acronyms with shortcuts to make it easy, easy, easy. Line 225 is where you list them. The format is -
\begin{quote}
    \verb=\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}=
\end{quote}

Shortcuts are - 
\begin{quote}
    `full'\\
    \verb=\acf{nrc}= = United States Nuclear Regulatory Commission (NRC)\\
    The () are automatic.
    \\ \\
    `long'\\
    \verb=\acl{nrc}= = United States Nuclear Regulatory Commission
    \\ \\
    `short'\\
    \verb=\acs{nrc}= = NRC
\end{quote}

Additionally, the above with `p' on the end; i.e., \verb=\acfp{}=, pluralizes the entry.

Trust me, this will save uncountable keystrokes. AND - the acronym tags work in \verb=\section{}=, etc.

It's set up when you compile to produce a list of the acronyms automatically. Only acronyms used in the text are rendered in the list. This is on line 272

\subsection*{Headings}
The tex file is set up for 5 levels of headings - 
\begin{quote}
    \verb=\section{},\subsection{},\subsubsection{},\paragraph{},\subparagraph{}=
\end{quote}

\end{document}

### 2022-02-21 proposal-documents/white-paper/white-paper-general-preproposal.tex

@@
 \usepackage{subcaption}
-\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
 
@@
 \usepackage{xargs} %for \newcommandx
-\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
 \usepackage[toc,page]{appendix}
@@
 \usepackage[firstpage]{draftwatermark}
-\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-\SetWatermarkScale{0.35}
-
-\usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+%\SetWatermarkScale{0.35}
 
@@
 \newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+\newcommandx{\rab}[2][1=]{\todo[author=RAB,tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
 
@@
 \bibliographystyle{nsf}
+%\bibliographystyle{neup}
 \setlength{\bibhang}{0pt}

### 2022-06-17 manuscript/document-package/draft-manuscript/draft-manuscript.tex
draft update
draft manuscript updated template

--- 2021-07-28 manuscript/document-package/draft-manuscript/draft-manuscript.tex
@@
 %@TheDoctorRAB
-%Use for original, revised, clean manuscripts
+%standard white paper/preproposal format
 %
@@
 %the rest list numerically
-%select reference style line 54
 %
 %%%%%
-%
 \documentclass[11pt,a4paper]{article}
@@
 \usepackage{filecontents}
+\usepackage{tablefootnote}
 \usepackage{footnotehyper}
+\usepackage{float}
 %\usepackage{subfig}
@@
 %\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+%\setlength{\bibsep}{7pt} %sets space between references
+%\renewcommand{\bibsection}{} %suppresses large 'references' heading
+%\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading
 %%%%%
@@
 \usepackage{multirow}
+\usepackage{tabto} %general tabbed spacing
+\usepackage{pdfpages}
+
+\usepackage{wrapfig} %wraps figures around text
+\setlength{\intextsep}{0.05mm}
+\setlength{\columnsep}{0.05mm}
 
@@
 \usepackage{subcaption}
-\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+\captionsetup[table]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
+\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
 
-\usepackage{wrapfig} %wraps figures around text
-\setlength{\intextsep}{0.20mm}
-\setlength{\columnsep}{0.20mm}
+%\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=1pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+%\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Tab.}} %sets space above caption, 'figure' format
 %%%%%
 
-\usepackage{tabto} %general tabbed spacing
 \usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-\usepackage{enumitem}
+\usepackage[inline]{enumitem}
 \usepackage{boldline}
@@
 \usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
+\usepackage{marginnote}
+\usepackage[toc,title]{appendix}
+\usepackage[figure,table]{totalcount}
 
-\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
-\usepackage[toc,page]{appendix}
-\usepackage[figure,table]{totalcount}
-\usepackage[acronym,nomain,nonumberlist]{glossaries}
-\makenoidxglossaries
+\usepackage[capitalise]{cleveref}
+
+\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
+\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+\SetWatermarkScale{0.20}
 
@@
 
-%%%%% user shortcuts
+%%%%% toc and glossaries
+\usepackage[acronym,nomain,nonumberlist]{glossaries}
+\makenoidxglossaries
+\usepackage{titlesec,titletoc}
+%\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
+%\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
+%\titleformat{\part}{\normalfont\Large\bfseries\filcenter}{\thepart}{}{}[]
+%\titlespacing\part{0pt}{0.75\baselineskip}{0.50\baselineskip}
+%\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
+%\titlespacing*\section{0pt}{0.55\baselineskip}{0.35\baselineskip}
+%\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
+%\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.30\baselineskip}
+\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
+\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
+
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
@@
 \newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
-\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
-\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+\newcommandx{\por}[2][1=]{\todo[author=Porter,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
+\newcommandx{\sam}[2][1=]{\todo[author=Sam,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
+\newcommandx{\rab}[2][1=]{\todo[author=RAB,tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
 
@@
 %    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
-%    {\normalfont \normalsize \bfseries}}%
+%    {\large \normalfont \bfseries}}%
 
@@
 %\renewcommand\paragraph{%
-%    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
+%    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
 %    {\normalfont \normalsize \bfseries}}%
@@
 %\renewcommand\subparagraph{%
-%    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
+%    \@startsection{subparagraph}{5}{\z@ }{0.40\baselineskip}{-1em}
 %    {\normalfont \normalsize \itshape }}%
@@
 %    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
-%    { \large \normalsize \bfseries}}%
-
-%\setlength{\bibsep}{0pt} %sets space between references
-%\renewcommand{\bibsection}{} %suppresses large 'references' heading
-%\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
-%%%%%
+%    {\large \normalfont \bfseries}}%
 
@@
     @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
+        hun19a,
+        author = {Hunton, Paul J. and England, Robert T.},
+        title = {{Addressing nuclear I\&C modernization through application of techniques employed in other industries}},
+        year = {2019},
+        note = {{INL/EXT-19-55799}}
+    }
+    @conference{
+        las18a,
+        author = {Lassell, S. A. and Hawari, A. I. and Benjamin, J. S. and Barnes, K. T. and Wright, V. L.},
+        title = {{Methodology development for cybersecurity robustness and vulnerability assessment of university research reactors}},
+        year = { 2018},
+        organization = {Proc., American Nuclear Society Annual Meeting },
+        address = {Philadelphia, Pennsylvania}
     }
     @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
+        mac19a,
+        author = {MacLean, Trevor and Borrelli, Robert and Haney, Michael},
+        title = {{Cybersecurity modeling of non-critical nuclear power plant digital instrumentation}},
+        journal = {{Critical Infrastructure Protection XIII, J. Staggs, S. Shenoi, eds.}},
+        volume = {{Chapter 5}},
+        year = {2019},
+        pages = {86}
     }
@@
     }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
+    @book{
+        ost19a,
+        author = {Ostrom, Lee T. and Wilhelmsen, Cheryl A.},
+        title = {{Risk assessment: Tools, techniques, and their applications}},
+        publisher = {John Wiley \& Sons, Inc.},
+        isbn = {978-1119483465},
+        year = {2019}
     }
@@
 % alphabetical ordering is automated
-%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
+\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
+\newacronym{inl}{INL}{Idaho National Laboratory}
+\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{anl}{ANL}{Argonne National Laboratory}
+\newacronym{npp}{NPP}{Nuclear Power Plant}
+\newacronym{smr}{SMR}{Small Modular Reactor}
+\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
+\newacronym{nus}{NuScale}{NuScale Power, LLC}
+\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
+\newacronym{ci}{CI}{Consistency Index}
+\newacronym{cr}{CR}{Consistency Ratio}
+\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
+\newacronym{lwr}{LWR}{Light Water Reactor}
+\newacronym{eia}{EIA}{U.S. Energy Information Administration}
+\newacronym{oer}{OER}{Online Educational Resource}
+\newacronym{lms}{LMS}{Learning Management System}
+\newacronym{cps}{CPS}{Cyber-Physical Systems}
+\newacronym{nsf}{NSF}{National Science Foundation}
+\newacronym{wsc}{WSC}{Western Services Corporation}
+\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
+\newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{roi}{ROI}{Return on Investment}
+\newacronym{ic}{I\&C}{Instrumentation \& Controls}
+\newacronym{mwe}{MWe}{Megawatts-electric}
+\newacronym{ics}{ICS}{Industrial Control Systems}
+\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
+\newacronym{ip}{IP}{Internet Protocol}
+\newacronym{udp}{UDP}{User Datagram Protocol}
+\newacronym{tva}{TVA}{Tennessee Valley Authority}
+\newacronym{plc}{PLC}{Programmable Logic Controller}
+\newacronym{vfd}{VFD}{Variable Frequency Drive}
+\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
+\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
+\newacronym{mim}{MITM}{Man in the Middle}
+\newacronym{dos}{DDoS}{Distributed Denial of Service}
+\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
+\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
+\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
+\newacronym{cs}{CS}{Critical System}
+\newacronym{loc}{LOCA}{Loss of Coolant Accident}
+\newacronym{hmi}{HMI}{Human Machine Interface}
+\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
+\newacronym{bol}{BOL}{beginning-of-life}
+\newacronym{eol}{EOL}{end-of-life}
+\newacronym{mol}{MOL}{middle-of-life}
+\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
+\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{neu}{NEUP}{Nuclear Energy University Program}
+\newacronym{doe}{DOE}{United States Department of Energy}
+\newacronym{nei}{NEI}{Nuclear Energy Institute}
+\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
 %\newacronym{}{}{}
 %%%%%
-
-%\newacronym{}{}{}
 
@@
 \begin{titlepage}
-    \title{}
+    \title{Title}
     \author{
-        , 
-        , 
-        \textsuperscript{*}
+        First, 
+        Second,
+        \textsuperscript{*}Third
         \\ \\ \\
-        \\
-
+        Affiliation 1\\
+        Affiliation 2\\
+        Affilation 3
         \\ \\ \\
-        \textsuperscript{*}
+        \textsuperscript{*}email
     }
@@
 
-%%%%% spacing options
+%spacing options
 \onehalfspacing %linespacing
@@
 
-%%%%% linenumbering
+%linenumbering
 \linenumbers %toggle line numbers
 \pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[3] %line numbering interval
-%%%%%
+\modulolinenumbers[1] %line numbering interval
 
@@
 \subsection{Goals} \label{sec-goals}
+We ask the following questions - 
+\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*,label=(\arabic*)]
+    \item 1 
+    \item 2
+    \item 3
+\end{enumerate}
 
-\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
-    \item 
-    \item  
-    \item 
+To address these, we have the following goals for this paper - 
+\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*,label=(\arabic*)]
+    \item a
+    \item b
+    \item c
 \end{enumerate}
@@
 Major results and implications include - 
-\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
-    \item
-    \item
-    \item
+\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item 1
+    \item 2
+    \item 3
 \end{itemize}
@@
 }
-
-\newpage
-
-%\begin{table}[h!]
-%    \centering
-%    \caption{Title}
-%        \begin{tabular}{|c|c|c|c|}
-%            \hline
-%            A&
-%            B&
-%            C&
-%            D
-%            \\
-%            \hline
-%            X
-%            &X
-%            &X
-%            &X
-%            \\
-%            \hline
-%        \end{tabular}
-%    \label{tab-label}
-%\end{table}
 
@@
 
-%\appendix
+\begin{appendices}
 
-%\begin{appendices}
+    \renewcommand{\thesection}{\Roman{section}}
+    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]
 
-%\renewcommand{\thesection}{\Roman{section}}
+\section{Title}\label{app-}
 
-%\section{} \label{}
-
-%\end{appendices}
+\end{appendices}
 

### 2022-06-17 proposal-documents/doe/narrative/doe-proposal-narrative.tex
inline for lists
reset

@@
 %\renewcommand{\familydefault}{\sfdefault}
+%%%%%
 
+%%%%% references
+%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
+\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+%%%%%
+
+%%%%% tables and figures
+\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+\usepackage{tablefootnote}
+\usepackage{tabularx}
+\usepackage{multirow}
 \usepackage{tabto} %general tabbed spacing
-\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
+
+\usepackage[singlelinecheck=false,labelfont=bf]{caption}
+\usepackage{subcaption}
+\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
+\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+
+\usepackage{wrapfig} %wraps figures around text
+\setlength{\intextsep}{0.20mm}
+\setlength{\columnsep}{0.20mm}
+%%%%%
+
 \usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
-\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
-\usepackage{enumitem}
+\usepackage[inline]{enumitem}
 \usepackage{boldline}
@@
 \usepackage{physics}
-\usepackage{tabularx}
-\usepackage{multirow}
 \usepackage{lscape}
 \usepackage{array}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage[labelfont=bf]{caption}
 \usepackage{chngcntr}
-%\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \usepackage{sectsty}
@@
 
-\usepackage[singlelinecheck=false]{caption}
-\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+\usepackage[firstpage]{draftwatermark}
+%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+%\SetWatermarkScale{0.35}
 
@@
 
+\newcommand{\acfp}{\acrfullpl} %full acronym plural
+\newcommand{\aclp}{\acrlongpl} %long acronym plural
+\newcommand{\acsp}{\acrshortpl} %short acronym plural
+
 \newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
@@
 \fancyhf{} %move page number to bottom right
-\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-%\lhead{\scriptsize Agency}
-%\chead{\scriptsize \textit{Title}}
-%\rhead{\scriptsize \today}
+%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+\lhead{\scriptsize Agency}
+\chead{\scriptsize \textit{Title}}
+\rhead{\scriptsize \today}
 \rfoot{\thepage}
@@
 %linenumbering
-%\linenumbers %toggle line numbers
-%\pagewiselinenumbers %reset line numbers on new page
-%\modulolinenumbers[3] %line numbering interval
+\linenumbers %toggle line numbers
+\pagewiselinenumbers %reset line numbers on new page
+\modulolinenumbers[1] %line numbering interval
 
@@
 \subsection*{Logical Path, Workscope, Description of Tasks} 
-\paragraph*{Workscope 1 - Title.} 
-\subparagraph*{Task I. Title.}
+\paragraph*{Workscope 1 - Title.} \textit{Lead - }
+\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Title.} Description. 
+\end{enumerate}
 
-\subparagraph*{Task II. Title.}
+\paragraph*{Workscope 2 - Title.} \textit{Lead - }
+\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Title.} Description. 
+\end{enumerate}
 
-\subparagraph*{Task III. Title.}
-
-\subparagraph*{Task IV. Title.}
-
-\paragraph*{Workscope 2 - Title.} 
-\subparagraph*{Task V. Title.}
-
-\paragraph*{Workscope 6. Conclusions.}
-\subparagraph*{Task N. Crosscutting Issues.} 
-\noindent Lessons learned will be identified for project outcomes. Selected additional discussion will cover, but not limited to, the following -
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
+\paragraph*{Workscope N. Conclusions.} \textit{Full team}
+\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Crosscutting issues.}
+    \item[]Lessons learned will be identified for project outcomes. Selected additional discussion will cover, but not limited to, the following -
+        \begin{enumerate}[,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
             \item 
@@
             \item 
+        \end{enumerate}
 \end{enumerate}

### 2022-06-17 journal/manuscript/document-package/draft-manuscript/draft-manuscript.tex
draft template

@@
 \usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
+\usepackage{marginnote}
 \usepackage{gensymb}
@@
 \usepackage[figure,table]{totalcount}
-\usepackage[acronym,nomain,nonumberlist]{glossaries}
-\makenoidxglossaries
+
+\usepackage[capitalise]{cleveref}
 
@@
 \SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+\SetWatermarkScale{0.20}
 \SetWatermarkScale{0.25}
@@
 \newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
+\newcommandx{\por}[2][1=]{\todo[author=Porter,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
+\newcommandx{\sam}[2][1=]{\todo[author=Sam,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
+\newcommandx{\rab}[2][1=]{\todo[author=RAB,tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 \newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
@@
 
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
 
@@
     }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
     @book{
-        saa80a,
-        author = {Saaty, Thomas L.},
-        title = {{The analytical hierarchy process}},
-        publisher = {{McGraw-Hill, Inc.}},
-        year = {1980},
-        address = {New York}
+        ost19a,
+        author = {Ostrom, Lee T. and Wilhelmsen, Cheryl A.},
+        title = {{Risk assessment: Tools, techniques, and their applications}},
+        publisher = {John Wiley \& Sons, Inc.},
+        isbn = {978-1119483465},
+        year = {2019}
     }

### 2022-06-22 proposal-documents/white-paper/white-paper-general-preproposal.tex

@@
 \usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+\setlength{\bibsep}{3pt} %sets space between references
+\renewcommand{\bibsection}{} %suppresses large 'references' heading
+%\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading
 %%%%%
@@
 \usepackage{tabto} %general tabbed spacing
+\usepackage{pdfpages}
+
+\usepackage{wrapfig} %wraps figures around text
+\setlength{\intextsep}{0.05mm}
+\setlength{\columnsep}{0.05mm}
 
@@
 \usepackage{subcaption}
-\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period,name={Tab.}} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+\captionsetup[table]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
+\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
 
-\usepackage{wrapfig} %wraps figures around text
-\setlength{\intextsep}{0.20mm}
-\setlength{\columnsep}{0.20mm}
+%\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=1pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+%\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Tab.}} %sets space above caption, 'figure' format
 %%%%%
@@
 \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
-\usepackage[toc,page]{appendix}
+\usepackage{marginnote}
+\usepackage{gensymb}
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
+\usepackage[toc,title]{appendix}
 \usepackage[figure,table]{totalcount}
-\usepackage[acronym,nomain,nonumberlist]{glossaries}
-\makenoidxglossaries
 
-\usepackage[firstpage]{draftwatermark}
+\usepackage[capitalise]{cleveref}
+
+%%%%% watermark
+%\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
 %\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-%\SetWatermarkScale{0.35}
-
-\usepackage{wrapfig}
-\setlength{\intextsep}{0.20mm}
-\setlength{\columnsep}{0.20mm}
+%\SetWatermarkScale{0.25}
+%%%%%
 
@@
 %\externaldocument{/path/to/auxfilename} %aux file needed
+
+%%%%% toc and glossaries
+\usepackage[acronym,nomain,nonumberlist]{glossaries}
+\makenoidxglossaries
+\usepackage{titlesec,titletoc}
+%\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
+%\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
+\titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
+\titlespacing\part{0pt}{0.75\baselineskip}{0.50\baselineskip}
+\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
+\titlespacing*\section{0pt}{0.55\baselineskip}{0.35\baselineskip}
+\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
+\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.30\baselineskip}
+\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
+\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
 
@@
 \newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
+\newcommandx{\por}[2][1=]{\todo[author=Porter,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
+%\newcommandx{\}[2][1=]{\todo[author=Sam,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
+%\newcommandx{\}[2][1=]{\todo[author=RAB,tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 \newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
 \newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\rab}[2][1=]{\todo[author=RAB,tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+\newcommandx{\rab}[2][1=]{\author=RAB,tickmarkheight=0.15cm,todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
 
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
 
@@
 
-\makeatletter
-\renewcommand\section{%
-    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
-    {\Large \normalfont \bfseries}}%
+%\makeatletter
+%\renewcommand\section{%
+%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
+%    {\large \normalfont \bfseries}}%
 
-\makeatletter
-\renewcommand\paragraph{%
-    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
-    {\normalfont \normalsize \bfseries}}%
+%\makeatletter
+%\renewcommand\paragraph{%
+%    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
+%    {\normalfont \normalsize \bfseries}}%
 
-\makeatletter
-\renewcommand\subparagraph{%
-    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
-    {\normalfont \normalsize \itshape }}%
+%\makeatletter
+%\renewcommand\subparagraph{%
+%    \@startsection{subparagraph}{5}{\z@ }{0.40\baselineskip}{-1em}
+%    {\normalfont \normalsize \itshape }}%
 
-\makeatletter
-\renewcommand\subsection{%
-    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
-    { \large \normalfont \bfseries}}%
+%\makeatletter
+%\renewcommand\subsection{%
+%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
+%    {\large \normalfont \bfseries}}%
 
-\setlength{\bibsep}{0pt} %sets space between references
-\renewcommand{\bibsection}{} %suppresses large 'references' heading
-\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading
-
+%%%%% header and footer
 \usepackage{fancyhdr}
@@
 \rfoot{\thepage}
+%%%%%
 
@@
 \newacronym{lms}{LMS}{Learning Management System}
+\newacronym{cps}{CPS}{Cyber-Physical Systems}
+\newacronym{nsf}{NSF}{National Science Foundation}
+\newacronym{wsc}{WSC}{Western Services Corporation}
+\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
+\newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{roi}{ROI}{Return on Investment}
+\newacronym{ic}{I\&C}{Instrumentation \& Controls}
+\newacronym{mwe}{MWe}{Megawatts-electric}
+\newacronym{ics}{ICS}{Industrial Control Systems}
+\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
+\newacronym{ip}{IP}{Internet Protocol}
+\newacronym{udp}{UDP}{User Datagram Protocol}
+\newacronym{tva}{TVA}{Tennessee Valley Authority}
+\newacronym{plc}{PLC}{Programmable Logic Controller}
+\newacronym{vfd}{VFD}{Variable Frequency Drive}
+\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
+\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
+\newacronym{mim}{MITM}{Man in the Middle}
+\newacronym{dos}{DDoS}{Distributed Denial of Service}
+\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
+\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
+\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
+\newacronym{cs}{CS}{Critical System}
+\newacronym{loc}{LOCA}{Loss of Coolant Accident}
+\newacronym{hmi}{HMI}{Human Machine Interface}
+\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
+\newacronym{bol}{BOL}{beginning-of-life}
+\newacronym{eol}{EOL}{end-of-life}
+\newacronym{mol}{MOL}{middle-of-life}
+\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
+\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{neu}{NEUP}{Nuclear Energy University Program}
+\newacronym{doe}{DOE}{United States Department of Energy}
+\newacronym{nei}{NEI}{Nuclear Energy Institute}
+\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
 %\newacronym{}{}{}
@@
     }
+    \vspace{0.10in}
     Name (PI) - Affiliation; Name (co-PI) - Affiliation\\
@@
 %may not be needed
-\begin{center}\subsection*{Abstract}\end{center}
+%\begin{center}\subsection*{Abstract}\end{center}
 
-\paragraph*{Summary of the Proposed Project.} 
-\subparagraph*{Proposal.}
+\section*{Summary of the Proposed Project} 
+\subsection*{Proposal}
+\subsection*{Key features of the project}
 
-\subparagraph*{Key features of the project.}
+\section*{Motivation}
+\subsection*{Context}
 
-\paragraph*{Motivation.}
-\subparagraph*{Context.}
+\section*{Overall Objective}
 
-\paragraph*{Overall Objective.}
-
-\subsection*{Research Focus and Workscopes.} 
-\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-    \item\textit{Workscope title (Lead - )}
-        \begin{itemize}[leftmargin=*,topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item Task 
-            \item Task 
-            \item Task 
-            \item Task 
-        \end{itemize}
-    \item\textit{Concluding work (Full team)}
-        \begin{itemize}[leftmargin=*,topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
-            \item Discuss crosscutting issues
-        \end{itemize}
+\section*{Workscopes in Brief}
+\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=0.5in]
+    \item\textbf{X.} (\textit{Lead - ; Support - , })
+        \begin{enumerate}[topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
+            \item\textit{x.}
+            \item\textit{x.}
+        \end{enumerate}
+    \item\textbf{X.} (\textit{Lead - ; Support - , })
+        \begin{enumerate}[resume,topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
+            \item\textit{x.}
+            \item\textit{x.}
+        \end{enumerate}
 \end{enumerate}
 
-\paragraph*{Importance and Relevance to Objectives.} 
-\subparagraph*{Background.}
+\section*{Importance and Relevance to Objectives} 
+\subsection*{Background}
 
-\subparagraph*{Relevant literature.}
+\subsection*{Relevant literature}
 
-\subparagraph*{Recently funded work.}
-%for a 3 page preproposal, limit above subject matter to the first page
-%research focus will have to go
+\subsection*{Recently funded work}
 
-\paragraph*{Unique project features.}
+\subsection*{Unique project features}
 
-\paragraph*{Logical Path, Work Scope, Description of Tasks.}
+\section*{Research Workscopes \& Tasks}
+\subsection*{Research activities}
 
-\paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
-\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{Title.}
-    \item\textit{Title.}
-    \item\textit{Title.}
+\subsection*{Workscope 1 - Title}
+\begin{enumerate}[topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{First task.}
+        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item Details.
+        \end{enumerate}
+    \item\textit{Second task.}
+        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item Details.
+        \end{enumerate}
 \end{enumerate}
 
-\paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
-\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{Title.}
-    \item\textit{Title.}
-    \item\textit{Title.}
+\vspace{0.05in}
+
+\noindent\textit{Through this Workscope, we will \ldots.}
+
+\subsection*{Workscope 2 - Title}
+\begin{enumerate}[resume,topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Next task.}
+        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item Details.
+        \end{enumerate}
+    \item\textit{Next task.}
+        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item Details.
+        \end{enumerate}
 \end{enumerate}
 
-\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
-\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{Crosscutting issues.}
-\end{enumerate}
+\vspace{0.05in}
 
-\paragraph*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
-We anticipate the following outcomes - 
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
+\noindent\textit{Through this Workscope, we will \ldots.}
+
+\section*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
+The following outcomes are anticipated - 
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
     \item
@@
 
-\paragraph*{Estimated Cost of the Project.} 
+\section*{Estimated Cost of the Project.} 
 We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
@@
 
+\part*{References}
+\bibliographystyle{nsf}
+\setlength{\bibhang}{0pt}
+\bibliography{references}
+
+%\newpage
+
+%\begin{appendices}
+
+%    \renewcommand{\thesection}{\Roman{section}}
+%    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]
+
+%\section{Title}\label{app-}
+
+%\end{appendices}
+
+%wrap figure around text
+%move to wherever in the text 
+%{l} fixes it on the left margin
+%{L} floats
+%\begin{wrapfigure}{l}{0.x\textwidth}
+%       \includegraphics[width=0.(x-2)\textwidth]{}
+%    \caption{}
+%    \label{fig-}
+%\end{wrapfigure}
+
+\end{document}
+
+\begin{document}
+
 \newpage

### 2022-06-22 proposal-documents/white-paper/white-paper-phd-proposal.tex

@@
 \usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+%\setlength{\bibsep}{7pt} %sets space between references
+\renewcommand{\bibsection}{} %suppresses large 'references' heading
+%\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading
 %%%%%
@@
 
-\begin{center}\subsection*{Abstract}\end{center}
+\section*{Summary of the Proposed Project}
 
-\paragraph*{Summary of the Proposed Project.}
+\section*{Motivation}
+\subsection*{Context}
 
-\paragraph*{Motivation.}
+\section*{Overall Objective}
 
-\paragraph*{Overall Objective.}
+\section*{Importance and Relevance to Objectives} 
+\subsection*{Background}
 
-\paragraph*{Importance and Relevance to Objectives.} 
-\subparagraph*{Background.}
+\subsection*{Relevant literature}
 
-\subparagraph*{Relevant literature.}
+\section*{Research Workscopes \& Tasks}
+\subsection*{Research activities}
 
-%for a 3 page preproposal, limit above subject matter to the first page
-
-\paragraph*{Logical Path, Work Scope, Description of Tasks.}
-
-\paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
-\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{Title.}
-    \item\textit{Title.}
-    \item\textit{Title.}
+\subsection*{Workscope 1 - Title}
+\begin{enumerate}[topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{First task.}
+        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item Details.
+        \end{enumerate}
+    \item\textit{Second task.}
+        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item Details.
+        \end{enumerate}
 \end{enumerate}
 
-\paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
-\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{Title.}
-    \item\textit{Title.}
-    \item\textit{Title.}
+\vspace{0.05in}
+
+\noindent\textit{Through this Workscope, we will \ldots.}
+
+\subsection*{Workscope 2 - Title}
+\begin{enumerate}[resume,topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
+    \item\textit{Next task.}
+        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item Details.
+        \end{enumerate}
+    \item\textit{Next task.}
+        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item Details.
+        \end{enumerate}
 \end{enumerate}
 
-\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
-\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{Crosscutting issues.}
-\end{enumerate}
+\vspace{0.05in}
 
-\paragraph*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
+\noindent\textit{Through this Workscope, we will identify plant systems vulnerable to cyberattacks applying a risk-informed approach and operate the reactor to collect relevant plant data.}
+
+\section*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
 The following outcomes are anticipated - 
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
     \item
@@
 
-%remove page break if there are page limits
-%\vspace{0.5\baselineskip}
-
-\paragraph*{References}
+\part*{References}
 \bibliographystyle{nsf}
@@
 \bibliography{references}
+
+%\newpage
+
+%\begin{appendices}
+
+%    \renewcommand{\thesection}{\Roman{section}}
+%    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]
+
+%\section{Title}\label{app-}
+
+%\end{appendices}
 

### 2022-06-24 proposal-documents/white-paper/white-paper-general-preproposal.tex

@@
 \section*{Workscopes in Brief}
-\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=0.5in]
-    \item\textbf{X.} (\textit{Lead - ; Support - , })
-        \begin{enumerate}[topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
-            \item\textit{x.}
-            \item\textit{x.}
+\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - , })
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
         \end{enumerate}
-    \item\textbf{X.} (\textit{Lead - ; Support - , })
-        \begin{enumerate}[resume,topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
-            \item\textit{x.}
-            \item\textit{x.}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{Identify lessons learned.}
+            \item\textit{Develop future work.}
+            \item\textit{Reproducibility \& validation.}
         \end{enumerate}
@@
 \subsection*{Research activities}
+Overview.
 
-\subsection*{Workscope 1 - Title}
-\begin{enumerate}[topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{First task.}
-        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - , })
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
                     \item Details.
                 \end{enumerate}
-    \item\textit{Second task.}
-        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
                     \item Details.
@@
         \end{enumerate}
+\end{enumerate}
 
-\vspace{0.05in}
+\paragraph*{Motivation}
 
-\noindent\textit{Through this Workscope, we will \ldots.}
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
 
-\subsection*{Workscope 2 - Title}
-\begin{enumerate}[resume,topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{Next task.}
-        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
                     \item Details.
                 \end{enumerate}
-    \item\textit{Next task.}
-        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
                     \item Details.
@@
         \end{enumerate}
+\end{enumerate}
 
-\vspace{0.05in}
+\paragraph*{Motivation}
 
-\noindent\textit{Through this Workscope, we will \ldots.}
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{Identify lessons learned.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{Develop future work.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{Reproducibility \& validation.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will wrapup the major findings of project activities and pursue new avenues of research with colleagues in the field.}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
 

### 2022-06-24 proposal-documents/white-paper/white-paper-phd-proposal.tex

@@
 
+\section*{Workscopes in Brief}
+\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - , })
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{Identify lessons learned.}
+            \item\textit{Develop future work.}
+            \item\textit{Reproducibility \& validation.}
+        \end{enumerate}
+\end{enumerate}
 \section*{Importance and Relevance to Objectives} 
@@
         \end{enumerate}
+\end{enumerate}
 
-\vspace{0.05in}
+\paragraph*{Motivation}
 
-\noindent\textit{Through this Workscope, we will identify plant systems vulnerable to cyberattacks applying a risk-informed approach and operate the reactor to collect relevant plant data.}
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
 
-\section*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
-The following outcomes are anticipated - 
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
-    \item
-    \item
-    \item
-    \item Identify lessons learned and engage in future pathways and partnerships.
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
                 \end{enumerate}
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{Identify lessons learned.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{Develop future work.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{Reproducibility \& validation.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will wrapup the major findings of project activities and pursue new avenues of research with colleagues in the field.}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\newpage
 

### 2022-07-07 acronyms/acronyms.tex
acronyms update

%%%%%%put this in preamble
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries
%%%%%

%%%%% put this in right before draft
%%%%% acronyms
% alphabetical ordering is automated
\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
\newacronym{anl}{ANL}{Argonne National Laboratory}
\newacronym{inl}{INL}{Idaho National Laboratory}
\newacronym{npp}{NPP}{Nuclear Power Plant}
\newacronym{nrs}{NHRES}{Nuclear Renewable Hybrid Energy System}
\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
\newacronym{smr}{SMR}{Small Modular Reactor}
\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
\newacronym{nus}{NuScale}{NuScale Power, LLC}
\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
\newacronym{epri}{EPRI}{Electric Power Research Institute}
\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
\newacronym{ci}{CI}{Consistency Index}
\newacronym{cr}{CR}{Consistency Ratio}
\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
\newacronym{lwr}{LWR}{Light Water Reactor}
\newacronym{aps}{APS}{Arizona Public Service} 
\newacronym{arm}{ARMA}{Autoregressive Moving Average} 
\newacronym{eia}{EIA}{Energy Information Agency}
\newacronym{epa}{EPA}{Environmental Protection Agency}
\newacronym{hx}{HX}{Heat exchanger} 
\newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
\newacronym{mwe}{MWe}{Megawatts electricity}
\newacronym{mwt}{MWth}{Megawatts thermal energy}
\newacronym{ies}{IES}{Integrated Energy System} 
\newacronym{pv}{PV}{Palo Verde Generating Station} 
\newacronym{rav}{RAVEN}{Risk Analysis Virtual Environment} 
\newacronym{ro}{RO}{Reverse Osmosis} 
\newacronym{rom}{ROM}{Reduced Order Model} 
\newacronym{spe}{SPECO}{Specific Exergy Costing} 
\newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
\newacronym{ieo}{IESO}{Independent Electricity System Operator}
\newacronym{us}{US}{United States}
\newacronym{med}{MED}{Multiple-Effect Distillation}
\newacronym{ed}{ED/EDR}{Electrodialysis Reversal}
\newacronym{nf}{NF}{Nanofiltration}
\newacronym{jls}{J}{Joules}
\newacronym{nre}{NREI}{Nuclear Renewable Energy Integration}
\newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
\newacronym{iso}{ISO}{Independent System Operator} 
\newacronym{msf}{MSF}{Multi-Stage Flash} 
\newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
\newacronym{un}{UN}{United Nations}
\newacronym{ict}{ICT}{Information and communications technologies}
\newacronym{nws}{NWS}{Nuclear Weapons States}
\newacronym{nnws}{NNWS}{Non Nuclear Weapons States}
\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
\newacronym{snm}{SNM}{Special Nuclear Material}
\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
\newacronym{nnsa}{NNSA}{National Nuclear Security Administration}
\newacronym{fbi}{FBI}{Federal Bureau of Investigation}
\newacronym{nsg}{NSG}{Nuclear Suppliers Group}
\newacronym{mad}{MAD}{Mutually Assured Destruction}
\newacronym{wmd}{WMD}{Weapons of Mass Destruction}
\newacronym{sq}{SQ}{Significant Quantity}
\newacronym{der}{DER}{Distributed Energy Resource}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
\newacronym{usa}{US}{United States}
\newacronym{doe}{DOE}{United States Department of Energy}
\newacronym{pfc}{PFC}{Primary Frequency Control}
\newacronym{sfc}{SFC}{Secondary Frequency Control}
\newacronym{ace}{ACE}{Area Control Error}
\newacronym{var}{VAr}{Volt-Amps Reactive}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{nyi}{NYISO}{New York Independent System Operator}
\newacronym{ac}{AC}{Alternating Current}
\newacronym{dc}{DC}{Direct Current}
\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
\newacronym{inc}{I\&C}{Instrumentation and Controls}
%%%%%

%%%%%put this in the document where the acronym list will appear - Acronyms is in section format
\printnoidxglossary%[title{}] %removes automated Acronyms title too add custom
%%%%%

### 2022-07-07 journal/reviewer-response/JOURNALID-RX.tex
new reviewer response upgrade

--- 2021-07-28 manuscript/document-package/draft-manuscript/draft-manuscript.tex
@@
 \setcounter{secnumdepth}{5} %set subsection to nth level
+%\usepackage{mypythonhighlight}
+%\usepackage{lipsum}
 
@@
 \usepackage{subcaption}
-\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
+\captionsetup[table]{justification=centering,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
+\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
 
-\usepackage{wrapfig} %wraps figures around text
-\setlength{\intextsep}{0.20mm}
-\setlength{\columnsep}{0.20mm}
+%\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=1pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+%\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Tab.}} %sets space above caption, 'figure' format
 %%%%%
 
-\usepackage{tabto} %general tabbed spacing
 \usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-\usepackage{enumitem}
+\usepackage[inline]{enumitem}
 \usepackage{boldline}
@@
 \usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
+\usepackage{marginnote}
+\usepackage[toc,title]{appendix}
+\usepackage[figure,table]{totalcount}
 
-\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
-\usepackage[toc,page]{appendix}
-\usepackage[figure,table]{totalcount}
+\usepackage[capitalise]{cleveref}
+
+%\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
+%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+%\SetWatermarkScale{0.20}
+
+%to crossref between files
+%clear both directories
+%pdflatex manuscript first
+%pdflatex this file next
+%manuscript needs correponding code here with /path/to/this-file
+\usepackage{xr}
+\externaldocument{/path/to/manuscript} %crossref through aux file
+
+\makeatletter %make text labels
+\newcommand{\labeltext}[3][]{%
+    \@bsphack%
+    \csname phantomsection\endcsname %in case hyperref is used
+    \def\tst{#1}%
+    \def\labelmarkup{} %how to markup the label itself
+    %\def\refmarkup{\labelmarkup} %How to markup the reference
+    \def\refmarkup{}%
+    \ifx\tst\empty\def\@currentlabel{\refmarkup{#2}}{\label{#3}}%
+    \else\def\@currentlabel{\refmarkup{#1}}{\label{#3}}\fi%
+    \@esphack%
+    \labelmarkup{#2}% visible printed text.
+}
+
+%%%%% toc and glossaries
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
 \makenoidxglossaries
+\usepackage{titlesec,titletoc}
+%\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
+%\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
 
-%\usepackage{xr} %for revisions - will cross reference from one file to here
-%\externaldocument{/path/to/auxfilename} %aux file needed
+\titleformat{\part}{\normalfont\large\bfseries\filcenter}{\thepart}{}{}[]
+\titlespacing\part{0pt}{0.75\baselineskip}{0.50\baselineskip}
 
-%%%%% user shortcuts
+\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
+\titlespacing*\section{0pt}{0.55\baselineskip}{0.35\baselineskip}
+
+\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
+\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.30\baselineskip}
+
+\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+\titlespacing*\paragraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
+
+%\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
+%\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
+
+\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
+
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Manuscript ID - Load following}
-\chead{\scriptsize \textit{First Author et al. - Draft Manuscript}}
+\lhead{\scriptsize JOURNAL-ID}
+\chead{\scriptsize \textit{Author et al.} - Reviewer X}
 \rhead{\scriptsize \today}
-\rfoot{\thepage}
+\rfoot{\thepage} %move page number to bottom right
 %%%%%
@@
 \begin{filecontents}{references.bib} 
-        @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
-    }
-    @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
-    }
-    @incollection{
-        mil17a,
-        author = {Miller, Steven E.},
-        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
-        booktitle = {Understanding Cyber Conflict: 14 Analogies},
-        publisher = {Georgetown University Press},
-        year = {2017},
-        editor = {Perkovich, George and Levite, Ariel E.},
-        pages = {161}
-    }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
 \end{filecontents}
@@
 %%%%% acronyms
-% alphabetical ordering is automated
-%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
 %\newacronym{}{}{}
 %%%%%
-
-%\newacronym{}{}{}
 
@@
 \begin{titlepage}
-    \title{}
+    \title{Title}
     \author{
-        , 
-        , 
-        \textsuperscript{*}
+        Author 1, 
+        Author 2, 
+        \textsuperscript{*}Author 3
         \\ \\ \\
-        \\
-
+        Affiliation
         \\ \\ \\
-        \textsuperscript{*}
+        \textsuperscript{*}rborrelli@uidaho.edu
+        \\ \\ \\ 
+        Response to Reviewer
     }
@@
 \maketitle
-\vspace*{\fill}
-\begin{flushright}{
-        \noindent Number of pages - \pageref{LastPage} \\
-        \noindent Number of tables - \totaltables \\
-        \noindent Number of figures - \totalfigures 
-}
-\end{flushright}
 \thispagestyle{empty} %start with page number 1 on second page
@@
 
-%%%%% spacing options
-\onehalfspacing %linespacing
-%\setstretch{1.05} %linespacing
-%\spacing{1.25} %equivalent to 1.5 line spacing in Word
+\part*{Reviewer X}
 
-%%%%% linenumbering
-\linenumbers %toggle line numbers
-\pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[3] %line numbering interval
-%%%%%
+\noindent Thank you for the peer review of this manuscript.
+Each comment was considered carefully.
+The manuscript has been revised accordingly in the hope that the updated paper is worthy of publication.
+A detailed response to each comment is provided in this document.
 
-\section*{Abstract}
+\section*{General comments}
+\begin{enumerate}[series=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
+    \item Comment
+\end{enumerate}
 
-\newpage
+\subsection*{Response}
+Response
 
-\printnoidxglossary
+\paragraph*{Revisions}
+Revisions
+\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
+    \item\labeltext{Statement.}{1-label}
+\end{enumerate}
 
-\newpage
+\begin{enumerate}[resume=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
+    \item Comment
+\end{enumerate}
 
-\section{Introduction} \label{sec-intro}
+\subsection*{Response}
+Response
 
-\subsection{Motivation} \label{sec-motiv}
-
-\subsection{Goals} \label{sec-goals}
-
-\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
-    \item 
-    \item  
-    \item 
+\paragraph*{Revisions}
+Revisions
+\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
+    \item\labeltext{Statement.}{1-label-2}
 \end{enumerate}
@@
 
-\section{Background} \label{sec-bak}
+\section*{Editorial comments}
+\begin{enumerate}[series=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
+    \item Abstract 1 - \labeltext{`...essential components \textit{to} back-end...' $\rightarrow$ `...essential components \textit{of} back-end...'}{1-ed1}
+\end{enumerate}
 
-\newpage
+\subsection*{Response}
+\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
+    \item Reply
+\end{enumerate}
 
-\section{Theory} \label{sec-theo}
+\begin{enumerate}[resume=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
+    \item Abstract 1 - \labeltext{`...essential components \textit{to} back-end...' $\rightarrow$ `...essential components \textit{of} back-end...'}{1-ed1}
+\end{enumerate}
 
-\newpage
+\subsection*{Response}
+\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
+    \item Reply
+\end{enumerate}
 
-\section{Methodology} \label{sec-meth}
+%\newpage
 
-\newpage
-
-\section{Results} \label{sec-res}
-\subsection{Objective} \label{sec-obj}
-
-\newpage
-
-\section{Discussion} \label{sec-disc}
-
-\newpage
-
-\section{Future work} \label{sec-fwk}
-
-\newpage
-
-\section{Summary remarks} \label{sec-sum}
-
-Major results and implications include - 
-\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
-    \item
-    \item
-    \item
-\end{itemize}
-
-\newpage
-
-\section*{Acknowledgements}
-
-\newpage
-
-\bibliographystyle{standard}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
-
-\newpage
-
-\section*{Tables}
-
-{%
-\let\oldnumberline\numberline%
-\renewcommand{\numberline}{\tablename~\oldnumberline}%
-\listoftables%
-}
-
-\newpage
-
-%\begin{table}[h!]
-%    \centering
-%    \caption{Title}
-%        \begin{tabular}{|c|c|c|c|}
-%            \hline
-%            A&
-%            B&
-%            C&
-%            D
-%            \\
-%            \hline
-%            X
-%            &X
-%            &X
-%            &X
-%            \\
-%            \hline
-%        \end{tabular}
-%    \label{tab-label}
-%\end{table}
-
-\newpage
-
-%\begin{spacing}{1}
-%\begin{longtable}{|c|c|c|c|c|}
-%    \caption{Title}
-%    \label{tab-label-name} \\
-%    \hline
-%    \multicolumn{1}{|c|}{A}&
-%    \multicolumn{1}{c|}{B}&
-%    \multicolumn{1}{c|}{C}&
-%    \multicolumn{1}{c|}{D}&
-%    \multicolumn{1}{c|}{E}
-%    \\
-%    \hline
-%    \endfirsthead
-%    \multicolumn{5}{c}{{\tablename\ \thetable{} - continued}} \\
-%    \hline
-%    \multicolumn{1}{|c|}{A}&
-%    \multicolumn{1}{c|}{B}&
-%    \multicolumn{1}{c|}{C}&
-%    \multicolumn{1}{c|}{D}&
-%    \multicolumn{1}{c|}{E}
-%    \\
-%    \hline
-%    \endhead
-%    \hline
-%    \endfoot
-%    \hline
-%    \endlastfoot
-%    X
-%    &X
-%    &X
-%    &X
-%    &X
-%    \\
-%    \hline
-%\end{longtable}
-%\end{spacing}
-
-\newpage
-
-\section*{Figures}
-
-{%
-\let\oldnumberline\numberline%
-\renewcommand{\numberline}{\figurename~\oldnumberline}%
-\listoffigures%
-}
-
-\newpage
-
-%\begin{figure}[h!]
-%    \centering
-%    \includegraphics[width=0.X\textwidth]{.png}
-%    \caption{}
-%    \label{fig-label-name}
-%\end{figure}
-
-\newpage
-
-%\appendix
-
-%\begin{appendices}
-
-%\renewcommand{\thesection}{\Roman{section}}
-
-%\section{} \label{}
-
-%\end{appendices}
+%\part*{References}
+%\bibliographystyle{nsf}
+%\setlength{\bibhang}{0pt}
+%\bibliography{references}
 

### 2022-08-07 presenations/general/general.tex
latex presentation general

--- 2021-08-10 manuscript/document-package/draft-manuscript/draft-manuscript.tex
@@
-%@TheDoctorRAB
-%Use for original, revised, clean manuscripts
-%
-%%%%%
-%
-%REFERENCES
-%
-%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
-%nsf.bst - numbered citations in order of appearance, full author list in references section
-%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
-%ans.bst is for ANS only. 
-%
-%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
-%bst renders the author list itself
-%
-%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
-%
-%title = {{}} for all
-%
-%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
-%standard.bst \cite{-} - Borrelli (2021) in the text
-%standard.bst lists references alphabetically
-%the rest list numerically
-%select reference style line 54
-%
-%%%%%
-%
-\documentclass[11pt,a4paper]{article}
-\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
-\usepackage[pagewise]{lineno} %line numbering
-\usepackage{setspace}
-\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
-\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
-\usepackage{graphicx}
-\usepackage{filecontents}
-\usepackage{footnotehyper}
-%\usepackage{subfig}
+\documentclass[aspectratio=1610,pdftex,dvipsnames,compress]{beamer}
+\usetheme{Boadilla}
+\usecolortheme{seahorse}
+\beamertemplatenavigationsymbolsempty
+
+\addtobeamertemplate{footnote}{\hskip -2em}{} %pushes footnote to margin
+
+\setbeamerfont{title}{series=\bfseries}
+
+\setbeamertemplate{page number in head/foot}[framenumber] %Just gives slide number; comment out for 1/7, 2/7, etc.
+
+\definecolor{BackGround}{RGB}{255,250,240}
+\setbeamercolor{background canvas}{bg=BackGround}
+
+\usepackage{caption}
+\captionsetup[figure]{labelformat=empty}
+
+%packages and definitions
+\usepackage{enumitem}
+\setlist[itemize]{label=\textbullet}
+\usepackage{nicefrac}
+\usepackage{ulem}
+\usepackage{graphicx,animate}
+\usepackage{mypythonhighlight}% allows inclusion of graphics
+\graphicspath{{../img/}} %path to graphics
 \usepackage[yyyymmdd]{datetime} %date format
 \renewcommand{\dateseparator}{.}
-\graphicspath{{../img/}} %path to graphics
-\setcounter{secnumdepth}{5} %set subsection to nth level
 
-%%%%% fonts
-\usepackage{times}
-%arial - uncomment next two lines
-%\usepackage{helvet}
-%\renewcommand{\familydefault}{\sfdefault}
+%%%%%
+\usepackage{pgf}
+\usepackage{tikz} % required for drawing custom shapes
+\usetikzlibrary{shapes,arrows,automata,trees}
 %%%%%
 
-%%%%% references
-\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
-%\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
-%%%%%
+\usepackage{booktabs} % nice rules (thick lines) for tables
+\usepackage{microtype} % improves typography for PDF
 
-%%%%% tables and figures
-\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
-\usepackage{tablefootnote}
-\usepackage{tabularx}
-\usepackage{multirow}
-
-\usepackage[singlelinecheck=false,labelfont=bf]{caption}
-\usepackage{subcaption}
-\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
-\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format
-
-\usepackage{wrapfig} %wraps figures around text
-\setlength{\intextsep}{0.20mm}
-\setlength{\columnsep}{0.20mm}
-%%%%%
-
-\usepackage{tabto} %general tabbed spacing
-\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-\usepackage{enumitem}
-\usepackage{boldline}
-\usepackage{makecell}
-\usepackage{booktabs}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{physics}
-\usepackage{lscape}
-\usepackage{array}
-\usepackage{chngcntr}
-%\usepackage{hyperref}
-\usepackage{sectsty}
-\usepackage{textcomp}
-\usepackage{lastpage}
-\usepackage{xargs} %for \newcommandx
-
-\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
-\usepackage[toc,page]{appendix}
-\usepackage[figure,table]{totalcount}
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
@@
 
-%\usepackage{xr} %for revisions - will cross reference from one file to here
-%\externaldocument{/path/to/auxfilename} %aux file needed
+\usepackage{xcolor,colortbl} %change font color
+\usepackage[numbers,sort&compress]{natbib} 
+\usepackage{bibentry}
 
-%%%%% user shortcuts
+\setlength{\bibsep}{0pt} %sets space between references
+%\renewcommand{\bibsection}{} %suppresses large 'references' heading
+\renewcommand\bibpreamble{\vspace{-0.2\baselineskip}} %sets spacing after heading if not using default references heading
+
+%\begin{filecontents}{references.bib}
+%\end{filecontents}
+
+%%%%% user commands
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  \addtocounter{footnote}{-1}%
+  \endgroup
+}
+
+\makeatletter
+\renewcommand{\@biblabel}[1]{#1.\hfill} %bibliography ordered list has numbers left flush
+\makeatother
+
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
@@
 \newcommand{\acs}{\acrshort} %short acronym
-
 \newcommand{\acfp}{\acrfullpl} %full acronym plural
@@
 \newcommand{\acsp}{\acrshortpl} %short acronym plural
-
-\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
-\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
-\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\omt}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
-
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}} %uses \raggedright with p{} in table column
-
-\makeatletter
-\renewcommand\tableofcontents{%
-    \@starttoc{toc}%
-}
-\makeatother
-
-\makeatletter
-\renewcommand\listoffigures{%
-    \@starttoc{lof}%
-}
-\makeatother
-
-\makeatletter
-\renewcommand\listoftables{%
-    \@starttoc{lot}%
-}
-\makeatother
-
-\makeatletter
-\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
-\makeatother
-
-%\makeatletter
-%\renewcommand\section{%
-%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
-%    {\normalfont \normalsize \bfseries}}%
-
-%\makeatletter
-%\renewcommand\paragraph{%
-%    \@startsection{paragraph}{4}{\z@ }{0.25\baselineskip}{-1em}
-%    {\normalfont \normalsize \bfseries}}%
-
-%\makeatletter
-%\renewcommand\subparagraph{%
-%    \@startsection{subparagraph}{5}{\z@ }{0.20\baselineskip}{-1em}
-%    {\normalfont \normalsize \itshape }}%
-
-%\makeatletter
-%\renewcommand\subsection{%
-%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
-%    { \large \normalsize \bfseries}}%
-
-%\setlength{\bibsep}{0pt} %sets space between references
-%\renewcommand{\bibsection}{} %suppresses large 'references' heading
-%\renewcommand\bibpreamble{\vspace{-0.30\baselineskip}} %sets spacing after heading if not using default references heading
+\newcommand{\Acf}{\Acrfull} %full acronym first letter capital
+\newcommand{\Acl}{\Acrlong} %long acronym first letter capital
 %%%%%
 
-%%%%% header and footer
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhf{} %move page number to bottom right
-%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Manuscript ID - Load following}
-\chead{\scriptsize \textit{First Author et al. - Draft Manuscript}}
-\rhead{\scriptsize \today}
-\rfoot{\thepage}
+%%%%%
+\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
+\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
+\newacronym{inl}{INL}{Idaho National Laboratory}
+\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{anl}{ANL}{Argonne National Laboratory}
+\newacronym{npp}{NPP}{Nuclear Power Plant}
+\newacronym{smr}{SMR}{Small Modular Reactor}
+\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
+\newacronym{nus}{NuScale}{NuScale Power, LLC}
+\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
+\newacronym{ci}{CI}{Consistency Index}
+\newacronym{cr}{CR}{Consistency Ratio}
+\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
+\newacronym{lwr}{LWR}{Light Water Reactor}
+\newacronym{eia}{EIA}{U.S. Energy Information Administration}
+\newacronym{oer}{OER}{Online Educational Resource}
+\newacronym{lms}{LMS}{Learning Management System}
+\newacronym{cps}{CPS}{Cyber-Physical Systems}
+\newacronym{nsf}{NSF}{National Science Foundation}
+\newacronym{wsc}{WSC}{Western Services Corporation}
+\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
+\newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{roi}{ROI}{Return on Investment}
+\newacronym{ic}{I\&C}{Instrumentation \& Controls}
+\newacronym{mwe}{MWe}{Megawatts-electric}
+\newacronym{ics}{ICS}{Industrial Control Systems}
+\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
+\newacronym{ip}{IP}{Internet Protocol}
+\newacronym{udp}{UDP}{User Datagram Protocol}
+\newacronym{tva}{TVA}{Tennessee Valley Authority}
+\newacronym{plc}{PLC}{Programmable Logic Controller}
+\newacronym{vfd}{VFD}{Variable Frequency Drive}
+\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
+\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
+\newacronym{mim}{MITM}{Man in the Middle}
+\newacronym{dos}{DDoS}{Distributed Denial of Service}
+\newacronym{ds}{DoS}{denial-of-service}
+\newacronym{MM}{MiTM}{Man in the Middle}
+\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
+\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
+\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
+\newacronym{cs}{CS}{Critical System}
+\newacronym{loca}{LOCA}{Loss of Coolant Accident}
+\newacronym{hmi}{HMI}{Human Machine Interface}
+\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
+\newacronym{bol}{BOL}{beginning-of-life}
+\newacronym{eol}{EOL}{end-of-life}
+\newacronym{mol}{MOL}{middle-of-life}
+\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
+\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{neu}{NEUP}{Nuclear Energy University Program}
+\newacronym{doe}{DOE}{United States Department of Energy}
+\newacronym{nei}{NEI}{Nuclear Energy Institute}
+\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
+\newacronym{rcs}{RCS}{Reactor Cooling System}
+\newacronym{generic}{GPWR}{Generic Pressurized Water Reactor}
+\newacronym{pcap}{PCAP}{packet capture file}
 %%%%%
 
-\begin{filecontents}{references.bib} 
-    @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
+\title[Short title for footer]{Long title for title page}
+
+\author[Short author for footer]{
+    Name\\
+    \vspace{0.25in}
+    Another name\\
+    \vspace{0.05in}
+    \includegraphics{img/} 
+    \includegraphics{img/}
 }
-    @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
+
+\institute[Short institute for footer]{
+    \vspace{0.05in}
+    Institution\\
+    Subtitle\\
+    \vspace{0.10in}
+    Subtitle\\
+    \vspace{0.15in}
+    \includegraphics[width=0.20\textwidth]{logo}
     }
-    @incollection{
-        mil17a,
-        author = {Miller, Steven E.},
-        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
-        booktitle = {Understanding Cyber Conflict: 14 Analogies},
-        publisher = {Georgetown University Press},
-        year = {2017},
-        editor = {Perkovich, George and Levite, Ariel E.},
-        pages = {161}
-    }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
-    @book{
-        saa80a,
-        author = {Saaty, Thomas L.},
-        title = {{The analytical hierarchy process}},
-        publisher = {{McGraw-Hill, Inc.}},
-        year = {1980},
-        address = {New York}
-    }
-\end{filecontents}
 
-%%%%% acronyms
-% alphabetical ordering is automated
-%\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
-%\newacronym{}{}{}
-%%%%%
-
-%\newacronym{}{}{}
+\date{\today}
 
@@
 
-\begin{titlepage}
-    \title{}
-    \author{
-        , 
-        , 
-        \textsuperscript{*}
-        \\ \\ \\
-        \\
-
-        \\ \\ \\
-        \textsuperscript{*}
-    }
-\clearpage %not have page number on title page
-\maketitle
-\vspace*{\fill}
-\begin{flushright}{
-        \noindent Number of pages - \pageref{LastPage} \\
-        \noindent Number of tables - \totaltables \\
-        \noindent Number of figures - \totalfigures 
-}
-\end{flushright}
-\thispagestyle{empty} %start with page number 1 on second page
-\end{titlepage}
-
-%%%%% spacing options
-\onehalfspacing %linespacing
-%\setstretch{1.05} %linespacing
-%\spacing{1.25} %equivalent to 1.5 line spacing in Word
-
-%%%%% linenumbering
-\linenumbers %toggle line numbers
-\pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[3] %line numbering interval
-%%%%%
-
-\section*{Abstract}
-
-\newpage
-
-\printnoidxglossary
-
-\newpage
-
-\section{Introduction} \label{sec-intro}
-
-\subsection{Motivation} \label{sec-motiv}
-
-\subsection{Goals} \label{sec-goals}
-
-\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
-    \item 
-    \item  
-    \item 
-\end{enumerate}
-
-\newpage
-
-\section{Background} \label{sec-bak}
-
-\newpage
-
-\section{Theory} \label{sec-theo}
-
-\newpage
-
-\section{Methodology} \label{sec-meth}
-
-\newpage
-
-\section{Results} \label{sec-res}
-\subsection{Objective} \label{sec-obj}
-
-\newpage
-
-\section{Discussion} \label{sec-disc}
-
-\newpage
-
-\section{Future work} \label{sec-fwk}
-
-\newpage
-
-\section{Summary remarks} \label{sec-sum}
-
-Major results and implications include - 
-\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
-    \item
-    \item
-    \item
-\end{itemize}
-
-\newpage
-
-\section*{Acknowledgements}
-
-\newpage
-
-\bibliographystyle{standard}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
-
-\newpage
-
-\section*{Tables}
-
-{%
-\let\oldnumberline\numberline%
-\renewcommand{\numberline}{\tablename~\oldnumberline}%
-\listoftables%
+%%%%% title page with no footer
+{
+    \setbeamertemplate{footline}{} 
+    \begin{frame}
+        \titlepage
+    \end{frame}
 }
 
-\newpage
+\begin{frame}{Title}
+    \begin{enumerate}[label=(\arabic*),leftmargin=*,itemsep=7pt]
+        \item .
+        \item .
+        \item .
+    \end{enumerate}
+    \vspace{0.25in}
+    \begin{itemize}[leftmargin=*,itemsep=7pt]
+        \item .
+        \item . 
+    \end{itemize}
+\end{frame}
 
-%\begin{table}[h!]
+\begin{frame}{Title}
+    \begin{itemize}[leftmargin=*,itemsep=7pt]
+        \item .  
+        \item .
+        \item .
+    \end{itemize}
+\end{frame}
+
+%\begin{frame}{Title}
+%    \begin{itemize}
+%            \only<1-2>{
+%            \item .
+%            }
+%
+%            \only<2>{
+%            \item .
+%            \item . \citep{citation}
+%            }
+%    \end{itemize}
+%
+%    \only<2>{
+%        \blfootnote{\tiny\cite{citation}\tiny\bibentry{citation}}
+%    }
+%\end{frame}
+
+%\begin{frame}{Title}
+%    \begin{itemize}
+%        \item . \citep{ref}
+%        \item . \citep{ref}
+%    \end{itemize}
+%    \blfootnote{\tiny\cite{ref}\tiny\bibentry{ref}}
+%    \blfootnote{\tiny\cite{ref}\tiny\bibentry{ref}}
+%\end{frame}
+
+%\begin{frame}{Title}
+%    \begin{columns}
+%        \begin{column}{0.75\textwidth}
+%            \begin{figure}
 %                \centering
-%    \caption{Title}
-%        \begin{tabular}{|c|c|c|c|}
-%            \hline
-%            A&
-%            B&
-%            C&
-%            D
-%            \\
-%            \hline
-%            X
-%            &X
-%            &X
-%            &X
-%            \\
-%            \hline
-%        \end{tabular}
-%    \label{tab-label}
-%\end{table}
+%                \includegraphics[width=0.95\textwidth]{figure}
+%                \caption{}
+%            \end{figure}
+%        \end{column}
+%
+%        \begin{column}{0.25\textwidth}
+%            \begin{itemize}
+%                \item .
+%                \item .
+%                \item .
+%            \end{itemize}
+%        \end{column}
+%    \end{columns}
+%\end{frame}
 
-\newpage
+%\begin{frame}{Acknowledgements}
+%    \centering
+%    Research was funded by .
+%\end{frame}
 
-%\begin{spacing}{1}
-%\begin{longtable}{|c|c|c|c|c|}
-%    \caption{Title}
-%    \label{tab-label-name} \\
-%    \hline
-%    \multicolumn{1}{|c|}{A}&
-%    \multicolumn{1}{c|}{B}&
-%    \multicolumn{1}{c|}{C}&
-%    \multicolumn{1}{c|}{D}&
-%    \multicolumn{1}{c|}{E}
-%    \\
-%    \hline
-%    \endfirsthead
-%    \multicolumn{5}{c}{{\tablename\ \thetable{} - continued}} \\
-%    \hline
-%    \multicolumn{1}{|c|}{A}&
-%    \multicolumn{1}{c|}{B}&
-%    \multicolumn{1}{c|}{C}&
-%    \multicolumn{1}{c|}{D}&
-%    \multicolumn{1}{c|}{E}
-%    \\
-%    \hline
-%    \endhead
-%    \hline
-%    \endfoot
-%    \hline
-%    \endlastfoot
-%    X
-%    &X
-%    &X
-%    &X
-%    &X
-%    \\
-%    \hline
-%\end{longtable}
-%\end{spacing}
-
-\newpage
-
-\section*{Figures}
-
-{%
-\let\oldnumberline\numberline%
-\renewcommand{\numberline}{\figurename~\oldnumberline}%
-\listoffigures%
-}
-
-\newpage
-
-%\begin{figure}[h!]
-%    \centering
-%    \includegraphics[width=0.X\textwidth]{.png}
-%    \caption{}
-%    \label{fig-label-name}
-%\end{figure}
-
-\newpage
-
-%\appendix
-
-%\begin{appendices}
-
-%\renewcommand{\thesection}{\Roman{section}}
-
-%\section{} \label{}
-
-%\end{appendices}
+%\begin{frame}{References}
+%    \bibliographystyle{neup}
+%    \footnotesize
+%    \bibliography{references}
+%\end{frame}
 

### 2022-08-23 acronyms/acronyms.tex
update acronym

@@
 % alphabetical ordering is automated
+\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
+\newacronym{anl}{ANL}{Argonne National Laboratory}
+\newacronym{bol}{BOL}{beginning-of-life}
+\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{ci}{CI}{Consistency Index}
+\newacronym{cps}{CPS}{Cyber-Physical Systems}
+\newacronym{cr}{CR}{Consistency Ratio}
+\newacronym{cs}{CS}{Critical System}
+\newacronym{doe}{DOE}{United States Department of Energy}
+\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
+\newacronym{dos}{DDoS}{Distributed Denial of Service}
+\newacronym{eia}{EIA}{U.S. Energy Information Administration}
+\newacronym{eol}{EOL}{end-of-life}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{hmi}{HMI}{Human Machine Interface}
+\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
+\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
+\newacronym{ic}{I\&C}{Instrumentation \& Controls}
+\newacronym{ics}{ICS}{Industrial Control Systems}
+\newacronym{ies}{IES}{Integrated Energy System}
+\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
+\newacronym{inl}{INL}{Idaho National Laboratory}
+\newacronym{ip}{IP}{Internet Protocol}
+\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
+\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
+\newacronym{kmp}{KMP}{key measurement point}
+\newacronym{lms}{LMS}{Learning Management System}
+\newacronym{loc}{LOCA}{Loss of Coolant Accident}
+\newacronym{mim}{MITM}{Man in the Middle}
+\newacronym{mol}{MOL}{middle-of-life}
+\newacronym{mwe}{MWe}{Megawatts-electric}
+\newacronym{nei}{NEI}{Nuclear Energy Institute}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
+\newacronym{neu}{NEUP}{Nuclear Energy University Program}
+\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
+\newacronym{npp}{NPP}{Nuclear Power Plant}
+\newacronym{nsf}{NSF}{National Science Foundation}
+\newacronym{nus}{NuScale}{NuScale Power, LLC}
+\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+\newacronym{oer}{OER}{Online Educational Resource}
+\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
+\newacronym{plc}{PLC}{Programmable Logic Controller}
+\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
+\newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{roi}{ROI}{Return on Investment}
+\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
+\newacronym{smr}{SMR}{Small Modular Reactor}
+\newacronym{snm}{SNM}{special nuclear material}
+\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
+\newacronym{tva}{TVA}{Tennessee Valley Authority}
+\newacronym{udp}{UDP}{User Datagram Protocol}
+\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
+\newacronym{vfd}{VFD}{Variable Frequency Drive}
+\newacronym{wsc}{WSC}{Western Services Corporation}
+\newacronym{mba}{MBA}{material balance area}
+\newacronym{nma}{NMA}{nuclear materials accounting}
+\newacronym{sei}{SEID}{standard error of the inventory difference}
+\newacronym{tru}{TRU}{transuranic element}
+\newacronym{des}{DES}{discrete event simulation}
+\newacronym{sq}{SQ}{significant quantity}
+\newacronym{pyn}{PyNE}{Python for Nuclear Engineering}
+\newacronym{haz}{HAZOP}{hazard and operability analysis}
+\newacronym{msr}{MSR}{molten salt reactor}
+\newacronym{mpt}{MPACT}{Materials Protection, Accounting and Control Technology}
+\newacronym{aoo}{AOO}{Anticipated Operational Occurrences}
+\newacronym{dbe}{DBE}{Design Basis Events}
+\newacronym{bde}{BDBE}{Beyond Design Basis Events}
+\newacronym{ies}{IES}{Integrated Energy Systems}
+\newacronym{mca}{MC\&A}{Materials Control and Accountability}
 \newacronym{ahp}{AHP}{Analytical Hierarchy Process}
@@
 \newacronym{epri}{EPRI}{Electric Power Research Institute}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{ci}{CI}{Consistency Index}
-\newacronym{cr}{CR}{Consistency Ratio}
 \newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
@@
 \newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
-\newacronym{mwe}{MWe}{Megawatts electricity}
 \newacronym{mwt}{MWth}{Megawatts thermal energy}
@@
 \newacronym{ieo}{IESO}{Independent Electricity System Operator}
-\newacronym{us}{US}{United States}
 \newacronym{med}{MED}{Multiple-Effect Distillation}
@@
 \newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
-\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
 \newacronym{ide}{IDE}{Israel Desalination Enterprises} 
 \newacronym{iso}{ISO}{Independent System Operator} 
-\newacronym{msf}{MSF}{Multi-Stage Flash} 
 \newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
@@
 \newacronym{iaea}{IAEA}{International Atomic Energy Agency}
-\newacronym{snm}{SNM}{Special Nuclear Material}
-\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
 \newacronym{nnsa}{NNSA}{National Nuclear Security Administration}
@@
 \newacronym{usa}{US}{United States}
-\newacronym{doe}{DOE}{United States Department of Energy}
 \newacronym{pfc}{PFC}{Primary Frequency Control}
@@
 \newacronym{dc}{DC}{Direct Current}
-\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{inc}{I\&C}{Instrumentation and Controls}
 %%%%%

### 2023-01-11 proposal-documents/white-paper/white-paper-general-preproposal.tex
white paper fix
new templates for preproposals

--- 2022-06-22 proposal-documents/white-paper/white-paper-general-preproposal.tex
@@
 %the rest list numerically
-%
 %%%%%
-\documentclass[11pt,letterpaper]{article}
+
+%%%%% general 
+\documentclass[11pt,a4paper]{article}
 \usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
@@
 \usepackage{float}
+\usepackage{mypythonhighlight,verbatim}
 %\usepackage{subfig}
@@
 \setcounter{secnumdepth}{5} %set subsection to nth level
+\usepackage{needspace}
+\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
+\usepackage[inline]{enumitem}
+\usepackage{boldline}
+\usepackage{makecell}
+\usepackage{booktabs}
+\usepackage{amssymb}
+\usepackage{gensymb}
+\usepackage{amsmath,nicefrac}
+\usepackage{physics}
+\usepackage{lscape}
+\usepackage{array}
+\usepackage{chngcntr}
+\usepackage{hyperref}
+\hypersetup{colorlinks,linkcolor=black,citecolor=black,urlcolor=blue} 
+\usepackage{sectsty}
+\usepackage{textcomp}
+\usepackage{lastpage}
+\usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
+\usepackage{soul}
+\usepackage{color}
+\usepackage{marginnote}
+\usepackage[figure,table]{totalcount}
+\usepackage[capitalise]{cleveref}
+%%%%%
+
+%%%%% tikz
+\usepackage{pgf}
+\usepackage{tikz} % required for drawing custom shapes
+\usetikzlibrary{shapes,arrows,automata,trees}
+%%%%%
 
@@
 \usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
-\setlength{\bibsep}{3pt} %sets space between references
-\renewcommand{\bibsection}{} %suppresses large 'references' heading
+\setlength{\bibsep}{7pt} %sets space between references
+%\renewcommand{\bibsection}{} %suppresses large 'references' heading
 %\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading
@@
 \usepackage{pdfpages}
-
 \usepackage{wrapfig} %wraps figures around text
-\setlength{\intextsep}{0.05mm}
-\setlength{\columnsep}{0.05mm}
-
+\setlength{\intextsep}{0.00mm}
+\setlength{\columnsep}{1.00mm}
 \usepackage[singlelinecheck=false,labelfont=bf]{caption}
 \usepackage{subcaption}
-\captionsetup[table]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
-\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
-
-%\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=1pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
-%\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Tab.}} %sets space above caption, 'figure' format
+\captionsetup[table]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
+\captionsetup[figure]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
+\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Table}} %sets space above caption, 'figure' format
 %%%%%
 
-\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-\usepackage[inline]{enumitem}
-\usepackage{boldline}
-\usepackage{makecell}
-\usepackage{booktabs}
-\usepackage{amssymb}
-\usepackage{gensymb}
-\usepackage{amsmath}
-\usepackage{physics}
-\usepackage{lscape}
-\usepackage{array}
-\usepackage{chngcntr}
-\usepackage[hidelinks]{hyperref}
-\usepackage{sectsty}
-\usepackage{textcomp}
-\usepackage{lastpage}
-\usepackage{xargs} %for \newcommandx
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
-\usepackage{marginnote}
-\usepackage{gensymb}
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
-\usepackage[toc,title]{appendix}
-\usepackage[figure,table]{totalcount}
-
-\usepackage[capitalise]{cleveref}
-
 %%%%% watermark
-%\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
+%\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
 %\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-%\SetWatermarkScale{0.25}
+%\SetWatermarkScale{0.20}
 %%%%%
 
+%%%%% cross referencing files
 %\usepackage{xr} %for revisions - will cross reference from one file to here
 %\externaldocument{/path/to/auxfilename} %aux file needed
+%%%%%
 
 %%%%% toc and glossaries
+\usepackage[toc,title]{appendix}
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
@@
 \titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
-\titlespacing\part{0pt}{0.75\baselineskip}{0.50\baselineskip}
+\titlespacing*\part{0pt}{0.95\baselineskip}{0.75\baselineskip}
 \titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
-\titlespacing*\section{0pt}{0.55\baselineskip}{0.35\baselineskip}
+\titlespacing*\section{0pt}{0.65\baselineskip}{0.55\baselineskip}
 \titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
-\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.30\baselineskip}
+\titlespacing*\subsection{0pt}{0.50\baselineskip}{0.35\baselineskip}
 \titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
-\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
+\titlespacing*\paragraph{0pt}{0.45\baselineskip}{0.25\baselineskip}
 \titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
-\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
+\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
+%\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
+%\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
+%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+%\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
+%%%%%
 
+%%%%% editing
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
@@
 \newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
-\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
-\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
+%\newcommand{\sk}[1]{\sout{#1}} %shortcut for default strikethrough - do not sk through citep
+\newcommand\sk{\bgroup\markoverwith{\textcolor{red}{\rule[0.5ex]{1pt}{1pt}}}\ULon} %strikethrough with red line; not in \section{}
+%\st{} does strikethrough using soul package but does not like acronyms
+\newcommand{\blucell}{\cellcolor{aliceblue}} %use to shade in table cell
+\newcommand{\grycekk}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\whicell}{\cellcolor{antiquewhite}} %use to shade in table cell
+%%%%%
 
+%%%%% colors
+%http://latexcolor.com/
+%https://en.wikibooks.org/wiki/LaTeX/Colors#:~:text=black%2C%20blue%2C%20brown%2C%20cyan,be%20available%20on%20all%20systems.
+\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
+\definecolor{antiquewhite}{rgb}{0.98, 0.92, 0.84}
+\definecolor{lightmauve}{rgb}{0.86, 0.82, 1.0}
+\definecolor{brilliantlavender}{rgb}{0.96, 0.73, 1.0}
+\definecolor{brandeisblue}{rgb}{0.0, 0.44, 1.0}
+\definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
+
+\newcommand{\x}{\cellcolor{aliceblue}} %use to shade in table cell
+\newcommand{\y}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\z}{\cellcolor{antiquewhite}} %use to shade in table cell
+%%%%%
+
+%%%%% acronyms
 \newcommand{\acf}{\acrfull} %full acronym
@@
 \newcommand{\acsp}{\acrshortpl} %short acronym plural
+%%%%%
 
-\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
-\newcommandx{\por}[2][1=]{\todo[author=Porter,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
-%\newcommandx{\}[2][1=]{\todo[author=Sam,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-%\newcommandx{\}[2][1=]{\todo[author=RAB,tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
-\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
-\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\rab}[2][1=]{\author=RAB,tickmarkheight=0.15cm,todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+%%%%% todonotes
+\newcommandx{\cmt}[2][1=]{\todo[author=\textbf{STRUCTURE},tickmarkheight=0.15cm,linecolor=red,backgroundcolor=red!25,bordercolor=black,#1]{#2}}
+\newcommandx{\con}[2][1=]{\todo[author=\textbf{CONTENT},tickmarkheight=0.15cm,linecolor=brilliantlavender,backgroundcolor=brilliantlavender,bordercolor=black,#1]{#2}}
+\newcommandx{\rab}[2][1=]{\todo[noline,author=\textbf{RAB},backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
 
+%\newcommandx{\jon}[2][1=]{\todo[noline,author=\textbf{ATTN: Johnson},backgroundcolor=blue!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\han}[2][1=]{\todo[noline,author=\textbf{ATTN: Haney},backgroundcolor=OliveGreen!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\rab}[2][1=]{\todo[author=\textbf{RAB},tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\han}[2][1=]{\todo[author=\textbf{ATTN: Haney},tickmarkheight=0.15cm,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
+%\newcommandx{\jon}[2][1=]{\todo[author=\textbf{ATTN: Johnson},tickmarkheight=0.15cm,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+
+% highlighting 
+\DeclareRobustCommand{\hlc}[1]{{\sethlcolor{LimeGreen}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlh}[2]{#1}
+    \else
+    \newcommand{\hlh}[2]{\han{#2}\hlc{#1}}
+    \fi
+    \makeatother
+
+\DeclareRobustCommand{\hld}[1]{{\sethlcolor{CornflowerBlue}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlj}[2]{#1}
+    \else
+    \newcommand{\hlj}[2]{\jon{#2}\hld{#1}}
+    \fi
+    \makeatother
+
+\DeclareRobustCommand{\hlf}[1]{{\sethlcolor{lightmauve}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlb}[2]{#1}
+    \else
+    \newcommand{\hlb}[2]{\rab{#2}\hlf{#1}}
+    \fi
+    \makeatother
+%%%%%
+
+%%%%% table alignments
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
@@
 \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
+%%%%%
 
+%%%%% table contents
 \makeatletter
@@
 \makeatother
+%%%%%
 
+%%%%% archived section commands - use titlesec
 %\makeatletter
@@
 %    {\large \normalfont \bfseries}}%
+%%%%%
 
@@
 
-%spacing options
-%\onehalfspacing %linespacing
-%\setstretch{1.05} %linespacing
-%\spacing{1.25} %equivalent to 1.5 line spacing in Word
-
-%linenumbering
-\linenumbers %toggle line numbers
-\pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[1] %line numbering interval
-
 \begin{document}
@@
 
+%%%%% spacing
+%\onehalfspacing %linespacing
+%\setstretch{1.05} %linespacing
+%\spacing{1.25} %equivalent to 1.5 line spacing in Word
+%%%%%
+
+%%%%% linenumbering
+\linenumbers %toggle line numbers
+\pagewiselinenumbers %reset line numbers on new page
+\modulolinenumbers[1] %line numbering interval
+%%%%%
+
 {\centering
@@
 
-%may not be needed
-%\begin{center}\subsection*{Abstract}\end{center}
-
-\section*{Summary of the Proposed Project} 
+\section*{Overview} 
 \subsection*{Proposal}
@@
 \section*{Research Workscopes \& Tasks}
-\subsection*{Research activities}
 
-\subsection*{Workscope 1 - Title}
-\begin{enumerate}[topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{First task.}
-        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
-            \item Details.
-        \end{enumerate}
-    \item\textit{Second task.}
-        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
-            \item Details.
+\section*{Logical path to work accomplishment} 
+\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Workscope title} 
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{This task.}
+            \item\textit{That task.}
+            \item\textit{Another task.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item A brief explanation or a subtask if needed.
+                \end{enumerate*}
         \end{enumerate}
@@
 
-\vspace{0.05in}
+\paragraph*{Goals}
+The goals of this Workscope are \ldots .
 
-\noindent\textit{Through this Workscope, we will \ldots.}
-
-\subsection*{Workscope 2 - Title}
-\begin{enumerate}[resume,topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
-    \item\textit{Next task.}
-        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
-            \item Details.
-        \end{enumerate}
-    \item\textit{Next task.}
-        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
-            \item Details.
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Workscope title} 
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{This task.}
+            \item\textit{That task.}
+            \item\textit{Another task.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item A brief explanation or a subtask if needed.
+                \end{enumerate*}
         \end{enumerate}
@@
 
-\vspace{0.05in}
+\paragraph*{Goals}
+The goals of this Workscope are \ldots .
 
-\noindent\textit{Through this Workscope, we will \ldots.}
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Workscope title} 
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{This task.}
+            \item\textit{That task.}
+            \item\textit{Another task.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item A brief explanation or a subtask if needed.
+                \end{enumerate*}
+        \end{enumerate}
+\end{enumerate}
 
-\section*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
-The following outcomes are anticipated - 
-\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
-    \item
-    \item
-    \item
-    \item Identify lessons learned and engage in future pathways and partnerships.
+\paragraph*{Goals}
+The goals of this Workscope are \ldots .
+
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Workscope title} 
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{This task.}
+            \item\textit{That task.}
+            \item\textit{Another task.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item A brief explanation or a subtask if needed.
+                \end{enumerate*}
         \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Goals}
+The goals of this Workscope are \ldots .
+
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Crosscutting discussions \& follow on activities.} 
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{Identify lessons learned.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Lessons learned will be applied to \ldots . 
+                \end{enumerate*}
+            \item\textit{Develop future work.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item \ldots.
+                    \item \ldots.
+                    \item \ldots.
+                \end{enumerate*}
+            \item\textit{Reproducibility \& validation.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Explore avenues to reproduce and validate results \ldots .
+                \end{enumerate*}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Goals}
+The goals of this Workscope are \ldots .
 
@@
 We request a total of \$X,XXX,XXX for this project for a timeframe of N years.
-
-%limiting tasks, deliverables to one page allows for more references to be included on the third page, for a 3 page limit
 
@@
         \hline
-        VII. Crosscutting issues
+        XI. Lessons learned
+        &
+        &
+        &
+        &
+        &\x
+        &\x
+        &\x
+        &\x
+        &\x
+        &\x
+        &
+        &
+        \\
+        \hline
+        XII. Future work
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &\x
+        &\x
+        &\x
+        &
+        \\
+        \hline
+        XIII. Reprod. \& validation
         &
@@
         &
-        &\x\textbf{X} 
-        &\x\textbf{X} 
-        \\
-        \hline
-\end{longtable}
-
-\newpage
-
-%not typically needed in a preproposal, but good to do 
-\begin{longtable}{|l|l|l|} %comment out for page limits
-    \caption*{\textbf{Milestones.}}
-    \label{tab-milestones}\\
-    \hline
-        \multicolumn{1}{|c|}{\textbf{Milestone}}
-        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
-        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-            0. Project logistics
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-            0.1. Kick-off report, roles, and responsibilities.\\
-            0.2. Annual reports.\\
-            0.3. Agency administrative requirements.\\
-            0.4. Final project report.\\
-            0.5. Journal paper submission.\\
-            0.6. Conference presentations.
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-            0.1. Y1-Q2\\
-            0.2. Annually\\
-            0.3. Quarterly\\
-            0.4. Y3-Q4\\
-            0.5. Annually\\
-            0.6. Annually
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-            1.
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-            1.1.
-
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-            1.1. YX-QN
-        \end{tabular}
-        \\
-        \hline
-        \begin{tabular}[c]{@{}l@{}}
-            15. Crosscutting\\issues
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-            15.1. Identify lessons learned.\\
-            15.2. Develop future pathways and partnerships.
-        \end{tabular}
-        &
-        \begin{tabular}[c]{@{}l@{}}
-            15.1. YEND-Q3\\
-            15.2. YEND-Q4
-        \end{tabular}
+        &\x
+        &\x
         \\
@@
 \end{document}
-
-\begin{document}
-
-\newpage
-
-%remove page break if there are page limits
-%\vspace{0.5\baselineskip}
-
-\paragraph*{References}
-\bibliographystyle{nsf}
-%\bibliographystyle{neup}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
-
-%wrap figure around text
-%move to wherever in the text 
-%{l} fixes it on the left margin
-%{L} floats
-%\begin{wrapfigure}{l}{0.x\textwidth}
-%       \includegraphics[width=0.(x-2)\textwidth]{}
-%    \caption{}
-%    \label{fig-}
-%\end{wrapfigure}
-
-\end{document}

### 2023-01-11 proposal-documents/white-paper/white-paper-phd-proposal.tex
white paper fix
new templates for preproposals

@@
 \usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
-%\setlength{\bibsep}{7pt} %sets space between references
-\renewcommand{\bibsection}{} %suppresses large 'references' heading
+\setlength{\bibsep}{7pt} %sets space between references
+%\renewcommand{\bibsection}{} %suppresses large 'references' heading
 %\renewcommand\bibpreamble{\vspace{\baselineskip}} %sets spacing after heading if not using default references heading
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Title Keyword}
-\chead{\scriptsize \textit{Name - PhD White Paper Project Proposal}}
+\lhead{\scriptsize Name}
+\chead{\scriptsize \textit{PhD White Paper Project Proposal}}
 \rhead{\scriptsize \today}
@@
 
+%%%%%%% citations
 \begin{filecontents}{references.bib}
@@
 \end{filecontents}
+%%%%%%%
 
@@
 \newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{bwr}{BWR}{Boiling Water Reactor}
 \newacronym{roi}{ROI}{Return on Investment}
@@
 \newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{bol}{BOL}{beginning-of-life}
-\newacronym{eol}{EOL}{end-of-life}
-\newacronym{mol}{MOL}{middle-of-life}
+\newacronym{bol}{BOL}{Beginning-of-Life}
+\newacronym{eol}{EOL}{End-of-Life}
+\newacronym{mol}{MOL}{Middle-of-Life}
 \newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
@@
 \newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
+\newacronym{rcs}{RCS}{Reactor Cooling System}
+\newacronym{con}{IC}{Initial Condition}
+\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
+\newacronym{pcap}{PCAP}{packet capture file}
+\newacronym{dc}{DC}{Direct-Current}
+\newacronym{ac}{AC}{Alternating-Current}
+\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
+\newacronym{snl}{SNL}{Sandia National Laboratory}
+\newacronym{cie}{CIE}{Cyber-Informed Engineering}
+\newacronym{cds}{CRDS}{Control Rod Drive System}
+\newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
+\newacronym{fma}{FMEA}{Failure Modes \& Effects Analysis}
+\newacronym{rpn}{RPN}{Risk Priority Number}
+\newacronym{scr}{SCR}{silicon controller rectifier}
+\newacronym{hvc}{HVAC}{Heating, Ventilation \& Air Conditioning}
+\newacronym{ttb}{TTB}{Time-to-Boil}
+\newacronym{sis}{SIS}{Safety Instrumented System}
 %\newacronym{}{}{}
@@
 
-%spacing options
+%%%%% spacing
 %\onehalfspacing %linespacing
@@
 %\spacing{1.25} %equivalent to 1.5 line spacing in Word
+%%%%%
 
-%linenumbering
-%\linenumbers %toggle line numbers
-%\pagewiselinenumbers %reset line numbers on new page
-%\modulolinenumbers[1] %line numbering interval
+%%%%% linenumbering
+\linenumbers %toggle line numbers
+\pagewiselinenumbers %reset line numbers on new page
+\modulolinenumbers[1] %line numbering interval
+%%%%%
 
@@
 
-\section*{Summary of the Proposed Project}
+\part*{Abstract}
+
+\section*{Overview}
+
+\section*{Overall objectives}
 
 \section*{Motivation}
+
 \subsection*{Context}
 
-\section*{Overall Objective}
+\section*{Relevant background}
 
-\section*{Workscopes in Brief}
-\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - , })
+\section*{Importance and relevance to objectives}
+
+\section*{Novelty of the work}
+
+\section*{Relevant literature}
+
+\section*{Logical path to work accomplishment} 
+\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Workscope title} 
         \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
-            \item\textit{.}
+            \item\textit{This task.}
+            \item\textit{That task.}
+            \item\textit{Another task.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item A brief explanation or a subtask if needed.
+                \end{enumerate*}
         \end{enumerate}
@@
 
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - })
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
-            \item\textit{.}
+\paragraph*{Goals}
+The goals of this Workscope are \ldots .
+
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Workscope title} 
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{This task.}
+            \item\textit{That task.}
+            \item\textit{Another task.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item A brief explanation or a subtask if needed.
+                \end{enumerate*}
         \end{enumerate}
@@
 
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - })
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
+\paragraph*{Goals}
+The goals of this Workscope are \ldots .
+
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Workscope title} 
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{This task.}
+            \item\textit{That task.}
+            \item\textit{Another task.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item A brief explanation or a subtask if needed.
+                \end{enumerate*}
         \end{enumerate}
@@
 
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - })
+\paragraph*{Goals}
+The goals of this Workscope are \ldots .
+
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Crosscutting discussions \& follow on activities.} 
         \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
-            \item\textit{.}
+            \item\textit{Identify lessons learned.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Lessons learned will be applied to \ldots . 
+                \end{enumerate*}
+            \item\textit{Develop future work.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item \ldots.
+                    \item \ldots.
+                    \item \ldots.
+                \end{enumerate*}
+            \item\textit{Reproducibility \& validation.}
+                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Explore avenues to reproduce and validate results \ldots .
+                \end{enumerate*}
         \end{enumerate}
@@
 
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{Identify lessons learned.}
-            \item\textit{Develop future work.}
-            \item\textit{Reproducibility \& validation.}
-        \end{enumerate}
-\end{enumerate}
-\section*{Importance and Relevance to Objectives} 
-\subsection*{Background}
-
-\subsection*{Relevant literature}
-
-\section*{Research Workscopes \& Tasks}
-\subsection*{Research activities}
-Overview.
-
-\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - , })
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-        \end{enumerate}
-\end{enumerate}
-
-\paragraph*{Motivation}
-
 \paragraph*{Goals}
-\textit{Through this Workscope, we will \ldots}
-
-\paragraph*{Investigator duties}
-\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
-    \item[].
-    \item[].
-    \item[].
-\end{itemize}
-
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - })
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-        \end{enumerate}
-\end{enumerate}
-
-\paragraph*{Motivation}
-
-\paragraph*{Goals}
-\textit{Through this Workscope, we will \ldots}
-
-\paragraph*{Investigator duties}
-\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
-    \item[].
-    \item[].
-    \item[].
-\end{itemize}
-
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - })
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-        \end{enumerate}
-\end{enumerate}
-
-\paragraph*{Motivation}
-
-\paragraph*{Goals}
-\textit{Through this Workscope, we will \ldots}
-
-\paragraph*{Investigator duties}
-\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
-    \item[].
-    \item[].
-    \item[].
-\end{itemize}
-
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - })
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-        \end{enumerate}
-\end{enumerate}
-
-\paragraph*{Motivation}
-
-\paragraph*{Goals}
-\textit{Through this Workscope, we will \ldots}
-
-\paragraph*{Investigator duties}
-\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
-    \item[].
-    \item[].
-    \item[].
-\end{itemize}
-
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{.} (\textit{Lead - ; Support - })
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-            \item\textit{.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-        \end{enumerate}
-\end{enumerate}
-
-\paragraph*{Motivation}
-
-\paragraph*{Goals}
-\textit{Through this Workscope, we will \ldots}
-
-\paragraph*{Investigator duties}
-\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
-    \item[].
-    \item[].
-    \item[].
-\end{itemize}
-
-\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{Identify lessons learned.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-            \item\textit{Develop future work.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-            \item\textit{Reproducibility \& validation.}
-                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Details.
-                    \item Details.
-                \end{enumerate}
-        \end{enumerate}
-\end{enumerate}
-
-\paragraph*{Motivation}
-
-\paragraph*{Goals}
-\textit{Through this Workscope, we will wrapup the major findings of project activities and pursue new avenues of research with colleagues in the field.}
-
-\paragraph*{Investigator duties}
-\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
-    \item[].
-    \item[].
-    \item[].
-\end{itemize}
-
-\newpage
+The goals of this Workscope are \ldots .
 
@@
         \hline
+        XX. Lessons learned
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &\x
+        &\x
+        \\
+        \hline
+        XX. Future work
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &\x
+        &\x
+        \\
+        \hline
+        XX. Reprod. \& validation
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &
+        &\x
+        &\x
+        \\
+        \hline
 \end{longtable}
@@
 
-%\newpage
+\newpage
 
-%\begin{appendices}
+\begin{appendices}
 
-%    \renewcommand{\thesection}{\Roman{section}}
-%    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]
+    \renewcommand{\thesection}{\Roman{section}}
+    \titleformat{\section}{\normalfont\large\bfseries}{Appendix \thesection:}{1ex}{}[]
 
-%\section{Title}\label{app-}
+    \section*{Acronyms}
+    \printnoidxglossary[title={}]
 
-%\end{appendices}
+\end{appendices}
 
-%wrap figure around text
+%%%%%%% wrap figure around text
 %move to wherever in the text 
 %{l} fixes it on the left margin
-%{L} floats
 %\begin{wrapfigure}{l}{0.x\textwidth}
-%       \includegraphics[width=0.(x-2)\textwidth]{}
+%        \includegraphics[width=0.(x-2)\textwidth]{filename.ext}
 %    \caption{}
@@
 %\end{wrapfigure}
+%%%%%%%
 

### 2023-01-16 proposal-documents/white-paper/white-paper-phd-proposal.tex
white paper phd

@@
 \lhead{\scriptsize Name}
+%\lhead{\scriptsize PNUCENE-D-22-xxxxx}
 \chead{\scriptsize \textit{PhD White Paper Project Proposal}}
@@
     }
-    \vspace{0.10in}
     Name\\
-    University\\
-    Department
+    University of Idaho $\sq$ Idaho Falls Center for Higher Education\\
+    Department of Nuclear Engineering and Industrial Management
 \par
@@
 
-\section*{Overall objectives}
+\section*{Overall objective}
 
 \section*{Motivation}
-
 \subsection*{Context}
-
-\section*{Relevant background}
-
-\section*{Importance and relevance to objectives}
 
@@
 
-\begin{scriptsize}
-\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+{\small
+\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|}
 %        \captionsetup{margin=-9pt}
-        \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
+        \caption*{\textbf{Timeframe for execution of proposed project.}}
         \label{tab-timeline}\\
@@
         \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}&
-        \multicolumn{4}{|c|}{\textbf{Y1}}&
-        \multicolumn{4}{|c|}{\textbf{Y2}}&
-        \multicolumn{4}{|c|}{\textbf{Y3}}&
-        \multicolumn{4}{|c|}{\textbf{Y4}}
+        \multicolumn{5}{|c|}{\textbf{MONTH}}
         \\
-        \cline{2-17}
+        \cline{2-6}
         &
-        \textbf{Q1}& 
-        \textbf{Q2}& 
-        \textbf{Q3}& 
-        \textbf{Q4}& 
-        \textbf{Q1}& 
-        \textbf{Q2}& 
-        \textbf{Q3}& 
-        \textbf{Q4}& 
-        \textbf{Q1}& 
-        \textbf{Q2}& 
-        \textbf{Q3}& 
-        \textbf{Q4}& 
-        \textbf{Q1}& 
-        \textbf{Q2}& 
-        \textbf{Q3}& 
-        \textbf{Q4}
+        \textbf{JAN}&
+        \textbf{FEB}&
+        \textbf{MAR}&
+        \textbf{APR}&
+        \textbf{MAY}
         \\
@@
         I.
-        &\x\textbf{X}
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
+        &\x
         &
@@
         II.
-        &\x\textbf{X}
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
+        &\x
         &
@@
         III.
-        &\x\textbf{X} 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
+        &\x
         &
@@
         IV.
-        &\x\textbf{X}
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
+        &\x
         &
@@
         V.
-        &\x\textbf{X} 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
+        &\x
         &
@@
         VI.
-        &\x\textbf{X} 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
+        &\x
         &
@@
         &
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        & 
-        &\x\textbf{X} 
-        &\x\textbf{X} 
+        &\x
         \\
@@
         XX. Lessons learned
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
         &
@@
         &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
-        &
         &\x
@@
 \end{longtable}
-\end{scriptsize}
+}
 

### 2023-02-11 test.py
Slither package,  include python and serpent code blocks

@@ -1,0 +1,9 @@
+string = 'This line won't show up in the document'
+""""
+This is a Multi-line Comment
+Using Triple Quotes
+"""
+
+x = 4
+print(f"The numeral four: {x}")
+#comment

### 2023-02-11 Serpent/main.tex
Rename main.tex to Serpent/main.tex

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{slither}%requires slither.sty to be in the working directory
\usepackage{verbatim}

\title{Slither Code Block Package}
\author{Sam Root}
\date{February 2023}

\begin{document}
\section*{Slither Package}
This is a \LaTeX package that makes it easy to include Python and Serpent  codes in your documents with an aesthetically pleasing code block. It builds on a great package called pythonhighlight by Oliver. This is a huge upgrade over just using the verbatim package to include code. \\

https://github.com/olivierverdier/python-latex-highlighting/blob/master/pythonhighlight.sty

\subsection*{Python Codes}
You can include code by typing it into the \verb|\begin{python}\end{python}| environment.

\begin{code}\caption{Hello!} \begin{python}
    x=10
    print("Hello World") #comment
    try:
        a=2/x
    except ZeroDivisionError:
        print('undefined')
\end{python}\label{code:hello}\end{code}

You can also use inline codes like \pyth{import numpy} or \pyth{lambda x: x if x<=1 else fib(x-1) + fib(x-2)} by using the \verb|\pyth{}| control sequence. \\

Or you can save python files into your working directory and include them without the need to retype/copy-paste them using the \\ \verb|\inputpython{<input.py>}{<firstline>}{<lastline>}| command. The line numbers are smart, so if \pyth{<firstline>!=1}, it will start from the appropriate line. Be careful with this, especially making sure not to break up multiline `lines' like multiline comments or dictionaries, or the syntax highlighting may fail.

\begin{code}\caption{F strings}
\inputpython{test.py}{2}{8}
\label{code:fstrings}\end{code}

\newpage
\subsection*{Serpent Input Files}
It is a bit more complicated to use the Serpent capabilities. While I know all of the Control Words in Serpent, I do not know what you are going to name materials etc. You will have to open slither.sty, and add things that you would like to follow the `Name' syntax highlighting file to the line under \serp{\%Add Names here}.

You can include input files by typing it into the \verb|\begin{serpent}\end{serpent}| environment.

\begin{code}\caption{Fuel!} \begin{serpent}
    /*
    Enriched (4%) Uranium Metal 
    */
    mat fuel     -10.1
    92235.03c    -0.04 
    92238.03c    -0.96
    'string'
\end{serpent}\label{code:fuel}\end{code}

You can include individual commands inline like \serp{surf s1 sqc 0.0 0.0 100.0}.

Or you can save serpent input files into your working directory and include them without the need to retype/copy-paste them using the \\ \verb|\inputserpent{<input.txt>}{<firstline>}{<lastline>}| command.

\begin{code}\caption{Physics Cards}
    \inputserpent{physics.txt}{1}{10}
    \label{code:physics}\end{code}

\newpage
\subsection*{Wrapping Files over the Page Break}
You'll likely have files long enough to wrap over multiple pages. This is simple to deal with using the input<python/serpent> commands, as these natively allow you to handle page numbers. It's a little hacky as part of the code lays outside of the code-float, but it still allows you to reference it using the label.

\begin{code}\caption{Python OOP Helium Cycle}
    \inputpython{HeliumCycle.py}{1}{39}
    \label{code:brayton}\end{code}
    \newpage
    \inputpython{HeliumCycle.py}{40}{86}
    \newpage
    \inputpython{HeliumCycle.py}{87}{130}
    \newpage
    \inputpython{HeliumCycle.py}{131}{178}
    \newpage
    \inputpython{HeliumCycle.py}{179}{195}

\end{document}

### 2023-04-06 presenations/research/research-presentation-template.tex
research presentation template

--- 2023-01-16 proposal-documents/white-paper/white-paper-phd-proposal.tex
@@
 
+%%%%% presentation settings
+\documentclass[aspectratio=1610,pdftex,dvipsnames,compress,xcolor={dvipsnames}]{beamer}
+\usetheme{Boadilla}
+\usecolortheme{seahorse}
+\beamertemplatenavigationsymbolsempty
+\setbeamerfont{title}{series=\bfseries}
+\setbeamertemplate{page number in head/foot}[framenumber] %just gives slide number; comment out for 1/7, 2/7...
+\setbeamertemplate{caption}[numbered] %numbers figures and tables
+\setbeamertemplate{footnote}{%
+  \parindent 1em\noindent%
+  \raggedright
+  \linespread{0.5}
+  \hbox to 1.8em{\hfil\insertfootnotemark}\insertfootnotetext\par\vspace*{-0.2em}%
+}
+\addtobeamertemplate{footnote}{\hskip -2em}{} %pushes footnote to margin
+\definecolor{BackGround}{RGB}{255,250,240}
+\setbeamercolor{background canvas}{bg=BackGround}
+%%%%%
+
 %%%%% general 
-\documentclass[11pt,a4paper]{article}
-\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
-\usepackage[pagewise]{lineno} %line numbering
-\usepackage{setspace}
+%\documentclass[11pt,a4paper]{article}
+%\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
+%\usepackage[pagewise]{lineno} %line numbering
+%\usepackage{setspace}
 \usepackage{ulem} %strikethrough - do not \sout{\cite{}}
-\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
 \usepackage{graphicx}
+\usepackage{pythonhighlight,verbatim}
+%\usepackage{mypythonhighlight,verbatim}
 \usepackage{filecontents}
@@
 \usepackage{float}
-\usepackage{mypythonhighlight,verbatim}
 %\usepackage{subfig}
@@
 \graphicspath{{../img/}} %path to graphics
-\setcounter{secnumdepth}{5} %set subsection to nth level
+%\setcounter{secnumdepth}{5} %set subsection to nth level
 \usepackage{needspace}
-\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
+%\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst; comment out on presentations
 \usepackage[inline]{enumitem}
+\setlist[itemize]{label=\textbullet}
 \usepackage{boldline}
@@
 \hypersetup{colorlinks,linkcolor=black,citecolor=black,urlcolor=blue} 
-\usepackage{sectsty}
+%\usepackage{sectsty}
 \usepackage{textcomp}
@@
 \usepackage[capitalise]{cleveref}
+\usepackage{microtype} %improves typography for pdf
+\usepackage[pdftex,dvipsnames]{colortbl} %change font color
 %%%%%
@@
 %%%%% references
+\usepackage{bibentry}
 %\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
 \usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
-\setlength{\bibsep}{7pt} %sets space between references
+\setlength{\bibsep}{5pt} %sets space between references
 %\renewcommand{\bibsection}{} %suppresses large 'references' heading
@@
 \usepackage{longtable} %need to put label at top under caption then \\ - use spacing
-\usepackage{tablefootnote}
+%\usepackage{tablefootnote}
 \usepackage{tabularx}
@@
 \usepackage{subcaption}
-\captionsetup[table]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
-\captionsetup[figure]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
+\captionsetup[table]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
+\captionsetup[figure]{justification=centering,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
 \captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
@@
 %%%%% toc and glossaries
-\usepackage[toc,title]{appendix}
+%\usepackage[toc,title]{appendix}
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
 \makenoidxglossaries
-\usepackage{titlesec,titletoc}
+%\usepackage{titlesec,titletoc}
 %\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
 %\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
-\titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
-\titlespacing*\part{0pt}{0.95\baselineskip}{0.75\baselineskip}
-\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
-\titlespacing*\section{0pt}{0.65\baselineskip}{0.55\baselineskip}
-\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
-\titlespacing*\subsection{0pt}{0.50\baselineskip}{0.35\baselineskip}
-\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
-\titlespacing*\paragraph{0pt}{0.45\baselineskip}{0.25\baselineskip}
-\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
-\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
+%\titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
+%\titlespacing*\part{0pt}{0.95\baselineskip}{0.75\baselineskip}
+%\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
+%\titlespacing*\section{0pt}{0.65\baselineskip}{0.55\baselineskip}
+%\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
+%\titlespacing*\subsection{0pt}{0.50\baselineskip}{0.35\baselineskip}
+%\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+%\titlespacing*\paragraph{0pt}{0.45\baselineskip}{0.25\baselineskip}
+%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+%\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
 %\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
@@
 %%%%% table contents
-\makeatletter
-\renewcommand\tableofcontents{%
-    \@starttoc{toc}%
+%\makeatletter
+%\renewcommand\tableofcontents{%
+%    \@starttoc{toc}%
+%}
+%\makeatother
+%
+%\makeatletter
+%\renewcommand\listoffigures{%
+%    \@starttoc{lof}%
+%}
+%\makeatother
+
+%\makeatletter
+%\renewcommand\listoftables{%
+%    \@starttoc{lot}%
+%}
+%\makeatother
+
+%\makeatletter
+%\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
+%\makeatother
+%%%%%
+
+%%%%% citations on the frame
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  \addtocounter{footnote}{-1}%
+  \endgroup
 }
-\makeatother
 
 \makeatletter
-\renewcommand\listoffigures{%
-    \@starttoc{lof}%
-}
-\makeatother
-
-\makeatletter
-\renewcommand\listoftables{%
-    \@starttoc{lot}%
-}
-\makeatother
-
-\makeatletter
-\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
+\renewcommand{\@biblabel}[1]{#1.\hfill} %bibliography ordered list has numbers left flush
 \makeatother
@@
 %%%%% header and footer
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhf{} %move page number to bottom right
+%\usepackage{fancyhdr}
+%\pagestyle{fancy}
+%\fancyhf{} %move page number to bottom right
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Name}
+%\lhead{\scriptsize Name}
 %\lhead{\scriptsize PNUCENE-D-22-xxxxx}
-\chead{\scriptsize \textit{PhD White Paper Project Proposal}}
-\rhead{\scriptsize \today}
-\rfoot{\thepage}
+%\chead{\scriptsize \textit{PhD White Paper Project Proposal}}
+%\rhead{\scriptsize \today}
+%\rfoot{\thepage}
 %%%%%
@@
 %%%%%%% citations
-\begin{filecontents}{references.bib}
-    @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
-    }
-    @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
-    }
-    @incollection{
-        mil17a,
-        author = {Miller, Steven E.},
-        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
-        booktitle = {Understanding Cyber Conflict: 14 Analogies},
-        publisher = {Georgetown University Press},
-        year = {2017},
-        editor = {Perkovich, George and Levite, Ariel E.},
-        pages = {161}
-    }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
-\end{filecontents}
+%\begin{filecontents}{references.bib}
+%\end{filecontents}
 %%%%%%%
@@
 \newacronym{sis}{SIS}{Safety Instrumented System}
+\newacronym{ui}{UI}{University of Idaho}
+\newacronym{mcp}{MCNP}{Monte Carlo N-Particle Transport Code}
+\newacronym{loca}{LOCA}{Loss of Coolant Accident}
 %\newacronym{}{}{}
@@
 %%%%% linenumbering
-\linenumbers %toggle line numbers
-\pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[1] %line numbering interval
+%\linenumbers %toggle line numbers
+%\pagewiselinenumbers %reset line numbers on new page
+%\modulolinenumbers[1] %line numbering interval
+%%%%%
+
+%%%%% title page
+\addtocounter{framenumber}{-1} %does not count the title slide in the slide count
+\title[short title will appear in left middle footer]{Presentation Title}
+\author[left footer]
+    {
+    Author 1,\textsuperscript{1}
+    Author 2\textsuperscript{2}\\
+    Author 3,\textsuperscript{2}
+    Author 4\textsuperscript{1}\\
+    \vspace{0.15in}
+    date
+    }
+\institute[what goes in here will be in () next to left footer]{
+    Institution\\
+    Research Group\\
+    \textsuperscript{1}Affiliation 1\\
+    \textsuperscript{2}Affiliation 2\\
+    \vspace{0.10in}
+    \includegraphics[width=0.20\textwidth]{logo.png}\\
+    }
+\date{} %if blank, compiled date will appear in middle right footer; can add something else like location, etc.
 %%%%%
@@
 
-{\centering 
-    \textbf{Title\\
-    PhD White Paper Project Proposal\\
+\nobibliography*
+
+%%%%% title page with no footer
+{
+    \setbeamertemplate{footline}{}
+    \begin{frame}
+        \titlepage
+    \end{frame}
 }
-    Name\\
-    University of Idaho $\sq$ Idaho Falls Center for Higher Education\\
-    Department of Nuclear Engineering and Industrial Management
-\par
-}
+%%%%%
 
-\noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}} %horizontal line spanning margins
-
-\part*{Abstract}
-
-\section*{Overview}
-
-\section*{Overall objective}
-
-\section*{Motivation}
-\subsection*{Context}
-
-\section*{Novelty of the work}
-
-\section*{Relevant literature}
-
-\section*{Logical path to work accomplishment} 
-\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
-        \end{enumerate}
+\begin{frame}{Title}
+    \begin{enumerate}[series=outerlist,topsep=0pt,itemsep=21pt,leftmargin=*,label=(\arabic*)]
+            \item[] item 
+            \item[] item
+            \item[] item \citep{citation}
     \end{enumerate}
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
+    \blfootnote{\tiny\cite{citation} \tiny\bibentry{citation}} %will appear in footnote on frame
+\end{frame}
 
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
+\begin{frame}{Title}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.95\textwidth]{}
+        \caption{}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Title with columns}
+    \begin{columns}
+
+        \begin{column}{0.65\textwidth}
+            \begin{figure}
+                \centering
+                \includegraphics[width=0.95\textwidth]{}
+                \caption{\acs{wsc} Platform}
+            \end{figure}
+        \end{column}
+
+        \begin{column}{0.35\textwidth}
+            \begin{enumerate}[series=outerlist,topsep=0pt,itemsep=21pt,leftmargin=*,label=(\arabic*)]
+                \item[] item
             \end{enumerate}
-\end{enumerate}
+        \end{column}
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
+    \end{columns}
+\end{frame}
 
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
-        \end{enumerate}
-\end{enumerate}
+\begin{frame}[plain]{} %subtitle slide will not have any footers or title
+    \centering\LARGE\textbf{}
+\end{frame}
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
-
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
-        \end{enumerate}
-\end{enumerate}
-
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
-
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Crosscutting discussions \& follow on activities.} 
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{Identify lessons learned.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Lessons learned will be applied to \ldots . 
-                \end{enumerate*}
-            \item\textit{Develop future work.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item \ldots.
-                    \item \ldots.
-                    \item \ldots.
-                \end{enumerate*}
-            \item\textit{Reproducibility \& validation.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Explore avenues to reproduce and validate results \ldots .
-                \end{enumerate*}
-        \end{enumerate}
-\end{enumerate}
-
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
-
-{\small
-\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|}
-%        \captionsetup{margin=-9pt}
-        \caption*{\textbf{Timeframe for execution of proposed project.}}
-        \label{tab-timeline}\\
+\addtocounter{framenumber}{-1} %this resumes numbering but does not count the subtitle slide
+\begin{frame}{Title}
+\begin{longtable}{|c|c|c|c|c|c|}
+    \caption[]{}
+    \label{tab-}
+    \\
         \hline
-        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}&
-        \multicolumn{5}{|c|}{\textbf{MONTH}}
+        \multirow{2}{*}{\textbf{}}
+        &\multicolumn{5}{c|}{\textbf{}} 
         \\ 
@@
         & 
-        \textbf{JAN}&
-        \textbf{FEB}&
-        \textbf{MAR}&
-        \textbf{APR}&
-        \textbf{MAY}
-        \\
-        \hline
-        I.
-        &\x
         & 
@@
         \hline
-        II.
-        &\x
+        \textbf{Catastrophic} 
+        & 
         & 
@@
         \hline
-        III.
-        &\x
+        \textbf{Critical}     
+        & 
         & 
@@
         \hline
-        IV.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        V.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        VI.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        VII.
-        &
-        &
-        &
-        &
-        &\x
-        \\
-        \hline
-        XX. Lessons learned
-        &
-        &
-        &
-        &\x
-        &\x
-        \\
-        \hline
-        XX. Future work
-        &
-        &
-        &
-        &\x
-        &\x
-        \\
-        \hline
-        XX. Reprod. \& validation
-        &
-        &
-        &
-        &\x
-        &\x
-        \\
-        \hline
 \end{longtable}
-}
+\end{frame}
 
-\newpage
+\begin{frame}{Future work}
+    \begin{enumerate}[series=outerlist,topsep=0pt,itemsep=21pt,leftmargin=*,label=(\arabic*)]
+        \item[] item
+    \end{enumerate}
+\end{frame}
 
-\part*{References}
-\bibliographystyle{nsf}
-\setlength{\bibhang}{0pt}
+\begin{frame}{Final remarks}
+    \begin{enumerate}[series=outerlist,topsep=0pt,itemsep=15pt,leftmargin=*,label=(\arabic*)]
+        \item[] item
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}{Acknowledgements}
+    \centering
+    Funding source
+\end{frame}
+
+\begin{frame}{References}
+    \bibliographystyle{neup}
+    \footnotesize
     \bibliography{references}
+\end{frame}
 
-\newpage
+\begin{frame}[plain]{}
+    \begin{figure}
+        \centering
+        \includegraphics[width=0.30\textwidth]{final.jpg}
+%        \caption{}
+    \end{figure}
+\end{frame}
 
-\begin{appendices}
+%\begin{frame}{}
+%    \begin{columns}
+%
+%        \begin{column}{0.75\textwidth}
+%        \end{column}
+%
+%        \begin{column}{0.25\textwidth}
+%        \end{column}
+%
+%    \end{columns}
+%\end{frame}
 
-    \renewcommand{\thesection}{\Roman{section}}
-    \titleformat{\section}{\normalfont\large\bfseries}{Appendix \thesection:}{1ex}{}[]
+%    \begin{figure}
+%        \centering
+%        \includegraphics[width=0.75\textwidth]{wsc.png}
+%        \caption{\acs{wsc}}
+%    \end{figure}
 
-    \section*{Acronyms}
-    \printnoidxglossary[title={}]
+%\begin{frame}{}
+%    \begin{enumerate}[series=outerlist,topsep=0pt,itemsep=21pt,leftmargin=*,label=(\arabic*)]
+%        \item[]
+%        \item[]
+%        \item[]
+%    \end{enumerate}
+%\end{frame}
 
-\end{appendices}
-
-%%%%%%% wrap figure around text
-%move to wherever in the text 
-%{l} fixes it on the left margin
-%\begin{wrapfigure}{l}{0.x\textwidth}
-%        \includegraphics[width=0.(x-2)\textwidth]{filename.ext}
-%    \caption{}
-%    \label{fig-}
-%\end{wrapfigure}
-%%%%%%%
+%\begin{frame}{References}
+%    \bibliographystyle{nsf}
+%    \footnotesize
+%    \bibliography{references}
+%\end{frame}
 

### 2023-05-11 sty/slither/test.py
cv template

@@ -1,9 +1,0 @@
-string = 'This line won't show up in the document'
-""""
-This is a Multi-line Comment
-Using Triple Quotes
-"""
-
-x = 4
-print(f"The numeral four: {x}")
-#comment

### 2023-05-11 cv-templates/cv-template-research-academic.tex

--- 2023-01-16 proposal-documents/white-paper/white-paper-phd-proposal.tex
@@
 %@TheDoctorRAB
-%standard white paper/preproposal format
+%resume
 %
-%%%%%
-%
-%REFERENCES
-%
-%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
-%nsf.bst - numbered citations in order of appearance, full author list in references section
-%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
-%ans.bst is for ANS only. 
-%
-%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
-%bst renders the author list itself
-%
-%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
-%
-%title = {{}} for all
-%
-%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
-%standard.bst \cite{-} - Borrelli (2021) in the text
-%standard.bst lists references alphabetically
-%the rest list numerically
-%%%%%
-
 %%%%% general 
-\documentclass[11pt,a4paper]{article}
+\documentclass[11pt,letterpaper]{article}
 \usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
@@
 \usepackage[capitalise]{cleveref}
-%%%%%
-
-%%%%% tikz
-\usepackage{pgf}
-\usepackage{tikz} % required for drawing custom shapes
-\usetikzlibrary{shapes,arrows,automata,trees}
+\usepackage{nameref}
+\usepackage{bold-extra}
+\usepackage{parskip}
 %%%%%
@@
 %%%%% references
-%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
-\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
-\setlength{\bibsep}{7pt} %sets space between references
+\usepackage{bibentry} %lists references without \citep
+\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
+%\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+%\setlength{\bibsep}{7pt} %sets space between references
 %\renewcommand{\bibsection}{} %suppresses large 'references' heading
@@
 
-%%%%% tables and figures
-\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
-\usepackage{tablefootnote}
-\usepackage{tabularx}
-\usepackage{multirow}
-\usepackage{tabto} %general tabbed spacing
-\usepackage{pdfpages}
-\usepackage{wrapfig} %wraps figures around text
-\setlength{\intextsep}{0.00mm}
-\setlength{\columnsep}{1.00mm}
-\usepackage[singlelinecheck=false,labelfont=bf]{caption}
-\usepackage{subcaption}
-\captionsetup[table]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
-\captionsetup[figure]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
-\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
-\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Table}} %sets space above caption, 'figure' format
-%%%%%
-
-%%%%% watermark
-%\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
-%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-%\SetWatermarkScale{0.20}
-%%%%%
-
-%%%%% cross referencing files
-%\usepackage{xr} %for revisions - will cross reference from one file to here
-%\externaldocument{/path/to/auxfilename} %aux file needed
-%%%%%
-
-%%%%% toc and glossaries
+%%%%% heading formatting
 \usepackage[toc,title]{appendix}
@@
 %\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
-\titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
-\titlespacing*\part{0pt}{0.95\baselineskip}{0.75\baselineskip}
-\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
-\titlespacing*\section{0pt}{0.65\baselineskip}{0.55\baselineskip}
-\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
-\titlespacing*\subsection{0pt}{0.50\baselineskip}{0.35\baselineskip}
-\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
-\titlespacing*\paragraph{0pt}{0.45\baselineskip}{0.25\baselineskip}
-\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
-\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
+%\titleformat{\part}{\normalfont\Large\bfseries\filcenter}{\thepart}{}{}[]
+%\titlespacing*\part{0pt}{0.95\baselineskip}{0.75\baselineskip}
+
+\titleformat{\section}{\normalfont\Large\bfseries\scshape}{\thesection}{}{}[]
+\titlespacing*\section{0pt}{0.95\baselineskip}{0.15\baselineskip}
+
+\titleformat{\subsection}{\normalfont\large\bfseries\scshape}{\thesubsection}{}{}[]
+\titlespacing*\subsection{0pt}{0.55\baselineskip}{0.10\baselineskip}
+
+\titleformat{\subsubsection}[runin]{\normalfont\normalsize\bfseries\scshape}{\thesubsubsection}{}{}[]
+\titlespacing*\subsubsection{0pt}{0.30\baselineskip}{0.05\baselineskip}
+
+\titleformat{\paragraph}[runin]{\normalfont\normalsize\itshape}{\theparagraph}{-1em}{}[]
+\titlespacing*\paragraph{0pt}{0.05\baselineskip}{0.05\baselineskip}
+
+%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+%\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
 %\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
@@
 %\st{} does strikethrough using soul package but does not like acronyms
-\newcommand{\blucell}{\cellcolor{aliceblue}} %use to shade in table cell
-\newcommand{\grycekk}{\cellcolor{lightgray}} %use to shade in table cell
-\newcommand{\whicell}{\cellcolor{antiquewhite}} %use to shade in table cell
 %%%%%
@@
 \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
-
-\newcommand{\x}{\cellcolor{aliceblue}} %use to shade in table cell
-\newcommand{\y}{\cellcolor{lightgray}} %use to shade in table cell
-\newcommand{\z}{\cellcolor{antiquewhite}} %use to shade in table cell
 %%%%%
@@
 
-%%%%% todonotes
-\newcommandx{\cmt}[2][1=]{\todo[author=\textbf{STRUCTURE},tickmarkheight=0.15cm,linecolor=red,backgroundcolor=red!25,bordercolor=black,#1]{#2}}
-\newcommandx{\con}[2][1=]{\todo[author=\textbf{CONTENT},tickmarkheight=0.15cm,linecolor=brilliantlavender,backgroundcolor=brilliantlavender,bordercolor=black,#1]{#2}}
-\newcommandx{\rab}[2][1=]{\todo[noline,author=\textbf{RAB},backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
-
-%\newcommandx{\jon}[2][1=]{\todo[noline,author=\textbf{ATTN: Johnson},backgroundcolor=blue!25,bordercolor=black,#1]{#2}}
-%\newcommandx{\han}[2][1=]{\todo[noline,author=\textbf{ATTN: Haney},backgroundcolor=OliveGreen!25,bordercolor=black,#1]{#2}}
-%\newcommandx{\rab}[2][1=]{\todo[author=\textbf{RAB},tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
-%\newcommandx{\han}[2][1=]{\todo[author=\textbf{ATTN: Haney},tickmarkheight=0.15cm,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
-%\newcommandx{\jon}[2][1=]{\todo[author=\textbf{ATTN: Johnson},tickmarkheight=0.15cm,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
-
-% highlighting 
-\DeclareRobustCommand{\hlc}[1]{{\sethlcolor{LimeGreen}\hl{#1}}}
-\makeatletter
-    \if@todonotes@disabled
-    \newcommand{\hlh}[2]{#1}
-    \else
-    \newcommand{\hlh}[2]{\han{#2}\hlc{#1}}
-    \fi
-    \makeatother
-
-\DeclareRobustCommand{\hld}[1]{{\sethlcolor{CornflowerBlue}\hl{#1}}}
-\makeatletter
-    \if@todonotes@disabled
-    \newcommand{\hlj}[2]{#1}
-    \else
-    \newcommand{\hlj}[2]{\jon{#2}\hld{#1}}
-    \fi
-    \makeatother
-
-\DeclareRobustCommand{\hlf}[1]{{\sethlcolor{lightmauve}\hl{#1}}}
-\makeatletter
-    \if@todonotes@disabled
-    \newcommand{\hlb}[2]{#1}
-    \else
-    \newcommand{\hlb}[2]{\rab{#2}\hlf{#1}}
-    \fi
-    \makeatother
-%%%%%
-
-%%%%% table alignments
-\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
-\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
-\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
-%%%%%
-
-%%%%% table contents
-\makeatletter
-\renewcommand\tableofcontents{%
-    \@starttoc{toc}%
-}
-\makeatother
-
-\makeatletter
-\renewcommand\listoffigures{%
-    \@starttoc{lof}%
-}
-\makeatother
-
-\makeatletter
-\renewcommand\listoftables{%
-    \@starttoc{lot}%
-}
-\makeatother
-
-\makeatletter
-\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
-\makeatother
-%%%%%
-
-%%%%% archived section commands - use titlesec
-%\makeatletter
-%\renewcommand\section{%
-%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
-%    {\large \normalfont \bfseries}}%
-
-%\makeatletter
-%\renewcommand\paragraph{%
-%    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
-%    {\normalfont \normalsize \bfseries}}%
-
-%\makeatletter
-%\renewcommand\subparagraph{%
-%    \@startsection{subparagraph}{5}{\z@ }{0.40\baselineskip}{-1em}
-%    {\normalfont \normalsize \itshape }}%
-
-%\makeatletter
-%\renewcommand\subsection{%
-%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
-%    {\large \normalfont \bfseries}}%
-%%%%%
-
 %%%%% header and footer
@@
 \pagestyle{fancy}
-\fancyhf{} %move page number to bottom right
-%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+\fancyhf{} %page number on bottom right
 \lhead{\scriptsize Name}
-%\lhead{\scriptsize PNUCENE-D-22-xxxxx}
-\chead{\scriptsize \textit{PhD White Paper Project Proposal}}
-\rhead{\scriptsize \today}
-\rfoot{\thepage}
+\chead{\scriptsize \textit{Vita}}
+\rhead{\scriptsize \today} %date
+\rfoot{\thepage} %page number
 %%%%%
 
-%%%%%%% citations
-\begin{filecontents}{references.bib}
-    @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
-    }
-    @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
-    }
-    @incollection{
-        mil17a,
-        author = {Miller, Steven E.},
-        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
-        booktitle = {Understanding Cyber Conflict: 14 Analogies},
-        publisher = {Georgetown University Press},
-        year = {2017},
-        editor = {Perkovich, George and Levite, Ariel E.},
-        pages = {161}
-    }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
+%%%%% citations
+\begin{filecontents}{journal.bib}
 \end{filecontents}
-%%%%%%%
+\begin{filecontents}{book.bib}
+\end{filecontents}
+\begin{filecontents}{conference.bib}
+\end{filecontents}
+\begin{filecontents}{report.bib}
+\end{filecontents}
+\begin{filecontents}{presentation.bib}
+\end{filecontents}
+%%%%%
 
@@
 \newacronym{sis}{SIS}{Safety Instrumented System}
+\newacronym{usb}{USB}{Universal Serial Bus}
+\newacronym{ack}{ACK}{Acknowledge}
+\newacronym{seq}{SEQ}{Sequence}
+\newacronym{npr}{NPR}{National Public Radio}
+\newacronym{cyd}{CYDEF}{Cyber Defence QCD Corporation}
+\newacronym{ara}{ARA}{Amsterdam-Rotterdam-Antwerp}
 %\newacronym{}{}{}
-%%%%%
-
-%%%%% spacing
-%\onehalfspacing %linespacing
-%\setstretch{1.05} %linespacing
-%\spacing{1.25} %equivalent to 1.5 line spacing in Word
-%%%%%
-
-%%%%% linenumbering
-\linenumbers %toggle line numbers
-\pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[1] %line numbering interval
 %%%%%
@@
 
+\nobibliography{journal,book,conference,report,presentation} %bib files
+\bibliographystyle{standard} %custom bst file
+
 {\centering
-    \textbf{Title\\
-    PhD White Paper Project Proposal\\
+        \textsc{ %block caps font
+            \textbf{
+                Name\\
+                {\footnotesize Title} \\
+                {\footnotesize Insitution} \\
+                {\footnotesize Department} \\
+                {\footnotesize Address}\\
+                {\footnotesize email $\sq$ Twitter $\sq$ web }
             }
-    Name\\
-    University of Idaho $\sq$ Idaho Falls Center for Higher Education\\
-    Department of Nuclear Engineering and Industrial Management
-\par
         }
+   \par}
 
@@
 
-\part*{Abstract}
-
-\section*{Overview}
-
-\section*{Overall objective}
-
-\section*{Motivation}
-\subsection*{Context}
-
-\section*{Novelty of the work}
-
-\section*{Relevant literature}
-
-\section*{Logical path to work accomplishment} 
-\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
-        \end{enumerate}
+\section*{Education}
+\subsection*{Institution 1}
+\subsubsection*{Doctor of Philosophy $\sq$ Major}\hfill{\textit{Month Year}}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]\textit{Dissertation Title}
+    \item[]Examination fields -- 
+    \item[]Committee -- 
 \end{enumerate}
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
-
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
-        \end{enumerate}
+\subsection*{Institution 2}
+\subsubsection*{Master of Science $\sq$ Major}\hfill{\textit{Month Year}}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]\textit{Thesis Title}
+    \item[]Examination fields -- 
+    \item[]Committee -- 
 \end{enumerate}
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
-
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
-        \end{enumerate}
+\subsection*{Institution 3}
+\subsubsection*{Bacheor of Science $\sq$ Major}\hfill{\textit{Month Year}}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]\textit{Capstone}
+    \item[]Advisor -- 
 \end{enumerate}
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\section*{Research Experience}
+\subsection*{Institution 1 $\sq$ Department}
+\subsubsection*{Title}\hfill{\textit{Time period}}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
+\end{enumerate}
+\subsubsection*{Other Title}\hfill{\textit{Time period}}\\
+Description
 
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
+\section*{Related Research Experience}
+\subsection*{Institution 1 $\sq$ Department}
+\subsubsection*{Title}\hfill{\textit{Time period}}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
 \end{enumerate}
+\subsubsection*{Other Title}\hfill{\textit{Time period}}\\
+Description
+
+\section*{Related Professional Experience}
+\subsection*{Institution 1 $\sq$ Department}
+\subsubsection*{Title}\hfill{\textit{Time period}}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
+    \item[]\indent\indent Other repsonsibilites, titles, positions \hfill{\textit{Time period}}
+\end{enumerate}
+\subsubsection*{Other Title}\hfill{\textit{Time period}}\\
+Description
+
+\section*{Awarded Projects} %chronologically
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item Big proposal 1
+    \item Big proposal 2
+    \item Big proposal 3
 \end{enumerate}
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\section*{Equipment Acquisitions}
+Fancy equipment
 
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Crosscutting discussions \& follow on activities.} 
-        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{Identify lessons learned.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Lessons learned will be applied to \ldots . 
-                \end{enumerate*}
-            \item\textit{Develop future work.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item \ldots.
-                    \item \ldots.
-                    \item \ldots.
-                \end{enumerate*}
-            \item\textit{Reproducibility \& validation.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Explore avenues to reproduce and validate results \ldots .
-                \end{enumerate*}
-        \end{enumerate}
+\section*{Thesis Committees}
+\subsection*{Major Professor}
+\subsubsection*{Current}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] Student
+    \item[] Student
+    \item[] Student
 \end{enumerate}
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\subsubsection*{Graduates}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] Student
+    \item[] Student
+    \item[] Student
+\end{enumerate}
 
-{\small
-\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|}
-%        \captionsetup{margin=-9pt}
-        \caption*{\textbf{Timeframe for execution of proposed project.}}
-        \label{tab-timeline}\\
-        \hline
-        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}&
-        \multicolumn{5}{|c|}{\textbf{MONTH}}
-        \\
-        \cline{2-6}
-        &
-        \textbf{JAN}&
-        \textbf{FEB}&
-        \textbf{MAR}&
-        \textbf{APR}&
-        \textbf{MAY}
-        \\
-        \hline
-        I.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        II.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        III.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        IV.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        V.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        VI.
-        &\x
-        &
-        &
-        &
-        &
-        \\
-        \hline
-        VII.
-        &
-        &
-        &
-        &
-        &\x
-        \\
-        \hline
-        XX. Lessons learned
-        &
-        &
-        &
-        &\x
-        &\x
-        \\
-        \hline
-        XX. Future work
-        &
-        &
-        &
-        &\x
-        &\x
-        \\
-        \hline
-        XX. Reprod. \& validation
-        &
-        &
-        &
-        &\x
-        &\x
-        \\
-        \hline
-\end{longtable}
-}
+\subsection*{Committee Member}
+\subsubsection*{Graduates}
+\paragraph*{University 1}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] Student
+    \item[] Student
+    \item[] Student
+\end{enumerate}
 
-\newpage
+\subsubsection*{Current}
+\paragraph*{University 1}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] Student
+    \item[] Student
+    \item[] Student
+\end{enumerate}
 
-\part*{References}
-\bibliographystyle{nsf}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
+\section*{Refereed Journal Publications}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item Big paper
+%    \item\bibentry{}
+\end{enumerate}
 
-\newpage
+\section*{Books \& Book Contributions}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item Book chapter
+%    \item\bibentry{}
+\end{enumerate}
 
-\begin{appendices}
+\section*{Refereed Conference Proceedings}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item Big paper
+%    \item\bibentry{}
+\end{enumerate}
 
-    \renewcommand{\thesection}{\Roman{section}}
-    \titleformat{\section}{\normalfont\large\bfseries}{Appendix \thesection:}{1ex}{}[]
+\section*{Non-Refereed Technical Reports}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item Big paper
+%    \item\bibentry{}
+\end{enumerate}
 
-    \section*{Acronyms}
-    \printnoidxglossary[title={}]
+\section*{Conference Presentations}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item Big paper
+%    \item\bibentry{}
+\end{enumerate}
 
-\end{appendices}
+\section*{Teaching Experience}
+\subsection*{Institution 1 $\sq$ Department}
+\subsubsection*{Title}
+\paragraph*{Course}\hfill{\textit{semester}}\\
+Description
 
-%%%%%%% wrap figure around text
-%move to wherever in the text 
-%{l} fixes it on the left margin
-%\begin{wrapfigure}{l}{0.x\textwidth}
-%        \includegraphics[width=0.(x-2)\textwidth]{filename.ext}
-%    \caption{}
-%    \label{fig-}
-%\end{wrapfigure}
-%%%%%%%
+\subsection*{Institution 1 $\sq$ Department}
+\subsubsection*{Title}
+\paragraph*{Course}\hfill{\textit{semester}}\\
+Description
+
+\section*{Related Teaching Experience}
+\subsection*{Institution 1 $\sq$ Department}
+\subsubsection*{Title}
+\paragraph*{Course}\hfill{\textit{semester}}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] Duties
+\end{enumerate}
+Description
+
+\section*{Professional Service}
+\subsection*{Institution 1}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] service things
+\end{enumerate}
+
+\subsection*{Academic Search Committees}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] committee
+\end{enumerate}
+
+\subsection*{Peer Reviewer}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] Journals, etc.
+\end{enumerate}
+
+\subsection*{Conference Committees}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] committee
+\end{enumerate}
+
+\subsection*{Technical Session Organizer}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] Session 
+\end{enumerate}
+
+\subsection*{Technical Session Chair}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[] Session 
+\end{enumerate}
+
+\subsection*{Panels}
+\subsubsection*{Moderator}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]Panel 
+\end{enumerate}
+
+\subsubsection*{Panelist}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]Panel 
+\end{enumerate}
+
+\subsection*{Workshops}
+\subsubsection*{Workshop}\hfill{\textit{Time}}\\
+Description
+
+\subsection*{Invited Talks}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]Big talk\hfill{\textit{Date}}
+\end{enumerate}
+
+\subsection*{Symposia Organizer}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]Symposium 1\hfill{\textit{Date}}
+\end{enumerate}
+
+\subsection*{Community Service}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]Service\hfill{\textit{Date}}
+\end{enumerate}
+
+\subsection*{Outreach \& Related Professional Activities}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]Activity\hfill{\textit{Date}}
+\end{enumerate}
+
+\section*{Professional Training}
+\subsection*{Event}
+\subsubsection*{Role}
+\paragraph*{Title}\hfill{\textit{Time}}\\
+Description
+
+\section*{Awards \& Fellowships}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]Award\hfill{\textit{Date}}
+\end{enumerate}
+
+\section*{Professional Societies \& Positions}
+\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item[]Member\hfill{\textit{Date}}
+\end{enumerate}
 

### 2023-05-11 acronyms/acronyms.tex
reset

--- 2022-07-07 acronyms/acronyms.tex
@@
-%%%%%%put this in preamble
+%put this in preamble
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
 \makenoidxglossaries
-%%%%%
-
-%%%%% put this in right before draft
 %%%%% acronyms
 % alphabetical ordering is automated
-\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
 \newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{nrs}{NHRES}{Nuclear Renewable Hybrid Energy System}
-\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{smr}{SMR}{Small Modular Reactor}
-\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
-\newacronym{nus}{NuScale}{NuScale Power, LLC}
-\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
-\newacronym{epri}{EPRI}{Electric Power Research Institute}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{ci}{CI}{Consistency Index}
-\newacronym{cr}{CR}{Consistency Ratio}
-\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
-\newacronym{lwr}{LWR}{Light Water Reactor}
 \newacronym{aps}{APS}{Arizona Public Service} 
@@
 \newacronym{epa}{EPA}{Environmental Protection Agency}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}  
 \newacronym{hx}{HX}{Heat exchanger} 
-\newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
+\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
+\newacronym{inl}{INL}{Idaho National Laboratory} 
+\newacronym{iso}{ISO}{Independent System Operator} 
+\newacronym{msf}{MSF}{Multi-Stage Flash} 
 \newacronym{mwe}{MWe}{Megawatts electricity}
 \newacronym{mwt}{MWth}{Megawatts thermal energy}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation} 
+\newacronym{npp}{NPP}{Nuclear Power Plant} 
+\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission} 
 \newacronym{ies}{IES}{Integrated Energy System} 
+\newacronym{ornl}{ORNL}{Oak Ridge National Laboratory} 
 \newacronym{pv}{PV}{Palo Verde Generating Station} 
@@
 \newacronym{ro}{RO}{Reverse Osmosis} 
-\newacronym{rom}{ROM}{Reduced Order Model} 
+\newacronym{rom}{ROM}{Reduced Order Models} 
+\newacronym{smr}{SMR}{Small Modular Reactor} 
 \newacronym{spe}{SPECO}{Specific Exergy Costing} 
 \newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
-\newacronym{ieo}{IESO}{Independent Electricity System Operator}
-\newacronym{us}{US}{United States}
-\newacronym{med}{MED}{Multiple-Effect Distillation}
-\newacronym{ed}{ED/EDR}{Electrodialysis Reversal}
-\newacronym{nf}{NF}{Nanofiltration}
-\newacronym{jls}{J}{Joules}
-\newacronym{nre}{NREI}{Nuclear Renewable Energy Integration}
-\newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
-\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
-\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
-\newacronym{iso}{ISO}{Independent System Operator} 
-\newacronym{msf}{MSF}{Multi-Stage Flash} 
+\newacronym{ahp}{AHP}{Analytic Hierarchy Procedure}
+\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
+\newacronym{ies}{IESO}{Independent Electricity System Operator}
 \newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
@@
 \newacronym{sq}{SQ}{Significant Quantity}
+\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
+\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
 \newacronym{der}{DER}{Distributed Energy Resource}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
 \newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
@@
 \newacronym{nyi}{NYISO}{New York Independent System Operator}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}
 \newacronym{ac}{AC}{Alternating Current}
 \newacronym{dc}{DC}{Direct Current}
+\newacronym{eia}{EIA}{United States Energy Information Administration}
 \newacronym{pha}{PHA}{Preliminary Hazards Analysis}
 \newacronym{inc}{I\&C}{Instrumentation and Controls}
+%\newacronym{}{}{}
 %%%%%
-
-%%%%%put this in the document where the acronym list will appear - Acronyms is in section format
-\printnoidxglossary%[title{}] %removes automated Acronyms title too add custom
-%%%%%
+%put this in the document somewhere
+\printnoidxglossary
+%%%%

### 2023-05-11 journal/manuscript/document-package/draft-manuscript/draft-manuscript.tex
Update draft-manuscript.tex
reset

@@
 %the rest list numerically
-%
 %%%%%
+
+%%%%% general 
 \documentclass[11pt,a4paper]{article}
@@
 %%%%% references
-\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
-%\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
-%\setlength{\bibsep}{7pt} %sets space between references
+%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
+\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+\setlength{\bibsep}{7pt} %sets space between references
 %\renewcommand{\bibsection}{} %suppresses large 'references' heading
@@
 \usepackage{pdfpages}
-
 \usepackage{wrapfig} %wraps figures around text
-\setlength{\intextsep}{0.05mm}
-\setlength{\columnsep}{0.05mm}
-
+\setlength{\intextsep}{0.00mm}
+\setlength{\columnsep}{1.00mm}
 \usepackage[singlelinecheck=false,labelfont=bf]{caption}
 \usepackage{subcaption}
-\captionsetup[table]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
-\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
-
-%\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=1pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
-%\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Tab.}} %sets space above caption, 'figure' format
+\captionsetup[table]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
+\captionsetup[figure]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
+\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Table}} %sets space above caption, 'figure' format
 %%%%%
 
-\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-\usepackage[inline]{enumitem}
-\usepackage{boldline}
-\usepackage{makecell}
-\usepackage{booktabs}
-\usepackage{amssymb}
-\usepackage{gensymb}
-\usepackage{amsmath}
-\usepackage{physics}
-\usepackage{lscape}
-\usepackage{array}
-\usepackage{chngcntr}
-\usepackage[hidelinks]{hyperref}
-\usepackage{sectsty}
-\usepackage{textcomp}
-\usepackage{lastpage}
-\usepackage{xargs} %for \newcommandx
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
-\usepackage{marginnote}
-\usepackage{gensymb}
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
-\usepackage[toc,title]{appendix}
-\usepackage[figure,table]{totalcount}
-
-\usepackage[capitalise]{cleveref}
-
 %%%%% watermark
-\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
-\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-\SetWatermarkScale{0.20}
-\SetWatermarkScale{0.25}
+%\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
+%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+%\SetWatermarkScale{0.20}
 %%%%%
 
+%%%%% cross referencing files
 %\usepackage{xr} %for revisions - will cross reference from one file to here
 %\externaldocument{/path/to/auxfilename} %aux file needed
+%%%%%
 
 %%%%% toc and glossaries
+\usepackage[title,titletoc]{appendix}
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
@@
 %\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
-%\titleformat{\part}{\normalfont\Large\bfseries\filcenter}{\thepart}{}{}[]
-%\titlespacing\part{0pt}{0.75\baselineskip}{0.50\baselineskip}
+%\titleformat{\part}{\normalfont\large\bfseries\filcenter}{\thepart}{}{}[]
+%\titlespacing*\part{0pt}{0.00\baselineskip}{0.75\baselineskip}
 %\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
-%\titlespacing*\section{0pt}{0.55\baselineskip}{0.35\baselineskip}
+%\titlespacing*\section{0pt}{0.65\baselineskip}{0.35\baselineskip}
 %\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
-%\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.30\baselineskip}
-\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+%\titlespacing*\subsection{0pt}{0.50\baselineskip}{0.25\baselineskip}
+%\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+%\titlespacing*\paragraph{0pt}{0.45\baselineskip}{0.25\baselineskip}
+%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+%\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
+\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
 \titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
@@
 \titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
+%%%%%
 
+%%%%% editing
 \newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
@@
 \newcommand{\acsp}{\acrshortpl} %short acronym plural
+%%%%%
 
-\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
-\newcommandx{\por}[2][1=]{\todo[author=Porter,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
-\newcommandx{\sam}[2][1=]{\todo[author=Sam,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\rab}[2][1=]{\todo[author=RAB,tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
-\newcommandx{\sug}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
-\newcommandx{\cmt}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\rab}[2][1=]{\author=RAB,tickmarkheight=0.15cm,todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+%%%%% todonotes
+\newcommandx{\cmt}[2][1=]{\todo[author=\textbf{STRUCTURE},tickmarkheight=0.15cm,linecolor=red,backgroundcolor=red!25,bordercolor=black,#1]{#2}}
+\newcommandx{\con}[2][1=]{\todo[author=\textbf{CONTENT},tickmarkheight=0.15cm,linecolor=brilliantlavender,backgroundcolor=brilliantlavender,bordercolor=black,#1]{#2}}
+\newcommandx{\rab}[2][1=]{\todo[noline,author=\textbf{RAB},backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
 
+%\newcommandx{\jon}[2][1=]{\todo[noline,author=\textbf{ATTN: Johnson},backgroundcolor=blue!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\han}[2][1=]{\todo[noline,author=\textbf{ATTN: Haney},backgroundcolor=OliveGreen!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\rab}[2][1=]{\todo[author=\textbf{RAB},tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\han}[2][1=]{\todo[author=\textbf{ATTN: Haney},tickmarkheight=0.15cm,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
+%\newcommandx{\jon}[2][1=]{\todo[author=\textbf{ATTN: Johnson},tickmarkheight=0.15cm,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+
+% highlighting 
+\DeclareRobustCommand{\hlc}[1]{{\sethlcolor{LimeGreen}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlh}[2]{#1}
+    \else
+    \newcommand{\hlh}[2]{\han{#2}\hlc{#1}}
+    \fi
+    \makeatother
+
+\DeclareRobustCommand{\hld}[1]{{\sethlcolor{CornflowerBlue}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlj}[2]{#1}
+    \else
+    \newcommand{\hlj}[2]{\jon{#2}\hld{#1}}
+    \fi
+    \makeatother
+
+\DeclareRobustCommand{\hlf}[1]{{\sethlcolor{lightmauve}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlb}[2]{#1}
+    \else
+    \newcommand{\hlb}[2]{\rab{#2}\hlf{#1}}
+    \fi
+    \makeatother
+%%%%%
+
+%%%%% table alignments
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
@@
 \makeatother
+
+\makeatletter
+\renewcommand*\l@section{\@dottedtocline{1}{0.25em}{2em}} %change first for indentation of label; second for title
+\makeatother
+
+\setcounter{tocdepth}{2}
 
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Manuscript ID - Load following}
+\lhead{\scriptsize Manuscript ID or Journal name}
 \chead{\scriptsize \textit{First Author et al. - Draft Manuscript}}
@@
 
+%%%%%%% citations
 \begin{filecontents}{references.bib}
     @misc{
-        hun19a,
-        author = {Hunton, Paul J. and England, Robert T.},
-        title = {{Addressing nuclear I\&C modernization through application of techniques employed in other industries}},
-        year = {2019},
-        note = {{INL/EXT-19-55799}}
-    }
-    @conference{
-        las18a,
-        author = {Lassell, S. A. and Hawari, A. I. and Benjamin, J. S. and Barnes, K. T. and Wright, V. L.},
-        title = {{Methodology development for cybersecurity robustness and vulnerability assessment of university research reactors}},
-        year = { 2018},
-        organization = {Proc., American Nuclear Society Annual Meeting },
-        address = {Philadelphia, Pennsylvania}
+        nye15a,
+        author = {Nye, Jr., Joseph S.},
+        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
+        year = {2015},
+        note = {{The Washington Post}}
     }
     @article{
-        mac19a,
-        author = {MacLean, Trevor and Borrelli, Robert and Haney, Michael},
-        title = {{Cybersecurity modeling of non-critical nuclear power plant digital instrumentation}},
-        journal = {{Critical Infrastructure Protection XIII, J. Staggs, S. Shenoi, eds.}},
-        volume = {{Chapter 5}},
-        year = {2019},
-        pages = {86}
+        mil20a,
+        author = {Miller, James N.},
+        title = {No to no first use — for now},
+        journal = {Bulletin of the Atomic Scientists},
+        volume = {76},
+        pages = {8},
+        year  = {2020}
     }
@@
     }
-    @book{
-        ost19a,
-        author = {Ostrom, Lee T. and Wilhelmsen, Cheryl A.},
-        title = {{Risk assessment: Tools, techniques, and their applications}},
-        publisher = {John Wiley \& Sons, Inc.},
-        isbn = {978-1119483465},
-        year = {2019}
+    @conference{
+        ben20a,
+        author = {Benjamin, Jacob and Haney, Michael},
+        title = {{Nonproliferation of Cyber Weapons}},
+        year = { 2020},
+        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
+        address = {Las Vegas, Nevada}
     }
 \end{filecontents}
+%%%%%%%
 
@@
 
-%spacing options
+%\listoftodos[List of revisions]
+%\newpage
+
+%%%%% spacing
 \onehalfspacing %linespacing
@@
 %\spacing{1.25} %equivalent to 1.5 line spacing in Word
+%%%%%
 
-%linenumbering
+%%%%% linenumbering
 \linenumbers %toggle line numbers
 \pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[1] %line numbering interval
+\modulolinenumbers[3] %line numbering interval
+%%%%%
 
@@
 \newpage
+%\section*{Table of Contents}
+%\tableofcontents
+%\newpage
 
@@
 \section*{Tables}
-
 {%
@@
 \section*{Figures}
-
 {%
@@
 
+%%%%% use for toc
+%    \titleformat{\part}{\normalfont\Large\bfseries\filcenter}{\thepart}{0ex}{}[]
+%    \part*{Appendices}
+%%%%%
+
+    \setcounter{section}{0}
     \renewcommand{\thesection}{\Roman{section}}
-    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]
+    \titleformat{\section}{\normalfont\Large\bfseries}{Appendix \thesection:}{1ex}{}[]
 
-\section{Title}\label{app-}
+    \section{Just appendix title} \label{app-}
 

### 2023-05-11 proposal-documents/white-paper/white-paper-general-preproposal.tex
reset

@@
 %%%%% watermark
-%\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
-%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-%\SetWatermarkScale{0.20}
+\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
+\SetWatermarkText{\shortstack{CONFIDENTIAL\\do not distribute}}
+\SetWatermarkScale{0.20}
 %%%%%
@@
 \section*{Workscopes in Brief}
-\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=0.5in]
-    \item\textbf{X.} (\textit{Lead - ; Support - , })
-        \begin{enumerate}[topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
-            \item\textit{x.}
-            \item\textit{x.}
-        \end{enumerate}
-    \item\textbf{X.} (\textit{Lead - ; Support - , })
-        \begin{enumerate}[resume,topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
-            \item\textit{x.}
-            \item\textit{x.}
+\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - , })
+        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
         \end{enumerate}
@@
 
-\section*{Importance and Relevance to Objectives} 
-\subsection*{Background}
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
 
-\subsection*{Relevant literature}
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
 
-\subsection*{Recently funded work}
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
 
-\subsection*{Unique project features}
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+            \item\textit{.}
+        \end{enumerate}
+\end{enumerate}
 
-\section*{Research Workscopes \& Tasks}
+\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Crosscutting discussions \& follow on activities.} (\textit{Full team})
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{Identify lessons learned.}
+            \item\textit{Develop future work.}
+            \item\textit{Reproducibility \& validation.}
+        \end{enumerate}
+\end{enumerate}
+
+\section*{Relevant Background}
+
+\section*{Related Research \& Funding Efforts}
+
+\section*{Team synergy}
+
+\section*{Unique project features}
 
@@
 \begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
+    \item\textbf{Workscope title} (\textit{Lead - ; Support - })
         \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
@@
 
+\paragraph*{Motivation}
+
 \paragraph*{Goals}
@@
 
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
 \begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
+    \item\textbf{Workscope title} (\textit{Lead - ; Support - })
         \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
@@
 
+\paragraph*{Motivation}
+
 \paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
 
 \begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Workscope title} 
-        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{This task.}
-            \item\textit{That task.}
-            \item\textit{Another task.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item A brief explanation or a subtask if needed.
-                \end{enumerate*}
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
         \end{enumerate}
@@
 
+\paragraph*{Motivation}
+
 \paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\textit{Through this Workscope, we will \ldots}
 
-\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
-    \item\textbf{Crosscutting discussions \& follow on activities.} 
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
         \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
-            \item\textit{Identify lessons learned.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Lessons learned will be applied to \ldots . 
-                \end{enumerate*}
-            \item\textit{Develop future work.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item \ldots.
-                    \item \ldots.
-                    \item \ldots.
-                \end{enumerate*}
-            \item\textit{Reproducibility \& validation.}
-                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
-                    \item Explore avenues to reproduce and validate results \ldots .
-                \end{enumerate*}
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
         \end{enumerate}
@@
 
+\paragraph*{Motivation}
+
 \paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{.} (\textit{Lead - ; Support - })
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will \ldots}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
+
+\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
+    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
+        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
+            \item\textit{Identify lessons learned.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{Develop future work.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+            \item\textit{Reproducibility \& validation.}
+                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
+                    \item Details.
+                    \item Details.
+                \end{enumerate}
+        \end{enumerate}
+\end{enumerate}
+
+\paragraph*{Motivation}
+
+\paragraph*{Goals}
+\textit{Through this Workscope, we will wrapup the major findings of project activities and pursue new avenues of research with colleagues in the field.}
+
+\paragraph*{Investigator duties}
+\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
+    \item[].
+    \item[].
+    \item[].
+\end{itemize}
 
@@
         I. 
-        &\x\textbf{X}
+        &\x
         & 
@@
         II. 
-        &\x\textbf{X} 
+        &\x
         & 
@@
         III. 
-        &\x\textbf{X} 
+        &\x 
         & 
@@
         IV. 
-        &\x\textbf{X}
+        &\x
         & 
@@
         V. 
-        &\x\textbf{X} 
+        &\x 
         & 
@@
         VI. 
-        &\x\textbf{X} 
+        &\x 
         & 
@@
         &
+        &
+        &
+        &
+        &
+        &
+        &
         &\x
         &\x
-        &\x
-        &\x
-        &\x
-        &\x
-        &
-        &
         \\
@@
         &
+        &
+        &
         &\x
         &\x
-        &\x
-        &
         \\
@@
 
-\part*{References}
-\bibliographystyle{nsf}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
-
 %\newpage
@@
 
-%\section{Title}\label{app-}
+%    \section{Acronyms}
+%    \printnoidxglossary[title={}]
+
+%    \section{Title}\label{app-}
 
@@
 
-%wrap figure around text
+%remove page break if there are page limits
+%\vspace{0.5\baselineskip}
+
+\part*{References}
+\bibliographystyle{nsf}
+%\bibliographystyle{neup}
+\setlength{\bibhang}{0pt}
+\bibliography{references}
+
+%%%%%%% wrap figure around text
 %move to wherever in the text
 %{l} fixes it on the left margin
-%{L} floats
 %\begin{wrapfigure}{l}{0.x\textwidth}
-%       \includegraphics[width=0.(x-2)\textwidth]{}
+%        \includegraphics[width=0.(x-2)\textwidth]{filename.ext}
 %    \caption{}

### 2023-05-11 sty/slither/HeliumCycle.py

@@ -1,0 +1,195 @@
+import convert
+
+class Fluid:
+    R = 8.3145 #kJ/kmol-K
+    cPs = {'helium': 5.1926,
+           'argon': 0.5203,
+           'neon': 1.0299,
+           'air':1.005,
+           'hydrogen':14.307}
+    MWs = {'helium': 4.003,
+           'argon': 39.948,
+           'neon': 20.183,
+           'air':28.97,
+           'hydrogen':2.016}
+
+    def __init__(self,gas):
+        self.cP = Fluid.cPs[gas] #kJ/kg-K
+        self.MW = Fluid.MWs[gas]
+        self.specR = self.R/self.MW #kJ/kg-K
+        self.cV = self.cP-self.specR #kJ/kg-K
+        self.gamma = self.cP/self.cV
+        self.gamma_bar = (self.gamma-1)/self.gamma
+
+
+############################################################
+class State:
+    MASSFLOW = 0 #kg/s
+
+    states = {1:'Compressor Inlet',
+              2:'Compressor Outlet',
+              3:'Expander Inlet',
+              4:'Expander Outlet'}
+
+    lowP,highP = 0.93,7
+    temperatures = {1:25,
+                    2:'???',
+                    3:900,
+                    4:'???'} #degC
+
+    pressures = {1:lowP,
+                 2:highP,
+                 3:highP,
+                 4:lowP} #MPa
+
+    list = []
+
+    def __init__(self, stream):
+        self.stream = stream
+        self.name = State.states[stream]
+        self.pressure = State.pressures[stream]
+        self.temperature = State.temperatures[stream]
+        State.list.append(self)
+
+
+    def get_info(self):
+        print(f'Stream {self.stream} is the {self.name}. T = {round(self.temperature,1)} degC, P= {self.pressure} MPa ')
+
+    @classmethod
+    def carnot_efficiency(cls):
+        hotT, coldT = max(stream.temperature for stream in cls.list), min(stream.temperature for stream in cls.list)
+        hotT, coldT = convert.Temperature(hotT,'C','K'), convert.Temperature(coldT,'C','K')
+        eta = 100*(1-coldT/hotT)
+        eta = round(eta,2)
+        print(f'Carnot Efficiency: {eta}%')
+
+    @classmethod
+    def massflow(cls):
+        print(f'Mass Flow Rate {round(cls.MASSFLOW,1)} kg/s')
+
+##################################
+class Equipment:
+    list=[]
+
[…]

### 2023-05-17 journal/manuscript/document-package/draft-manuscript/draft-manuscript.tex
journal draft update

@@
 %%%%% references
-%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
-\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
+\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
+%\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
 \setlength{\bibsep}{7pt} %sets space between references
@@
 %%%%% watermark
-%\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
-%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-%\SetWatermarkScale{0.20}
+\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
+\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+\SetWatermarkScale{0.20}
 %%%%%
@@
 %\st{} does strikethrough using soul package but does not like acronyms
-\newcommand{\blucell}{\cellcolor{aliceblue}} %use to shade in table cell
-\newcommand{\grycekk}{\cellcolor{lightgray}} %use to shade in table cell
-\newcommand{\whicell}{\cellcolor{antiquewhite}} %use to shade in table cell
+\newcommand{\blc}{\cellcolor{aliceblue}} %use to shade in table cell
+\newcommand{\grc}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\whc}{\cellcolor{antiquewhite}} %use to shade in table cell
 %%%%%
@@
 % highlighting 
-\DeclareRobustCommand{\hlc}[1]{{\sethlcolor{LimeGreen}\hl{#1}}}
-\makeatletter
-    \if@todonotes@disabled
-    \newcommand{\hlh}[2]{#1}
-    \else
-    \newcommand{\hlh}[2]{\han{#2}\hlc{#1}}
-    \fi
-    \makeatother
+%\DeclareRobustCommand{\hlc}[1]{{\sethlcolor{LimeGreen}\hl{#1}}}
+%\makeatletter
+%    \if@todonotes@disabled
+%    \newcommand{\hlh}[2]{#1}
+%    \else
+%    \newcommand{\hlh}[2]{\han{#2}\hlc{#1}}
+%    \fi
+%    \makeatother
 
-\DeclareRobustCommand{\hld}[1]{{\sethlcolor{CornflowerBlue}\hl{#1}}}
-\makeatletter
-    \if@todonotes@disabled
-    \newcommand{\hlj}[2]{#1}
-    \else
-    \newcommand{\hlj}[2]{\jon{#2}\hld{#1}}
-    \fi
-    \makeatother
+%\DeclareRobustCommand{\hld}[1]{{\sethlcolor{CornflowerBlue}\hl{#1}}}
+%\makeatletter
+%    \if@todonotes@disabled
+%    \newcommand{\hlj}[2]{#1}
+%    \else
+%    \newcommand{\hlj}[2]{\jon{#2}\hld{#1}}
+%    \fi
+%    \makeatother
 
@@
 \makeatother
-%%%%%
-
-%%%%% archived section commands - use titlesec
-%\makeatletter
-%\renewcommand\section{%
-%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
-%    {\large \normalfont \bfseries}}%
-
-%\makeatletter
-%\renewcommand\paragraph{%
-%    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
-%    {\normalfont \normalsize \bfseries}}%
-
-%\makeatletter
-%\renewcommand\subparagraph{%
-%    \@startsection{subparagraph}{5}{\z@ }{0.40\baselineskip}{-1em}
-%    {\normalfont \normalsize \itshape }}%
-
-%\makeatletter
-%\renewcommand\subsection{%
-%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
-%    {\large \normalfont \bfseries}}%
 %%%%%
@@
     \author{
-        First, 
-        Second,
-        \textsuperscript{*}Third
+        \textsuperscript{a}First, 
+        \textsuperscript{b}Second,
+        \textsuperscript{c,*}Third
         \\ \\ \\
-        Affiliation 1\\
-        Affiliation 2\\
-        Affilation 3
+        \textsuperscript{a}Affiliation 1\\
+        \textsuperscript{b}Affiliation 2\\
+        \textsuperscript{c}Affilation 3
         \\ \\ \\
@@
 
-\begin{appendices}
+%\begin{appendices}
 
@@
 
-    \setcounter{section}{0}
-    \renewcommand{\thesection}{\Roman{section}}
-    \titleformat{\section}{\normalfont\Large\bfseries}{Appendix \thesection:}{1ex}{}[]
+%    \setcounter{section}{0}
+%    \renewcommand{\thesection}{\Roman{section}}
+%    \titleformat{\section}{\normalfont\Large\bfseries}{Appendix \thesection:}{1ex}{}[]
 
-    \section{Just appendix title} \label{app-}
+%    \section{Just appendix title} \label{app-}
 
-\end{appendices}
+%\end{appendices}
 

### 2023-09-13 journal/manuscript/document-package/draft-manuscript/draft-manuscript.tex
journal paper template

@@
 \makenoidxglossaries
+\AtBeginEnvironment{appendices}{\crefalias{section}{appendix}}
 \usepackage{titlesec,titletoc}
@@
 \titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
-\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
+\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
 %%%%%
@@
 %%%%% todonotes
-\newcommandx{\cmt}[2][1=]{\todo[author=\textbf{STRUCTURE},tickmarkheight=0.15cm,linecolor=red,backgroundcolor=red!25,bordercolor=black,#1]{#2}}
-\newcommandx{\con}[2][1=]{\todo[author=\textbf{CONTENT},tickmarkheight=0.15cm,linecolor=brilliantlavender,backgroundcolor=brilliantlavender,bordercolor=black,#1]{#2}}
+\newcommandx{\cmt}[2][1=]{\todo[author=\textbf{STRUCTURE},tickmarkheight=0.15cm,linecolor=black,backgroundcolor=red!25,bordercolor=black,#1]{#2}}
+\newcommandx{\con}[2][1=]{\todo[author=\textbf{CONTENT},tickmarkheight=0.15cm,linecolor=black,backgroundcolor=brilliantlavender,bordercolor=black,#1]{#2}}
 \newcommandx{\rab}[2][1=]{\todo[noline,author=\textbf{RAB},backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
@@
 
-%%%%%%% citations
+%%%%% citations
 \begin{filecontents}{references.bib}
@@
 \end{filecontents}
-%%%%%%%
+%%%%%
 

### 2023-10-04 journal/manuscript/document-package/draft-manuscript/draft-manuscript.tex
journal template update

@@
+%%%%%
 %@TheDoctorRAB
-%standard white paper/preproposal format
-%
+%standard journal format
 %%%%%
@@
 \usepackage[capitalise]{cleveref}
+\usepackage{nameref}
+%\usepackage{parskip}
 %%%%%
@@
 \makenoidxglossaries
-\AtBeginEnvironment{appendices}{\crefalias{section}{appendix}}
+\AtBeginEnvironment{appendices}{\crefalias{section}{appendix}} %for cleveref to use Appendix
 \usepackage{titlesec,titletoc}
@@
 \titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
-\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
+\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
 %%%%%
@@
 %\st{} does strikethrough using soul package but does not like acronyms
-\newcommand{\blc}{\cellcolor{aliceblue}} %use to shade in table cell
-\newcommand{\grc}{\cellcolor{lightgray}} %use to shade in table cell
-\newcommand{\whc}{\cellcolor{antiquewhite}} %use to shade in table cell
 %%%%%
@@
 \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
+\newcommand{\x}{\cellcolor{aliceblue}} %use to shade in table cell
+\newcommand{\y}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\z}{\cellcolor{antiquewhite}} %use to shade in table cell
 %%%%%
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Manuscript ID or Journal name}
+\lhead{\scriptsize Consent based siting -- Communities of place}
 \chead{\scriptsize \textit{First Author et al. - Draft Manuscript}}
@@
 
-%%%%% citations
+%%%%%%% citations
 \begin{filecontents}{references.bib}
@@
 \end{filecontents}
-%%%%%
+%%%%%%%
 
@@
 %    \renewcommand{\thesection}{\Roman{section}}
-%    \titleformat{\section}{\normalfont\Large\bfseries}{Appendix \thesection:}{1ex}{}[]
+%    \titleformat{\section}{\normalfont\large\bfseries}{Appendix \thesection:}{1ex}{}[]
 

### 2023-10-04 journal/reviewer-response/JOURNALID-RX.tex

@@
 \setcounter{secnumdepth}{5} %set subsection to nth level
-%\usepackage{mypythonhighlight}
-%\usepackage{lipsum}
+\usepackage{needspace}
+\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
+\usepackage[inline]{enumitem}
+\usepackage{boldline}
+\usepackage{makecell}
+\usepackage{booktabs}
+\usepackage{amssymb}
+\usepackage{gensymb}
+\usepackage{amsmath,nicefrac}
+\usepackage{physics}
+\usepackage{lscape}
+\usepackage{array}
+\usepackage{chngcntr}
+\usepackage{hyperref}
+\hypersetup{colorlinks,linkcolor=black,citecolor=black,urlcolor=blue} 
+\usepackage{sectsty}
+\usepackage{textcomp}
+\usepackage{lastpage}
+\usepackage{xargs} %for \newcommandx
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
+\usepackage{soul}
+\usepackage{color}
+\usepackage{marginnote}
+\usepackage[figure,table]{totalcount}
+\usepackage[capitalise]{cleveref}
+\usepackage{nameref}
+\usepackage{parskip} %\noindent
+%%%%%
+
+%%%%% tikz
+\usepackage{pgf}
+\usepackage{tikz} % required for drawing custom shapes
+\usetikzlibrary{shapes,arrows,automata,trees}
+%%%%%
 
@@
 \usepackage{pdfpages}
-
 \usepackage{wrapfig} %wraps figures around text
-\setlength{\intextsep}{0.05mm}
-\setlength{\columnsep}{0.05mm}
-
+\setlength{\intextsep}{0.00mm}
+\setlength{\columnsep}{1.00mm}
 \usepackage[singlelinecheck=false,labelfont=bf]{caption}
 \usepackage{subcaption}
-\captionsetup[table]{justification=centering,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
-\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
-
-%\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=1pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
-%\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Tab.}} %sets space above caption, 'figure' format
+\captionsetup[table]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
+\captionsetup[figure]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
+\captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
+\captionsetup[wraptable]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Table}} %sets space above caption, 'figure' format
 %%%%%
 
-\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
-\usepackage[inline]{enumitem}
-\usepackage{boldline}
-\usepackage{makecell}
-\usepackage{booktabs}
-\usepackage{amssymb}
-\usepackage{gensymb}
-\usepackage{amsmath}
-\usepackage{physics}
-\usepackage{lscape}
-\usepackage{array}
-\usepackage{chngcntr}
-\usepackage[hidelinks]{hyperref}
-\usepackage{sectsty}
-\usepackage{textcomp}
-\usepackage{lastpage}
-\usepackage{xargs} %for \newcommandx
-\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes} %makes colored boxes for commenting
-\usepackage{marginnote}
-\usepackage[toc,title]{appendix}
-\usepackage[figure,table]{totalcount}
+%%%%% watermark
+\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
+\SetWatermarkText{\shortstack{CONFIDENTIAL\\do not distribute}}
+\SetWatermarkScale{0.20}
+%%%%%
 
-\usepackage[capitalise]{cleveref}
-
-%\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
-%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-%\SetWatermarkScale{0.20}
-
+%%%%% cross referencing files
+\usepackage{xr} %for revisions - will cross reference from one file to here
+\externaldocument{../marked-manuscript/JOURNAL-ID-marked-manuscript} %crossref through aux file
 %to crossref between files
@@
 %pdflatex this file next
-%manuscript needs correponding code here with /path/to/this-file
-\usepackage{xr}
-\externaldocument{/path/to/manuscript} %crossref through aux file
+%%%%%
 
-\makeatletter %make text labels
+%%%%% toc and glossaries
+\usepackage[toc,title]{appendix}
+\usepackage[acronym,nomain,nonumberlist]{glossaries}
+\makenoidxglossaries
+\AtBeginEnvironment{appendices}{\crefalias{section}{appendix}}
+\usepackage{titlesec,titletoc}
+\titleformat{\part}{\normalfont\large\bfseries\filcenter}{\thepart}{}{}[]
+\titlespacing\part{0pt}{0.0\baselineskip}{0.70\baselineskip}
+\titleformat{\section}{\normalfont\large\bfseries\filcenter}{\thesection}{-1em}{}[]
+\titlespacing*\section{0pt}{0.95\baselineskip}{0.50\baselineskip}
+\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
+\titlespacing*\subsection{0pt}{0.55\baselineskip}{0.30\baselineskip}
+\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
+%\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
+%\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
+\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+\titlespacing*\subparagraph{0pt}{0.45\baselineskip}{0.20\baselineskip}
+%%%%%
+
+%%%%% editing
+\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
+\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
+\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
+%\newcommand{\sk}[1]{\sout{#1}} %shortcut for default strikethrough - do not sk through citep
+\newcommand\sk{\bgroup\markoverwith{\textcolor{red}{\rule[0.5ex]{1pt}{1pt}}}\ULon} %strikethrough with red line; not in \section{}
+%\st{} does strikethrough using soul package but does not like acronyms
+\newcommand{\blucell}{\cellcolor{aliceblue}} %use to shade in table cell
+\newcommand{\grycekk}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\whicell}{\cellcolor{antiquewhite}} %use to shade in table cell
+
+% make text labels
+% \labeltext{Comment to include in marked manuscript}{reviewernumber-keyword-keyword}
+% in marked manuscript - \ref{reviewernumber-keyword-keyword}
+\makeatletter 
 \newcommand{\labeltext}[3][]{%
@@
 }
+%%%%%
 
-%%%%% toc and glossaries
-\usepackage[acronym,nomain,nonumberlist]{glossaries}
-\makenoidxglossaries
-\usepackage{titlesec,titletoc}
-%\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
-%\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
+%%%%% colors
+%http://latexcolor.com/
+%https://en.wikibooks.org/wiki/LaTeX/Colors#:~:text=black%2C%20blue%2C%20brown%2C%20cyan,be%20available%20on%20all%20systems.
+\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
+\definecolor{antiquewhite}{rgb}{0.98, 0.92, 0.84}
+\definecolor{lightmauve}{rgb}{0.86, 0.82, 1.0}
+\definecolor{brilliantlavender}{rgb}{0.96, 0.73, 1.0}
+\definecolor{brandeisblue}{rgb}{0.0, 0.44, 1.0}
+\definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
+%%%%%
 
-\titleformat{\part}{\normalfont\large\bfseries\filcenter}{\thepart}{}{}[]
-\titlespacing\part{0pt}{0.75\baselineskip}{0.50\baselineskip}
-
-\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
-\titlespacing*\section{0pt}{0.55\baselineskip}{0.35\baselineskip}
-
-\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
-\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.30\baselineskip}
-
-\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
-\titlespacing*\paragraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
-
-%\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
-%\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
-
-\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
-\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
-
-\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
-\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
-\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
-\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
-\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
-
+%%%%% acronyms
 \newcommand{\acf}{\acrfull} %full acronym
@@
 \newcommand{\acsp}{\acrshortpl} %short acronym plural
+%%%%%
 
-\newcommandx{\que}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}} %query
-\newcommandx{\por}[2][1=]{\todo[author=Porter,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}} %suggested change
-\newcommandx{\sam}[2][1=]{\todo[author=Sam,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}} %comment
-\newcommandx{\rab}[2][1=]{\todo[author=RAB,tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}} %omit
+%%%%% todonotes
+\newcommandx{\cmt}[2][1=]{\todo[author=\textbf{STRUCTURE},tickmarkheight=0.15cm,linecolor=black,backgroundcolor=red!25,bordercolor=black,#1]{#2}}
+\newcommandx{\con}[2][1=]{\todo[author=\textbf{CONTENT},tickmarkheight=0.15cm,linecolor=black,backgroundcolor=aliceblue,bordercolor=black,#1]{#2}}
+\newcommandx{\rab}[2][1=]{\todo[noline,author=\textbf{RAB},backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
+\newcommandx{\one}[2][1=]{\todo[author=\textbf{Reviewer 1},tickmarkheight=0.15cm,linecolor=Black,backgroundcolor=OliveGreen!25,bordercolor=black,#1]{#2}} 
+\newcommandx{\two}[2][1=]{\todo[author=\textbf{Reviewer 2},tickmarkheight=0.15cm,linecolor=Black,backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
+\newcommandx{\thr}[2][1=]{\todo[author=\textbf{Reviewer 3},tickmarkheight=0.15cm,linecolor=black,backgroundcolor=brilliantlavender,bordercolor=black,#1]{#2}} %omit
 
+%\newcommandx{\jon}[2][1=]{\todo[noline,author=\textbf{ATTN: Johnson},backgroundcolor=blue!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\han}[2][1=]{\todo[noline,author=\textbf{ATTN: Haney},backgroundcolor=OliveGreen!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\rab}[2][1=]{\todo[author=\textbf{RAB},tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
+%\newcommandx{\han}[2][1=]{\todo[author=\textbf{ATTN: Haney},tickmarkheight=0.15cm,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
+%\newcommandx{\jon}[2][1=]{\todo[author=\textbf{ATTN: Johnson},tickmarkheight=0.15cm,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+
+% highlighting 
+\DeclareRobustCommand{\hlc}[1]{{\sethlcolor{LimeGreen}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlh}[2]{#1}
+    \else
+    \newcommand{\hlh}[2]{\han{#2}\hlc{#1}}
+    \fi
+    \makeatother
+
+\DeclareRobustCommand{\hld}[1]{{\sethlcolor{CornflowerBlue}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlj}[2]{#1}
+    \else
+    \newcommand{\hlj}[2]{\jon{#2}\hld{#1}}
+    \fi
+    \makeatother
+
+\DeclareRobustCommand{\hlf}[1]{{\sethlcolor{lightmauve}\hl{#1}}}
+\makeatletter
+    \if@todonotes@disabled
+    \newcommand{\hlb}[2]{#1}
+    \else
+    \newcommand{\hlb}[2]{\rab{#2}\hlf{#1}}
+    \fi
+    \makeatother
+%%%%%
+
+%%%%% table alignments
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}} %uses \raggedright with m,p{} in table column
@@
 \makeatother
-
-%\makeatletter
-%\renewcommand\section{%
-%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
-%    {\large \normalfont \bfseries}}%
-
-%\makeatletter
-%\renewcommand\paragraph{%
-%    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
-%    {\normalfont \normalsize \bfseries}}%
-
-%\makeatletter
-%\renewcommand\subparagraph{%
-%    \@startsection{subparagraph}{5}{\z@ }{0.40\baselineskip}{-1em}
-%    {\normalfont \normalsize \itshape }}%
-
-%\makeatletter
-%\renewcommand\subsection{%
-%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
-%    {\large \normalfont \bfseries}}%
+%%%%%
 
@@
 \lhead{\scriptsize JOURNAL-ID}
-\chead{\scriptsize \textit{Author et al.} - Reviewer X}
+\chead{\scriptsize \textit{Response to Peer Review}}
 \rhead{\scriptsize \today}
-\rfoot{\thepage} %move page number to bottom right
+\rfoot{\thepage}
 %%%%%
 
-\begin{filecontents}{references.bib} 
-\end{filecontents}
+%%%%% citations
+%\begin{filecontents}{references.bib} 
+%\end{filecontents}
+%%%%%
 
 %%%%% acronyms
+% alphabetical ordering is automated
+\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{smr}{SMR}{Small Modular Reactor}
+\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
+\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{ci}{CI}{Consistency Index}
+\newacronym{cr}{CR}{Consistency Ratio}
+\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
+\newacronym{lwr}{LWR}{Light Water Reactor}
+\newacronym{oer}{OER}{Online Educational Resource}
+\newacronym{lms}{LMS}{Learning Management System}
+\newacronym{cps}{CPS}{Cyber-Physical Systems}
+\newacronym{nsf}{NSF}{National Science Foundation}
+\newacronym{wsc}{WSC}{Western Services Corporation}
+\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
+\newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{bwr}{BWR}{Boiling Water Reactor}
+\newacronym{roi}{ROI}{Return on Investment}
+\newacronym{ic}{I\&C}{Instrumentation \& Controls}
+\newacronym{ics}{ICS}{Industrial Control Systems}
+\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
+\newacronym{ip}{IP}{Internet Protocol}
+\newacronym{udp}{UDP}{User Datagram Protocol}
+\newacronym{tva}{TVA}{Tennessee Valley Authority}
+\newacronym{plc}{PLC}{Programmable Logic Controller}
+\newacronym{vfd}{VFD}{Variable Frequency Drive}
+\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
+\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
+\newacronym{mim}{MITM}{Man in the Middle}
+\newacronym{dos}{DDoS}{Distributed Denial of Service}
+\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
+\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
+\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
+\newacronym{cs}{CS}{Critical System}
+\newacronym{loc}{LOCA}{Loss of Coolant Accident}
+\newacronym{hmi}{HMI}{Human Machine Interface}
+\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
+\newacronym{bol}{BOL}{Beginning-of-Life}
+\newacronym{eol}{EOL}{End-of-Life}
+\newacronym{mol}{MOL}{Middle-of-Life}
+\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
+\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{neu}{NEUP}{Nuclear Energy University Program}
+\newacronym{doe}{DOE}{United States Department of Energy}
+\newacronym{nei}{NEI}{Nuclear Energy Institute}
+\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
+\newacronym{rcs}{RCS}{Reactor Cooling System}
+\newacronym{con}{IC}{Initial Condition}
+\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
+\newacronym{pcap}{PCAP}{packet capture file}
+\newacronym{dc}{DC}{Direct-Current}
+\newacronym{ac}{AC}{Alternating-Current}
+\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
+\newacronym{snl}{SNL}{Sandia National Laboratory}
+\newacronym{cie}{CIE}{Cyber-Informed Engineering}
+\newacronym{cds}{CRDS}{Control Rod Drive System}
+\newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
+\newacronym{fma}{FMEA}{Failure Modes \& Effects Analysis}
+\newacronym{rpn}{RPN}{Risk Priority Number}
+\newacronym{scr}{SCR}{silicon controller rectifier}
+\newacronym{hvc}{HVAC}{Heating, Ventilation \& Air Conditioning}
+\newacronym{ttb}{TTB}{Time-to-Boil}
+\newacronym{sis}{SIS}{Safety Instrumented System}
+\newacronym{anl}{ANL}{Argonne National Laboratory}
+\newacronym{aps}{APS}{Arizona Public Service} 
+\newacronym{arm}{ARMA}{Autoregressive Moving Average} 
+\newacronym{eia}{EIA}{Energy Information Agency}
+\newacronym{epa}{EPA}{Environmental Protection Agency}
+\newacronym{hx}{HX}{Heat exchanger} 
+\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
+\newacronym{inl}{INL}{Idaho National Laboratory} 
+\newacronym{iso}{ISO}{Independent System Operator} 
+\newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
+\newacronym{mwe}{MWe}{Megawatts electricity}
+\newacronym{mwt}{MWth}{Megawatts thermal energy}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation} 
+\newacronym{npp}{NPP}{Nuclear Power Plant} 
+\newacronym{ies}{IES}{Integrated Energy System} 
+\newacronym{ornl}{ORNL}{Oak Ridge National Laboratory} 
+\newacronym{pv}{PV}{Palo Verde Generating Station} 
+\newacronym{rav}{RAVEN}{Risk Analysis Virtual Environment} 
+\newacronym{ro}{RO}{Reverse Osmosis} 
+\newacronym{rom}{ROM}{Reduced Order Model} 
+\newacronym{spe}{SPECO}{Specific Exergy Costing} 
+\newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
+\newacronym{ahp}{AHP}{Analytic Hierarchy Procedure}
+\newacronym{ieo}{IESO}{Independent Electricity System Operator}
+\newacronym{us}{US}{United States}
+\newacronym{med}{MED}{Multiple-Effect Distillation}
+\newacronym{ed}{ED/EDR}{Electrodialysis Reversal}
+\newacronym{nf}{NF}{Nanofiltration}
+\newacronym{jls}{J}{Joules}
+\newacronym{nre}{NREI}{Nuclear Renewable Energy Integration}
+\newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
+\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
+\newacronym{nus}{NuScale}{NuScale Power, LLC}
+\newacronym{eu}{EU}{European Union}
 %\newacronym{}{}{}
@@
 
-\part*{Reviewer X}
+\pagenumbering{gobble}
 
-\noindent Thank you for the peer review of this manuscript.
+\section*{Abstract}
+
+\newpage
+
+\section*{Brief Remarks from the Authors}
+Thank you for the peer review of this manuscript.
 Each comment was considered carefully.
-The manuscript has been revised accordingly in the hope that the updated paper is worthy of publication.
+The manuscript has been revised substantially in accordance with the reviews to update the paper for publication.
 A detailed response to each comment is provided in this document.
 
+In the `Marked Manuscript', omitted text is indicated by \sk{strikethrough}; omitted section titles by \sout{strikethrough}.
+Added content is shown in \edit{color}.
+For major reviewer comments, there will be a text box with an accompanying explanation.\one{This content was added/removed based on the reviewer comment, and this is why the content is being replaced.} Please note the manuscript was significantly revised, and the section numbers have changed as a result.
+There is a lot of discussion provided in this document because this authorship takes peer review very seriously.
+The responses were intended to illuminate the reasoning in revising the manuscript.
+
+A `Clean Manuscript' is also provided based on the revisions.
+
+\newpage
+
+\pagenumbering{arabic}
+
+\section*{Preface from the Reviewer} %if provided
+
 \section*{General comments}
-\begin{enumerate}[series=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
+\begin{enumerate}[series=general,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.50in,rightmargin=0.50in]
     \item Comment
@@
 Revisions
-\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*),leftmargin=*]
     \item\labeltext{Statement.}{1-label}
@@
 
-\begin{enumerate}[resume=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
+\begin{enumerate}[resume=general,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.50in,rightmargin=0.50in]
     \item Comment
@@
 Revisions
-\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*),leftmargin=*]
     \item\labeltext{Statement.}{1-label-2}
@@
 \section*{Editorial comments}
-\begin{enumerate}[series=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
-    \item Abstract 1 - \labeltext{`...essential components \textit{to} back-end...' $\rightarrow$ `...essential components \textit{of} back-end...'}{1-ed1}
+\begin{enumerate}[series=editorial,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.50in,rightmargin=0.50in]
+    \item Abstract 1 -- \labeltext{`...essential components \textit{to} back-end...' $\rightarrow$ `...essential components \textit{of} back-end...'}{1-ed1}
 \end{enumerate}
@@
 \subsection*{Response}
-\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
+\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*),leftmargin=*]
     \item Reply
@@
 
-\begin{enumerate}[resume=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
-    \item Abstract 1 - \labeltext{`...essential components \textit{to} back-end...' $\rightarrow$ `...essential components \textit{of} back-end...'}{1-ed1}
+\begin{enumerate}[resume=editorial,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.50in,rightmargin=0.50in]
+    \item Abstract 1 -- \labeltext{`...essential components \textit{to} back-end...' $\rightarrow$ `...essential components \textit{of} back-end...'}{1-ed1}
 \end{enumerate}
@@
 
-%\part*{References}
 %\bibliographystyle{nsf}
@@
 
+\begin{appendices}
+
+    \pagenumbering{gobble}
+    \renewcommand{\thesection}{\Roman{section}}
+    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]
+
+\newpage
+
+    \section{Acronyms}
+    \printnoidxglossary[title={}]
+
+%\newpage
+
+%    \section{Figures}\label{app-figures}
+
+\end{appendices}
+
 \end{document}

### 2023-10-10 acronyms/acronyms.tex
acronyms

--- 2022-08-23 acronyms/acronyms.tex
@@
-%%%%%%put this in preamble
+%put this in preamble
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
 \makenoidxglossaries
-%%%%%
-
-%%%%% put this in right before draft
 %%%%% acronyms
 % alphabetical ordering is automated
+\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
 \newacronym{ahp}{AHP}{Analytical Hierarchy Process}
+\newacronym{inl}{INL}{Idaho National Laboratory}
+\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
 \newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{bol}{BOL}{beginning-of-life}
-\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
-\newacronym{ccc}{CCC}{Computing Community Consortium}
-\newacronym{ci}{CI}{Consistency Index}
-\newacronym{cps}{CPS}{Cyber-Physical Systems}
-\newacronym{cr}{CR}{Consistency Ratio}
-\newacronym{cs}{CS}{Critical System}
-\newacronym{doe}{DOE}{United States Department of Energy}
-\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
-\newacronym{dos}{DDoS}{Distributed Denial of Service}
-\newacronym{eia}{EIA}{U.S. Energy Information Administration}
-\newacronym{eol}{EOL}{end-of-life}
-\newacronym{epri}{EPRI}{Electric Power Research Institute}
-\newacronym{hmi}{HMI}{Human Machine Interface}
-\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
-\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
-\newacronym{ic}{I\&C}{Instrumentation \& Controls}
-\newacronym{ics}{ICS}{Industrial Control Systems}
-\newacronym{ies}{IES}{Integrated Energy System}
-\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{ip}{IP}{Internet Protocol}
-\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
-\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
-\newacronym{kmp}{KMP}{key measurement point}
-\newacronym{lms}{LMS}{Learning Management System}
-\newacronym{loc}{LOCA}{Loss of Coolant Accident}
-\newacronym{mim}{MITM}{Man in the Middle}
-\newacronym{mol}{MOL}{middle-of-life}
-\newacronym{mwe}{MWe}{Megawatts-electric}
-\newacronym{nei}{NEI}{Nuclear Energy Institute}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{neu}{NEUP}{Nuclear Energy University Program}
-\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
 \newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{nsf}{NSF}{National Science Foundation}
-\newacronym{nus}{NuScale}{NuScale Power, LLC}
-\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
-\newacronym{oer}{OER}{Online Educational Resource}
-\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{plc}{PLC}{Programmable Logic Controller}
-\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
-\newacronym{pwr}{PWR}{Pressurized Water Reactor}
-\newacronym{roi}{ROI}{Return on Investment}
-\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
-\newacronym{smr}{SMR}{Small Modular Reactor}
-\newacronym{snm}{SNM}{special nuclear material}
-\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
-\newacronym{tva}{TVA}{Tennessee Valley Authority}
-\newacronym{udp}{UDP}{User Datagram Protocol}
-\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
-\newacronym{vfd}{VFD}{Variable Frequency Drive}
-\newacronym{wsc}{WSC}{Western Services Corporation}
-\newacronym{mba}{MBA}{material balance area}
-\newacronym{nma}{NMA}{nuclear materials accounting}
-\newacronym{sei}{SEID}{standard error of the inventory difference}
-\newacronym{tru}{TRU}{transuranic element}
-\newacronym{des}{DES}{discrete event simulation}
-\newacronym{sq}{SQ}{significant quantity}
-\newacronym{pyn}{PyNE}{Python for Nuclear Engineering}
-\newacronym{haz}{HAZOP}{hazard and operability analysis}
-\newacronym{msr}{MSR}{molten salt reactor}
-\newacronym{mpt}{MPACT}{Materials Protection, Accounting and Control Technology}
-\newacronym{aoo}{AOO}{Anticipated Operational Occurrences}
-\newacronym{dbe}{DBE}{Design Basis Events}
-\newacronym{bde}{BDBE}{Beyond Design Basis Events}
-\newacronym{ies}{IES}{Integrated Energy Systems}
-\newacronym{mca}{MC\&A}{Materials Control and Accountability}
-\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
-\newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{nrs}{NHRES}{Nuclear Renewable Hybrid Energy System}
-\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
 \newacronym{smr}{SMR}{Small Modular Reactor}
@@
 \newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
+\newacronym{ci}{CI}{Consistency Index}
+\newacronym{cr}{CR}{Consistency Ratio}
 \newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
 \newacronym{lwr}{LWR}{Light Water Reactor}
-\newacronym{aps}{APS}{Arizona Public Service} 
-\newacronym{arm}{ARMA}{Autoregressive Moving Average} 
-\newacronym{eia}{EIA}{Energy Information Agency}
-\newacronym{epa}{EPA}{Environmental Protection Agency}
-\newacronym{hx}{HX}{Heat exchanger} 
-\newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
-\newacronym{mwt}{MWth}{Megawatts thermal energy}
-\newacronym{ies}{IES}{Integrated Energy System} 
-\newacronym{pv}{PV}{Palo Verde Generating Station} 
-\newacronym{rav}{RAVEN}{Risk Analysis Virtual Environment} 
-\newacronym{ro}{RO}{Reverse Osmosis} 
-\newacronym{rom}{ROM}{Reduced Order Model} 
-\newacronym{spe}{SPECO}{Specific Exergy Costing} 
-\newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
-\newacronym{ieo}{IESO}{Independent Electricity System Operator}
-\newacronym{med}{MED}{Multiple-Effect Distillation}
-\newacronym{ed}{ED/EDR}{Electrodialysis Reversal}
-\newacronym{nf}{NF}{Nanofiltration}
-\newacronym{jls}{J}{Joules}
-\newacronym{nre}{NREI}{Nuclear Renewable Energy Integration}
-\newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
-\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
-\newacronym{iso}{ISO}{Independent System Operator} 
-\newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
-\newacronym{un}{UN}{United Nations}
-\newacronym{ict}{ICT}{Information and communications technologies}
-\newacronym{nws}{NWS}{Nuclear Weapons States}
-\newacronym{nnws}{NNWS}{Non Nuclear Weapons States}
-\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
-\newacronym{nnsa}{NNSA}{National Nuclear Security Administration}
-\newacronym{fbi}{FBI}{Federal Bureau of Investigation}
-\newacronym{nsg}{NSG}{Nuclear Suppliers Group}
-\newacronym{mad}{MAD}{Mutually Assured Destruction}
-\newacronym{wmd}{WMD}{Weapons of Mass Destruction}
-\newacronym{sq}{SQ}{Significant Quantity}
-\newacronym{der}{DER}{Distributed Energy Resource}
-\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
+\newacronym{eia}{EIA}{U.S. Energy Information Administration}
+\newacronym{oer}{OER}{Online Educational Resource}
+\newacronym{lms}{LMS}{Learning Management System}
+\newacronym{cps}{CPS}{Cyber-Physical Systems}
+\newacronym{nsf}{NSF}{National Science Foundation}
+\newacronym{wsc}{WSC}{Western Services Corporation}
+\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
+\newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{roi}{ROI}{Return on Investment}
+\newacronym{ic}{I\&C}{Instrumentation \& Controls}
+\newacronym{mwe}{MWe}{Megawatts-electric}
+\newacronym{ics}{ICS}{Industrial Control System}
+\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
+\newacronym{ip}{IP}{Internet Protocol}
+\newacronym{udp}{UDP}{User Datagram Protocol}
+\newacronym{tva}{TVA}{Tennessee Valley Authority}
+\newacronym{plc}{PLC}{Programmable Logic Controller}
+\newacronym{vfd}{VFD}{Variable Frequency Drive}
+\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
+\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
+\newacronym{mim}{MITM}{Man in the Middle}
+\newacronym{dos}{DDoS}{Distributed Denial of Service}
+\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
+\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
+\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
+\newacronym{cs}{CS}{Critical System}
+\newacronym{loc}{LOCA}{Loss of Coolant Accident}
+\newacronym{hmi}{HMI}{Human Machine Interface}
+\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
+\newacronym{bol}{BOL}{beginning-of-life}
+\newacronym{eol}{EOL}{end-of-life}
+\newacronym{mol}{MOL}{middle-of-life}
+\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator}
+\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{neu}{NEUP}{Nuclear Energy University Program}
+\newacronym{doe}{DOE}{United States Department of Energy}
+\newacronym{nei}{NEI}{Nuclear Energy Institute}
+\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
+\newacronym{rcs}{RCS}{Reactor Cooling System}
+\newacronym{nic}{NIC}{Network Interface Card}
+\newacronym{gui}{GUI}{Graphical User Interface}
+\newacronym{pc}{PCAP}{Packet Capture File}
+\newacronym{dc}{DC}{direct-current}
+\newacronym{ac}{AC}{alternating-current}
+\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
+\newacronym{ste}{STEM}{Science, Technology, Engineering, and Mathematics}
+\newacronym{pi}{PI}{Principal Investigator}
+\newacronym{ans}{ANS}{American Nuclear Society}
+\newacronym{sac}{SACNAS}{Society for the Advancement of Chicanos/Hispanics and Native Americans in Science}
+\newacronym{ore}{ORED}{Office of Research and Economic Development}
+\newacronym{rfd}{RFD}{Office of Research and Faculty Development}
+\newacronym{nbe}{NSBE}{National Society of Black Engineers}
+\newacronym{inp}{INPO}{Institute of Nuclear Power Operations}
+\newacronym{nan}{NANTeL}{National Academy for Nuclear Training e-Learning}
+\newacronym{cda}{CDA}{Critical Digital Assets}
+\newacronym{nca}{NCA-CD}{National Center of Excellence in Cyber Defense}
+\newacronym{ttx}{TTX}{Tabletop Exercise}
+\newacronym{cie}{CIE}{Cyber-Informed Engineering}
+\newacronym{aas}{AAS}{Adversary-As-A-Service}
 \newacronym{usa}{US}{United States}
-\newacronym{pfc}{PFC}{Primary Frequency Control}
-\newacronym{sfc}{SFC}{Secondary Frequency Control}
-\newacronym{ace}{ACE}{Area Control Error}
-\newacronym{var}{VAr}{Volt-Amps Reactive}
-\newacronym{dsm}{DSM}{Demand Side Management}
-\newacronym{nyi}{NYISO}{New York Independent System Operator}
-\newacronym{ac}{AC}{Alternating Current}
-\newacronym{dc}{DC}{Direct Current}
+\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
+\newacronym{fy}{FY}{Fiscal Year}
+%\newacronym{}{}{}
 %%%%%
-
-%%%%%put this in the document where the acronym list will appear - Acronyms is in section format
-\printnoidxglossary%[title{}] %removes automated Acronyms title too add custom
-%%%%%
+%put this in the document somewhere
+\printnoidxglossary
+%%%%

### 2024-02-08 acronyms/acronyms.tex
acronyms
thesis defense presentation

@@
 \newacronym{fy}{FY}{Fiscal Year}
+\newacronym{eps}{EPSCoR}{Established Program to Stimulate Competitive Research}
+\newacronym{nas}{NAS}{National Academies}
+\newacronym{brc}{BRC}{Blue Ribbon Commission on America's Nuclear Future}
+\newacronym{hlw}{HLW}{High-Level Radioactive Waste}
+\newacronym{cbs}{CBS}{Consent-Based Siting}
+\newacronym{wpp}{WIPP}{Waste Isolation Pilot Plant}
+\newacronym{cfr}{CFR}{Code of Federal Regulations}
 %\newacronym{}{}{}

### 2024-04-10 acronyms/acronyms.tex
global acronyms file

@@
-%put this in preamble
-\usepackage[acronym,nomain,nonumberlist]{glossaries}
-\makenoidxglossaries
-%%%%% acronyms
-% alphabetical ordering is automated
 \newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
@@
 \newacronym{cfr}{CFR}{Code of Federal Regulations}
-%\newacronym{}{}{}
-%%%%%
-%put this in the document somewhere
-\printnoidxglossary
-%%%%
+\newacronym{gao}{GAO}{Government Accountability Office}
+\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
+\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
+\newacronym{inl}{INL}{Idaho National Laboratory}
+\newacronym{anl}{ANL}{Argonne National Laboratory}
+\newacronym{npp}{NPP}{Nuclear Power Plant}
+\newacronym{smr}{SMR}{Small Modular Reactor}
+\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
+\newacronym{nus}{NuScale}{NuScale Power, LLC}
+\newacronym{nrc}{NRC}{Nuclear Regulatory Commission}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
+\newacronym{ci}{CI}{Consistency Index}
+\newacronym{cr}{CR}{Consistency Ratio}
+\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
+\newacronym{lwr}{LWR}{Light Water Reactor}
+\newacronym{eia}{EIA}{U.S. Energy Information Administration}
+\newacronym{oer}{OER}{Online Educational Resource}
+\newacronym{lms}{LMS}{Learning Management System}
+\newacronym{cps}{CPS}{Cyber-Physical Systems}
+\newacronym{nsf}{NSF}{National Science Foundation}
+\newacronym{wsc}{WSC}{Western Services Corporation}
+\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
+\newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{bwr}{BWR}{Boiling Water Reactor}
+\newacronym{roi}{ROI}{Return on Investment}
+\newacronym{ic}{I\&C}{Instrumentation \& Controls}
+\newacronym{mwe}{MWe}{Megawatts-electric}
+\newacronym{ics}{ICS}{Industrial Control Systems}
+\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
+\newacronym{ip}{IP}{Internet Protocol}
+\newacronym{udp}{UDP}{User Datagram Protocol}
+\newacronym{tva}{TVA}{Tennessee Valley Authority}
+\newacronym{plc}{PLC}{Programmable Logic Controller}
+\newacronym{vfd}{VFD}{Variable Frequency Drive}
+\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
+\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
+\newacronym{mim}{MITM}{Man in the Middle}
+\newacronym{dos}{DDoS}{Distributed Denial of Service}
+\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
+\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
+\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
+\newacronym{dra}{DRA}{Dynamic Risk Assessment}
+\newacronym{cs}{CS}{Critical System}
+\newacronym{loc}{LOCA}{Loss of Coolant Accident}
+\newacronym{hmi}{HMI}{Human Machine Interface}
+\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
+\newacronym{bol}{BOL}{Beginning-of-Life}
+\newacronym{eol}{EOL}{End-of-Life}
+\newacronym{mol}{MOL}{Middle-of-Life}
+\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
+\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{neu}{NEUP}{Nuclear Energy University Program}
+\newacronym{doe}{DOE}{Department of Energy}
+\newacronym{nei}{NEI}{Nuclear Energy Institute}
+\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
+\newacronym{rcs}{RCS}{Reactor Cooling System}
+\newacronym{con}{IC}{Initial Condition}
+\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
+\newacronym{pcap}{PCAP}{packet capture file}
+\newacronym{dc}{DC}{Direct-Current}
+\newacronym{ac}{AC}{Alternating-Current}
+\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
+\newacronym{snl}{SNL}{Sandia National Laboratory}
+\newacronym{cie}{CIE}{Cyber-Informed Engineering}
+\newacronym{cds}{CRDS}{Control Rod Drive System}
+\newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
+\newacronym{fma}{FMEA}{Failure Modes \& Effects Analysis}
+\newacronym{rpn}{RPN}{Risk Priority Number}
+\newacronym{scr}{SCR}{silicon controller rectifier}
+\newacronym{hvc}{HVAC}{Heating, Ventilation \& Air Conditioning}
+\newacronym{ttb}{TTB}{Time-to-Boil}
+\newacronym{sis}{SIS}{Safety Instrumented System}
+\newacronym{cis}{CISF}{Consolidated Interim Storage Facility}
+\newacronym{iea}{IEA}{International Energy Agency}
+\newacronym{snf}{SNF}{Spent Nuclear Fuel}
+\newacronym{cic}{CISAC}{Center for Interantional Security and Cooperation}
+\newacronym{usa}{US}{United states}
+\newacronym{nwa}{NWPA}{Nuclear Waste Policy Act}
+\newacronym{brc}{BRC}{Blue Ribbon Commission on America's Nuclear Future}
+\newacronym{one}{NE}{Office of Nuclear Energy}
+\newacronym{hlw}{HLW}{High-Level Radioactive Waste}
+\newacronym{cbs}{CBS}{Consent-Based Siting}
+\newacronym{cgc}{CGC}{Common Ground Consortium}
+\newacronym{cop}{CoPL}{Communities of Place}
+\newacronym{cor}{CoPR}{Communities of Practice}
+\newacronym{coh}{CoH}{Communities of Historical Experience}
+\newacronym{ej}{EJ}{Environmental Justice}
+\newacronym{ite}{ITEK}{Indigenous Traditional Technical Ecological Knowledge}
+\newacronym{wpp}{WIPP}{Waste Isolation Pilot Plant}
+\newacronym{iae}{IAEA}{International Atomic Energy Agency}
+\newacronym{rfi}{RFI}{Request for Information}
+\newacronym{sta}{STAND}{Siting Tool for Advanced Nuclear Development}
+\newacronym{ors}{OR-SAGE}{Oak Ridge Siting Analysis for Power Generation Expansion}
+\newacronym{cfr}{CFR}{Code of Federal Regulations}
+\newacronym{gis}{GIS}{Geographic Information System}
+\newacronym{mtu}{MTU}{Metric Ton of Uranium}
+\newacronym{mth}{MTHM}{Metric Ton of Heavy Metal}
+\newacronym{isa}{ISA}{Idaho Settlement Agreement}
+\newacronym{tru}{TRU}{Transuranic Waste}
+\newacronym{cej}{CEJEST}{Climate and Economic Justice Screening Tool}
+\newacronym{eja}{EJAtlas}{Global Atlas of Environmental Justice}
+\newacronym{ejs}{EJScreen}{Environmental Justice Screening and Mapping Tool}
+\newacronym{fpz}{FPTZ}{Fastest Path to Zero}
+\newacronym{tra}{WebTRAGIS}{Web-Based Transportation Routing Analysis Geographic Information System}
+\newacronym{lit}{LITE}{Land-area Identification, Tagging, and Exploration}
+\newacronym{str}{START}{Stakeholder Tool for Assessing Radioactive Transportation}
+\newacronym{nri}{NRIC}{National Reactor Innovation Center}
+\newacronym{sec}{SEC}{Site Evaluation Criteria}
+\newacronym{ceq}{CEQ}{Council on Environmental Quality}
+\newacronym{epa}{EPA}{Environmental Protection Agency}
+\newacronym{unf}{UNF-ST\&DARDS}{Used Nuclear Fuel-Storage, Transportation \& Disposal Analysis Resource and Data System}
+\newacronym{gui}{GUI}{Graphical User Interface}
+\newacronym{fem}{FEMA}{Federal Emergency Management Agency}
+\newacronym{rap}{RAPT}{Resilience Analysis and Planning Tool}
+\newacronym{gid}{GEOID}{Geographic Identifier}
+\newacronym{icr}{I-CREWS}{Idaho Community-Engaged Resilience for Energy-Water Systems}
+\newacronym{ew}{E-W}{Energy-Water}
+\newacronym{ml}{ML}{Machine Learning}
+\newacronym{set}{SETS}{Socio-Environmental Technological System}
+\newacronym{eps}{EPSCoR}{Established Program to Stimulate Competitive Research}
+\newacronym{rii}{RII}{Research Infrastructure Improvement}
+\newacronym{aoo}{AOO}{Anticipated Operational Occurrence}
+\newacronym{dbe}{DBE}{Design Basis Event}
+\newacronym{bbe}{BDBE}{Beyond Design Basis Event}
+\newacronym{fta}{FTA}{Fault Tree Analysis}
+\newacronym{eta}{ETA}{Event Tree Analysis}
+\newacronym{haz}{HAZOP}{hazard and operability analysis}

### 2024-04-10 presenations/research/research-presentation-template.tex
thesis defense presentation
global acronyms file

@@
 %@TheDoctorRAB
-%standard white paper/preproposal format
+%
+%presentation template for class slides and research presentations
+%allows for citations in slide and a list at the end
 %
@@
 %the rest list numerically
+%
+%
+%%% citations on slides 
+%
+%\citep{xxxnna} where the citation should go
+%\blfootnote{\fontsize\cite{xxxnna}\fontsize\bibentry{xxxnna}} before \end{frame}
+%
+%
 %%%%%
@@
 \beamertemplatenavigationsymbolsempty
+\addtobeamertemplate{footnote}{\hskip -2em}{} %pushes footnote to margin
+%%% font style - can add size, etc.
+%https://tug.ctan.org/macros/latex/contrib/beamer/doc/beameruserguide.pdf
 \setbeamerfont{title}{series=\bfseries}
+\setbeamerfont{frametitle}{series=\bfseries}
+\setbeamerfont{footline}{series=\bfseries}
+\setbeamerfont{author}{series=\bfseries}
+\setbeamerfont{institute}{series=\bfseries}
+\setbeamerfont{date}{series=\bfseries}
 \setbeamertemplate{page number in head/foot}[framenumber] %just gives slide number; comment out for 1/7, 2/7...
-\setbeamertemplate{caption}[numbered] %numbers figures and tables
-\setbeamertemplate{footnote}{%
-  \parindent 1em\noindent%
-  \raggedright
-  \linespread{0.5}
-  \hbox to 1.8em{\hfil\insertfootnotemark}\insertfootnotetext\par\vspace*{-0.2em}%
-}
-\addtobeamertemplate{footnote}{\hskip -2em}{} %pushes footnote to margin
+%%%%%
+
+%%%%% colors
+%http://latexcolor.com/
+%https://en.wikibooks.org/wiki/LaTeX/Colors#:~:text=black%2C%20blue%2C%20brown%2C%20cyan,be%20available%20on%20all%20systems.
+%sam root
 \definecolor{BackGround}{RGB}{255,250,240}
+\definecolor{PrideGold}{RGB}{241,179,0}
+\definecolor{Silver}{RGB}{165,169,180}
+\definecolor{White}{RGB}{255,255,255}
+\definecolor{Black}{RGB}{25,25,25}
+\definecolor{Chrome}{RGB}{245,245,245}
+%%% general
+\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
+\definecolor{antiquewhite}{rgb}{0.98, 0.92, 0.84}
+\definecolor{lightmauve}{rgb}{0.86, 0.82, 1.0}
+\definecolor{brilliantlavender}{rgb}{0.96, 0.73, 1.0}
+\definecolor{brandeisblue}{rgb}{0.0, 0.44, 1.0}
+\definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
+%%% set slides
 \setbeamercolor{background canvas}{bg=BackGround}
+%%%
+\setbeamercolor{block title}{bg=Silver,fg=Black}
+\setbeamercolor{block body}{bg=Silver!20,fg=Black}
+\setbeamercolor{block title alerted}{bg=Black,fg=Silver}
+\setbeamercolor{block body alerted}{bg=PrideGold,fg=Black}
+\setbeamercolor{alerted text}{fg=Silver}
+\setbeamercolor*{block title example}{bg=PrideGold,fg=Black}
+\setbeamercolor*{block body example}{bg=PrideGold!20,fg=Black}
+%%%
+\setbeamercolor*{palette primary}{bg=PrideGold,fg=Black}
+\setbeamercolor*{palette secondary}{bg=PrideGold,fg=Black}
+\setbeamercolor*{palette tertiary}{bg=PrideGold,fg=Black}
+%%%
+\setbeamercolor*{titlelike}{bg=PrideGold,fg=Black}
+\setbeamercolor*{title}{bg=PrideGold,fg=Black}
+\setbeamercolor*{item}{fg=PrideGold}
+\setbeamercolor*{caption name}{fg=PrideGold}
+%%%
+\setbeamercolor*{sidebar}{fg=PrideGold,bg=Black}
+\setbeamercolor*{title in sidebar}{fg=PrideGold}
+\setbeamercolor*{author in sidebar}{fg=PrideGold}
+\setbeamercolor*{section in sidebar}{fg=PrideGold}
+%%%
+\setbeamercolor{section in toc}{fg=Black}
+\setbeamercolor{subsection in toc}{fg=Black}
+%%%
+\setbeamercolor{page number in head/foot}{fg=Black,bg=PrideGold}
+%\setbeamercolor{footline}{bg=Black}
+%%%
+\setbeamercolor{bibliography entry author}{fg=Black}
+\setbeamercolor{bibliography entry note}{fg=Black}
+\setbeamercolor{bibliography entry title}{fg=Black}
+%%%
+\newcommand{\x}{\cellcolor{aliceblue}} %use to shade in table cell
+\newcommand{\y}{\cellcolor{lightgray}} %use to shade in table cell
+\newcommand{\z}{\cellcolor{antiquewhite}} %use to shade in table cell
+
 %%%%%
@@
 %\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
-%\usepackage[pagewise]{lineno} %line numbering
-%\usepackage{setspace}
+\usepackage[pagewise]{lineno} %line numbering
+\usepackage{setspace}
 \usepackage{ulem} %strikethrough - do not \sout{\cite{}}
 \usepackage{graphicx}
-\usepackage{pythonhighlight,verbatim}
-%\usepackage{mypythonhighlight,verbatim}
+\usepackage{mypythonhighlight,verbatim}
 \usepackage{filecontents}
@@
 \renewcommand{\dateseparator}{.}
-\graphicspath{{../img/}} %path to graphics
-%\setcounter{secnumdepth}{5} %set subsection to nth level
+\graphicspath{{img/}} %path to graphics
+\setcounter{secnumdepth}{5} %set subsection to nth level
 \usepackage{needspace}
-%\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst; comment out on presentations
+\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
 \usepackage[inline]{enumitem}
@@
 \usepackage{times}
+%\renewcommand{\sfdefault}{ubuntu}
 %arial - uncomment next two lines
@@
 %%%%% references
-\usepackage{bibentry}
 %\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
 \usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
-\setlength{\bibsep}{5pt} %sets space between references
+\usepackage{bibentry}
+\setlength{\bibsep}{7pt} %sets space between references
 %\renewcommand{\bibsection}{} %suppresses large 'references' heading
@@
 \usepackage{longtable} %need to put label at top under caption then \\ - use spacing
-%\usepackage{tablefootnote}
+\usepackage{tablefootnote}
 \usepackage{tabularx}
@@
 \usepackage{subcaption}
-\captionsetup[table]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
-\captionsetup[figure]{justification=centering,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
+\captionsetup[table]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
+\captionsetup[figure]{justification=justified,skip=5pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format
 \captionsetup[wrapfigure]{justification=centering,aboveskip=0pt,belowskip=0pt,labelformat={default},labelsep=period,name={Fig.}} %sets space above caption, 'figure' format
@@
 %%%%% toc and glossaries
-%\usepackage[toc,title]{appendix}
+\usepackage[toc,title]{appendix}
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
@@
 
-%%%%% colors
-%http://latexcolor.com/
-%https://en.wikibooks.org/wiki/LaTeX/Colors#:~:text=black%2C%20blue%2C%20brown%2C%20cyan,be%20available%20on%20all%20systems.
-\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
-\definecolor{antiquewhite}{rgb}{0.98, 0.92, 0.84}
-\definecolor{lightmauve}{rgb}{0.86, 0.82, 1.0}
-\definecolor{brilliantlavender}{rgb}{0.96, 0.73, 1.0}
-\definecolor{brandeisblue}{rgb}{0.0, 0.44, 1.0}
-\definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
-
-\newcommand{\x}{\cellcolor{aliceblue}} %use to shade in table cell
-\newcommand{\y}{\cellcolor{lightgray}} %use to shade in table cell
-\newcommand{\z}{\cellcolor{antiquewhite}} %use to shade in table cell
-%%%%%
-
 %%%%% acronyms
@@
 \newcommandx{\rab}[2][1=]{\todo[noline,author=\textbf{RAB},backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
-
+%%%
 %\newcommandx{\jon}[2][1=]{\todo[noline,author=\textbf{ATTN: Johnson},backgroundcolor=blue!25,bordercolor=black,#1]{#2}}
@@
 %\newcommandx{\jon}[2][1=]{\todo[author=\textbf{ATTN: Johnson},tickmarkheight=0.15cm,linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
-
-% highlighting 
+%%% highlighting 
 \DeclareRobustCommand{\hlc}[1]{{\sethlcolor{LimeGreen}\hl{#1}}}
@@
 %%%%% table contents
-%\makeatletter
-%\renewcommand\tableofcontents{%
-%    \@starttoc{toc}%
-%}
-%\makeatother
-%
-%\makeatletter
-%\renewcommand\listoffigures{%
-%    \@starttoc{lof}%
-%}
-%\makeatother
+\makeatletter
+\renewcommand\tableofcontents{%
+    \@starttoc{toc}%
+}
+\makeatother
 
-%\makeatletter
-%\renewcommand\listoftables{%
-%    \@starttoc{lot}%
-%}
-%\makeatother
+\makeatletter
+\renewcommand\listoffigures{%
+    \@starttoc{lof}%
+}
+\makeatother
 
-%\makeatletter
-%\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
-%\makeatother
+\makeatletter
+\renewcommand\listoftables{%
+    \@starttoc{lot}%
+}
+\makeatother
+
+\makeatletter
+\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
+\makeatother
 %%%%%
 
-%%%%% citations on the frame
+%%%%% user commands
 \newcommand\blfootnote[1]{%
@@
 \makeatother
-%%%%%
 
-%%%%% archived section commands - use titlesec
-%\makeatletter
-%\renewcommand\section{%
-%    \@startsection{section}{1}{\z@ }{0.50\baselineskip}{0.25\baselineskip}
-%    {\large \normalfont \bfseries}}%
+\AtBeginSection[]{
+    \begin{frame}[plain]{}
 
-%\makeatletter
-%\renewcommand\paragraph{%
-%    \@startsection{paragraph}{4}{\z@ }{0.55\baselineskip}{-1em}
-%    {\normalfont \normalsize \bfseries}}%
+         \vfill
 
-%\makeatletter
-%\renewcommand\subparagraph{%
-%    \@startsection{subparagraph}{5}{\z@ }{0.40\baselineskip}{-1em}
-%    {\normalfont \normalsize \itshape }}%
+         \centering
+         \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{titlelike}
+             \usebeamerfont{title}\insertsectionhead\par
+         \end{beamercolorbox}
 
-%\makeatletter
-%\renewcommand\subsection{%
-%    \@startsection{subsection}{2}{\z@ }{0.45\baselineskip}{0.25\baselineskip}
-%    {\large \normalfont \bfseries}}%
+         \vfill
+
+     \end{frame}
+ }
 %%%%%
@@
 \newacronym{ui}{UI}{University of Idaho}
-\newacronym{mcp}{MCNP}{Monte Carlo N-Particle Transport Code}
-\newacronym{loca}{LOCA}{Loss of Coolant Accident}
+\newacronym{ala}{ALARA}{As Low As Reasonably Achievable}
+\newacronym{icr}{I-CREWS}{Idaho Community-Engaged Resilience for Energy-Water Systems}
 %\newacronym{}{}{}
@@
 \date{} %if blank, compiled date will appear in middle right footer; can add something else like location, etc.
+\titlegraphic{\includegraphics[width=0.20\textwidth]{anotherlogo.png}}
+%%%%%
+
+%%%%%
+\logo{\includegraphics[width=0.05\textwidth]{icrews-modified.png}} %lower right on every slide
 %%%%%
@@
 
-\nobibliography*
+\nobibliography* %allows \bibentry citations in the footers of frames/slides; does NOT effect putting bibliography slide at the end
 
@@
     \setbeamertemplate{footline}{}
-    \begin{frame}
+    \begin{frame}[plain]{}
         \titlepage
@@
 \begin{frame}{Title with columns}
-    \begin{columns}
+    \begin{columns}[t]
 
@@
 
-\begin{frame}[plain]{} %subtitle slide will not have any footers or title
-    \centering\LARGE\textbf{}
-\end{frame}
+\section{Section} %Like title slide format (in bubble) will not have any footers or title [plain] frame
 
@@
 \end{longtable}
+\end{frame}
+
+\begin{frame}{The neutron multiplication factor describes a chain reaction}
+    \begin{equation} %will include equation number rightflush as (1)
+        \LARGE
+        \eta \equiv \frac{\nu \Sigma_F}{\Sigma_A}
+    \end{equation}
+
+    \vspace*{\fill}
+
+    \begin{enumerate}[series=outerlist,topsep=0pt,itemsep=21pt,leftmargin=*,label=(\arabic*)]
+        \item[]
+        \item[]
+        \item[]
+        \item[]
+    \end{enumerate}
 \end{frame}

### 2024-04-15 acronyms/acronyms.tex
global acronyms file
acronyms
hazop

@@
 \newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{npp}{NPP}{Nuclear Power Plant}
 \newacronym{smr}{SMR}{Small Modular Reactor}
-\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
 \newacronym{nus}{NuScale}{NuScale Power, LLC}
-\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
 \newacronym{epri}{EPRI}{Electric Power Research Institute}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
 \newacronym{ci}{CI}{Consistency Index}
 \newacronym{cr}{CR}{Consistency Ratio}
-\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
 \newacronym{lwr}{LWR}{Light Water Reactor}
-\newacronym{eia}{EIA}{U.S. Energy Information Administration}
 \newacronym{oer}{OER}{Online Educational Resource}
-\newacronym{lms}{LMS}{Learning Management System}
 \newacronym{cps}{CPS}{Cyber-Physical Systems}
-\newacronym{nsf}{NSF}{National Science Foundation}
 \newacronym{wsc}{WSC}{Western Services Corporation}
-\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
 \newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
-\newacronym{pwr}{PWR}{Pressurized Water Reactor}
 \newacronym{roi}{ROI}{Return on Investment}
-\newacronym{ic}{I\&C}{Instrumentation \& Controls}
 \newacronym{mwe}{MWe}{Megawatts-electric}
-\newacronym{ics}{ICS}{Industrial Control System}
 \newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
-\newacronym{ip}{IP}{Internet Protocol}
 \newacronym{udp}{UDP}{User Datagram Protocol}
-\newacronym{tva}{TVA}{Tennessee Valley Authority}
 \newacronym{plc}{PLC}{Programmable Logic Controller}
-\newacronym{vfd}{VFD}{Variable Frequency Drive}
 \newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
-\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
 \newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
 \newacronym{mim}{MITM}{Man in the Middle}
-\newacronym{dos}{DDoS}{Distributed Denial of Service}
 \newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
-\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
 \newacronym{pra}{PRA}{Probabilistic Risk Assessment}
@@
 \newacronym{loc}{LOCA}{Loss of Coolant Accident}
-\newacronym{hmi}{HMI}{Human Machine Interface}
 \newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{bol}{BOL}{beginning-of-life}
-\newacronym{eol}{EOL}{end-of-life}
-\newacronym{mol}{MOL}{middle-of-life}
 \newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator}
@@
 \newacronym{nic}{NIC}{Network Interface Card}
-\newacronym{gui}{GUI}{Graphical User Interface}
 \newacronym{pc}{PCAP}{Packet Capture File}
-\newacronym{dc}{DC}{direct-current}
-\newacronym{ac}{AC}{alternating-current}
 \newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
@@
 \newacronym{aas}{AAS}{Adversary-As-A-Service}
-\newacronym{usa}{US}{United States}
 \newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
@@
 \newacronym{gao}{GAO}{Government Accountability Office}
-\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
-\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{anl}{ANL}{Argonne National Laboratory}
 \newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{smr}{SMR}{Small Modular Reactor}
 \newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
-\newacronym{nus}{NuScale}{NuScale Power, LLC}
 \newacronym{nrc}{NRC}{Nuclear Regulatory Commission}
-\newacronym{epri}{EPRI}{Electric Power Research Institute}
 \newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{ci}{CI}{Consistency Index}
-\newacronym{cr}{CR}{Consistency Ratio}
 \newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
-\newacronym{lwr}{LWR}{Light Water Reactor}
 \newacronym{eia}{EIA}{U.S. Energy Information Administration}
-\newacronym{oer}{OER}{Online Educational Resource}
 \newacronym{lms}{LMS}{Learning Management System}
-\newacronym{cps}{CPS}{Cyber-Physical Systems}
 \newacronym{nsf}{NSF}{National Science Foundation}
-\newacronym{wsc}{WSC}{Western Services Corporation}
 \newacronym{cae}{CAES}{Center for Advanced Energy Studies}
-\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
 \newacronym{pwr}{PWR}{Pressurized Water Reactor}
 \newacronym{bwr}{BWR}{Boiling Water Reactor}
-\newacronym{roi}{ROI}{Return on Investment}
 \newacronym{ic}{I\&C}{Instrumentation \& Controls}
-\newacronym{mwe}{MWe}{Megawatts-electric}
 \newacronym{ics}{ICS}{Industrial Control Systems}
-\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
 \newacronym{ip}{IP}{Internet Protocol}
-\newacronym{udp}{UDP}{User Datagram Protocol}
 \newacronym{tva}{TVA}{Tennessee Valley Authority}
-\newacronym{plc}{PLC}{Programmable Logic Controller}
 \newacronym{vfd}{VFD}{Variable Frequency Drive}
-\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
 \newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
-\newacronym{mim}{MITM}{Man in the Middle}
 \newacronym{dos}{DDoS}{Distributed Denial of Service}
-\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
 \newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
-\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
 \newacronym{dra}{DRA}{Dynamic Risk Assessment}
-\newacronym{cs}{CS}{Critical System}
-\newacronym{loc}{LOCA}{Loss of Coolant Accident}
 \newacronym{hmi}{HMI}{Human Machine Interface}
-\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
 \newacronym{bol}{BOL}{Beginning-of-Life}
@@
 \newacronym{mol}{MOL}{Middle-of-Life}
-\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
-\newacronym{ccc}{CCC}{Computing Community Consortium}
-\newacronym{neu}{NEUP}{Nuclear Energy University Program}
-\newacronym{doe}{DOE}{Department of Energy}
-\newacronym{nei}{NEI}{Nuclear Energy Institute}
-\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
-\newacronym{rcs}{RCS}{Reactor Cooling System}
 \newacronym{con}{IC}{Initial Condition}
-\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
-\newacronym{pcap}{PCAP}{packet capture file}
 \newacronym{dc}{DC}{Direct-Current}
 \newacronym{ac}{AC}{Alternating-Current}
-\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
 \newacronym{snl}{SNL}{Sandia National Laboratory}
-\newacronym{cie}{CIE}{Cyber-Informed Engineering}
 \newacronym{cds}{CRDS}{Control Rod Drive System}
@@
 \newacronym{nwa}{NWPA}{Nuclear Waste Policy Act}
-\newacronym{brc}{BRC}{Blue Ribbon Commission on America's Nuclear Future}
 \newacronym{one}{NE}{Office of Nuclear Energy}
-\newacronym{hlw}{HLW}{High-Level Radioactive Waste}
-\newacronym{cbs}{CBS}{Consent-Based Siting}
 \newacronym{cgc}{CGC}{Common Ground Consortium}
@@
 \newacronym{ite}{ITEK}{Indigenous Traditional Technical Ecological Knowledge}
-\newacronym{wpp}{WIPP}{Waste Isolation Pilot Plant}
 \newacronym{iae}{IAEA}{International Atomic Energy Agency}
@@
 \newacronym{ors}{OR-SAGE}{Oak Ridge Siting Analysis for Power Generation Expansion}
-\newacronym{cfr}{CFR}{Code of Federal Regulations}
 \newacronym{gis}{GIS}{Geographic Information System}
@@
 \newacronym{set}{SETS}{Socio-Environmental Technological System}
-\newacronym{eps}{EPSCoR}{Established Program to Stimulate Competitive Research}
 \newacronym{rii}{RII}{Research Infrastructure Improvement}
@@
 \newacronym{eta}{ETA}{Event Tree Analysis}
-\newacronym{haz}{HAZOP}{hazard and operability analysis}
+\newacronym{haz}{HAZOP}{Hazard and Operability Analysis}
+\newacronym{onr}{ONR}{Office of Naval Research}
+\newacronym{ui}{UI}{University of Idaho}
+\newacronym{isu}{ISU}{Idaho State University}
+\newacronym{bsu}{BSU}{Boise State University}
+\newacronym{skp}{SKP}{Senior Key Personnel}
+\newacronym{bpc}{BPC}{Broadening Participation in Computing}
+\newacronym{epi}{EPI}{Energy Policy Institute}
+%\newacronym{}{}{}

### 2024-05-14 acronyms/acronyms.tex
more acronyms
aec
acronyms
acro
erda
HEAD
R&D
nts
acronym
nwt
irg

@@
 \newacronym{epi}{EPI}{Energy Policy Institute}
+\newacronym{ym}{YM}{Yucca Mountain}
+\newacronym{nwf}{NWF}{Nuclear Waste Fund}
+\newacronym{aea}{AEA}{Atomic Energy Act}
+\newacronym{aec}{AEC}{Atomic Energy Commission}
+\newacronym{un}{UN}{United Nations}
+\newacronym{des}{DES}{Discrete Event Simulation}
+\newacronym{nem}{NEIM}{Nuclear Engineering \& Industrial Management}
+\newacronym{erd}{ERDA}{Energy Research and Development Administration}
+\newacronym{rd}{R\&D}{Research \& Development}
+\newacronym{nts}{NTS}{Nevada Test Site}
+\newacronym{nrm}{NRMSAC}{Nevada Radioactive Materials Storage Advisory Committee}
+\newacronym{tmi}{TMI}{Three Mile Island}
+\newacronym{nwt}{NWTS}{National Waste Terminal Storage}
+\newacronym{irg}{IRG}{Interagency Review Group on Nuclear Waste Management}
 %\newacronym{}{}{}
+%Add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file

### 2024-06-03 acronyms/acronyms.tex
kwh
ocm
dot
mrs
eis
head fix
nepa
mca
cce
ic3

@@
 \newacronym{irg}{IRG}{Interagency Review Group on Nuclear Waste Management}
+\newacronym{kwh}{kWh}{Kilowatt-Hour}
+\newacronym{eis}{EIS}{Environmental Impact Statement}
+\newacronym{ocm}{OCRWM}{Office of Civilian Radioactive Waste Management}
+\newacronym{dot}{DOT}{Department of Transportation}
+\newacronym{mrs}{MRS}{Monitored Retrievable Storage}
+\newacronym{nep}{NEPA}{National Environmental Policy Act}
+\newacronym{mca}{MC\&A}{Materials Control and Accountability}
+\newacronym{rv}{R\&V}{Reproducibility \& Validation}
+\newacronym{cce}{CCE}{Consequence-Driven Cyber-informed Engineering}
+\newacronym{ic3}{IC3I}{Intermountain Center for the Cybersecurity of Critical Infrastructure}
 %\newacronym{}{}{}

### 2024-06-04 acronyms/acronyms.tex
ies

--- 2024-05-14 acronyms/acronyms.tex
@@
-\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
+vnewacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
 \newacronym{ahp}{AHP}{Analytical Hierarchy Process}
@@
 \newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
+\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
 \newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
@@
 \newacronym{irg}{IRG}{Interagency Review Group on Nuclear Waste Management}
+\newacronym{kwh}{kWh}{Kilowatt-Hour}
+\newacronym{ocm}{OCRWM}{Office of Civilian Radioactive Waste Management}
+\newacronym{dot}{DOT}{Department of Transportation}
+\newacronym{mrs}{MRS}{Monitored Retrievable Storage}
+\newacronym{nju}{NJUS}{Nome Joint Utility System}
+\newacronym{irr}{IRR}{Internal Rate of Return}
+\newacronym{tci}{TCI}{Total Capital Investment}
+\newacronym{lce}{LCOE}{Levelized Cost of Electricity}
+\newacronym{npv}{NPV}{Net Present Value}
+\newacronym{lcs}{LCOS}{Levelized Cost of Storage}
+\newacronym{lac}{LACE}{Levelized Avoided Cost of Electricity}
+\newacronym{ece}{ECOE}{Effective Cost of Energy}
+\newacronym{llp}{LOLP}{Loss of Load Probability}
+\newacronym{ies}{IES}{Integrated Energy System}
+\newacronym{nrl}{NREL}{National Renewable Energy Laboratory}
+\newacronym{hop}{HOPP}{Hybrid Optimization and Performance Platform}
+\newacronym{lch}{LCOH}{Levelized Cost of Hydrogen}
+\newacronym{fom}{FOM}{Figure of Merit}
 %\newacronym{}{}{}
-%Add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file
+%Add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file/

### 2024-06-04 acronyms/acronyms.tex
ies

@@
-vnewacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
+\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
 \newacronym{ahp}{AHP}{Analytical Hierarchy Process}
@@
 \newacronym{kwh}{kWh}{Kilowatt-Hour}
+\newacronym{eis}{EIS}{Environmental Impact Statement}
 \newacronym{ocm}{OCRWM}{Office of Civilian Radioactive Waste Management}
@@
 \newacronym{fom}{FOM}{Figure of Merit}
+\newacronym{nep}{NEPA}{National Environmental Policy Act}
+\newacronym{mca}{MC\&A}{Materials Control and Accountability}
+\newacronym{rv}{R\&V}{Reproducibility \& Validation}
+\newacronym{cce}{CCE}{Consequence-Driven Cyber-informed Engineering}
+\newacronym{ic3}{IC3I}{Intermountain Center for the Cybersecurity of Critical Infrastructure}
 %\newacronym{}{}{}

### 2024-06-25 acronyms/acronyms.tex
p2x
nwr
acronym
acronyms
des
nwtrb
nwn

@@
 \newacronym{ic3}{IC3I}{Intermountain Center for the Cybersecurity of Critical Infrastructure}
+\newacronym{p2x}{P2X}{Power-to-X}
+\newacronym{nwr}{NWRPO}{Nuclear Waste Repository Project Office}
+\newacronym{aul}{AULG}{Affected Unit of Local Government}
+\newacronym{osc}{OSCM}{Office of Standard Contract Management}
+\newacronym{mrm}{mrem}{millirem}
+\newacronym{can}{CANT}{Citizens Against Nuclear Trash}
+\newacronym{kmp}{KMP}{Key Measurement Point}
+\newacronym{nwb}{NWTRB}{Nuclear Waste Technical Review Board}
+\newacronym{nwn}{NWN}{Office of the Nuclear Waste Negotiator}
 %\newacronym{}{}{}

### 2024-07-11 acronyms/acronyms.tex
nas
ept
nwf
cdo
ne585

@@
 \newacronym{eps}{EPSCoR}{Established Program to Stimulate Competitive Research}
-\newacronym{nas}{NAS}{National Academies}
+\newacronym{nas}{NAS}{National Academy of Sciences}
 \newacronym{brc}{BRC}{Blue Ribbon Commission on America's Nuclear Future}
@@
 \newacronym{nwn}{NWN}{Office of the Nuclear Waste Negotiator}
+\newacronym{ept}{EPAct}{Energy Policy Act}
+\newacronym{nau}{NARUC}{National Association of Regulatory Utility Commissioners}
+\newacronym{cdo}{CD-0}{Critical Decision-0}
+\newacronym{mcp}{MCNP}{Monte Carlo N-Particle Transport Code}
+\newacronym{ke}{KE}{Kinetic Energy}
+\newacronym{swu}{SWU}{Separative Work Unit}
+\newacronym{cp1}{CP-1}{Chicago Pile-1}
+\newacronym{eb1}{EBR-I}{Experimental Breeder Reactor I}
+\newacronym{eb2}{EBR-II}{Experimental Breeder Reactor II}
+\newacronym{trt}{TREAT}{Transient Reactor Test Facility}
+\newacronym{cdu}{CANDU}{Canada Deuterium Uranium Reactor}
+\newacronym{sfr}{SFR}{Sodium Fast Reactor}
+\newacronym{pur}{PUREX}{Plutonium Uranium Reduction Extraction}
+\newacronym{mox}{MOX}{Mixed Oxide}
+\newacronym{tbp}{TBP}{Tributyl Phosphate}
+\newacronym{fp}{FP}{Fission Product}
+\newacronym{lft}{LFTR}{Liquid Fluoride Thorium Reactor}
+\newacronym{atr}{ATR}{Advanced Test Reactor}
+\newacronym{rtg}{RTG}{Radioisotope Thermoelectric Generator}
+\newacronym{vov}{VOV}{Variance of Variance}
+\newacronym{wwg}{WWG}{Weight Window Generator}
+\newacronym{ges}{GESMO}{Generic Environmental Impact Statement for Mixed Oxide Fuel}
+\newacronym{omb}{OMB}{Office of Management and Budget}
+\newacronym{tpa}{TSPA}{Total System Performance Assessment}
+\newacronym{llw}{LLW}{Low Level Waste}
+\newacronym{dnd}{D\&D}{Decontamination \& Decommissioning}
+\newacronym{ebs}{EBS}{Engineered Barrier System}
+\newacronym{ala}{ALARA}{As Low As Reasonably Achievable}
 %\newacronym{}{}{}

### 2024-09-23 proposal-documents/white-paper/white-paper-phd-proposal.tex
white paper cleanup
new white paper

@@
 \usepackage{titlesec,titletoc}
+%%%
+\titleformat{\part}{\normalfont\normalsize\bfseries\filcenter}{\thepart}{}{}[]
+\titlespacing*\part{0pt}{0.50\baselineskip}{0.25\baselineskip}
+
+\titleformat{\section}[runin]{\normalfont\normalsize\bfseries}{\thesection.}{0.5em}{}[]
+\titlespacing*\section{0pt}{0.50\baselineskip}{0.50\baselineskip}
+
+\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesection\alph{subsection}.}{0.25em}{}[]
+\titlespacing*\subsection{0pt}{0.40\baselineskip}{0.50\baselineskip}
+
+\titleformat{\subsubsection}[runin]{\normalfont\normalsize\bfseries}{\roman{subsubsection}.}{0.25em}{}[]
+\titlespacing*\subsubsection{9pt}{0.25\baselineskip}{0.50\baselineskip}
+
+\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries}{\theparagraph}{-1em}{}[]
+\titlespacing*\paragraph{0pt}{0.40\baselineskip}{0.50\baselineskip}
+
+\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{0.25em}{}[]
+\titlespacing*\subparagraph{15pt}{0.25\baselineskip}{0.50\baselineskip}
+%%%
+%\titleformat{\part}{\normalfont\large\bfseries\filcenter}{\thepart}{}{}[]
+%\titlespacing*\part{0pt}{0.65\baselineskip}{0.20\baselineskip}
+%\titleformat{\section}{\normalfont\normalsize\bfseries\filcenter}{\thesection}{}{}[]
+%\titlespacing*\section{0pt}{0.50\baselineskip}{0.15\baselineskip}
+%\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
+%\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.25\baselineskip}
+%\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+%\titlespacing*\paragraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
+%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+%\titlespacing*\subparagraph{0pt}{0.35\baselineskip}{0.25\baselineskip}
+%%%
 %\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
 %\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
-\titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
-\titlespacing*\part{0pt}{0.95\baselineskip}{0.75\baselineskip}
-\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
-\titlespacing*\section{0pt}{0.65\baselineskip}{0.55\baselineskip}
-\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
-\titlespacing*\subsection{0pt}{0.50\baselineskip}{0.35\baselineskip}
-\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
-\titlespacing*\paragraph{0pt}{0.45\baselineskip}{0.25\baselineskip}
-\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
-\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.25\baselineskip}
+%\titleformat{\part}{\normalfont\large\bfseries}{\thepart}{}{}[]
+%\titlespacing*\part{0pt}{0.50\baselineskip}{0.75\baselineskip}
+%\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[]
+%\titleformat{\section}{\normalfont\large\bfseries\filcenter}{\thesection}{}{}[]
+%\titlespacing*\section{0pt}{0.75\baselineskip}{0.45\baselineskip}
+%\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
+%\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.25\baselineskip}
+%\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
+%\titlespacing*\paragraph{0pt}{0.35\baselineskip}{0.15\baselineskip}
+%\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
+%\titlespacing*\subparagraph{0pt}{0.30\baselineskip}{0.10\baselineskip}
 %\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
@@
 \pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[1] %line numbering interval
+\modulolinenumbers[5] %line numbering interval
 %%%%%
@@
 
-\part*{Abstract}
+\part*{Overview}
 
-\section*{Overview}
+\section{Proposed research}
 
-\section*{Overall objective}
+\section{Overall objective}
 
-\section*{Motivation}
-\subsection*{Context}
+\section{Motivation}
+\subsection{Context}
 
-\section*{Novelty of the work}
+\section{Novelty of the work}
 
-\section*{Relevant literature}
+\section{Relevant literature}
 
-\section*{Logical path to work accomplishment} 
+\section{Methodoloy}
+
+\part*{Major Outcomes \& Deliverables}
+
+\section{Preliminary results}
+
+\section{Research scope} 
 \begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
@@
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\begin{enumerate}[series=milestone,topsep=0pt,itemsep=-0.5ex,partopsep=0ex,parsep=1ex,label=\textbf{\textit{Milestone \arabic*.}},align=left,leftmargin=*]
+    \item\textit{.}
+\end{enumerate}
 
@@
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\begin{enumerate}[resume=milestone,topsep=0pt,itemsep=-0.5ex,partopsep=0ex,parsep=1ex,label=\textbf{\textit{Milestone \arabic*.}},align=left,leftmargin=*]
+    \item\textit{.}
+\end{enumerate}
 
@@
 
-\paragraph*{Goals}
-The goals of this Workscope are \ldots .
+\begin{enumerate}[resume=milestone,topsep=0pt,itemsep=-0.5ex,partopsep=0ex,parsep=1ex,label=\textbf{\textit{Milestone \arabic*.}},align=left,leftmargin=*]
+    \item\textit{.}
+\end{enumerate}
 
+\newpage
+
+\part*{\textbf{Timeframe for Execution}}
 {\small
@@
 %        \captionsetup{margin=-9pt}
-        \caption*{\textbf{Timeframe for execution of proposed project.}}
+        \caption*{}
         \label{tab-timeline}\\
@@
         \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}&
-        \multicolumn{5}{|c|}{\textbf{MONTH}}
+        \multicolumn{5}{|c|}{\textbf{MONTH/YEAR}}
         \\
@@
     \renewcommand{\thesection}{\Roman{section}}
-    \titleformat{\section}{\normalfont\large\bfseries}{Appendix \thesection:}{1ex}{}[]
+    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]
 
-    \section*{Acronyms}
+    \section{Acronyms}
     \printnoidxglossary[title={}]

### 2024-10-23 acronyms/acronyms.tex
ipcc
wef
bea
ians acronyms
acronyms
neup
bpc acronyms

@@
 \newacronym{ala}{ALARA}{As Low As Reasonably Achievable}
+\newacronym{ipc}{IPCC}{Intergovernmental Panel on Climate Change}
+\newacronym{wef}{WEF}{World Economic Forum}
+\newacronym{bea}{BEA}{Battelle Energy Alliance}
+\newacronym{cd}{CD}{Certificate of Deposit}
+\newacronym{bn}{BN}{Bayesian Network}
+\newacronym{ann}{ANN}{Artificial Neural Network}
+\newacronym{gsa}{GSA}{General Services Administration}
+\newacronym{gra}{GRA}{Graduate Research Assistant}
+\newacronym{fna}{F\&A}{Facilities and Administrative}
+\newacronym{mdc}{MTDC}{Modified Total Direct Cost}
+\newacronym{nce}{NCES}{National Center for Education Statistics}
+\newacronym{sde}{SDE}{Idaho State Department of Education}
+\newacronym{usd}{USDA}{United States Department of Agriculture}
+\newacronym{hrc}{HERC}{Higher Education Research Council}
+\newacronym{igm}{IGEM}{Idaho Global Entrepreneurial Mission Initiative}
+\newacronym{rad}{RADICL}{Reconfigurable Attack-Defend Instructional Computing Laboratory}
+\newacronym{lea}{LEA}{Local Educational Agency}
+\newacronym{ida}{IDAPA}{Idaho Administrative Procedures Act}
+\newacronym{iee}{IEEE}{Institute of Electrical and Electronics Engineers}
+\newacronym{cis}{CISSE}{Colloquium for Information Systems Security Education}
+\newacronym{ngo}{NGO}{Non-Governmental Organization}
+\newacronym{vo}{CPS-VO}{CPS Virtual Organization}
+\newacronym{nkn}{NKN}{Northwest Knowledge Network}
 %\newacronym{}{}{}

### 2024-11-26 acronyms/acronyms.tex
bpc
acronyms
new

@@
 \newacronym{iee}{IEEE}{Institute of Electrical and Electronics Engineers}
-\newacronym{cis}{CISSE}{Colloquium for Information Systems Security Education}
+\newacronym{css}{CISSE}{Colloquium for Information Systems Security Education}
 \newacronym{ngo}{NGO}{Non-Governmental Organization}
@@
 \newacronym{nkn}{NKN}{Northwest Knowledge Network}
+\newacronym{nss}{NASA}{National Aeronautics and Space Administration}
+\newacronym{trl}{TRL}{Technology Readiness Level}
+\newacronym{nis}{NIST}{National Institute of Standards and Technology}
+\newacronym{cvr}{CVaR}{Conditional Value at Risk}
 %\newacronym{}{}{}

### 2024-12-16 acronyms/acronyms.tex
acronyms
ne529

@@
 \newacronym{cvr}{CVaR}{Conditional Value at Risk}
+\newacronym{phd}{Ph.D.}{Doctor of Philosophy}
+\newacronym{fte}{FTE}{Full Time Equivalent}
+\newacronym{ay}{AY}{Academic Year}
+\newacronym{hra}{HRA}{Human Reliability Analysis}
+\newacronym{pdf}{PDF}{Probability Density Function}
+\newacronym{osa}{OSHA}{Occupational Safety and Health Administration}
+\newacronym{mtb}{MTBF}{Mean Time Before Failure}
+\newacronym{mtf}{MTTF}{Mean Time To Failure}
+\newacronym{ecs}{ECCS}{Emergency Core Cooling System}
+\newacronym{trp}{THERP}{Technique for Human Error Rate Prediction}
+\newacronym{pid}{P\&ID}{Piping \& Instrumentation Diagram}
+\newacronym{cdc}{CDC}{Center for Disease Control}
 %\newacronym{}{}{}

### 2024-12-20 guidelines/guidelines.tex
latex guidelines

--- 2023-10-04 journal/manuscript/document-package/draft-manuscript/draft-manuscript.tex
@@
 \renewcommand{\dateseparator}{.}
-\graphicspath{{../img/}} %path to graphics
+\graphicspath{{$TEXIMG/}} %path to graphics
 \setcounter{secnumdepth}{5} %set subsection to nth level
@@
 \usepackage[figure,table]{totalcount}
-\usepackage[capitalise]{cleveref}
+\usepackage[capitalise,noabbrev]{cleveref}
 \usepackage{nameref}
-%\usepackage{parskip}
+\usepackage{parskip}
+\usepackage[font=itshape]{quoting}
+\usepackage{upgreek,textgreek}
 %%%%%
@@
 %%%%% watermark
-\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
-\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
-\SetWatermarkScale{0.20}
+%\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
+%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
+%\SetWatermarkScale{0.20}
 %%%%%
@@
 %%%%% toc and glossaries
-\usepackage[title,titletoc]{appendix}
+\usepackage[title,toc]{appendix}
 \usepackage[acronym,nomain,nonumberlist]{glossaries}
@@
 \AtBeginEnvironment{appendices}{\crefalias{section}{appendix}} %for cleveref to use Appendix
+\crefname{paragraph}{Section}{Sections}
 \usepackage{titlesec,titletoc}
@@
 \titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
-\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
-\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}
+\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{0.5em}{}[.]
+\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.50\baselineskip}
 %%%%%
@@
 %\newcommandx{\han}[2][1=]{\todo[noline,author=\textbf{ATTN: Haney},backgroundcolor=OliveGreen!25,bordercolor=black,#1]{#2}}
-%\newcommandx{\rab}[2][1=]{\todo[author=\textbf{RAB},tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
+\newcommandx{\ral}[2][1=]{\todo[author=\textbf{RAB},tickmarkheight=0.15cm,linecolor=Plum,backgroundcolor=Plum!25,bordercolor=black,#1]{#2}}
 %\newcommandx{\han}[2][1=]{\todo[author=\textbf{ATTN: Haney},tickmarkheight=0.15cm,linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
@@
 
-\setcounter{tocdepth}{2}
+\setcounter{tocdepth}{5}
 
@@
 
-%%%%% header and footer
 \usepackage{fancyhdr}
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Consent based siting -- Communities of place}
-\chead{\scriptsize \textit{First Author et al. - Draft Manuscript}}
+\lhead{\scriptsize Latex guidelines}
+\chead{\scriptsize \textit{Prof. R. A. Borrelli -- \acl{ui} $\sq$ \acl{iff}}}
 \rhead{\scriptsize \today}
 \rfoot{\thepage}
+
+%%%%% citations
+% do not use \acf in author field; screws up alphabetical on standard.bst
 %%%%%
 
-%%%%%%% citations
-\begin{filecontents}{references.bib}
-    @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
-    }
-    @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
-    }
-    @incollection{
-        mil17a,
-        author = {Miller, Steven E.},
-        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
-        booktitle = {Understanding Cyber Conflict: 14 Analogies},
-        publisher = {Georgetown University Press},
-        year = {2017},
-        editor = {Perkovich, George and Levite, Ariel E.},
-        pages = {161}
-    }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
-\end{filecontents}
-%%%%%%%
-
 %%%%% acronyms
-% alphabetical ordering is automated
-\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
-\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{smr}{SMR}{Small Modular Reactor}
-\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
-\newacronym{nus}{NuScale}{NuScale Power, LLC}
-\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
-\newacronym{epri}{EPRI}{Electric Power Research Institute}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{ci}{CI}{Consistency Index}
-\newacronym{cr}{CR}{Consistency Ratio}
-\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
-\newacronym{lwr}{LWR}{Light Water Reactor}
-\newacronym{eia}{EIA}{U.S. Energy Information Administration}
-\newacronym{oer}{OER}{Online Educational Resource}
-\newacronym{lms}{LMS}{Learning Management System}
-\newacronym{cps}{CPS}{Cyber-Physical Systems}
-\newacronym{nsf}{NSF}{National Science Foundation}
-\newacronym{wsc}{WSC}{Western Services Corporation}
-\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
-\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
-\newacronym{pwr}{PWR}{Pressurized Water Reactor}
-\newacronym{bwr}{BWR}{Boiling Water Reactor}
-\newacronym{roi}{ROI}{Return on Investment}
-\newacronym{ic}{I\&C}{Instrumentation \& Controls}
-\newacronym{mwe}{MWe}{Megawatts-electric}
-\newacronym{ics}{ICS}{Industrial Control Systems}
-\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
-\newacronym{ip}{IP}{Internet Protocol}
-\newacronym{udp}{UDP}{User Datagram Protocol}
-\newacronym{tva}{TVA}{Tennessee Valley Authority}
-\newacronym{plc}{PLC}{Programmable Logic Controller}
-\newacronym{vfd}{VFD}{Variable Frequency Drive}
-\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
-\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
-\newacronym{mim}{MITM}{Man in the Middle}
-\newacronym{dos}{DDoS}{Distributed Denial of Service}
-\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
-\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
-\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
-\newacronym{cs}{CS}{Critical System}
-\newacronym{loc}{LOCA}{Loss of Coolant Accident}
-\newacronym{hmi}{HMI}{Human Machine Interface}
-\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{bol}{BOL}{Beginning-of-Life}
-\newacronym{eol}{EOL}{End-of-Life}
-\newacronym{mol}{MOL}{Middle-of-Life}
-\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
-\newacronym{ccc}{CCC}{Computing Community Consortium}
-\newacronym{neu}{NEUP}{Nuclear Energy University Program}
-\newacronym{doe}{DOE}{United States Department of Energy}
-\newacronym{nei}{NEI}{Nuclear Energy Institute}
-\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
-\newacronym{rcs}{RCS}{Reactor Cooling System}
-\newacronym{con}{IC}{Initial Condition}
-\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
-\newacronym{pcap}{PCAP}{packet capture file}
-\newacronym{dc}{DC}{Direct-Current}
-\newacronym{ac}{AC}{Alternating-Current}
-\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
-\newacronym{snl}{SNL}{Sandia National Laboratory}
-\newacronym{cie}{CIE}{Cyber-Informed Engineering}
-\newacronym{cds}{CRDS}{Control Rod Drive System}
-\newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
-\newacronym{fma}{FMEA}{Failure Modes \& Effects Analysis}
-\newacronym{rpn}{RPN}{Risk Priority Number}
-\newacronym{scr}{SCR}{silicon controller rectifier}
-\newacronym{hvc}{HVAC}{Heating, Ventilation \& Air Conditioning}
-\newacronym{ttb}{TTB}{Time-to-Boil}
-\newacronym{sis}{SIS}{Safety Instrumented System}
-%\newacronym{}{}{}
+\input{$ACRONYM/acronyms}
 %%%%%
@@
 
-\begin{titlepage}
-    \title{Title}
-    \author{
-        \textsuperscript{a}First, 
-        \textsuperscript{b}Second,
-        \textsuperscript{c,*}Third
-        \\ \\ \\
-        \textsuperscript{a}Affiliation 1\\
-        \textsuperscript{b}Affiliation 2\\
-        \textsuperscript{c}Affilation 3
-        \\ \\ \\
-        \textsuperscript{*}email
-    }
-\clearpage %not have page number on title page
-\maketitle
-\vspace*{\fill}
-\begin{flushright}{
-        \noindent Number of pages - \pageref{LastPage} \\
-        \noindent Number of tables - \totaltables \\
-        \noindent Number of figures - \totalfigures 
-}
-\end{flushright}
-\thispagestyle{empty} %start with page number 1 on second page
-\end{titlepage}
+\section{General}
+Latex is going to make your life far easier.
+You will be producing better technical documents with the highest efficiency.
+Yes, the learning curve is not easy.
+However, tex files have been prepared in advance to ease your path.
 
-%\listoftodos[List of revisions]
-%\newpage
+\section{Why?}
+The advantage of latex is that is automates literally all of the clerical nonsense in document preparation that wastes so, so much time.
+For example, when references have to be numbered; [1], [2], and then you or co-authors make changes to the content.
+The renumbering is a waste of time and invites errors.
+Then, on top of references, there are section numbers, equations, figures, tables.
+That time all adds up quick.
+Not with latex.
+All done on compile.
+Acronyms too.
 
-%%%%% spacing
-\onehalfspacing %linespacing
-%\setstretch{1.05} %linespacing
-%\spacing{1.25} %equivalent to 1.5 line spacing in Word
-%%%%%
+%There are a lot of documents to prepare when submitting a manuscript to the journal.
+These are all teed up in the document-package folder.
+\textit{Do them last.} Start by actually writing the paper with the draft-manuscript.tex file.
+The rest is leftover from before the digital age.
 
-%%%%% linenumbering
-\linenumbers %toggle line numbers
-\pagewiselinenumbers %reset line numbers on new page
-\modulolinenumbers[3] %line numbering interval
-%%%%%
+\section{Images}
+Put all images in a single folder (with subfolders).
+The templates have the \verb=\graphicspath{-}= setup so you don't have to specify it in the file, just the subfolder/filename.
+If you're fancy, you can set up an environmental variable in your local space to a single image repository and not copy the image directory over and over for each new tex document.
+In Overleaf, just make an \verb=img= folder.
 
-\section*{Abstract}
+\section{Citations}
+References are probably the biggest advantage with latex.
+References are stored in a \verb=filename.bib= file.
+See samples.
+Then specifcy that filename in the tex file.
+A \verb=bst= file determines the references format.
+I set up three citations formats -- \verb=neup.bsf, standard.bst, nsf.bst=.
+\verb=neup.bst= is just a short version of \verb=nsf.bst=.
+Both of those are for numbering.
+The correct line has to be selected in the preamble in the references section.
+It is labeled which to select depending on what format is desired.
+The \verb=bst= file is designated in the citations section in the tex file along with the \verb=bib= file.
+
+For standard.bst, you have to use \verb=\citep{bor20a}=.
+This gives (Borrelli, 2020) in the text.
+It's a common form for most journals.
+If you do \verb=\cite{bor20a}=, then you get Borrelli (2020) in the text.
+
+The latter helps if you want to write something like -- 
+\begin{quote}
+    Borrelli (2020) argues that object-orientied programming can effectively model safeguards-by-design.
+\end{quote}
+
+For multiple citations, just do \verb=\citep{bor20a,clo19a}= and it will do (Borrelli 2020; Clooney 2019) automatically.
+
+If you have to use \verb=nsf.bst=, then \verb=\citep= and \verb=\cite= both with just give \texttt{[1]}, but if you used \verb=\cite= with standard and switch to \verb=nsf.bst=, then you have to put `Ref.' in front of it, so it's a pain.
+I've submitted all my papers with \verb=standard.bst= and literally no reviewer has commented on it.
+For proposals, it saves space to use numbering.
+For journal papers, reviewers prefer the author names in the citationi, in the text, so they can easily see that.
+And, what is even better about latex is that if you mouse over the reference, the full citation pops up.
+Clicking on the citation will take you to that entry in wherever the references section is in the document.
+
+\subsection{Making citations}\label{sec-make-cite}
+References can be input into one single \verb=bib= file or multiple files.
+I use multiple files because I set an environmental variable in my local space and that way I do not have to copy the same references over and over.
+In Overleaf, just upload the files to a \verb=bib= folder, and these can be just designated in the citations section.
+In general, people go way overboard on the citation information or use ridiculous types.
+All that is needed is enough for someone to do a quick search and find the citation quickly.
+Really, I have only used \verb=@article= for a journal paper, \verb=@misc= for a technical report and anything else, like a news article, \verb=@conference= for a conference proceedings.
+I also use, less frequently, \verb=@book= and \verb=@incollection=.
+The latter is rare.
+Anything outside of these can be covered with \verb=@misc=.
+Web page addresses are not needed.
+If using the digital object identifier, do not include \verb=doi.org=, just start with \verb=10.1012\...whatever=.
+If the journal article volume and page number or report number is available, then do not use the digital object identifier.
+Only use it if there is not any other information.
+Do not use \verb=@techreport= because it renders `Tec.
+Rep.' in the citation list, and it drives me up the wall.
+For techical reports, use \verb=@misc= with the report number in the \verb=note= = \verb={{}}= field.
+Everyone knows it is a technical report.
+
+Keep the \verb={{}}= for \verb=title= = \verb={{}}= and \verb=note= = \verb={{}}= because it will output verbatim what is in the field.
+
+For a journal paper, you don't need the issue number; the volume is sufficient, and you don't need the page range; the starting page is sufficient.
+
+For authors of any reference type, the format is --
+\begin{quote}
+    \verb=@author= = \verb={Borrelli, R. A. and Clooney, George}=
+\end{quote}
+
+I'm throwing George a bone giving him the last author credit.
+Note there is no comma between author names.
+On compile, latex will look for the comma for the names and will crash if the comma is somewhere else.
+Also note that author name order depends on the \verb=bst= file.
+No need to change the formatting of any of the fields.
+So nice!
+
+Enter all authors into the author field, even if there's 17.
+\verb=standard.bst= is set up to add `et al.' if there are more than two of them inline, in the text of the document.
+All the authors will be rendered in the references section.
+
+\verb=nsf.bst= will also list all the authors in the references.
+\acs{nsf} requires this.
+It's also just a courtesy to include everyone on a paper.
+\verb=neup.bst= will render only the first author with the first name abbreviated and `et al.' in the references section.
+Use this if references are included in the page limitations, which is patently absurd, but I don't make the rules.
+Just say something like -- `Please limit references to 2 pages.' Not that difficult.
+Because then when reviwers look at the references, if they count in the page limits, they're going to say, `Well you didn't include this paper or that'; i.e., `You didn't put mine in', and no matter how thorough you are, that's always going to happen.
+
+If the author is an organization, like an \acs{nrc} report, then just do -- 
+\begin{quote}
+    \verb=@author= = \verb={{Nuclear Regulatory Commission}}= 
+\end{quote}
+with the double \verb={{}}=.
 
@@
 
-\printnoidxglossary
+\section{Manuscript}
+\subsection{Sections}
+Section numbering is not required. Use --
 
-\newpage
-%\section*{Table of Contents}
-%\tableofcontents
-%\newpage
+\verb=\section{},\subsection{},\subsubsection{},\paragraph{},\subparagraph{}=.
 
-\section{Introduction} \label{sec-intro}
+Additionally, each of these can be customized in the `toc and glossaries' section.
+For a journal paper, the defaults are fine.
+For other documents, like a proposal, where page limits are a concern, I have other templates with the headings customized.
+The sections in this document are the defaults, except the 4th and 5th level headings, which I modified to look like the rest.
 
-\subsection{Motivation} \label{sec-motiv}
+%The \verb=\section{}= level headings are suggestions, but generally common to journal papers.
+I strongly recommend to keep Motivation and Goals.
+I typically like to separate Results; where you talk about the data, and Discussion; where you say what the data means and why it's important.
+Future Work is always important because it tells reviewers that you know the context of the work.
+You can also discuss here if you've made any assumptions, how you can test/verify them, etc.
 
-\subsection{Goals} \label{sec-goals}
-We ask the following questions - 
-\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*,label=(\arabic*)]
-    \item 1 
-    \item 2
-    \item 3
+\subsection{Acronyms}
+One of the biggest advantages of latex is the automation of the acronyms. This is especially important in any technical document because they are always loaded with acronyms.
+
+I set up acronyms with shortcuts to make it easy, easy, easy.
+There is an acronyms.tex file that I continually add to that anyone can access.
+Then you can just include that file in the text document with \verb=\input{$ACRONYM/acronyms}= where \verb=$ACRONYM= is just the path to the file.
+In Overleaf, just make an acronym folder.
+
+The format is --
+\begin{quote}
+    \verb=\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}=
+\end{quote}
+
+Shortcuts are -- 
+\begin{quote}
+    `full'\\
+    \verb=\acf{nrc}= = United States Nuclear Regulatory Commission (NRC)\\
+    The () are automatic.
+    \\ \\
+    `long'\\
+    \verb=\acl{nrc}= = United States Nuclear Regulatory Commission
+    No ().
+    \\ \\
+    `short'\\
+    \verb=\acs{nrc}= = NRC
+\end{quote}
+
+Additionally, the above codes with with `p' on the end; i.e., \verb=\acfp{}=, pluralizes the entry. So --
+\begin{quote}
+    \verb=\acfp{smr}= = Small Modular Reactors (SMRs)\\
+    The `s' is automatically rendered.
+\end{quote}
+
+Observe --
+\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
+    \item\acf{smr}
+    \item\acfp{smr}
+    \item\acf{ui}
+    \item\acf{dbe}
+    \item\acfp{dbe}
+    \item\acsp{dbe}
 \end{enumerate}
 
-To address these, we have the following goals for this paper - 
-\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*,label=(\arabic*)]
-    \item a
-    \item b
-    \item c
-\end{enumerate}
+So, all the acronyms are automated, but you still have to type them into a glossary?
+Call Lana Kane because nooooooopppppe.
+Adding \verb=\printnoidxglossary= automatically generates a list on compiling, with a section title.
+Or, you can make your own title.
+Latex only compiles the acronyms used in the document.
+Therefore, just having a giant list of them makes sense.
+And, mousing over the acronyms pops up its entry in the Acronyms section, just like the references.
+
+Trust me, this will save uncountable keystrokes. AND - the acronym tags work in \verb=\section{}=, etc.
+
+\subsection*{Clever references}
+The \verb=\cleveref= package is probably the most powerful package in all of latex.
+
+All you need is to input a \verb=\label{something}= next to what you want to reference; figure, table, section, equation --
+\begin{quote}
+\verb=\section{Making citations}\label{sec-make-cite}=
+\end{quote}
+
+Then, all that's needed anywhere in the document is to use \verb=\cref{sec-make-cite}=.
+
+Observe --
+\begin{quote}
+    See \cref{sec-make-cite} for guidance on how to prepare a bibliography.
+\end{quote}
+
+No need to type in `Section'.
+
+Let's try one more.
+
+Einstein came up with the famous formula --
+\begin{equation}\label{eq-mc2}
+    e = mc^2
+\end{equation}
+
+Note here that the `(1)' is also automatically generated on compile.
+
+Now, using clever references, we can see that \cref{eq-mc2} relates mass to energy proportional to the speed of light.
+
+Use \verb=\Cref{tab-name}= for tables.
+
+With page limits, the package can abbreviate; Sec., Fig., Eq. Also, Figures and Equations are automatically pluralized if using \verb=\cref{eq-name,eq-othername}=.
+
+Another example --
+\begin{equation}\label{eq-newton-second}
+    F = ma
+\end{equation}
+
+Two of the most important matematical relationships are also two of the simplest, as we see in \cref{eq-mc2,eq-newton-second}.
+
+Finally, a note on best practices in labeling -- I use sec-, fig-, tab-, eq- so I know to what I'm referencing.
+Also, it is good practice if multiple authors are working on a centralized document, like you would for Overleaf.
+
+\section{Wrapping up for now}
+The information here should be enough to get going with latex on the templates that I have provided.
+This tex file is in my public latex-templates github repository.
+Feel free to fork and submit a pull request with other tips and tricks.
 
@@
 
-\section{Background} \label{sec-bak}
-
-\newpage
-
-\section{Theory} \label{sec-theo}
-
-\newpage
-
-\section{Methodology} \label{sec-meth}
-
-\newpage
-
-\section{Results} \label{sec-res}
-\subsection{Objective} \label{sec-obj}
-
-\newpage
-
-\section{Discussion} \label{sec-disc}
-
-\newpage
-
-\section{Future work} \label{sec-fwk}
-
-\newpage
-
-\section{Summary remarks} \label{sec-sum}
-
-Major results and implications include - 
-\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*]
-    \item 1
-    \item 2
-    \item 3
-\end{itemize}
-
-\newpage
-
-\section*{Acknowledgements}
-
-\newpage
-
-\bibliographystyle{standard}
-\setlength{\bibhang}{0pt}
-\bibliography{references}
-
-\newpage
-
-\section*{Tables}
-{%
-\let\oldnumberline\numberline%
-\renewcommand{\numberline}{\tablename~\oldnumberline}%
-\listoftables%
-}
-
-\newpage
-
-%\begin{spacing}{1}
-%\begin{longtable}{|c|c|c|c|c|}
-%    \caption{Title}
-%    \label{tab-label-name} \\
-%    \hline
-%    \multicolumn{1}{|c|}{A}&
-%    \multicolumn{1}{c|}{B}&
-%    \multicolumn{1}{c|}{C}&
-%    \multicolumn{1}{c|}{D}&
-%    \multicolumn{1}{c|}{E}
-%    \\
-%    \hline
-%    \endfirsthead
-%    \multicolumn{5}{c}{{\tablename\ \thetable{} - continued}} \\
-%    \hline
-%    \multicolumn{1}{|c|}{A}&
-%    \multicolumn{1}{c|}{B}&
-%    \multicolumn{1}{c|}{C}&
-%    \multicolumn{1}{c|}{D}&
-%    \multicolumn{1}{c|}{E}
-%    \\
-%    \hline
-%    \endhead
-%    \hline
-%    \endfoot
-%    \hline
-%    \endlastfoot
-%    X
-%    &X
-%    &X
-%    &X
-%    &X
-%    \\
-%    \hline
-%\end{longtable}
-%\end{spacing}
-
-\newpage
-
-\section*{Figures}
-{%
-\let\oldnumberline\numberline%
-\renewcommand{\numberline}{\figurename~\oldnumberline}%
-\listoffigures%
-}
-
-\newpage
-
-%\begin{figure}[h!]
-%    \centering
-%    \includegraphics[width=0.X\textwidth]{.png}
-%    \caption{}
-%    \label{fig-label-name}
-%\end{figure}
-
-\newpage
-
-%\begin{appendices}
+\begin{appendices}
 
@@
 
-%    \setcounter{section}{0}
-%    \renewcommand{\thesection}{\Roman{section}}
-%    \titleformat{\section}{\normalfont\large\bfseries}{Appendix \thesection:}{1ex}{}[]
+    \setcounter{section}{0}
+    \renewcommand{\thesection}{\Roman{section}}
+    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]
 
-%    \section{Just appendix title} \label{app-}
+    \section{Acronyms}
+    \printnoidxglossary[title={}]
 
-%\end{appendices}
+\end{appendices}
 

### 2025-01-20 acronyms/acronyms.tex
HEAD
HEAD error in file
acronyms
und acronyms

@@
 \newacronym{cdc}{CDC}{Center for Disease Control}
+\newacronym{ms}{MS}{Master of Science}
+\newacronym{bs}{BS}{Bachelor of Science}
+\newacronym{gsi}{GSI}{Graduate Student Instructor}
+\newacronym{nrf}{NRF}{Naval Reactors Facility}
+\newacronym{lnl}{LANL}{Los Alamos National Laboratory}
+\newacronym{utk}{UTK}{University of Tennessee--Knoxville}
+\newacronym{nna}{NNSA}{National Nuclear Security Administration}
+\newacronym{byu}{BYU}{Brigham Young University}
+\newacronym{usu}{USU}{Utah State University}
+\newacronym{dod}{DOD}{Department of Defense}
+\newacronym{pnl}{PNNL}{Pacific Northwest National Laboratory}
+\newacronym{pr}{PR}{Proliferation Resistance}
+\newacronym{pp}{PP}{Physical Protection}
+\newacronym{dt}{DigitTwin}{Digital Twin}
+\newacronym{ai}{AI}{Artificial Intelligence}
+\newacronym{hitl}{HITL}{Human-in-the-Loop}
+\newacronym{sra}{SRA}{Safety Risk Analysis}
+\newacronym{rl}{RL}{Reinforcement Learning}
+\newacronym{xai}{XAI}{Explainable Artificial Intelligence}
+\newacronym{triga}{TRIGA}{Training, Research, Isotopes, General Atomics}
+\newacronym{mars}{MARS}{Maintenance of Advanced Reactor Sensors and Components}
+\newacronym{wsu}{WSU}{Washington State University}
+\newacronym{irb}{IRB}{Institutional Review Board}
+\newacronym{ddml}{DDML}{Data Driven Machine Learning}
+\newacronym{und}{UND}{University of North Dakota}
+\newacronym{dmp}{DMP}{Data Management Plan}
+\newacronym{prm}{PRM}{Project Risk Management}
 %\newacronym{}{}{}

### 2025-01-21 journal/manuscript/document-package/draft-manuscript/draft-manuscript.tex
draft manuscript update

@@
 \usepackage{float}
-\usepackage{mypythonhighlight,verbatim}
+%\usepackage{mypythonhighlight,verbatim}
 %\usepackage{subfig}
@@
 \usepackage[figure,table]{totalcount}
-\usepackage[capitalise]{cleveref}
+\usepackage[capitalise,noabbrev]{cleveref}
 \usepackage{nameref}
 %\usepackage{parskip}
+\usepackage[font=itshape]{quoting}
+\usepackage{upgreek,textgreek}
 %%%%%
@@
 %\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
-\lhead{\scriptsize Consent based siting -- Communities of place}
-\chead{\scriptsize \textit{First Author et al. - Draft Manuscript}}
+\lhead{\scriptsize Subject}
+\chead{\scriptsize \textit{First Author et al. -- Draft Manuscript}}
 \rhead{\scriptsize \today}
@@
 
-%%%%%%% citations
-\begin{filecontents}{references.bib}
-    @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
-    }
-    @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
-    }
-    @incollection{
-        mil17a,
-        author = {Miller, Steven E.},
-        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
-        booktitle = {Understanding Cyber Conflict: 14 Analogies},
-        publisher = {Georgetown University Press},
-        year = {2017},
-        editor = {Perkovich, George and Levite, Ariel E.},
-        pages = {161}
-    }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
-\end{filecontents}
-%%%%%%%
+%%%%% citations
+% do not use \acf in author field; screws up alphabetical on standard.bst
+%%%%%
 
 %%%%% acronyms
-% alphabetical ordering is automated
-\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
-\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{smr}{SMR}{Small Modular Reactor}
-\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
-\newacronym{nus}{NuScale}{NuScale Power, LLC}
-\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
-\newacronym{epri}{EPRI}{Electric Power Research Institute}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{ci}{CI}{Consistency Index}
-\newacronym{cr}{CR}{Consistency Ratio}
-\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
-\newacronym{lwr}{LWR}{Light Water Reactor}
-\newacronym{eia}{EIA}{U.S. Energy Information Administration}
-\newacronym{oer}{OER}{Online Educational Resource}
-\newacronym{lms}{LMS}{Learning Management System}
-\newacronym{cps}{CPS}{Cyber-Physical Systems}
-\newacronym{nsf}{NSF}{National Science Foundation}
-\newacronym{wsc}{WSC}{Western Services Corporation}
-\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
-\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
-\newacronym{pwr}{PWR}{Pressurized Water Reactor}
-\newacronym{bwr}{BWR}{Boiling Water Reactor}
-\newacronym{roi}{ROI}{Return on Investment}
-\newacronym{ic}{I\&C}{Instrumentation \& Controls}
-\newacronym{mwe}{MWe}{Megawatts-electric}
-\newacronym{ics}{ICS}{Industrial Control Systems}
-\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
-\newacronym{ip}{IP}{Internet Protocol}
-\newacronym{udp}{UDP}{User Datagram Protocol}
-\newacronym{tva}{TVA}{Tennessee Valley Authority}
-\newacronym{plc}{PLC}{Programmable Logic Controller}
-\newacronym{vfd}{VFD}{Variable Frequency Drive}
-\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
-\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
-\newacronym{mim}{MITM}{Man in the Middle}
-\newacronym{dos}{DDoS}{Distributed Denial of Service}
-\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
-\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
-\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
-\newacronym{cs}{CS}{Critical System}
-\newacronym{loc}{LOCA}{Loss of Coolant Accident}
-\newacronym{hmi}{HMI}{Human Machine Interface}
-\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{bol}{BOL}{Beginning-of-Life}
-\newacronym{eol}{EOL}{End-of-Life}
-\newacronym{mol}{MOL}{Middle-of-Life}
-\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
-\newacronym{ccc}{CCC}{Computing Community Consortium}
-\newacronym{neu}{NEUP}{Nuclear Energy University Program}
-\newacronym{doe}{DOE}{United States Department of Energy}
-\newacronym{nei}{NEI}{Nuclear Energy Institute}
-\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
-\newacronym{rcs}{RCS}{Reactor Cooling System}
-\newacronym{con}{IC}{Initial Condition}
-\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
-\newacronym{pcap}{PCAP}{packet capture file}
-\newacronym{dc}{DC}{Direct-Current}
-\newacronym{ac}{AC}{Alternating-Current}
-\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
-\newacronym{snl}{SNL}{Sandia National Laboratory}
-\newacronym{cie}{CIE}{Cyber-Informed Engineering}
-\newacronym{cds}{CRDS}{Control Rod Drive System}
-\newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
-\newacronym{fma}{FMEA}{Failure Modes \& Effects Analysis}
-\newacronym{rpn}{RPN}{Risk Priority Number}
-\newacronym{scr}{SCR}{silicon controller rectifier}
-\newacronym{hvc}{HVAC}{Heating, Ventilation \& Air Conditioning}
-\newacronym{ttb}{TTB}{Time-to-Boil}
-\newacronym{sis}{SIS}{Safety Instrumented System}
-%\newacronym{}{}{}
+\input{$ACRONYM/acronyms}
 %%%%%
@@
 
-%\listoftodos[List of revisions]
-%\newpage
+\listoftodos[Notes] %Mouseover acronyms, figure/table number, citations for more information.
+
+\newpage
 

### 2025-01-22 proposal-documents/white-paper/white-paper-general-preproposal.tex
white paper

@@
 %%%%% acronyms
-% alphabetical ordering is automated
-\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
-\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{smr}{SMR}{Small Modular Reactor}
-\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
-\newacronym{nus}{NuScale}{NuScale Power, LLC}
-\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
-\newacronym{epri}{EPRI}{Electric Power Research Institute}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{ci}{CI}{Consistency Index}
-\newacronym{cr}{CR}{Consistency Ratio}
-\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
-\newacronym{lwr}{LWR}{Light Water Reactor}
-\newacronym{eia}{EIA}{U.S. Energy Information Administration}
-\newacronym{oer}{OER}{Online Educational Resource}
-\newacronym{lms}{LMS}{Learning Management System}
-\newacronym{cps}{CPS}{Cyber-Physical Systems}
-\newacronym{nsf}{NSF}{National Science Foundation}
-\newacronym{wsc}{WSC}{Western Services Corporation}
-\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
-\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
-\newacronym{pwr}{PWR}{Pressurized Water Reactor}
-\newacronym{roi}{ROI}{Return on Investment}
-\newacronym{ic}{I\&C}{Instrumentation \& Controls}
-\newacronym{mwe}{MWe}{Megawatts-electric}
-\newacronym{ics}{ICS}{Industrial Control Systems}
-\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
-\newacronym{ip}{IP}{Internet Protocol}
-\newacronym{udp}{UDP}{User Datagram Protocol}
-\newacronym{tva}{TVA}{Tennessee Valley Authority}
-\newacronym{plc}{PLC}{Programmable Logic Controller}
-\newacronym{vfd}{VFD}{Variable Frequency Drive}
-\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
-\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
-\newacronym{mim}{MITM}{Man in the Middle}
-\newacronym{dos}{DDoS}{Distributed Denial of Service}
-\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
-\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
-\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
-\newacronym{cs}{CS}{Critical System}
-\newacronym{loc}{LOCA}{Loss of Coolant Accident}
-\newacronym{hmi}{HMI}{Human Machine Interface}
-\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{bol}{BOL}{beginning-of-life}
-\newacronym{eol}{EOL}{end-of-life}
-\newacronym{mol}{MOL}{middle-of-life}
-\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
-\newacronym{ccc}{CCC}{Computing Community Consortium}
-\newacronym{neu}{NEUP}{Nuclear Energy University Program}
-\newacronym{doe}{DOE}{United States Department of Energy}
-\newacronym{nei}{NEI}{Nuclear Energy Institute}
-\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
-%\newacronym{}{}{}
+\input{$ACRONYM/acronyms}
 %%%%%

### 2025-01-22 proposal-documents/white-paper/white-paper-phd-proposal.tex
white paper

@@
 
-%%%%%%% citations
-\begin{filecontents}{references.bib}
-    @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
-    }
-    @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
-    }
-    @incollection{
-        mil17a,
-        author = {Miller, Steven E.},
-        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
-        booktitle = {Understanding Cyber Conflict: 14 Analogies},
-        publisher = {Georgetown University Press},
-        year = {2017},
-        editor = {Perkovich, George and Levite, Ariel E.},
-        pages = {161}
-    }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
-\end{filecontents}
-%%%%%%%
-
 %%%%% acronyms
-% alphabetical ordering is automated
-\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
-\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{smr}{SMR}{Small Modular Reactor}
-\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
-\newacronym{nus}{NuScale}{NuScale Power, LLC}
-\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
-\newacronym{epri}{EPRI}{Electric Power Research Institute}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{ci}{CI}{Consistency Index}
-\newacronym{cr}{CR}{Consistency Ratio}
-\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
-\newacronym{lwr}{LWR}{Light Water Reactor}
-\newacronym{eia}{EIA}{U.S. Energy Information Administration}
-\newacronym{oer}{OER}{Online Educational Resource}
-\newacronym{lms}{LMS}{Learning Management System}
-\newacronym{cps}{CPS}{Cyber-Physical Systems}
-\newacronym{nsf}{NSF}{National Science Foundation}
-\newacronym{wsc}{WSC}{Western Services Corporation}
-\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
-\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
-\newacronym{pwr}{PWR}{Pressurized Water Reactor}
-\newacronym{bwr}{BWR}{Boiling Water Reactor}
-\newacronym{roi}{ROI}{Return on Investment}
-\newacronym{ic}{I\&C}{Instrumentation \& Controls}
-\newacronym{mwe}{MWe}{Megawatts-electric}
-\newacronym{ics}{ICS}{Industrial Control Systems}
-\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
-\newacronym{ip}{IP}{Internet Protocol}
-\newacronym{udp}{UDP}{User Datagram Protocol}
-\newacronym{tva}{TVA}{Tennessee Valley Authority}
-\newacronym{plc}{PLC}{Programmable Logic Controller}
-\newacronym{vfd}{VFD}{Variable Frequency Drive}
-\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
-\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
-\newacronym{mim}{MITM}{Man in the Middle}
-\newacronym{dos}{DDoS}{Distributed Denial of Service}
-\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
-\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
-\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
-\newacronym{cs}{CS}{Critical System}
-\newacronym{loc}{LOCA}{Loss of Coolant Accident}
-\newacronym{hmi}{HMI}{Human Machine Interface}
-\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{bol}{BOL}{Beginning-of-Life}
-\newacronym{eol}{EOL}{End-of-Life}
-\newacronym{mol}{MOL}{Middle-of-Life}
-\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
-\newacronym{ccc}{CCC}{Computing Community Consortium}
-\newacronym{neu}{NEUP}{Nuclear Energy University Program}
-\newacronym{doe}{DOE}{United States Department of Energy}
-\newacronym{nei}{NEI}{Nuclear Energy Institute}
-\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
-\newacronym{rcs}{RCS}{Reactor Cooling System}
-\newacronym{con}{IC}{Initial Condition}
-\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
-\newacronym{pcap}{PCAP}{packet capture file}
-\newacronym{dc}{DC}{Direct-Current}
-\newacronym{ac}{AC}{Alternating-Current}
-\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
-\newacronym{snl}{SNL}{Sandia National Laboratory}
-\newacronym{cie}{CIE}{Cyber-Informed Engineering}
-\newacronym{cds}{CRDS}{Control Rod Drive System}
-\newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
-\newacronym{fma}{FMEA}{Failure Modes \& Effects Analysis}
-\newacronym{rpn}{RPN}{Risk Priority Number}
-\newacronym{scr}{SCR}{silicon controller rectifier}
-\newacronym{hvc}{HVAC}{Heating, Ventilation \& Air Conditioning}
-\newacronym{ttb}{TTB}{Time-to-Boil}
-\newacronym{sis}{SIS}{Safety Instrumented System}
-%\newacronym{}{}{}
+\input{$ACRONYM/acronyms}
 %%%%%

### 2025-01-23 acronyms/acronyms.tex
acronyms

@@
 \newacronym{snf}{SNF}{Spent Nuclear Fuel}
-\newacronym{cic}{CISAC}{Center for Interantional Security and Cooperation}
+\newacronym{cic}{CISAC}{Center for International Security and Cooperation}
 \newacronym{usa}{US}{United states}
@@
 \newacronym{prm}{PRM}{Project Risk Management}
+\newacronym{saf}{SAFSTOR}{Safe Storage}
+\newacronym{dec}{DECON}{Decontamination \& Dismantlement}
+\newacronym{mse}{MSRE}{Molten Salt Reactor Experiment}
+\newacronym{psd}{PSDAR}{Post Shutdown Decommissioning Activities Report}
+\newacronym{ap}{AP}{Activation Product}
+\newacronym{hdap}{HDAP}{High-Dose Activation Product}
+\newacronym{gtcc}{GTCC}{Greater than Class C}
+\newacronym{isfsf}{ISFSF}{Interim Spent Fuel Storage Facility}
 %\newacronym{}{}{}

### 2025-02-21 acronyms/acronyms.tex
acronyms
acronyms reorg
redi
ece

@@
+%%%%% acronyms
+%
+% add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file/
+% best practice is to pick a code of 2 or 3 letters
+% loosely organized
+% just to make it easier to read
+%
+% \newacronym{}{}{}
+%
+%%%%%
+%
+%%%%% universities, education
+\newacronym{bsu}{BSU}{Boise State University}
+\newacronym{byu}{BYU}{Brigham Young University}
+\newacronym{isu}{ISU}{Idaho State University}
+\newacronym{ui}{UI}{University of Idaho}
+\newacronym{und}{UND}{University of North Dakota}
+\newacronym{usu}{USU}{Utah State University}
+\newacronym{utk}{UTK}{University of Tennessee--Knoxville}
+\newacronym{wsu}{WSU}{Washington State University}
+%
+\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{css}{CISSE}{Colloquium for Information Systems Security Education}
+\newacronym{ece}{ECE}{Electrical \& Computer Engineering}
+\newacronym{epi}{EPI}{Energy Policy Institute}
+\newacronym{hrc}{HERC}{Higher Education Research Council}
+\newacronym{ic3}{IC3I}{Intermountain Center for the Cybersecurity of Critical Infrastructure}
+\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
+\newacronym{igm}{IGEM}{Idaho Global Entrepreneurial Mission Initiative}
+\newacronym{nem}{NEIM}{Nuclear Engineering \& Industrial Management}
+\newacronym{ore}{ORED}{Office of Research and Economic Development}
+\newacronym{rfd}{RFD}{Office of Research and Faculty Development}
+\newacronym{sbe}{SBE}{Idaho State Board of Education}
+\newacronym{sde}{SDE}{Idaho State Department of Education}
+%
+\newacronym{bs}{BS}{Bachelor of Science}
+\newacronym{ms}{MS}{Master of Science}
+\newacronym{phd}{Ph.D.}{Doctor of Philosophy}
+\newacronym{gsi}{GSI}{Graduate Student Instructor}
+\newacronym{gra}{GRA}{Graduate Research Assistant}
+%%%%% national laboratories
+\newacronym{anl}{ANL}{Argonne National Laboratory}
+\newacronym{inl}{INL}{Idaho National Laboratory}
+\newacronym{lnl}{LANL}{Los Alamos National Laboratory}
+\newacronym{nrl}{NREL}{National Renewable Energy Laboratory}
+\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
+\newacronym{pnl}{PNNL}{Pacific Northwest National Laboratory}
+\newacronym{snl}{SNL}{Sandia National Laboratory}
+%
+\newacronym{bea}{BEA}{Battelle Energy Alliance}
+\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
+\newacronym{nri}{NRIC}{National Reactor Innovation Center}
+\newacronym{nrf}{NRF}{Naval Reactors Facility}
+%%%%% government, societies, ngo 
+\newacronym{ans}{ANS}{American Nuclear Society}
+\newacronym{brc}{BRC}{Blue Ribbon Commission on America's Nuclear Future}
+\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{cdc}{CDC}{Center for Disease Control}
+\newacronym{ceq}{CEQ}{Council on Environmental Quality}
+\newacronym{cfr}{CFR}{Code of Federal Regulations}
+\newacronym{cic}{CISAC}{Center for International Security and Cooperation}
+\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
+\newacronym{dod}{DOD}{Department of Defense}
+\newacronym{doe}{DOE}{United States Department of Energy}
+\newacronym{dot}{DOT}{Department of Transportation}
+\newacronym{eia}{EIA}{U.S. Energy Information Administration}
+\newacronym{epa}{EPA}{Environmental Protection Agency}
+\newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{eps}{EPSCoR}{Established Program to Stimulate Competitive Research}
+\newacronym{erd}{ERDA}{Energy Research and Development Administration}
+\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
+\newacronym{fem}{FEMA}{Federal Emergency Management Agency}
+\newacronym{gao}{GAO}{Government Accountability Office}
+\newacronym{iae}{IAEA}{International Atomic Energy Agency}
+\newacronym{iea}{IEA}{International Energy Agency}
+\newacronym{iee}{IEEE}{Institute of Electrical and Electronics Engineers}
+\newacronym{inp}{INPO}{Institute of Nuclear Power Operations}
+\newacronym{nan}{NANTeL}{National Academy for Nuclear Training e-Learning}
+\newacronym{nas}{NAS}{National Academy of Sciences}
+\newacronym{nbe}{NSBE}{National Society of Black Engineers}
+\newacronym{nca}{NCA-CD}{National Center of Excellence in Cyber Defense}
+\newacronym{nei}{NEI}{Nuclear Energy Institute}
+\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
+\newacronym{ngo}{NGO}{Non-Governmental Organization}
+\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
+\newacronym{nis}{NIST}{National Institute of Standards and Technology}
+\newacronym{nna}{NNSA}{National Nuclear Security Administration}
+\newacronym{nrc}{NRC}{Nuclear Regulatory Commission}
+\newacronym{nrm}{NRMSAC}{Nevada Radioactive Materials Storage Advisory Committee}
+\newacronym{nss}{NASA}{National Aeronautics and Space Administration}
+\newacronym{rdi}{REDI}{Regional Economic Development for Eastern Idaho}
+\newacronym{sac}{SACNAS}{Society for the Advancement of Chicanos/Hispanics and Native Americans in Science}
+\newacronym{usd}{USDA}{United States Department of Agriculture}
+\newacronym{un}{UN}{United Nations}
+\newacronym{usa}{US}{United States}
+\newacronym{wpp}{WIPP}{Waste Isolation Pilot Plant}
+%%%%% industry
+\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
+\newacronym{nau}{NARUC}{National Association of Regulatory Utility Commissioners}
+\newacronym{nju}{NJUS}{Nome Joint Utility System}
+\newacronym{nus}{NuScale}{NuScale Power, LLC}
+\newacronym{tva}{TVA}{Tennessee Valley Authority}
+\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
+\newacronym{wsc}{WSC}{Western Services Corporation}
+%%%%% nuclear
+\newacronym{ala}{ALARA}{As Low As Reasonably Achievable}
+\newacronym{ap}{AP}{Activation Product}
+\newacronym{atr}{ATR}{Advanced Test Reactor}
+\newacronym{bol}{BOL}{Beginning-of-Life}
+\newacronym{bwr}{BWR}{Boiling Water Reactor}
+\newacronym{cbs}{CBS}{Consent-Based Siting}
+\newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
+\newacronym{cds}{CRDS}{Control Rod Drive System}
+\newacronym{cdu}{CANDU}{Canada Deuterium Uranium Reactor}
+\newacronym{cis}{CISF}{Consolidated Interim Storage Facility}
+\newacronym{con}{IC}{Initial Condition}
+\newacronym{cp1}{CP-1}{Chicago Pile-1}
+\newacronym{dec}{DECON}{Decontamination \& Dismantlement}
+\newacronym{dnd}{D\&D}{Decontamination \& Decommissioning}
+\newacronym{eb1}{EBR-I}{Experimental Breeder Reactor I}
+\newacronym{eb2}{EBR-II}{Experimental Breeder Reactor II}
+\newacronym{ebs}{EBS}{Engineered Barrier System}
+\newacronym{eol}{EOL}{End-of-Life}
+\newacronym{fp}{FP}{Fission Product}
+\newacronym{gtcc}{GTCC}{Greater than Class C}
+\newacronym{hlw}{HLW}{High-Level Radioactive Waste}
+\newacronym{hdap}{HDAP}{High-Dose Activation Product}
+\newacronym{hop}{HOPP}{Hybrid Optimization and Performance Platform}
+\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
+\newacronym{hvc}{HVAC}{Heating, Ventilation \& Air Conditioning}
+\newacronym{ies}{IES}{Integrated Energy System}
+\newacronym{isfsf}{ISFSF}{Interim Spent Fuel Storage Facility}
+\newacronym{ke}{KE}{Kinetic Energy}
+\newacronym{kmp}{KMP}{Key Measurement Point}
+\newacronym{kwh}{kWh}{Kilowatt-Hour}
+\newacronym{lft}{LFTR}{Liquid Fluoride Thorium Reactor}
+\newacronym{llw}{LLW}{Low Level Waste}
+\newacronym{loc}{LOCA}{Loss of Coolant Accident}
+\newacronym{lwr}{LWR}{Light Water Reactor}
+\newacronym{mca}{MC\&A}{Materials Control and Accountability}
+\newacronym{mcp}{MCNP}{Monte Carlo N-Particle Transport Code}
+\newacronym{mol}{MOL}{Middle-of-Life}
+\newacronym{mox}{MOX}{Mixed Oxide}
+\newacronym{mrm}{mrem}{millirem}
+\newacronym{mse}{MSRE}{Molten Salt Reactor Experiment}
+\newacronym{mth}{MTHM}{Metric Ton of Heavy Metal}
+\newacronym{mtu}{MTU}{Metric Ton of Uranium}
+\newacronym{mwe}{MWe}{Megawatts-electric}
+\newacronym{mrs}{MRS}{Monitored Retrievable Storage}
+\newacronym{pwr}{PWR}{Pressurized Water Reactor}
+\newacronym{npp}{NPP}{Nuclear Power Plant}
 \newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
+\newacronym{nts}{NTS}{Nevada Test Site}
+\newacronym{nwt}{NWTS}{National Waste Terminal Storage}
+\newacronym{psd}{PSDAR}{Post Shutdown Decommissioning Activities Report}
+\newacronym{pur}{PUREX}{Plutonium Uranium Reduction Extraction}
+\newacronym{rcs}{RCS}{Reactor Cooling System}
+\newacronym{rtg}{RTG}{Radioisotope Thermoelectric Generator}
+\newacronym{saf}{SAFSTOR}{Safe Storage}
+\newacronym{sec}{SEC}{Site Evaluation Criteria}
+\newacronym{sfr}{SFR}{Sodium Fast Reactor}
+\newacronym{sis}{SIS}{Safety Instrumented System}
+\newacronym{snf}{SNF}{Spent Nuclear Fuel}
+\newacronym{smr}{SMR}{Small Modular Reactor}
+\newacronym{swu}{SWU}{Separative Work Unit}
+\newacronym{tbp}{TBP}{Tributyl Phosphate}
+\newacronym{tmi}{TMI}{Three Mile Island}
+\newacronym{triga}{TRIGA}{Training, Research, Isotopes, General Atomics}
+\newacronym{trt}{TREAT}{Transient Reactor Test Facility}
+\newacronym{tru}{TRU}{Transuranic Waste}
+\newacronym{ttb}{TTB}{Time-to-Boil}
+\newacronym{wwg}{WWG}{Weight Window Generator}
+\newacronym{vov}{VOV}{Variance of Variance}
+\newacronym{ym}{YM}{Yucca Mountain}
+%%%%% cybersecurity
+\newacronym{aas}{AAS}{Adversary-As-A-Service}
+\newacronym{ac}{AC}{Alternating-Current}
+\newacronym{ai}{AI}{Artificial Intelligence}
+\newacronym{cce}{CCE}{Consequence-Driven Cyber-informed Engineering}
+\newacronym{cda}{CDA}{Critical Digital Assets}
+\newacronym{cdo}{CD-0}{Critical Decision-0}
+\newacronym{cie}{CIE}{Cyber-Informed Engineering}
+\newacronym{cs}{CS}{Critical System}
+\newacronym{cps}{CPS}{Cyber-Physical Systems}
+\newacronym{dc}{DC}{Direct-Current}
+\newacronym{ddml}{DDML}{Data Driven Machine Learning}
+\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
+\newacronym{dos}{DDoS}{Distributed Denial of Service}
+\newacronym{dt}{DigitTwin}{Digital Twin}
+\newacronym{ecs}{ECCS}{Emergency Core Cooling System}
+\newacronym{gui}{GUI}{Graphical User Interface}
+\newacronym{hitl}{HITL}{Human-in-the-Loop}
+\newacronym{hmi}{HMI}{Human Machine Interface}
+\newacronym{hpc}{HPC}{High Performance Computing}
+\newacronym{ic}{I\&C}{Instrumentation \& Controls}
+\newacronym{ics}{ICS}{Industrial Control Systems}
+\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator}
+\newacronym{ip}{IP}{Internet Protocol}
+\newacronym{mars}{MARS}{Maintenance of Advanced Reactor Sensors and Components}
+\newacronym{mim}{MITM}{Man in the Middle}
+\newacronym{ml}{ML}{Machine Learning}
+\newacronym{nic}{NIC}{Network Interface Card}
+\newacronym{p2x}{P2X}{Power-to-X}
+\newacronym{pcp}{PCAP}{Packet Capture File}
+\newacronym{plc}{PLC}{Programmable Logic Controller}
+\newacronym{pp}{PP}{Physical Protection}
+\newacronym{pr}{PR}{Proliferation Resistance}
+\newacronym{rad}{RADICL}{Reconfigurable Attack-Defend Instructional Computing Laboratory}
+\newacronym{rl}{RL}{Reinforcement Learning}
+\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
+\newacronym{scr}{SCR}{silicon controller rectifier}
+\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
+\newacronym{ttx}{TTX}{Tabletop Exercise}
+\newacronym{udp}{UDP}{User Datagram Protocol}
+\newacronym{vfd}{VFD}{Variable Frequency Drive}
+\newacronym{xai}{XAI}{Explainable Artificial Intelligence}
+%%%%% risk
 \newacronym{ahp}{AHP}{Analytical Hierarchy Process}
-\newacronym{inl}{INL}{Idaho National Laboratory}
-\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{anl}{ANL}{Argonne National Laboratory}
-\newacronym{smr}{SMR}{Small Modular Reactor}
-\newacronym{nus}{NuScale}{NuScale Power, LLC}
-\newacronym{epri}{EPRI}{Electric Power Research Institute}
+\newacronym{ann}{ANN}{Artificial Neural Network}
+\newacronym{aoo}{AOO}{Anticipated Operational Occurrence}
+\newacronym{bbe}{BDBE}{Beyond Design Basis Event}
+\newacronym{bn}{BN}{Bayesian Network}
+\newacronym{cd}{CD}{Certificate of Deposit}
 \newacronym{ci}{CI}{Consistency Index}
 \newacronym{cr}{CR}{Consistency Ratio}
-\newacronym{lwr}{LWR}{Light Water Reactor}
+\newacronym{cvr}{CVaR}{Conditional Value at Risk}
+\newacronym{des}{DES}{Discrete Event Simulation}
+\newacronym{dra}{DRA}{Dynamic Risk Assessment}
+\newacronym{dbe}{DBE}{Design Basis Event}
+\newacronym{eco}{ECOE}{Effective Cost of Energy}
+\newacronym{eta}{ETA}{Event Tree Analysis}
+\newacronym{fma}{FMEA}{Failure Modes \& Effects Analysis}
+\newacronym{fom}{FOM}{Figure of Merit}
+\newacronym{fta}{FTA}{Fault Tree Analysis}
+\newacronym{haz}{HAZOP}{Hazard and Operability Analysis}
+\newacronym{hra}{HRA}{Human Reliability Analysis}
+\newacronym{lac}{LACE}{Levelized Avoided Cost of Electricity}
+\newacronym{lce}{LCOE}{Levelized Cost of Electricity}
+\newacronym{lch}{LCOH}{Levelized Cost of Hydrogen}
+\newacronym{lcs}{LCOS}{Levelized Cost of Storage}
+\newacronym{llp}{LOLP}{Loss of Load Probability}
+\newacronym{irr}{IRR}{Internal Rate of Return}
+\newacronym{mtb}{MTBF}{Mean Time Before Failure}
+\newacronym{mtf}{MTTF}{Mean Time To Failure}
+\newacronym{npv}{NPV}{Net Present Value}
+\newacronym{pdf}{PDF}{Probability Density Function}
+\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
+\newacronym{pid}{P\&ID}{Piping \& Instrumentation Diagram}
+\newacronym{pn}{PN}{Petri Net}
+\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
+\newacronym{prm}{PRM}{Project Risk Management}
+\newacronym{roi}{ROI}{Return on Investment}
+\newacronym{rpn}{RPN}{Risk Priority Number}
+\newacronym{sra}{SRA}{Safety Risk Analysis}
+\newacronym{tci}{TCI}{Total Capital Investment}
+\newacronym{trp}{THERP}{Technique for Human Error Rate Prediction}
+%%%%% education
+\newacronym{ihe}{IHE}{Institution of Higher Education}
+\newacronym{lms}{LMS}{Learning Management System}
 \newacronym{oer}{OER}{Online Educational Resource}
-\newacronym{cps}{CPS}{Cyber-Physical Systems}
-\newacronym{wsc}{WSC}{Western Services Corporation}
-\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
-\newacronym{roi}{ROI}{Return on Investment}
-\newacronym{mwe}{MWe}{Megawatts-electric}
-\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
-\newacronym{udp}{UDP}{User Datagram Protocol}
-\newacronym{plc}{PLC}{Programmable Logic Controller}
-\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
-\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
-\newacronym{mim}{MITM}{Man in the Middle}
-\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
-\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
-\newacronym{cs}{CS}{Critical System}
-\newacronym{loc}{LOCA}{Loss of Coolant Accident}
-\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
-\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator}
-\newacronym{ccc}{CCC}{Computing Community Consortium}
+\newacronym{ste}{STEM}{Science, Technology, Engineering, and Mathematics}
+%%%%% proposals
+\newacronym{ate}{ATE}{Advanced Technological Education}
+\newacronym{ay}{AY}{Academic Year}
+\newacronym{bpc}{BPC}{Broadening Participation in Computing}
+\newacronym{cgc}{CGC}{Common Ground Consortium}
+\newacronym{dmp}{DMP}{Data Management Plan}
+\newacronym{fna}{F\&A}{Facilities and Administrative}
+\newacronym{fte}{FTE}{Full Time Equivalent}
+\newacronym{fy}{FY}{Fiscal Year}
+\newacronym{icr}{I-CREWS}{Idaho Community-Engaged Resilience for Energy-Water Systems}
+\newacronym{irb}{IRB}{Institutional Review Board}
+\newacronym{mdc}{MTDC}{Modified Total Direct Cost}
 \newacronym{neu}{NEUP}{Nuclear Energy University Program}
-\newacronym{doe}{DOE}{United States Department of Energy}
-\newacronym{nei}{NEI}{Nuclear Energy Institute}
-\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
-\newacronym{rcs}{RCS}{Reactor Cooling System}
-\newacronym{nic}{NIC}{Network Interface Card}
-\newacronym{pc}{PCAP}{Packet Capture File}
-\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
-\newacronym{ste}{STEM}{Science, Technology, Engineering, and Mathematics}
-\newacronym{pi}{PI}{Principal Investigator}
-\newacronym{ans}{ANS}{American Nuclear Society}
-\newacronym{sac}{SACNAS}{Society for the Advancement of Chicanos/Hispanics and Native Americans in Science}
-\newacronym{ore}{ORED}{Office of Research and Economic Development}
-\newacronym{rfd}{RFD}{Office of Research and Faculty Development}
-\newacronym{nbe}{NSBE}{National Society of Black Engineers}
-\newacronym{inp}{INPO}{Institute of Nuclear Power Operations}
-\newacronym{nan}{NANTeL}{National Academy for Nuclear Training e-Learning}
-\newacronym{cda}{CDA}{Critical Digital Assets}
-\newacronym{nca}{NCA-CD}{National Center of Excellence in Cyber Defense}
-\newacronym{ttx}{TTX}{Tabletop Exercise}
-\newacronym{cie}{CIE}{Cyber-Informed Engineering}
-\newacronym{aas}{AAS}{Adversary-As-A-Service}
-\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
-\newacronym{fy}{FY}{Fiscal Year}
-\newacronym{eps}{EPSCoR}{Established Program to Stimulate Competitive Research}
-\newacronym{nas}{NAS}{National Academy of Sciences}
-\newacronym{brc}{BRC}{Blue Ribbon Commission on America's Nuclear Future}
-\newacronym{hlw}{HLW}{High-Level Radioactive Waste}
-\newacronym{cbs}{CBS}{Consent-Based Siting}
-\newacronym{wpp}{WIPP}{Waste Isolation Pilot Plant}
-\newacronym{cfr}{CFR}{Code of Federal Regulations}
-\newacronym{gao}{GAO}{Government Accountability Office}
-\newacronym{npp}{NPP}{Nuclear Power Plant}
-\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
-\newacronym{nrc}{NRC}{Nuclear Regulatory Commission}
-\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
-\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
-\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
-\newacronym{eia}{EIA}{U.S. Energy Information Administration}
-\newacronym{lms}{LMS}{Learning Management System}
+\newacronym{nkn}{NKN}{Northwest Knowledge Network}
 \newacronym{nsf}{NSF}{National Science Foundation}
-\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
-\newacronym{pwr}{PWR}{Pressurized Water Reactor}
-\newacronym{bwr}{BWR}{Boiling Water Reactor}
-\newacronym{ic}{I\&C}{Instrumentation \& Controls}
-\newacronym{ics}{ICS}{Industrial Control Systems}
-\newacronym{ip}{IP}{Internet Protocol}
-\newacronym{tva}{TVA}{Tennessee Valley Authority}
-\newacronym{vfd}{VFD}{Variable Frequency Drive}
-\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
-\newacronym{dos}{DDoS}{Distributed Denial of Service}
-\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
-\newacronym{dra}{DRA}{Dynamic Risk Assessment}
-\newacronym{hmi}{HMI}{Human Machine Interface}
-\newacronym{bol}{BOL}{Beginning-of-Life}
-\newacronym{eol}{EOL}{End-of-Life}
-\newacronym{mol}{MOL}{Middle-of-Life}
-\newacronym{con}{IC}{Initial Condition}
-\newacronym{dc}{DC}{Direct-Current}
-\newacronym{ac}{AC}{Alternating-Current}
-\newacronym{snl}{SNL}{Sandia National Laboratory}
-\newacronym{cds}{CRDS}{Control Rod Drive System}
-\newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
-\newacronym{fma}{FMEA}{Failure Modes \& Effects Analysis}
-\newacronym{rpn}{RPN}{Risk Priority Number}
-\newacronym{scr}{SCR}{silicon controller rectifier}
-\newacronym{hvc}{HVAC}{Heating, Ventilation \& Air Conditioning}
-\newacronym{ttb}{TTB}{Time-to-Boil}
-\newacronym{sis}{SIS}{Safety Instrumented System}
-\newacronym{cis}{CISF}{Consolidated Interim Storage Facility}
-\newacronym{iea}{IEA}{International Energy Agency}
-\newacronym{snf}{SNF}{Spent Nuclear Fuel}
-\newacronym{cic}{CISAC}{Center for International Security and Cooperation}
-\newacronym{usa}{US}{United states}
-\newacronym{nwa}{NWPA}{Nuclear Waste Policy Act}
 \newacronym{one}{NE}{Office of Nuclear Energy}
-\newacronym{cgc}{CGC}{Common Ground Consortium}
+\newacronym{onr}{ONR}{Office of Naval Research}
+\newacronym{pi}{PI}{Principal Invesigator}
+\newacronym{rd}{R\&D}{Research \& Development}
+\newacronym{rfi}{RFI}{Request for Information}
+\newacronym{rii}{RII}{Research Infrastructure Improvement}
+\newacronym{rv}{R\&V}{Reproducibility \& Validation}
+\newacronym{skp}{SKP}{Senior Key Personnel}
+\newacronym{trl}{TRL}{Technology Readiness Level}
+\newacronym{vo}{CPS-VO}{CPS Virtual Organization}
+%%%%% social science, policy
+\newacronym{aea}{AEA}{Atomic Energy Act}
+\newacronym{aec}{AEC}{Atomic Energy Commission}
+\newacronym{aul}{AULG}{Affected Unit of Local Government}
+\newacronym{can}{CANT}{Citizens Against Nuclear Trash}
+\newacronym{cej}{CEJEST}{Climate and Economic Justice Screening Tool}
+\newacronym{coh}{CoH}{Communities of Historical Experience}
 \newacronym{cop}{CoPL}{Communities of Place}
 \newacronym{cor}{CoPR}{Communities of Practice}
-\newacronym{coh}{CoH}{Communities of Historical Experience}
+\newacronym{eis}{EIS}{Environmental Impact Statement}
 \newacronym{ej}{EJ}{Environmental Justice}
-\newacronym{ite}{ITEK}{Indigenous Traditional Technical Ecological Knowledge}
-\newacronym{iae}{IAEA}{International Atomic Energy Agency}
-\newacronym{rfi}{RFI}{Request for Information}
-\newacronym{sta}{STAND}{Siting Tool for Advanced Nuclear Development}
-\newacronym{ors}{OR-SAGE}{Oak Ridge Siting Analysis for Power Generation Expansion}
-\newacronym{gis}{GIS}{Geographic Information System}
-\newacronym{mtu}{MTU}{Metric Ton of Uranium}
-\newacronym{mth}{MTHM}{Metric Ton of Heavy Metal}
-\newacronym{isa}{ISA}{Idaho Settlement Agreement}
-\newacronym{tru}{TRU}{Transuranic Waste}
-\newacronym{cej}{CEJEST}{Climate and Economic Justice Screening Tool}
 \newacronym{eja}{EJAtlas}{Global Atlas of Environmental Justice}
 \newacronym{ejs}{EJScreen}{Environmental Justice Screening and Mapping Tool}
+\newacronym{ept}{EPAct}{Energy Policy Act}
+\newacronym{ew}{E-W}{Energy-Water}
 \newacronym{fpz}{FPTZ}{Fastest Path to Zero}
+\newacronym{ges}{GESMO}{Generic Environmental Impact Statement for Mixed Oxide Fuel}
+\newacronym{gid}{GEOID}{Geographic Identifier}
+\newacronym{gis}{GIS}{Geographic Information System}
+\newacronym{gsa}{GSA}{General Services Administration}
+\newacronym{ida}{IDAPA}{Idaho Administrative Procedures Act}
+\newacronym{ipc}{IPCC}{Intergovernmental Panel on Climate Change}
+\newacronym{irg}{IRG}{Interagency Review Group on Nuclear Waste Management}
+\newacronym{isa}{ISA}{Idaho Settlement Agreement}
+\newacronym{ite}{ITEK}{Indigenous Traditional Technical Ecological Knowledge}
+\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
+\newacronym{lea}{LEA}{Local Educational Agency}
+\newacronym{lit}{LITE}{Land-area Identification, Tagging, and Exploration}
+\newacronym{nce}{NCES}{National Center for Education Statistics}
+\newacronym{nep}{NEPA}{National Environmental Policy Act}
+\newacronym{nwa}{NWPA}{Nuclear Waste Policy Act}
+\newacronym{nwb}{NWTRB}{Nuclear Waste Technical Review Board}
+\newacronym{nwf}{NWF}{Nuclear Waste Fund}
+\newacronym{nwn}{NWN}{Office of the Nuclear Waste Negotiator}
+\newacronym{nwr}{NWRPO}{Nuclear Waste Repository Project Office}
+\newacronym{ocm}{OCRWM}{Office of Civilian Radioactive Waste Management}
+\newacronym{omb}{OMB}{Office of Management and Budget}
+\newacronym{ors}{OR-SAGE}{Oak Ridge Siting Analysis for Power Generation Expansion}
+\newacronym{osa}{OSHA}{Occupational Safety and Health Administration}
+\newacronym{osc}{OSCM}{Office of Standard Contract Management}
+\newacronym{rap}{RAPT}{Resilience Analysis and Planning Tool}
+\newacronym{set}{SETS}{Socio-Environmental Technological System}
+\newacronym{sta}{STAND}{Siting Tool for Advanced Nuclear Development}
+\newacronym{tpa}{TSPA}{Total System Performance Assessment}
 \newacronym{tra}{WebTRAGIS}{Web-Based Transportation Routing Analysis Geographic Information System}
-\newacronym{lit}{LITE}{Land-area Identification, Tagging, and Exploration}
 \newacronym{str}{START}{Stakeholder Tool for Assessing Radioactive Transportation}
-\newacronym{nri}{NRIC}{National Reactor Innovation Center}
-\newacronym{sec}{SEC}{Site Evaluation Criteria}
-\newacronym{ceq}{CEQ}{Council on Environmental Quality}
-\newacronym{epa}{EPA}{Environmental Protection Agency}
 \newacronym{unf}{UNF-ST\&DARDS}{Used Nuclear Fuel-Storage, Transportation \& Disposal Analysis Resource and Data System}
-\newacronym{gui}{GUI}{Graphical User Interface}
-\newacronym{fem}{FEMA}{Federal Emergency Management Agency}
-\newacronym{rap}{RAPT}{Resilience Analysis and Planning Tool}
-\newacronym{gid}{GEOID}{Geographic Identifier}
-\newacronym{icr}{I-CREWS}{Idaho Community-Engaged Resilience for Energy-Water Systems}
-\newacronym{ew}{E-W}{Energy-Water}
-\newacronym{ml}{ML}{Machine Learning}
-\newacronym{set}{SETS}{Socio-Environmental Technological System}
-\newacronym{rii}{RII}{Research Infrastructure Improvement}
-\newacronym{aoo}{AOO}{Anticipated Operational Occurrence}
-\newacronym{dbe}{DBE}{Design Basis Event}
-\newacronym{bbe}{BDBE}{Beyond Design Basis Event}
-\newacronym{fta}{FTA}{Fault Tree Analysis}
-\newacronym{eta}{ETA}{Event Tree Analysis}
-\newacronym{haz}{HAZOP}{Hazard and Operability Analysis}
-\newacronym{onr}{ONR}{Office of Naval Research}
-\newacronym{ui}{UI}{University of Idaho}
-\newacronym{isu}{ISU}{Idaho State University}
-\newacronym{bsu}{BSU}{Boise State University}
-\newacronym{skp}{SKP}{Senior Key Personnel}
-\newacronym{bpc}{BPC}{Broadening Participation in Computing}
-\newacronym{epi}{EPI}{Energy Policy Institute}
-\newacronym{ym}{YM}{Yucca Mountain}
-\newacronym{nwf}{NWF}{Nuclear Waste Fund}
-\newacronym{aea}{AEA}{Atomic Energy Act}
-\newacronym{aec}{AEC}{Atomic Energy Commission}
-\newacronym{un}{UN}{United Nations}
-\newacronym{des}{DES}{Discrete Event Simulation}
-\newacronym{nem}{NEIM}{Nuclear Engineering \& Industrial Management}
-\newacronym{erd}{ERDA}{Energy Research and Development Administration}
-\newacronym{rd}{R\&D}{Research \& Development}
-\newacronym{nts}{NTS}{Nevada Test Site}
-\newacronym{nrm}{NRMSAC}{Nevada Radioactive Materials Storage Advisory Committee}
-\newacronym{tmi}{TMI}{Three Mile Island}
-\newacronym{nwt}{NWTS}{National Waste Terminal Storage}
-\newacronym{irg}{IRG}{Interagency Review Group on Nuclear Waste Management}
-\newacronym{kwh}{kWh}{Kilowatt-Hour}
-\newacronym{eis}{EIS}{Environmental Impact Statement}
-\newacronym{ocm}{OCRWM}{Office of Civilian Radioactive Waste Management}
-\newacronym{dot}{DOT}{Department of Transportation}
-\newacronym{mrs}{MRS}{Monitored Retrievable Storage}
-\newacronym{nju}{NJUS}{Nome Joint Utility System}
-\newacronym{irr}{IRR}{Internal Rate of Return}
-\newacronym{tci}{TCI}{Total Capital Investment}
-\newacronym{lce}{LCOE}{Levelized Cost of Electricity}
-\newacronym{npv}{NPV}{Net Present Value}
-\newacronym{lcs}{LCOS}{Levelized Cost of Storage}
-\newacronym{lac}{LACE}{Levelized Avoided Cost of Electricity}
-\newacronym{ece}{ECOE}{Effective Cost of Energy}
-\newacronym{llp}{LOLP}{Loss of Load Probability}
-\newacronym{ies}{IES}{Integrated Energy System}
-\newacronym{nrl}{NREL}{National Renewable Energy Laboratory}
-\newacronym{hop}{HOPP}{Hybrid Optimization and Performance Platform}
-\newacronym{lch}{LCOH}{Levelized Cost of Hydrogen}
-\newacronym{fom}{FOM}{Figure of Merit}
-\newacronym{nep}{NEPA}{National Environmental Policy Act}
-\newacronym{mca}{MC\&A}{Materials Control and Accountability}
-\newacronym{rv}{R\&V}{Reproducibility \& Validation}
-\newacronym{cce}{CCE}{Consequence-Driven Cyber-informed Engineering}
-\newacronym{ic3}{IC3I}{Intermountain Center for the Cybersecurity of Critical Infrastructure}
-\newacronym{p2x}{P2X}{Power-to-X}
-\newacronym{nwr}{NWRPO}{Nuclear Waste Repository Project Office}
-\newacronym{aul}{AULG}{Affected Unit of Local Government}
-\newacronym{osc}{OSCM}{Office of Standard Contract Management}
-\newacronym{mrm}{mrem}{millirem}
-\newacronym{can}{CANT}{Citizens Against Nuclear Trash}
-\newacronym{kmp}{KMP}{Key Measurement Point}
-\newacronym{nwb}{NWTRB}{Nuclear Waste Technical Review Board}
-\newacronym{nwn}{NWN}{Office of the Nuclear Waste Negotiator}
-\newacronym{ept}{EPAct}{Energy Policy Act}
-\newacronym{nau}{NARUC}{National Association of Regulatory Utility Commissioners}
-\newacronym{cdo}{CD-0}{Critical Decision-0}
-\newacronym{mcp}{MCNP}{Monte Carlo N-Particle Transport Code}
-\newacronym{ke}{KE}{Kinetic Energy}
-\newacronym{swu}{SWU}{Separative Work Unit}
-\newacronym{cp1}{CP-1}{Chicago Pile-1}
-\newacronym{eb1}{EBR-I}{Experimental Breeder Reactor I}
-\newacronym{eb2}{EBR-II}{Experimental Breeder Reactor II}
-\newacronym{trt}{TREAT}{Transient Reactor Test Facility}
-\newacronym{cdu}{CANDU}{Canada Deuterium Uranium Reactor}
-\newacronym{sfr}{SFR}{Sodium Fast Reactor}
-\newacronym{pur}{PUREX}{Plutonium Uranium Reduction Extraction}
-\newacronym{mox}{MOX}{Mixed Oxide}
-\newacronym{tbp}{TBP}{Tributyl Phosphate}
-\newacronym{fp}{FP}{Fission Product}
-\newacronym{lft}{LFTR}{Liquid Fluoride Thorium Reactor}
-\newacronym{atr}{ATR}{Advanced Test Reactor}
-\newacronym{rtg}{RTG}{Radioisotope Thermoelectric Generator}
-\newacronym{vov}{VOV}{Variance of Variance}
-\newacronym{wwg}{WWG}{Weight Window Generator}
-\newacronym{ges}{GESMO}{Generic Environmental Impact Statement for Mixed Oxide Fuel}
-\newacronym{omb}{OMB}{Office of Management and Budget}
-\newacronym{tpa}{TSPA}{Total System Performance Assessment}
-\newacronym{llw}{LLW}{Low Level Waste}
-\newacronym{dnd}{D\&D}{Decontamination \& Decommissioning}
-\newacronym{ebs}{EBS}{Engineered Barrier System}
-\newacronym{ala}{ALARA}{As Low As Reasonably Achievable}
-\newacronym{ipc}{IPCC}{Intergovernmental Panel on Climate Change}
 \newacronym{wef}{WEF}{World Economic Forum}
-\newacronym{bea}{BEA}{Battelle Energy Alliance}
-\newacronym{cd}{CD}{Certificate of Deposit}
-\newacronym{bn}{BN}{Bayesian Network}
-\newacronym{ann}{ANN}{Artificial Neural Network}
-\newacronym{gsa}{GSA}{General Services Administration}
-\newacronym{gra}{GRA}{Graduate Research Assistant}
-\newacronym{fna}{F\&A}{Facilities and Administrative}
-\newacronym{mdc}{MTDC}{Modified Total Direct Cost}
-\newacronym{nce}{NCES}{National Center for Education Statistics}
-\newacronym{sde}{SDE}{Idaho State Department of Education}
-\newacronym{usd}{USDA}{United States Department of Agriculture}
-\newacronym{hrc}{HERC}{Higher Education Research Council}
-\newacronym{igm}{IGEM}{Idaho Global Entrepreneurial Mission Initiative}
-\newacronym{rad}{RADICL}{Reconfigurable Attack-Defend Instructional Computing Laboratory}
-\newacronym{lea}{LEA}{Local Educational Agency}
-\newacronym{ida}{IDAPA}{Idaho Administrative Procedures Act}
-\newacronym{iee}{IEEE}{Institute of Electrical and Electronics Engineers}
-\newacronym{css}{CISSE}{Colloquium for Information Systems Security Education}
-\newacronym{ngo}{NGO}{Non-Governmental Organization}
-\newacronym{vo}{CPS-VO}{CPS Virtual Organization}
-\newacronym{nkn}{NKN}{Northwest Knowledge Network}
-\newacronym{nss}{NASA}{National Aeronautics and Space Administration}
-\newacronym{trl}{TRL}{Technology Readiness Level}
-\newacronym{nis}{NIST}{National Institute of Standards and Technology}
-\newacronym{cvr}{CVaR}{Conditional Value at Risk}
-\newacronym{phd}{Ph.D.}{Doctor of Philosophy}
-\newacronym{fte}{FTE}{Full Time Equivalent}
-\newacronym{ay}{AY}{Academic Year}
-\newacronym{hra}{HRA}{Human Reliability Analysis}
-\newacronym{pdf}{PDF}{Probability Density Function}
-\newacronym{osa}{OSHA}{Occupational Safety and Health Administration}
-\newacronym{mtb}{MTBF}{Mean Time Before Failure}
-\newacronym{mtf}{MTTF}{Mean Time To Failure}
-\newacronym{ecs}{ECCS}{Emergency Core Cooling System}
-\newacronym{trp}{THERP}{Technique for Human Error Rate Prediction}
-\newacronym{pid}{P\&ID}{Piping \& Instrumentation Diagram}
-\newacronym{cdc}{CDC}{Center for Disease Control}
-\newacronym{ms}{MS}{Master of Science}
-\newacronym{bs}{BS}{Bachelor of Science}
-\newacronym{gsi}{GSI}{Graduate Student Instructor}
-\newacronym{nrf}{NRF}{Naval Reactors Facility}
-\newacronym{lnl}{LANL}{Los Alamos National Laboratory}
-\newacronym{utk}{UTK}{University of Tennessee--Knoxville}
-\newacronym{nna}{NNSA}{National Nuclear Security Administration}
-\newacronym{byu}{BYU}{Brigham Young University}
-\newacronym{usu}{USU}{Utah State University}
-\newacronym{dod}{DOD}{Department of Defense}
-\newacronym{pnl}{PNNL}{Pacific Northwest National Laboratory}
-\newacronym{pr}{PR}{Proliferation Resistance}
-\newacronym{pp}{PP}{Physical Protection}
-\newacronym{dt}{DigitTwin}{Digital Twin}
-\newacronym{ai}{AI}{Artificial Intelligence}
-\newacronym{hitl}{HITL}{Human-in-the-Loop}
-\newacronym{sra}{SRA}{Safety Risk Analysis}
-\newacronym{rl}{RL}{Reinforcement Learning}
-\newacronym{xai}{XAI}{Explainable Artificial Intelligence}
-\newacronym{triga}{TRIGA}{Training, Research, Isotopes, General Atomics}
-\newacronym{mars}{MARS}{Maintenance of Advanced Reactor Sensors and Components}
-\newacronym{wsu}{WSU}{Washington State University}
-\newacronym{irb}{IRB}{Institutional Review Board}
-\newacronym{ddml}{DDML}{Data Driven Machine Learning}
-\newacronym{und}{UND}{University of North Dakota}
-\newacronym{dmp}{DMP}{Data Management Plan}
-\newacronym{prm}{PRM}{Project Risk Management}
-\newacronym{saf}{SAFSTOR}{Safe Storage}
-\newacronym{dec}{DECON}{Decontamination \& Dismantlement}
-\newacronym{mse}{MSRE}{Molten Salt Reactor Experiment}
-\newacronym{psd}{PSDAR}{Post Shutdown Decommissioning Activities Report}
-\newacronym{ap}{AP}{Activation Product}
-\newacronym{hdap}{HDAP}{High-Dose Activation Product}
-\newacronym{gtcc}{GTCC}{Greater than Class C}
-\newacronym{isfsf}{ISFSF}{Interim Spent Fuel Storage Facility}
-%\newacronym{}{}{}
-%Add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file/
+%%%%%

### 2025-03-13 acronyms/acronyms.tex
miles
acronyms
gps

@@
 \newacronym{igm}{IGEM}{Idaho Global Entrepreneurial Mission Initiative}
+\newacronym{msm}{MSE}{Micron School of Materials Science and Engineering}
 \newacronym{nem}{NEIM}{Nuclear Engineering \& Industrial Management}
@@
 \newacronym{rfd}{RFD}{Office of Research and Faculty Development}
-\newacronym{sbe}{SBE}{Idaho State Board of Education}
-\newacronym{sde}{SDE}{Idaho State Department of Education}
+\newacronym{sbe}{ISBE}{Idaho State Board of Education}
+\newacronym{sde}{ISDE}{Idaho State Department of Education}
 %
@@
 \newacronym{ecs}{ECCS}{Emergency Core Cooling System}
+\newacronym{gps}{GPS}{Global Positioning System}
 \newacronym{gui}{GUI}{Graphical User Interface}
@@
 \newacronym{mdc}{MTDC}{Modified Total Direct Cost}
+\newacronym{mls}{MILES}{Managing Idaho's Landscapes for Ecosystem Services}
 \newacronym{neu}{NEUP}{Nuclear Energy University Program}

### 2025-06-12 acronyms/acronyms.tex
colleges
bpc
CBS
acronyms
alt futures
eoi
acse

@@
 \newacronym{byu}{BYU}{Brigham Young University}
+\newacronym{cei}{CEI}{College of Eastern Idaho}
 \newacronym{isu}{ISU}{Idaho State University} 
+\newacronym{cos}{CSI}{College of Southern Idaho}
+\newacronym{cwi}{CWI}{College of Western Idaho}
+\newacronym{noc}{NIC}{North Idaho College}
 \newacronym{ui}{UI}{University of Idaho}
+\newacronym{um}{UM}{University of Michigan}
 \newacronym{und}{UND}{University of North Dakota}
@@
 \newacronym{cae}{CAES}{Center for Advanced Energy Studies}
+\newacronym{csn}{CSNR}{Center for Space Nuclear Research}
 \newacronym{css}{CISSE}{Colloquium for Information Systems Security Education}
@@
 \newacronym{ans}{ANS}{American Nuclear Society}
+\newacronym{asc}{ASCE}{American Society of Civil Engineers}
 \newacronym{brc}{BRC}{Blue Ribbon Commission on America's Nuclear Future}
@@
 \newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
+\newacronym{dhs}{DHS}{Department of Homeland Security}
 \newacronym{dod}{DOD}{Department of Defense}
@@
 \newacronym{bwr}{BWR}{Boiling Water Reactor}
-\newacronym{cbs}{CBS}{Consent-Based Siting}
+\newacronym{cbs}{CBS}{Collaborative-Based Siting}
+%\newacronym{cbs}{CBS}{Consent-Based Siting}
 \newacronym{cdm}{CRDM}{Control Rod Drive Mechanism}
@@
 \newacronym{mse}{MSRE}{Molten Salt Reactor Experiment}
+\newacronym{msr}{MSR}{Molten Salt Reactor}
 \newacronym{mth}{MTHM}{Metric Ton of Heavy Metal}
@@
 \newacronym{smr}{SMR}{Small Modular Reactor}
+\newacronym{snm}{SNM}{Special Nuclear Material}
 \newacronym{swu}{SWU}{Separative Work Unit}
@@
 \newacronym{hpc}{HPC}{High Performance Computing}
+\newacronym{hri}{HRI}{Human Risk Index}
 \newacronym{ic}{I\&C}{Instrumentation \& Controls}
@@
 \newacronym{npv}{NPV}{Net Present Value}
+\newacronym{nrx}{NRI}{National Risk Index}
 \newacronym{pdf}{PDF}{Probability Density Function}
@@
 \newacronym{aec}{AEC}{Atomic Energy Commission}
+\newacronym{afs}{AF}{Alternative Future}
 \newacronym{aul}{AULG}{Affected Unit of Local Government}
+\newacronym{caa}{CAA}{Consolidated Appropriations Act}
 \newacronym{can}{CANT}{Citizens Against Nuclear Trash}
@@
 \newacronym{ejs}{EJScreen}{Environmental Justice Screening and Mapping Tool}
+\newacronym{eoi}{EoI}{Expression of Interest}
 \newacronym{ept}{EPAct}{Energy Policy Act}

### 2025-07-08 acronyms/acronyms.tex
iso
risk indices
risk index
wsi
nsf
sfs

@@
 \newacronym{inp}{INPO}{Institute of Nuclear Power Operations}
+\newacronym{iso}{ISO}{International Organization for Standardization}
 \newacronym{nan}{NANTeL}{National Academy for Nuclear Training e-Learning}
@@
 \newacronym{cgc}{CGC}{Common Ground Consortium}
+\newacronym{dcl}{DCL}{Dear Colleague Letter}
 \newacronym{dmp}{DMP}{Data Management Plan}
@@
 \newacronym{rap}{RAPT}{Resilience Analysis and Planning Tool}
-\newacronym{set}{SETS}{Socio-Environmental Technological System}
+\newacronym{set}{SETS}{Socio-Environmental Technological Systems}
+\newacronym{sfs}{SFS}{Sustainable Future Scenarios}
 \newacronym{sta}{STAND}{Siting Tool for Advanced Nuclear Development}
@@
 \newacronym{wef}{WEF}{World Economic Forum}
+%%%%% water
+\newacronym{adi}{ADI}{Agricultural Drought Index}
+\newacronym{app}{AP}{Average Annual Rainfall Volume}
+\newacronym{cq}{CI}{Consequence Subindex}
+\newacronym{exi}{ExI}{Exposure Indicator}
+\newacronym{hi}{HI}{Drought Hazard Subindex}
+\newacronym{hdi}{HDI}{Hydrological Drought Index}
+\newacronym{kde}{KDE}{Kernel Density Estimation}
+\newacronym{mdi}{MDI}{Meteorological Drought Index}
+\newacronym{ndi}{NDI}{Normalized Deficit Index}
+\newacronym{ndc}{NDC}{Normalized Deficit Cumulated}
+\newacronym{sic}{SIC}{Stress Index Cumulated}
+\newacronym{sii}{SII}{Stress Index Intra-annual}
+\newacronym{vi}{VI}{Vulnerability Indicator}
+\newacronym{wri}{WSRI}{Water Shortage Risk Index}
+\newacronym{wsi}{W-ScaRI}{Water Scarcity Risk Index}
 %%%%%
+%\newacronym{}{}{}
+%%%%%

### 2025-10-09 acronyms/acronyms.tex
water
iri
acronyms
rwr
risk index
eo
g7
wrc
bws
acronyms TOP

@@
 \newacronym{eia}{EIA}{U.S. Energy Information Administration}
+\newacronym{eo}{EO}{Executive Order}
 \newacronym{epa}{EPA}{Environmental Protection Agency}
@@
 \newacronym{fem}{FEMA}{Federal Emergency Management Agency}
+\newacronym{g7}{G7}{Group of Seven}
 \newacronym{gao}{GAO}{Government Accountability Office}
@@
 \newacronym{rpn}{RPN}{Risk Priority Number}
+\newacronym{sca}{SECA}{Simultaneous Evaluation of Criteria and Alternatives}
 \newacronym{sra}{SRA}{Safety Risk Analysis}
 \newacronym{tci}{TCI}{Total Capital Investment}
+\newacronym{top}{TOPSIS}{Technique for Order of Preference by Similarity to Ideal Solution}
 \newacronym{trp}{THERP}{Technique for Human Error Rate Prediction}
@@
 \newacronym{onr}{ONR}{Office of Naval Research}
-\newacronym{pi}{PI}{Principal Invesigator}
+\newacronym{pi}{PI}{Principal Investigator}
 \newacronym{rd}{R\&D}{Research \& Development}
@@
 \newacronym{app}{AP}{Average Annual Rainfall Volume}
+\newacronym{bws}{BWS}{Baseline Water Stress}
 \newacronym{cq}{CI}{Consequence Subindex}
+\newacronym{ds}{DS}{Drought Severity}
+\newacronym{dta}{DTA}{Demand to Available}
+\newacronym{edr}{EDR}{External Dependency Ratio}
+\newacronym{efr}{EFR}{Environmental Flow Requirements}
+\newacronym{ewr}{EWR}{Environmental Water Requirements}
 \newacronym{exi}{ExI}{Exposure Indicator}
+\newacronym{fri}{FRI}{Flood Risk Index}
+\newacronym{gr}{GR}{Governance \& Regulation}
 \newacronym{hi}{HI}{Drought Hazard Subindex}
@@
 \newacronym{ndc}{NDC}{Normalized Deficit Cumulated}
+\newacronym{rfr}{RFR}{Return Flow Ratio}
+\newacronym{rwr}{RWR}{Renewable Water Resource}
 \newacronym{sic}{SIC}{Stress Index Cumulated}
 \newacronym{sii}{SII}{Stress Index Intra-annual}
+\newacronym{ssd}{SS-DTA}{Sectoral and Statistical Demand to Availability}
+\newacronym{sv}{SV}{Seasonal Variability}
 \newacronym{vi}{VI}{Vulnerability Indicator}
+\newacronym{wrc}{WRCC}{Water Resources Carrying Capacity}
 \newacronym{wri}{WSRI}{Water Shortage Risk Index}
 \newacronym{wsi}{W-ScaRI}{Water Scarcity Risk Index}
+\newacronym{wta}{WTA}{Withdrawl To Availability}
+%%%%% energy
+\newacronym{iri}{IESRI}{International Energy Security Risk Index}
 %%%%%

### 2025-12-09 acronyms/acronyms.tex
double fix
cisf
ITEST

@@
 \newacronym{iee}{IEEE}{Institute of Electrical and Electronics Engineers}
+\newacronym{ihl}{IHLRWM}{International High Level Radioactive Waste Management}
 \newacronym{inp}{INPO}{Institute of Nuclear Power Operations}
@@
 \newacronym{rpn}{RPN}{Risk Priority Number}
-\newacronym{sca}{SECA}{Simultaneous Evaluation of Criteria and Alternatives}
+\newacronym{sea}{SECA}{Simultaneous Evaluation of Criteria and Alternatives}
 \newacronym{sra}{SRA}{Safety Risk Analysis}
@@
 \newacronym{irb}{IRB}{Institutional Review Board}
+\newacronym{its}{ITEST}{Innovative Technology Experiences for Students and Teachers}
 \newacronym{mdc}{MTDC}{Modified Total Direct Cost}

### 2025-12-13 proposal-documents/white-paper/white-paper-general-preproposal.tex
white paper clean up

@@
 
-\begin{filecontents}{references.bib} 
-    @misc{
-        nye15a,
-        author = {Nye, Jr., Joseph S.},
-        title = {{The World Needs an Arms-control Treaty for Cybersecurity}},
-        year = {2015},
-        note = {{The Washington Post}}
-    }
-    @article{
-        mil20a,
-        author = {Miller, James N.},
-        title = {No to no first use — for now},
-        journal = {Bulletin of the Atomic Scientists},
-        volume = {76},
-        pages = {8},
-        year  = {2020}
-    }
-    @incollection{
-        mil17a,
-        author = {Miller, Steven E.},
-        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
-        booktitle = {Understanding Cyber Conflict: 14 Analogies},
-        publisher = {Georgetown University Press},
-        year = {2017},
-        editor = {Perkovich, George and Levite, Ariel E.},
-        pages = {161}
-    }
-    @conference{
-        ben20a,
-        author = {Benjamin, Jacob and Haney, Michael},
-        title = {{Nonproliferation of Cyber Weapons}},
-        year = { 2020},
-        organization = {Symposium on Cyber Warfare, Cyber Defense, \& Cyber Security },
-        address = {Las Vegas, Nevada}
-    }
-\end{filecontents}
-
 %%%%% acronyms
@@
 \setlength{\bibhang}{0pt}
-\bibliography{references}
+\bibliography{}
 

### 2025-12-13 proposal-documents/white-paper/white-paper-phd-proposal.tex
phd proposal
white paper clean up

@@
 %%%%% general 
-\documentclass[11pt,a4paper]{article}
+\documentclass[11pt,letterpaper]{article}
 \usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
@@
 %%%
-\titleformat{\part}{\normalfont\normalsize\bfseries\filcenter}{\thepart}{}{}[]
+\titleformat{\part}{\normalfont\large\bfseries\filcenter}{\thepart}{}{}[]
 \titlespacing*\part{0pt}{0.50\baselineskip}{0.25\baselineskip}
@@
 
+\part*{Contribution to Advancing State of the Art}
+This project will advance the state-of-the-art in nuclear fuel cycle analysis by --
+\begin{enumerate*}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=*]
+    \item ; 
+    \item ;
+    \item .
+\end{enumerate*}
+
 \newpage
+
+%%%%% header and footer
+\nolinenumbers
+\pagestyle{fancy}
+\fancyhf{} %move page number to bottom right
+\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
+%\lhead{\scriptsize }
+%\chead{\scriptsize }
+%\rhead{\scriptsize }
+%\lfoot{\scriptsize }
+\rfoot{\thepage}
+%%%%%
 
